### 2018-10-04 AurigaGCS.tex
MNRAS Template /w v0.01 of paper outline (w/o 'img/')

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}    % Including figure files
\usepackage{amsmath}    % Advanced maths commands
\usepackage{amssymb}    % Extra maths symbols

\usepackage{todonotes}
\graphicspath{{img/}}   % Set image path

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}    % per cm-squared
\newcommand{\Sun}[0]{\ensuremath{_{\odot}}}
\renewcommand{\deg}{\ensuremath{^{\circ}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Auriga GCS]{The Globular Cluster System of the Auriga Simulations}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[T. L. R. Halbesma et al.]{
Timo L. R. Halbesma,$^{1}$\thanks{E-mail: Halbesma@MPA-Garching.MPG.DE}
Simon D. M. White,$^{1}$
\\
% List of institutions
$^{1}$Max-Planck-Institut f\"ur Astrophysik, Postfach 1317, D-85741 Garching, Germany\\
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2019}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy formation model used for the Auriga simulations 
can produce a realistic globular cluster population at redshift zero. We compare
properties of the simulated star particles in selected Auriga haloes with
catalogues of observations of the Milky Way globular cluster population available
in the literature. We find that the Auriga simulations produce sufficient mass
at radii and metallicities that are typical for the MW GCS, although we observe
a varying mass-excess for the different $R_{\text{GC}}$-[Fe/H] bins. This implies
different values for the combined product of the bound cluster formation efficiency
and the globular cluster disruption rate.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
methods: numerical -- galaxies: formation -- galaxies: star clusters: general.
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}
\todo[inline]{Paragraph: General introduction of GCs}
\begin{itemize}
    \item ``GCs among oldest astrophysical objects. GCs form in the early Universe in highest density peaks \citep[e.g.][]{2005MNRAS.364..367D, 2009ApJ...706L.192B}''
    \item ``Hence, they witness most of the formation and evolution processes of galaxies, and can be used to probe them'' \citep{2006ARA&A..44..193B}
    \item ``colour bimodality, blue and red clusters \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L, 2006ApJ...639...95P}
    \item ``blue metal-poor (with distribution peaking at [Fe/H] $\approx -1.5$ for the Milky Way), no sign of rotation as a population (..) more metal-rich (peak at [Fe/H] $\approx -0.5$ in the Milky  Way) more spatially concentrated and rotating with the galaxy.'' \citep{1996AJ....112.1487H}
\end{itemize}

\todo[inline]{Paragraph: ``Bimodality suggests two formation mechanisms''}
\begin{itemize}
    \item ``Blue clusters from in early Universe in galaxies that merge later. In (wet) merger process starbursts generate red population \cite{1992ApJ...384...50A, 1987nngp.proc...18S}''
    \item ``\citet{1997AJ....113.1652F} propose instead that blue globulars form when the protogalaxy itself collapses, in a metal-poor and turbulence media. The red population would form later, once the galactic disc has settled. The formation of globular clusters would then be a multiphase process, with the first phase being interrupted possibly by cosmic reionization \citep{2002MNRAS.333..383B}.''
    \item ``\citet{2005ApJ...623..650K, 2014ApJ...796...10L} advocate
that major mergers are at the origin of both sub-populations: blue
clusters form during early mergers (z > 4) while the red ones appear
in mergers at lower redshifts (even after z = 1). Although, this
scenario, combined with star formation enhancement in mergers,
seems appropriate in dense galactic environment leading to the
assembly of massive elliptical galaxies, like in the Virgo Cluster
as tested by \citet{2014ApJ...796...10L}, it does not apply to Milky Way-
like systems where no recent major merger took place (Wyse 2001;
Deason et al. 2013; Ruchti et al. 2014, 2015).
\item ``\citet{1998ApJ...501..554C} argue that red clusters form in situ while the blue ones are accreted, either via merging satellite galaxies, or by tidal capture of the clusters themselves \citep[see also][]{2013ApJ...762...39T}.''
\end{itemize}

\todo[inline]{Work of other groups}
\begin{itemize}
\item Origin of the Milky Way globular clusters \citep{2017MNRAS.465.3622R}
\item GCs in FIRE \citep{2018MNRAS.474.4232K}
\item EMOSAICS project \citep{2018MNRAS.475.4309P}
\item Origin of GC bimodality? \citep{2018MNRAS.479..200F}
\item \textit{GAIA} DR2: GC kinematics \citep{2018A&A...616A..12G}, Dating GC Tidal Disruption \citep{2018ApJ...859L..13B}
\item GC in N-body simulation \citep{2018ApJ...861...69C}
\item Tangentially related? role of GC mass evolution on stream properties \citep{2018MNRAS.474.2479B}
\item GC formation from dwarfs to giants \citep{2018MNRAS.480.2343C}
\item GC contribution to EOR \citep{2018MNRAS.479..332B}
\item Early Universe supermassive star / GC formation \citep{2018MNRAS.478.2461G}
\item GC formation in cold filaments \citep{2018ApJ...861..148M}
\item GC formation in high-redshift dwarf galaxies \citep{2018MNRAS.477..480Z}
\item GCs in MW outer region \citep{2017arXiv170804542P}
\end{itemize}

\section{Methodology and definitions}
\label{sec:methods}
\subsection{The Auriga Simulations}
\label{sec:auriga}
We use the Auriga \citep[][hereafter G17]{2017MNRAS.467..179G} simulations, a suite of high-resolution cosmological zoom simulations ran with a galaxy formation model that produces realistic Milky Way-like galaxies at redshift $z=0$. The simulations are performed with \textsc{arepo} \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} that solves the magnetohydrodynamical equations on a moving mesh. See G17 for further details; here we briefly summarise the relevant properties.
\todo[inline]{Paragraph: Auriga boilerplate, paraphrased}

\todo[inline]{What is the star formation density threshold?}

\subsection{Definition of stellar halo}
\todo[inline]{Possibly also relevant here. See \citet{2018arXiv180407798M}.}

\subsection{Definition of accreted and in-situ component}
\todo[inline]{Possibly also relevant here. See \citet{2018arXiv180407798M}.}

\section{Comparison with observations}
\label{sec:observations}

\begin{figure*}
    \includegraphics[width=\textwidth]{{Au4-24_GCS_250_10}.pdf}
    \caption{TODO: combine upper left and mid left panel, remove upper right panel,
             remove lower panels (because mid right panel already shows the 
             relevant info). The point of this figure is to compare metallicity 
             distribution and radial distribution}
    \label{fig:FeH_Rcs_MWvsAu424_1D}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\textwidth]{{Au4-24_FeH_vs_Rgc}.pdf}
    \caption{Comparison of [Fe/H] and galactocentric radius of the Milky Way GCS
             (red dots) with the star particles in Au4-24. TODO: only show the
             panel on the right-hand side. TODO: include details of exactly which
             star particles are shown. TODO: generate the same figure but color-coded
             by mass?}
    \label{fig:FeH_Rcs_MWvsAu424_2D}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\columnwidth]{vandenBergh2013.png}
    \includegraphics[width=\columnwidth]{{Au4-24_Renaud2017_figure8}.png}
    \caption{TODO: add observed age-FeH data points \citep{2013ApJ...775..134V}
             to simulation plot, investigate starbursts by making pictures of
             these events, check if the observed data set shows a representative
             sample of the MW GCS, fix overlapping axes labels}
    \label{fig:bla}
\end{figure*}
\begin{figure}
    \includegraphics[width=\columnwidth]{{Au4-24_Renaud2017_figure6}.png}
    \caption{}
    \label{fig:bla}
\end{figure}

\section{Discussion}
\label{sec:discussion}

\section{Summary and conclusions}
\label{sec:summary}

\section*{Acknowledgements}
TLRH acknowledges support from the International Max-Planck Research School (IMPRS) on Astrophysics.

\todo[inline]{Check Auriga boilerplate that we need to acknowledge}
RG and VS acknowledge support by the DFG Research Centre SFB-881 `The
Milky Way System' through project A1. This work has also been
supported by the European Research Council under ERC-StG grant
EXAGAL- 308037. Part of the simulations of this paper used the
SuperMUC system at the Leibniz Computing Centre, Garching,
under the project PR85JE of the Gauss Centre for Supercomputing.
This work used the DiRAC Data Centric system at Durham
University, operated by the Institute for Computational Cosmology
on behalf of the STFC DiRAC HPC Facility `www.dirac.ac.uk'.
This equipment was funded by BIS National E-infrastructure capital 
grant ST/K00042X/1, STFC capital grant ST/H008519/1 and
STFC DiRAC Operations grant ST/K003267/1 and Durham University. 
DiRAC is part of the UK National E-Infrastructure.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{mnras}
\bibliography{AurigaGCS} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
%\begin{thebibliography}{99}
%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
%Others S., 2012, Journal of Interesting Stuff, 17, 198
%\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Some extra material}

If you want to present additional material which would interrupt the flow of the main paper,
it can be placed in an Appendix which appears after the list of references.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp    % typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2018-10-04 AurigaGCS.tex
Added paragraphs in Introduction. Added subsections in Results section /w questions to be answered.

@@
 
-\todo[inline]{Paragraph: ``Bimodality suggests two formation mechanisms''}
+\todo[inline]{Paragraph: ``Bimodality suggests two formation mechanisms''. In-situ vs. Accreted}
 \begin{itemize}
@@
 
-\todo[inline]{Work of other groups}
+\todo[inline]{Paragraph: scientific motivation}
+\begin{itemize}
+    \item The star formation model implemented in the Auriga simulations is capable of producing a suite/population of realistic Milky Way-like galaxies at redshift zero.
+    \item (However) State of the art simulations still face numerical restrictions that requires a subgrid approach to star formation and feedback because individual stars (and their evolution) cannot yet be accounted for.
+Star formation thus occurs in a heuristic/probabilistic fashion for gas cells that fulfill some star formation criterion.
+The star particles enrich the gas with metals and energy, both according to pre-defined/pre-calculated yields for specific feedback processes (supernova type I and II, strong stellar winds of asymptotic giant branch stars, ).
+In addition, black holes are seeded in eligible haloes to account for feedback associated with an active galactic nucleus.
+    \item The end-result of the star formation model is the production of simulated Milky Way-like galaxies.
+Therefore the question naturally arises whether or not the Auriga simulations are also capable of faithfully producing a globular cluster population as observed in the Milky Way.
+    \item Globular cluster formation in cosmological zoom simulations is very interesting for two reasons.
+First of all, extragalactic observations typically show the integrated properties of globular clusters rather than that of the individual stars within the clusters.
+Moreover, the typical mass scale of globular clusters is comparable to the numerical (mass) resolution of cosmological zoom simulations.
+The detailed small scale physics that is at play for real world globular clusters appears in observations as the combined effect of the $10^{3-6}$ M\Sun, compared to a mass resolution of $10^{3-5}$ M\Sun for the Auriga simulations.
+Globular clusters can therefore serve as an ultimate test to the star formation model that is implemented in the numerical simulations.
+Secondly, cosmological zoom simulations provide an accurate recording of the full and detailed merger history of the simulated galaxy.
+This is important because theoretical paradigms for globular cluster formation in the literature know two distinct classes of GCs that are separated by their exact formation sites: an in-situ versus an accreted population.
+Cosmological zoom simulations are uniquely allow for an investigation into globular cluster formation with particular focus on the in-situ and accreted populations.
+\end{itemize}
+
+\todo[inline]{Paragraph: previous work / work of other groups}
 \begin{itemize}
@@
 
-\section{Methodology and definitions}
-\label{sec:methods}
-\subsection{The Auriga Simulations}
+\todo[inline]{Paper outline}
+We summarise the relevant characteristics of the Auriga simulations in section~\ref{sec:auriga}, followed by a summary of the observations of the Milky Way (MW) globular cluster system (GCS) in section~\ref{sec:observations} that we use to compare our simulations to in section~\ref{sec:results}.
+We discuss our findings in section~\ref{sec:discussion} to come to our conclusions in section~\ref{sec:conclusions}.
+
+\section{The Auriga simulations}
 \label{sec:auriga}
@@
 \todo[inline]{What is the star formation density threshold?}
+``The gas is assumed to be star-forming and thermally unstable for densities higher than a threshold density that we derive from the parameters of the two gas phases and the desired star formation time-scale to be $n = 0.13 \text{cm}^{−3}$.'' - \citep{2017MNRAS.467..179G}
 
@@
 
-\section{Comparison with observations}
+\section{The Milky Way globular cluster system}
 \label{sec:observations}
 
-\begin{figure*}
-    \includegraphics[width=\textwidth]{{Au4-24_GCS_250_10}.pdf}
-    \caption{TODO: combine upper left and mid left panel, remove upper right panel,
-             remove lower panels (because mid right panel already shows the 
-             relevant info). The point of this figure is to compare metallicity 
-             distribution and radial distribution}
-    \label{fig:FeH_Rcs_MWvsAu424_1D}
-\end{figure*}
+\subsection{Harris catalogue}
+\label{sec:harris}
+\citet[][2010 edition]{1996AJ....112.1487H} provides the most up-to-date and comprehensive catalog of the MW GCS that contains properties of 157 globular clusters.
+The catalogue is believed to be roughly 90\% complete.
 
-\begin{figure*}
-    \includegraphics[width=\textwidth]{{Au4-24_FeH_vs_Rgc}.pdf}
-    \caption{Comparison of [Fe/H] and galactocentric radius of the Milky Way GCS
-             (red dots) with the star particles in Au4-24. TODO: only show the
-             panel on the right-hand side. TODO: include details of exactly which
-             star particles are shown. TODO: generate the same figure but color-coded
-             by mass?}
-    \label{fig:FeH_Rcs_MWvsAu424_2D}
-\end{figure*}
+\subsection{Age estimates}
+\label{sec:vandenberg}
+\citet{2013ApJ...775..134V} measured [Fe/H] and obtained age-estimates for 55 globular clusters in the MW GCS.
 
-\begin{figure*}
-    \includegraphics[width=\columnwidth]{vandenBergh2013.png}
-    \includegraphics[width=\columnwidth]{{Au4-24_Renaud2017_figure8}.png}
-    \caption{TODO: add observed age-FeH data points \citep{2013ApJ...775..134V}
-             to simulation plot, investigate starbursts by making pictures of
-             these events, check if the observed data set shows a representative
-             sample of the MW GCS, fix overlapping axes labels}
-    \label{fig:bla}
-\end{figure*}
-\begin{figure}
-    \includegraphics[width=\columnwidth]{{Au4-24_Renaud2017_figure6}.png}
-    \caption{}
-    \label{fig:bla}
-\end{figure}
+\section{Results}
+\label{sec:results}
+\subsection{Metallicity distribution}
+\label{sec:metallicity}
+Can the Auriga simulations produce star particles of $>10$~Gyr (GC candidates) with a metallicity distribution that is consistent with the MW GCS?
+
+\subsection{Spatial distribution}
+\label{sec:spatial}
+Is the spatial distribution of the GC candidates in the Auriga simulations consistent with the MW GCS?
+
+\subsection{Age-metallicity distribution}
+\label{sec:agemetallicity}
+What age-metallicity distribution is produced by star formation events in the Auriga simulations?
+
+\subsection{Mass budget} 
+\label{sec:mass}
+Does the star formation model implemented in the Auriga simulations produce sufficient mass in star particles with properties that are consistent with the MW GCS?
+
+What efficiencies could we afford if we would take into account the combined mass loss effect of converting from star particles to bound star clusters and globular cluster disruption?
+
+How does the total stellar mass in $R_\textbf{GC}$-[Fe/H] bins compare to the MW GCS?
+
+\subsection{Formation history} 
+\label{sec:history}
+Can we identify particular star formation events that generate GC candidates with the correct age, metallicity, and radial properties as expected or the MW GCS?
+
+Can we distinguish between particles that have formed in-situ and those that have been accreted?
+Can we identify specific features in the age-metallicity plane, or in the $R_\textbf{GC}$-[Fe/H] plane, that result from one of both populations?
+How does this connect to proposed mechanisms for globular cluster formation in the literature?
+
+\subsection{Scatter for different Auriga haloes} 
+\label{sec:convergence}
+Are the properties of the Auriga globular cluster candidates converged for runs with different initial conditions but at the same resolution level?
+How much scatter do we observe in the properties of the globular cluster candidates across the full suite of Auriga haloes?
+
+\subsection{Numerical convergence} 
+\label{sec:convergence}
+Are the properties of the Auriga globular cluster candidates converged for runs with the same initial conditions but at different resolution levels?
+
+% \begin{figure*}
+%     \includegraphics[width=\textwidth]{{Au4-24_GCS_250_10}.pdf}
+%     \caption{TODO: combine upper left and mid left panel, remove upper right panel,
+%              remove lower panels (because mid right panel already shows the 
+%              relevant info). The point of this figure is to compare metallicity 
+%              distribution and radial distribution}
+%     \label{fig:FeH_Rcs_MWvsAu424_1D}
+% \end{figure*}
+% 
+% 
+% \begin{figure*}
+%     \includegraphics[width=\textwidth]{{Au4-24_FeH_vs_Rgc}.pdf}
+%     \caption{Comparison of [Fe/H] and galactocentric radius of the Milky Way GCS
+%              (red dots) with the star particles in Au4-24. TODO: only show the
+%              panel on the right-hand side. TODO: include details of exactly which
+%              star particles are shown. TODO: generate the same figure but color-coded
+%              by mass?}
+%     \label{fig:FeH_Rcs_MWvsAu424_2D}
+% \end{figure*}
+% 
+% 
+% \begin{figure*}
+%     \includegraphics[width=\columnwidth]{vandenBergh2013.png}
+%     \includegraphics[width=\columnwidth]{{Au4-24_Renaud2017_figure8}.png}
+%     \caption{TODO: add observed age-FeH data points \citep{2013ApJ...775..134V}
+%              to simulation plot, investigate starbursts by making pictures of
+%              these events, check if the observed data set shows a representative
+%              sample of the MW GCS, fix overlapping axes labels}
+%     \label{fig:bla}
+% \end{figure*}
+% \begin{figure}
+%     \includegraphics[width=\columnwidth]{{Au4-24_Renaud2017_figure6}.png}
+%     \caption{}
+%     \label{fig:bla}
+% \end{figure}
 
@@
 \section{Summary and conclusions}
-\label{sec:summary}
+\label{sec:conclusions}
 

### 2018-12-23 AurigaGCS.tex
Some things were updated, I guess

@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[T. L. R. Halbesma et al.]{
-Timo L. R. Halbesma,$^{1}$\thanks{E-mail: Halbesma@MPA-Garching.MPG.DE}
-Simon D. M. White,$^{1}$
-\\
-% List of institutions
-$^{1}$Max-Planck-Institut f\"ur Astrophysik, Postfach 1317, D-85741 Garching, Germany\\
+\author[T. L. R. Halbesma et al.]{\parbox[t]{\textwidth}{
+    Timo L. R. Halbesma$^{1}$\thanks{E-mail: Halbesma@MPA-Garching.MPG.DE},
+    Wilma Trick$^{1}$,
+    Robert J. J. Grand$^{1}$, 
+    Volker Springel$^{1}$, 
+    Facundo A. G\'{o}mez$^{2,3}$, 
+    Federico Marinacci$^{4,5}$,
+    R\"{u}diger Pakmor$^{1}$, 
+    Simon D. M. White$^{1}$
+} \vspace{10pt} \\
+$^{1}$ Max-Planck-Institut f\"ur Astrophysik, Postfach 1317, D-85741 Garching, Germany \\
+$^{2}$ Instituto de Investigaci\'{o}n Multidisciplinar en Ciencia yTecnolog\'{i}a, Universidad de La Serena, Ra\'{u}l Bitr\'{a}n 1305, La Serena, Chile \\
+$^{3}$ Departamento de F\'{i}sica y Astronom\'{i}a, Universidad de La Serena, Av. Juan Cisternas 1200 N, La Serena, Chile \\
+$^{4}$ Department of Physics, Kavli Institute for Astrophysics and Space Research, MIT, Cambridge, MA 02139, USA \\
+$^{5}$ Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA \\
 }
@@
 can produce a realistic globular cluster population at redshift zero. We compare
-properties of the simulated star particles in selected Auriga haloes with
+properties of the simulated star particles in the Auriga haloes with
 catalogues of observations of the Milky Way globular cluster population available
@@
 different values for the combined product of the bound cluster formation efficiency
-and the globular cluster disruption rate.
+and the globular cluster disruption rate. We investigate wether these differences
+could result from formation insitu vs. accreted star particles. We find ...
 \end{abstract}
@@
 \todo[inline]{Paragraph: General introduction of GCs}
+
+\citet{2005MNRAS.364..367D}: ``The radial profile of the stellar halo and metal-poor globular
+clusters of the Milky Way suggest that these components formed in rare early peaks above $2.5 \sigma$ at redshift above 10. ''
+
+\citet{2017MNRAS.465.3622R}: ``GCs among oldest astrophysical objects. GCs form in the early Universe in highest density peaks \citep[e.g.][]{2005MNRAS.364..367D, 2009ApJ...706L.192B}''
+
 \begin{itemize}
-    \item ``GCs among oldest astrophysical objects. GCs form in the early Universe in highest density peaks \citep[e.g.][]{2005MNRAS.364..367D, 2009ApJ...706L.192B}''
     \item ``Hence, they witness most of the formation and evolution processes of galaxies, and can be used to probe them'' \citep{2006ARA&A..44..193B}
@@
 
+Dark Matter - GC connection
+
 \todo[inline]{Paragraph: scientific motivation}
@@
 \todo[inline]{Paragraph: previous work / work of other groups}
+This goes before the GC formation mechanism paragraph.
 \begin{itemize}
@@
 \item GCs in MW outer region \citep{2017arXiv170804542P}
+\item Impact of the Cutoff of the Cluster Initial Mass Function \citep{2018arXiv181001888C}
+\item Metallicity gradients in the globular cluster systems of early-type galaxies: in situ and accreted components \citep{2018MNRAS.479.4760F}
+\item Globular clusters in M31, Local Group, and external galaxies \citep{2016IAUS..317..120L}
+\item Globular Clusters Formed within Dark Halos I: present-day abundance, distribution and kinematics \citep{2019MNRAS.482..219C}
+\item The mass of the Milky Way from satellite dynamics \citep{2018arXiv180810456C}
+\item Globular cluster formation and evolution in the context of cosmological galaxy assembly: open questions \citep{2018RSPSA.47470616F}
+\item The kinematics of globular clusters systems in the outer halos of the Aquarius simulations \citep{2016A&A...592A..55V}
+\item Star Cluster Formation in Cosmological Simulations \citep{2017ApJ...834...69L, 2018ApJ...861..107L, 2018arXiv181011036L}
+\item A systematic analysis of star cluster disruption by tidal shocks -- I. Controlled N-body simulations and a new theoretical model \citep{2018arXiv181200014W}
+\item Spatial mixing of binary stars in multiple-population globular clusters \citep{2018MNRAS.tmp.3147H}
+\item Star Clusters Across Cosmic Time \citep{2018arXiv181201615K}
+\item Kinematics of Subclusters in Star Cluster Complexes: Imprint of their Parental Molecular Clouds \citep{2018arXiv181201858F}
+\item Investigating the population of Galactic star formation regions and star clusters within a Wide-Fast-Deep Coverage of the Galactic Plane  \citep{2018arXiv181203025P}
+% TODO: last checked arXiv Dec 15, 2018
 \end{itemize}
@@
 
+``The simulations include a comprehensive model for galaxy formation physics which includes important baryonic processes, such as
+
+primordial and metal-line cooling \citep{2013MNRAS.436.3031V};
+
+a sub-grid model for the interstellar medium that utilises an equation of state representing a two-phase medium in pressure equilibrium \citep{2003MNRAS.339..289S}
+u
+a model for the star formation and stellar feedback that includes a phenomenological wind model \citep{2014MNRAS.437.1750M, 2017MNRAS.467..179G}
+
+and metal enrichment from SNII, SNIa and AGB stars \citep{2013MNRAS.436.3031V}
+
+black hole formation and active galactic nucleus feedback (\citep{2005MNRAS.361..776S, 2014MNRAS.437.1750M, 2017MNRAS.467..179G}
+
+a spatially uniform, time-varying UV background after reionization at redshift six \citep{2009ApJ...703.1416F, 2013MNRAS.436.3031V}
+
+and magnetic fields \citep{2013MNRAS.432..176P, 2014ApJ...783L..20P}
+
+The model was specifically developed for the \textsc{arepo} code and was calibrated to reproduce several observational results such as the stellar mass to halo mass relation, galaxy luminosity functions and the history of the cosmic star formation rate density.
+''
+
 \todo[inline]{What is the star formation density threshold?}
-``The gas is assumed to be star-forming and thermally unstable for densities higher than a threshold density that we derive from the parameters of the two gas phases and the desired star formation time-scale to be $n = 0.13 \text{cm}^{−3}$.'' - \citep{2017MNRAS.467..179G}
+``The gas is assumed to be star-forming and thermally unstable for densities higher than a threshold density that we derive from the parameters of the two gas phases and the desired star formation time-scale to be $n = 0.13 \text{cm}^{-3}$.'' - \citep{2017MNRAS.467..179G}
+
+\todo[inline]
+``The diversity in morphological properties of these simulated galaxies reflects the stochasticity inherent to the process of galaxy formation and evolution \citep[e.g.][]{2005ApJ...635..931B, 2010MNRAS.406..744C, 2010ApJ...708.1398T}.''
 
@@
 
-\section{The Milky Way globular cluster system}
+\section{Relevant observational data for Local Group spirals}
+The Milky Way + M31 globular cluster system
 \label{sec:observations}
@@
 
+How is this particular sample selected? What biases does this introduce?
+Is this sample drawn from the same underlying distribution as the Harris sample (plot distributions of FeH, compare mean/std, do t-test)
+
+\subsection{M31}
+\todo[inline]{Get big dataset of M31 GCS}
+\label{sec:m31}
+\citep{2011AJ....141...61C}
+\citep{2014MNRAS.442.2165H, 2014MNRAS.442.2929V}
+
 \section{Results}
 \label{sec:results}
+\citet{2013ApJ...775..134V} presents age measurements of 55 GCs in the MW. The
+mean age of GCs in the MW is $11.9$~Gyr with a dispersion of $0.8$~Gyr. 
+Therefore we select all star particles in the Auriga simulations that are older 
+than $10$~Gyr. Henceforth we will refer the this subset of star particles as the 
+`GC candidates'. Our approach is similar to the one taken by \citep{2017MNRAS.465.3622R},
+where we know we are oversampling the real GC population with the contribution
+of field stars in our subset. This will be further addressed in the discussion.
+
 \subsection{Metallicity distribution}
 \label{sec:metallicity}
+
 Can the Auriga simulations produce star particles of $>10$~Gyr (GC candidates) with a metallicity distribution that is consistent with the MW GCS?
+
+Fig.~\ref{fig:FeH}
+
+Split into insitu / accreted
+
+Conclusion: too many metal-rich star particles.
+
+\begin{figure*}
+    \includegraphics[width=\columnwidth]{{logMFeH_OldStars}.png}
+    \includegraphics[width=\columnwidth]{{logMFeH}.png}
+\end{figure*}
+\begin{figure*}
+    \includegraphics[width=\columnwidth]{{logMFeH_OldInsitu}.png}
+    \includegraphics[width=\columnwidth]{{logMFeH_OldAccreted}.png}
+    \caption{Caption}
+    \label{fig:FeH}
+\end{figure*}
 
@@
 Is the spatial distribution of the GC candidates in the Auriga simulations consistent with the MW GCS?
+
+Look into Pandromeda survey? Star counts, very wide angle survey
+
+\begin{figure*}
+    \includegraphics[width=\columnwidth]{{logMRgc_OldStars}.png}
+    \includegraphics[width=\columnwidth]{{logMRgc}.png}
+\end{figure*}
+\begin{figure*}
+    \includegraphics[width=\columnwidth]{{logMRgc_OldInsitu}.png}
+    \includegraphics[width=\columnwidth]{{logMRgc_OldAccreted}.png}
+    \caption{Caption}
+    \label{fig:Rgc}
+\end{figure*}
 
@@
 
+Orbits: are the pericentres different? Look at velocity + specific angular momentum distribution in the different FeH/Rgc bins as proxy for the pericenter
+
 \subsection{Scatter for different Auriga haloes} 
@@
 
-\subsection{Numerical convergence} 
+\subsection{Numerical convergence (possibly in appendix)} 
 \label{sec:convergence}
 Are the properties of the Auriga globular cluster candidates converged for runs with the same initial conditions but at different resolution levels?
+
+\begin{figure*}
+    \includegraphics[width=0.31\textwidth]{{logMFeH_Au6}.png}
+    \includegraphics[width=0.31\textwidth]{{logMFeH_Au16}.png}
+    \includegraphics[width=0.31\textwidth]{{logMFeH_Au24}.png}
+    \caption{Caption}
+    \label{fig:FeH_l345}
+\end{figure*}
+\begin{figure*}
+    \includegraphics[width=0.31\textwidth]{{logMRgc_Au6}.png}
+    \includegraphics[width=0.31\textwidth]{{logMRgc_Au16}.png}
+    \includegraphics[width=0.31\textwidth]{{logMRgc_Au24}.png}
+    \caption{Caption}
+    \label{fig:Rgc_l345}
+\end{figure*}
 

### 2018-12-23 Partial/FeH_logM.tex
Some things were updated, I guess

\documentclass[12pt, a4paper]{article}

\usepackage[english]{babel}
% Here the text area, the left margin and the top margin are set. 
% The right and bottom margins are automatically computed to fit the page. 
\usepackage{geometry}
\geometry{
    a4paper,  % 210 x 297 mm
    total={170mm,257mm},
    left=20mm,  % 210 - 170 = 40, so right margin will also be 20mm ?
    top=15mm,   % 297 - 257 = 40, so bottom margin will be 25mm ?
}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}
\hypersetup{pdfborder=0 0 0, colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=blue}
\usepackage{todonotes}
\usepackage{enumerate}
\usepackage{afterpage}    % Hack to remove page number from one specific page
\usepackage{transparent}  % Use transparent image to move float to right of two-col figure

\usepackage{natbib}
\usepackage{aas_macros}
\citestyle{aa}
\bibpunct{(}{)}{;}{a}{,}{,}

\graphicspath{{../img/}}   % Set image path

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand*{\thesection}{4.\arabic{section}}
\setcounter{section}{-1}

\makeatletter
\renewcommand{\fnum@figure}{Fig. \thefigure}
\makeatother

\begin{document}
\part*{Sec. 4 \quad Results}
\textbf{Question.} Is the star formation model implemented for the Auriga simulations 
capable of producing a population of star particles that is consistent with the
observed properties of the Milky Way (MW) globular cluster system (GCS)? 
\begin{itemize}
    \item What data do we have available for MW and M31? \\ 
        \null\qquad $\rightarrow$ Sec.~\ref{sec:data} on p.~\pageref{sec:data}
    \item Does Auriga's star formation model produce sufficient star particles 
        with the right age and metallicity ([Fe/H]) to be consistent with the
        MW GCS? \\ 
        \null\qquad $\rightarrow$ Sec.~\ref{sec:FeH} on p.~\pageref{sec:FeH}
    \item Does Auriga's star formation model produce sufficient star particles
        with the right age and radial distribution to be consistent with the
        MW GCS? \\ 
        \null\qquad $\rightarrow$ Sec.~\ref{sec:Rgc} on p.~\pageref{sec:Rgc}
    \item Does Auriga's star formation model produce sufficient star particles
        with the right age, metallicity ([Fe/H]) and radial distribution to be
        consistent with the MW GCS? \\ 
        \null\qquad $\rightarrow$ Sec.~\ref{sec:FeH-Rgc} on p.~\pageref{sec:FeH-Rgc}
\end{itemize}
\textbf{Question.} What does the picture look like when broaden the scope to 
consider spirals in the Local Group (i.e. including Andromeda/M31)? \\

\noindent \textbf{Assumption I.} All star particles in the Auriga simulations with age
$> 10$~Gyr are globular cluster candidates. \\

\textbf{Justification} 
\begin{enumerate}[i)]
    {\setlength\itemindent{25pt} \item 
        \citet{2013ApJ...775..134V} measured [Fe/H] of 55 globular clusters in
        the MW and obtained age-estimates. The mean age of the MW GCS is 11.9~Gyr 
        with a dispersion of 0.9~Gyr. Furthermore, only one of the 55 GC 
        age-estimates is below 10~Gyr.
    }
    {\setlength\itemindent{25pt} \item 
        \citet{2017MNRAS.465.3622R} performed one simulation of a MW-like galaxy 
        (down to z=0.5, T$_{\rm lookback}\approx$~5~Gyr) and performs the entire
        analysis using a subset of star particles with ages $>10$~Gyr that is 
        referred to as `globular cluster candidates'.
    }
\end{enumerate}

\textbf{Weaknesses}
\begin{enumerate}[i)]
    {\setlength\itemindent{25pt} \item 
        \citet{2018MNRAS.475.4309P} show that star clusters do not simply follow 
        the same distribution as the field stars. In our approach we don't just 
        oversample the `real' population of globular clusters (by ignoring/excluding
        dynamical evolution), but the retrieved distributions of old star particles in 
        the simulations may not even faithfully represent the `true' distribution of 
        globulars.
    }
    {\setlength\itemindent{25pt} \item 
        \citet{2011AJ....141...61C} measured [Fe/H] of 87 globular clusters
        in M31 and obtained age-estimates. The mean age is 10.8~Gyr with a 
        dispersion of 2.3~Gyr. Furthermore, 27 GCs have age-estimates below 10~Gyr,
        with a minimum age-estimate of 4.8~Gyr. Perhaps an age cut of 6~Gyr 
        would would be more appropriate for M31, see Fig.~\ref{fig:MW-M31-age}.
    }
\end{enumerate}

\afterpage{%
\section{Available data for the Milky Way and Andromeda}
\label{sec:data}
\thispagestyle{empty}
\begin{figure*}[h!]
    \includegraphics[width=0.5\textwidth]{{MW_M31_Age_HistogramMassWeighted}.png}
    \includegraphics[width=0.49\textwidth]{{MW_M31_FeH_HistogramMassWeighted}.png}
    \caption{
        \emph{Left:} Mass-weighted age distribution of 55 GCs in the MW 
        \citep[data from][]{2013ApJ...775..134V} and 87 GCs 
        in M31 \citep[data from][]{2011AJ....141...61C}.
        \emph{Right:} Mass-weighted [Fe/H] distribution of 151 GCs in the MW 
        \citep[data from][2010 ed.]{1996AJ....112.1487H} and 314 GCs in M31.
        \label{fig:MW-M31-ageFeH}
    }

    \includegraphics[width=0.49\textwidth]{{MW_M31_Rgc_HistogramMassWeighted}.png}
    \includegraphics[width=0.53\textwidth]
        {{MW_M31_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \caption{
        \emph{Left:} Mass-weighted R$_{\rm GC}$ distribution of 156 GCs in the MW.
        \emph{Right:} Mass-weighted [Fe/H]-R$_{\rm GC}$ distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
        is 98.19 \% of the total MW GCS mass.
        \label{fig:MW-M31-Rgc-FeHRgc}
    }

    \transparent{0.0}\includegraphics[width=0.49\textwidth]
        {{MW_M31_Rgc_HistogramMassWeighted}.png}
    \transparent{1.0}\includegraphics[width=0.53\textwidth]
        {{MW_M31_RgcFeH_HistogramMassWeighted_VandenBerg2013data}.png}
    \caption{
        Mass-weighted [Fe/H]-R$_{\rm GC}$ distribution of
        55 GCs in the Milky Way \citep[data from][]{2013ApJ...775..134V}, which
        is 43.27\% of the total MW GCS mass.
        \label{fig:MW-M31-FeHRgc2}
    }
\end{figure*}
\clearpage
}
\newpage

\afterpage{%
\newgeometry{
    a4paper,  % 210 x 297 mm
    total={170mm,257mm},
    left=20mm,  % 210 - 170 = 40, so right margin will also be 20mm ?
    top=5mm,   % 297 - 257 = 40, so bottom margin will be 25mm ?
}
\begin{table}[ht!]
    \centering
    \caption{
        The [Fe/H]-R$_{\rm GC}$ plot is generated using 
        \textsc{scipy.stats.binned\_statistic\_2d}. This table shows a manual 
        calculation of Msum and Ngc in each bin for debug purposes, just to check
        that \textsc{scipy}'s built-in method is used correctly. 
        Data from \citet[][2010 ed.]{1996AJ....112.1487H}.
        \label{tab:MW-FeH-Rgc}
    }
    \begin{tabular}{rrrrrrc}
        \hline
        xmin   & xmax   & ymin   & ymax   & Ngc    & Msum   & log$_{10}$(Msun) \\
        \hline
        1      & 3      & -2.5   & -1.5   & 7      & 1.7e+06 & 6.24       \\
        1      & 3      & -1.5   & -1.0   & 12     & 1.9e+06 & 6.27       \\
        1      & 3      & -1.0   & -0.5   & 9      & 7.7e+05 & 5.89       \\
        1      & 3      & -0.5   & -0.3   & 4      & 1.0e+06 & 6.02       \\
        1      & 3      & -0.3   & 0      & 2      & 3.2e+05 & 5.51       \\
        \hline
        3      & 8      & -2.5   & -1.5   & 16     & 4.6e+06 & 6.66       \\
        3      & 8      & -1.5   & -1.0   & 12     & 2.4e+06 & 6.37       \\
        3      & 8      & -1.0   & -0.5   & 10     & 2.5e+06 & 6.39       \\
        3      & 8      & -0.5   & -0.3   & 6      & 1.9e+06 & 6.29       \\
        3      & 8      & -0.3   & 0      & 1      & 3.0e+04 & 4.48       \\
        \hline
        8      & 15     & -2.5   & -1.5   & 11     & 3.0e+06 & 6.47       \\
        8      & 15     & -1.5   & -1.0   & 6      & 1.9e+06 & 6.27       \\
        8      & 15     & -1.0   & -0.5   & 1      & 6.5e+03 & 3.81       \\
        8      & 15     & -0.5   & -0.3   & 1      & 8.5e+04 & 4.93       \\
        8      & 15     & -0.3   & 0      & 0      & 0.0e+00 & -inf       \\
        \hline
        15     & 30     & -2.5   & -1.5   & 16     & 2.1e+06 & 6.31       \\
        15     & 30     & -1.5   & -1.0   & 6      & 2.2e+06 & 6.34       \\
        15     & 30     & -1.0   & -0.5   & 2      & 1.0e+04 & 4.02       \\
        15     & 30     & -0.5   & -0.3   & 1      & 1.5e+04 & 4.17       \\
        15     & 30     & -0.3   & 0      & 0      & 0.0e+00 & -inf       \\
        \hline
        30     & 125    & -2.5   & -1.5   & 6      & 1.1e+06 & 6.04       \\
        30     & 125    & -1.5   & -1.0   & 4      & 3.1e+05 & 5.49       \\
        30     & 125    & -1.0   & -0.5   & 1      & 1.4e+03 & 3.15       \\
        30     & 125    & -0.5   & -0.3   & 0      & 0.0e+00 & -inf       \\
        30     & 125    & -0.3   & 0      & 0      & 0.0e+00 & -inf       \\
        \hline
        \multicolumn{7}{c}{Data from \citet[][55 GCs]{2013ApJ...775..134V}} \\
        \hline
        1      & 3      & -2.5   & -1.5   & 3      & 5.5e+05 & 5.74       \\
        1      & 3      & -1.5   & -1.0   & 2      & 2.2e+05 & 5.35       \\
        1      & 3      & -1.0   & -0.5   & 2      & 2.3e+05 & 5.37       \\
        1      & 3      & -0.5   & -0.3   & 2      & 2.6e+05 & 5.42       \\
        1      & 3      & -0.3   & 0      & 0      & 0.0e+00 & -inf       \\
        \hline
        3      & 8      & -2.5   & -1.5   & 9      & 1.7e+06 & 6.22       \\
        3      & 8      & -1.5   & -1.0   & 5      & 9.1e+05 & 5.96       \\
        3      & 8      & -1.0   & -0.5   & 4      & 9.6e+05 & 5.98       \\
        3      & 8      & -0.5   & -0.3   & 1      & 1.1e+05 & 5.04       \\
        3      & 8      & -0.3   & 0      & 1      & 1.9e+05 & 5.29       \\
        \hline
        8      & 15     & -2.5   & -1.5   & 10     & 3.0e+06 & 6.48       \\
        8      & 15     & -1.5   & -1.0   & 4      & 1.3e+06 & 6.13       \\
        8      & 15     & -1.0   & -0.5   & 0      & 0.0e+00 & -inf       \\
        8      & 15     & -0.5   & -0.3   & 0      & 0.0e+00 & -inf       \\
        8      & 15     & -0.3   & 0      & 0      & 0.0e+00 & -inf       \\
        \hline
        15     & 30     & -2.5   & -1.5   & 6      & 6.8e+05 & 5.83       \\
        15     & 30     & -1.5   & -1.0   & 3      & 1.9e+06 & 6.29       \\
        15     & 30     & -1.0   & -0.5   & 1      & 8.9e+03 & 3.95       \\
        15     & 30     & -0.5   & -0.3   & 0      & 0.0e+00 & -inf       \\
        15     & 30     & -0.3   & 0      & 0      & 0.0e+00 & -inf       \\
        \hline
        30     & 125    & -2.5   & -1.5   & 0      & 0.0e+00 & -inf       \\
        30     & 125    & -1.5   & -1.0   & 0      & 0.0e+00 & -inf       \\
        30     & 125    & -1.0   & -0.5   & 0      & 0.0e+00 & -inf       \\
        30     & 125    & -0.5   & -0.3   & 0      & 0.0e+00 & -inf       \\
        30     & 125    & -0.3   & 0      & 0      & 0.0e+00 & -inf       \\
        \hline
    \end{tabular}
\end{table}
\clearpage
\restoregeometry
}
\clearpage

\section{Distribution of metallicity [Fe/H]}
\label{sec:FeH}

\section{Distribution of Galactocentric radii R$_{\rm GC}$}
\label{sec:Rgc}

\section{Distribution of [Fe/H]-R$_{\rm GC}$}
\label{sec:FeH-Rgc}

\newpage
\bibliographystyle{../mnras}
\bibliography{../AurigaGCS}

\end{document}

### 2018-12-23 Partial/introduction.tex
Some things were updated, I guess

--- 2018-10-04 AurigaGCS.tex
@@
-% mnras_template.tex
-%
-% LaTeX template for creating an MNRAS paper
-%
-% v3.0 released 14 May 2015
-% (version numbers match those of mnras.cls)
-%
-% Copyright (C) Royal Astronomical Society 2015
-% Authors:
-% Keith T. Smith (Royal Astronomical Society)
-
-% Change log
-%
-% v3.0 May 2015
-%    Renamed to match the new package name
-%    Version number matches mnras.cls
-%    A few minor tweaks to wording
-% v1.0 September 2013
-%    Beta testing only - never publicly released
-%    First version: a simple (ish) template for creating an MNRAS paper
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Basic setup. Most papers should leave these options alone.
 \documentclass[a4paper,fleqn,usenatbib]{mnras}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
 \usepackage{newtxtext,newtxmath}
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
 \usepackage[T1]{fontenc}
 \usepackage{ae,aecompl}
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-
-% Only include extra packages if you really need them. Common packages are:
-\usepackage{graphicx}    % Including figure files
-\usepackage{amsmath}    % Advanced maths commands
-\usepackage{amssymb}    % Extra maths symbols
-
-\usepackage{todonotes}
-\graphicspath{{img/}}   % Set image path
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-%\newcommand{\pcm}{\,cm$^{-2}$}    % per cm-squared
+\usepackage{graphicx} 
+\usepackage{amsmath} 
+\usepackage{amssymb}
+\graphicspath{{img/}} 
 \newcommand{\Sun}[0]{\ensuremath{_{\odot}}}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage[most]{tcolorbox} 
+\definecolor{block-gray}{gray}{0.95}
+\newtcolorbox{zitat}[2][]{%
+    colback=block-gray,
+    grow to right by=-10mm,
+    grow to left by=-10mm, 
+    boxrule=0pt,
+    boxsep=0pt,
+    breakable,
+    enhanced jigsaw,
+    borderline west={4pt}{0pt}{gray},
+    title={#2\par},
+    colbacktitle={block-gray},
+    coltitle={black},
+    fonttitle={\large\bfseries},
+    attach title to upper={},
+    #1,
+}
 
-%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
-
-% Title of the paper, and the short title which is used in the headers.
-% Keep the title short and informative.
 \title[Auriga GCS]{The Globular Cluster System of the Auriga Simulations}
 
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
-\author[T. L. R. Halbesma et al.]{
-Timo L. R. Halbesma,$^{1}$\thanks{E-mail: Halbesma@MPA-Garching.MPG.DE}
-Simon D. M. White,$^{1}$
-\\
-% List of institutions
-$^{1}$Max-Planck-Institut f\"ur Astrophysik, Postfach 1317, D-85741 Garching, Germany\\
+\author[T. L. R. Halbesma et al.]{\parbox[t]{\textwidth}{
+    Timo L. R. Halbesma$^{1}$\thanks{E-mail: Halbesma@MPA-Garching.MPG.DE},
+    Wilma Trick$^{1}$,
+    Robert J. J. Grand$^{1}$, 
+    Volker Springel$^{1}$, 
+    Facundo A. G\'{o}mez$^{2,3}$, 
+    Federico Marinacci$^{4,5}$,
+    R\"{u}diger Pakmor$^{1}$, 
+    Simon D. M. White$^{1}$
+} \vspace{10pt} \\
+$^{1}$ Max-Planck-Institut f\"ur Astrophysik, Postfach 1317, D-85741 Garching, Germany \\
+$^{2}$ Instituto de Investigaci\'{o}n Multidisciplinar en Ciencia yTecnolog\'{i}a, Universidad de La Serena, Ra\'{u}l Bitr\'{a}n 1305, La Serena, Chile \\
+$^{3}$ Departamento de F\'{i}sica y Astronom\'{i}a, Universidad de La Serena, Av. Juan Cisternas 1200 N, La Serena, Chile \\
+$^{4}$ Department of Physics, Kavli Institute for Astrophysics and Space Research, MIT, Cambridge, MA 02139, USA \\
+$^{5}$ Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA \\
 }
@@
 \section{Introduction}
-\todo[inline]{Paragraph: General introduction of GCs}
-\begin{itemize}
-    \item ``GCs among oldest astrophysical objects. GCs form in the early Universe in highest density peaks \citep[e.g.][]{2005MNRAS.364..367D, 2009ApJ...706L.192B}''
-    \item ``Hence, they witness most of the formation and evolution processes of galaxies, and can be used to probe them'' \citep{2006ARA&A..44..193B}
-    \item ``colour bimodality, blue and red clusters \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L, 2006ApJ...639...95P}
-    \item ``blue metal-poor (with distribution peaking at [Fe/H] $\approx -1.5$ for the Milky Way), no sign of rotation as a population (..) more metal-rich (peak at [Fe/H] $\approx -0.5$ in the Milky  Way) more spatially concentrated and rotating with the galaxy.'' \citep{1996AJ....112.1487H}
-\end{itemize}
 
-\todo[inline]{Paragraph: ``Bimodality suggests two formation mechanisms''}
-\begin{itemize}
-    \item ``Blue clusters from in early Universe in galaxies that merge later. In (wet) merger process starbursts generate red population \cite{1992ApJ...384...50A, 1987nngp.proc...18S}''
-    \item ``\citet{1997AJ....113.1652F} propose instead that blue globulars form when the protogalaxy itself collapses, in a metal-poor and turbulence media.
-The red population would form later, once the galactic disc has settled.
-The formation of globular clusters would then be a multiphase process, with the first phase being interrupted possibly by cosmic reionization \citep{2002MNRAS.333..383B}.''
-    \item ``\citet{2005ApJ...623..650K, 2014ApJ...796...10L} advocate
-that major mergers are at the origin of both sub-populations: blue
-clusters form during early mergers (z > 4) while the red ones appear
-in mergers at lower redshifts (even after z = 1). Although, this
-scenario, combined with star formation enhancement in mergers,
-seems appropriate in dense galactic environment leading to the
-assembly of massive elliptical galaxies, like in the Virgo Cluster
-as tested by \citet{2014ApJ...796...10L}, it does not apply to Milky Way-
-like systems where no recent major merger took place (Wyse 2001;
-Deason et al. 2013; Ruchti et al. 2014, 2015).
-\item ``\citet{1998ApJ...501..554C} argue that red clusters form in situ while the blue ones are accreted, either via merging satellite galaxies, or by tidal capture of the clusters themselves \citep[see also][]{2013ApJ...762...39T}.''
-\end{itemize}
+\subsection{GC form under special circumstances in high-z Universe}
+\begin{zitat}{\citet{2017MNRAS.465.3622R}}
+GCs are among the oldest astrophysical objects. They form in the early Universe in
+highest density peaks \citep[e.g.][]{2005MNRAS.364..367D, 2009ApJ...706L.192B}
+\end{zitat}
 
-\todo[inline]{Work of other groups}
-\begin{itemize}
-\item Origin of the Milky Way globular clusters \citep{2017MNRAS.465.3622R}
-\item GCs in FIRE \citep{2018MNRAS.474.4232K}
-\item EMOSAICS project \citep{2018MNRAS.475.4309P}
-\item Origin of GC bimodality? \citep{2018MNRAS.479..200F}
-\item \textit{GAIA} DR2: GC kinematics \citep{2018A&A...616A..12G}, Dating GC Tidal Disruption \citep{2018ApJ...859L..13B}
-\item GC in N-body simulation \citep{2018ApJ...861...69C}
-\item Tangentially related? role of GC mass evolution on stream properties \citep{2018MNRAS.474.2479B}
-\item GC formation from dwarfs to giants \citep{2018MNRAS.480.2343C}
-\item GC contribution to EOR \citep{2018MNRAS.479..332B}
-\item Early Universe supermassive star / GC formation \citep{2018MNRAS.478.2461G}
-\item GC formation in cold filaments \citep{2018ApJ...861..148M}
-\item GC formation in high-redshift dwarf galaxies \citep{2018MNRAS.477..480Z}
-\item GCs in MW outer region \citep{2017arXiv170804542P}
-\end{itemize}
+\begin{zitat}{\citet{2005MNRAS.364..367D}}
+The radial profile of the stellar halo and metal-poor globular
+clusters of the Milky Way suggest that these components formed in rare
+early peaks above $2.5 \sigma$ at redshift above 10.
+\end{zitat}
 
-\section{Methodology and definitions}
-\label{sec:methods}
-\subsection{The Auriga Simulations}
-\label{sec:auriga}
-We use the Auriga \citep[][hereafter G17]{2017MNRAS.467..179G} simulations, a suite of high-resolution cosmological zoom simulations ran with a galaxy formation model that produces realistic Milky Way-like galaxies at redshift $z=0$.
-The simulations are performed with \textsc{arepo} \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} that solves the magnetohydrodynamical equations on a moving mesh.
-See G17 for further details; here we briefly summarise the relevant properties.
-\todo[inline]{Paragraph: Auriga boilerplate, paraphrased}
+\begin{zitat}{\citet{2005MNRAS.364..367D}}
+The  clustering  properties  of  metal-poor  globular  clusters  contain
+clues on their formation sites and the epoch when star formation
+was suppressed by feedback processes (e.g. reionization, supernova-
+driven winds) in low-mass haloes. In the Milky Way metal-poor
+globular clusters follow the same radial profile as halo stars, suggesting
+within the framework of our model a common origin within
+early $2.5\sigma$ peak progenitors at $z\approx12$. Observations of the
+distribution of globular clusters within present-day haloes of different
+masses could provide information on feedback effects as a function
+of environment (Moore et al. 2005). The suppression of globular
+cluster formation at some early epoch may also explain the bimodality 
+observed in cluster metallicities (e.g. Strader et al. 2005). The
+widely  used  assumption  that  globular  cluster  formation  is  a  fair
+tracer of star formation, combined with the suppression of the formation  
+of  metal-poor  globulars  after  reionization,  imply  that  the
+amount of high-$\sigma$ material in a halo is proportional to the number of
+metal-poor globular clusters. From the results in Section 3.4 it follows 
+then that a simple universal reionization epoch would lead to a
+constant abundance of metal-poor globular clusters per virial mass.
+Deviations from this simplest case may provide information about
+the local reionization epoch, and whether regions with more (less)
+metal-poor globulars per virial mass were reionized later (earlier)
+(see Moore et al. 2005).
+\end{zitat}
 
-\todo[inline]{What is the star formation density threshold?}
+\subsection{YMC and GC formation governed by same physics; differences 
+due to nearly a Hubble time of evolution}
+``The widely  used  assumption  that  globular  cluster  formation  is  a  fair
+tracer of star formation'' $\rightarrow$ disputed?!
 
-\subsection{Definition of stellar halo}
-\todo[inline]{Possibly also relevant here. See \citet{2018arXiv180407798M}.}
+\subsection{Understand GC formation \& evolution $\rightarrow$ 
+understand MW formation \& evolution}
+This seems to shift the problem from `why care about GC formation and evolution'
+to `why care about MW formation and evolution'. People seems to accept this
+form of what-about-ism / diversion of focus. Actually, this is expansion of focus
+so probably people accept this as the bigger picture that we're all after.
 
-\subsection{Definition of accreted and in-situ component}
-\todo[inline]{Possibly also relevant here. See \citet{2018arXiv180407798M}.}
+\begin{zitat}{\citet{2017MNRAS.465.3622R}}
+Hence, they witness most of the formation and evolution processes of galaxies, and can be used to probe them \citep{2006ARA&A..44..193B}
+\end{zitat}
 
-\section{Comparison with observations}
-\label{sec:observations}
+\subsection{Colour bimodality}
+\begin{zitat}{\citet{2017MNRAS.465.3622R}}
+colour bimodality, blue and red clusters \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L, 2006ApJ...639...95P}
+\end{zitat}
 
-\begin{figure*}
-    \includegraphics[width=\textwidth]{{Au4-24_GCS_250_10}.pdf}
-    \caption{TODO: combine upper left and mid left panel, remove upper right panel,
-             remove lower panels (because mid right panel already shows the 
-             relevant info). The point of this figure is to compare metallicity 
-             distribution and radial distribution}
-    \label{fig:FeH_Rcs_MWvsAu424_1D}
-\end{figure*}
-
-\begin{figure*}
-    \includegraphics[width=\textwidth]{{Au4-24_FeH_vs_Rgc}.pdf}
-    \caption{Comparison of [Fe/H] and galactocentric radius of the Milky Way GCS
-             (red dots) with the star particles in Au4-24. TODO: only show the
-             panel on the right-hand side. TODO: include details of exactly which
-             star particles are shown. TODO: generate the same figure but color-coded
-             by mass?}
-    \label{fig:FeH_Rcs_MWvsAu424_2D}
-\end{figure*}
-
-\begin{figure*}
-    \includegraphics[width=\columnwidth]{vandenBergh2013.png}
-    \includegraphics[width=\columnwidth]{{Au4-24_Renaud2017_figure8}.png}
-    \caption{TODO: add observed age-FeH data points \citep{2013ApJ...775..134V}
-             to simulation plot, investigate starbursts by making pictures of
-             these events, check if the observed data set shows a representative
-             sample of the MW GCS, fix overlapping axes labels}
-    \label{fig:bla}
-\end{figure*}
-\begin{figure}
-    \includegraphics[width=\columnwidth]{{Au4-24_Renaud2017_figure6}.png}
-    \caption{}
-    \label{fig:bla}
-\end{figure}
-
-\section{Discussion}
-\label{sec:discussion}
-
-\section{Summary and conclusions}
-\label{sec:summary}
-
-\section*{Acknowledgements}
-TLRH acknowledges support from the International Max-Planck Research School (IMPRS) on Astrophysics.
-
-\todo[inline]{Check Auriga boilerplate that we need to acknowledge}
-RG and VS acknowledge support by the DFG Research Centre SFB-881 `The
-Milky Way System' through project A1. This work has also been
-supported by the European Research Council under ERC-StG grant
-EXAGAL- 308037. Part of the simulations of this paper used the
-SuperMUC system at the Leibniz Computing Centre, Garching,
-under the project PR85JE of the Gauss Centre for Supercomputing.
-This work used the DiRAC Data Centric system at Durham
-University, operated by the Institute for Computational Cosmology
-on behalf of the STFC DiRAC HPC Facility `www.dirac.ac.uk'.
-This equipment was funded by BIS National E-infrastructure capital 
-grant ST/K00042X/1, STFC capital grant ST/H008519/1 and
-STFC DiRAC Operations grant ST/K003267/1 and Durham University. 
-DiRAC is part of the UK National E-Infrastructure.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
+\begin{zitat}{\citet{2017MNRAS.465.3622R}}
+blue metal-poor (with distribution peaking at [Fe/H] $\approx -1.5$ for the Milky Way), no sign of rotation as a population (..) more metal-rich (peak at [Fe/H] $\approx -0.5$ in the Milky  Way) more spatially concentrated and rotating with the galaxy.
+\citep{1996AJ....112.1487H}
+\end{zitat}
 
@@
 
-% Alternatively you could enter them by hand, like this:
-% This method is tedious and prone to error if you have lots of references
-%\begin{thebibliography}{99}
-%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
-%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-%Others S., 2012, Journal of Interesting Stuff, 17, 198
-%\end{thebibliography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\section{Some extra material}
-
-If you want to present additional material which would interrupt the flow of the main paper,
-it can be placed in an Appendix which appears after the list of references.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Don't change these lines
-\bsp    % typesetting comment
-\label{lastpage}
 \end{document}
-
-% End of mnras_template.tex

### 2018-12-29 Partial/FeH_logM.tex
Mass-weighted FeH binning v1.0 done

@@
         1      & 3      & -2.5   & -1.5   & 7      & 1.7e+06 & 6.24       \\
-        1      & 3      & -1.5   & -1.0   & 12     & 1.9e+06 & 6.27       \\
-        1      & 3      & -1.0   & -0.5   & 9      & 7.7e+05 & 5.89       \\
+        1      & 3      & -1.5   & -1.0   & 15     & 1.9e+06 & 6.28       \\
+        1      & 3      & -1.0   & -0.5   & 10     & 8.2e+05 & 5.91       \\
         1      & 3      & -0.5   & -0.3   & 4      & 1.0e+06 & 6.02       \\
@@
         3      & 8      & -2.5   & -1.5   & 16     & 4.6e+06 & 6.66       \\
-        3      & 8      & -1.5   & -1.0   & 12     & 2.4e+06 & 6.37       \\
-        3      & 8      & -1.0   & -0.5   & 10     & 2.5e+06 & 6.39       \\
-        3      & 8      & -0.5   & -0.3   & 6      & 1.9e+06 & 6.29       \\
+        3      & 8      & -1.5   & -1.0   & 15     & 2.8e+06 & 6.44       \\
+        3      & 8      & -1.0   & -0.5   & 11     & 2.8e+06 & 6.44       \\
+        3      & 8      & -0.5   & -0.3   & 7      & 1.9e+06 & 6.29       \\
         3      & 8      & -0.3   & 0      & 1      & 3.0e+04 & 4.48       \\
@@
         8      & 15     & -2.5   & -1.5   & 11     & 3.0e+06 & 6.47       \\
-        8      & 15     & -1.5   & -1.0   & 6      & 1.9e+06 & 6.27       \\
+        8      & 15     & -1.5   & -1.0   & 7      & 2.4e+06 & 6.38       \\
         8      & 15     & -1.0   & -0.5   & 1      & 6.5e+03 & 3.81       \\
@@
         \hline
+        xmin   & xmax   & ymin   & ymax   & Ngc    & Msum   & log$_{10}$(Msun) \\
+        \hline
         1      & 3      & -2.5   & -1.5   & 3      & 5.5e+05 & 5.74       \\
@@
         3      & 8      & -2.5   & -1.5   & 9      & 1.7e+06 & 6.22       \\
-        3      & 8      & -1.5   & -1.0   & 5      & 9.1e+05 & 5.96       \\
+        3      & 8      & -1.5   & -1.0   & 6      & 1.1e+06 & 6.03       \\
         3      & 8      & -1.0   & -0.5   & 4      & 9.6e+05 & 5.98       \\
@@
         8      & 15     & -2.5   & -1.5   & 10     & 3.0e+06 & 6.48       \\
-        8      & 15     & -1.5   & -1.0   & 4      & 1.3e+06 & 6.13       \\
+        8      & 15     & -1.5   & -1.0   & 5      & 1.9e+06 & 6.27       \\
         8      & 15     & -1.0   & -0.5   & 0      & 0.0e+00 & -inf       \\
@@
 
+\afterpage{%
 \section{Distribution of metallicity [Fe/H]}
 \label{sec:FeH}
+\thispagestyle{empty}
+\begin{figure*}[h!]
+    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_plot-all}.png}
+    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_normalization_fit0}.png}
+    \caption{
+        \scriptsize \emph{Left:} Mass-weighted [Fe/H]-R$_{\rm GC}$ distribution of 
+        all Auriga haloes (level 3, 4 and 5).
+        \emph{Right:} There seems to be a trent of constant mass increase with
+        increasing metallicity in the range -3 to -1, and roughly 1 order of 
+        magnitude scatter in mass normalization. We use linear regression to 
+        obtain log$_{10}$(mass normalization) (i.e. we fit $a\cdot(x+3) + b$)
+        \label{fig:todo1}
+    }
+
+    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_normalization_fit1}.png}
+    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_normalization_fit3}.png}
+    \caption{
+        \scriptsize \emph{Left:} Scatter plot of log$_{10}$(mass normalization)
+        [i.e. $b$ obtained above] against the virial mass M$_{200,c}$ of the 
+        Auriga haloes. We use linear regression to see whether there is a 
+        correlation, and find $a_2 = 0.00388$, $b_2 = 6.597$. Colours indicate 
+        resolution: L3 red, L4 green, and L5 blue.
+        \emph{Right:} Same `data', but MCMC fit. Red dotted line shows 
+        `central' x value; yellow region 1$\sigma$ interval; blue dashed lines 
+        intrinsic scatter. Fake Error bars (1\% of the obtained values).
+        \label{fig:todo2}
+    }
+
+    { \centering
+    \includegraphics[width=0.4\textwidth]{{logMFeH_OldStars_normalization_fit2}.png}
+    \caption{
+        \scriptsize TODO: corner plot of the MCMC. Conclusion: there is a positive 
+        correlation of the normalization of old stellar mass with the virial
+        mass $M_{200,c}.$
+        \label{fig:todo3}
+    }
+    }
+\end{figure*}
+\clearpage
+}
+\clearpage
+
+\begin{figure*}[h!]
+    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_plot-errorbar}.png}
+    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_plot-hist2d}.png}
+    \caption{
+        % Au3-6, 16, 21, 23, 24, 27; Au4-1-30; Au5-6, 9 16 24
+        \emph{Left:} Mean value of all 40 simulations in orange.
+        \emph{Right:} Colorbar shows the number of simulations that fall in
+        (arbitrary) bins in y-direction.
+        \label{fig:todo4}
+    }
+
+    \includegraphics[width=0.49\textwidth]
+        {{logMFeH_OldAccreted_plot-hist2d-with-mean}.png}
+    \includegraphics[width=0.49\textwidth]
+        {{logMFeH_OldInsitu_plot-hist2d-with-mean}.png}
+    \caption{
+        \emph{Left:} Mass-weighted [Fe/H] distribution of 
+        \textbf{Old accreted} (age $>$~10~Gyr) star particles.
+        Solid orange line shows the mean of all old star particles in all Auriga
+        simulation. The dotted orange line shows the mean of all star particles
+        in all Auriga simulations (i.e. not enforcing an age cut).
+        \emph{Right:} Mass-weighted [Fe/H] distribution of \textbf{Old insitu} 
+        (age $>$~10~Gyr) star particles. 
+        \emph{Both / Conclusion:} The metallicity range $-3 <$ [Fe/H] $< -1$ is
+        only populated star particles older than ten Gyr; [Fe/H] $> -1$ is dominated
+        by star particles younger than 10~Gyr (two orders of magnitude difference). 
+        Furthermore, the old accreted star particles contribute most significantly 
+        to the range $-3 <$ [Fe/H] $< -1$, and the contribution of the old insitu
+        star particles at these metallicities declines steeper with declining
+        metallicity than the old accreted population. The old insitu population
+        provides the dominant contribution of the old population for 
+        [Fe/H] $> -1$.
+        \label{fig:todo5}
+    }
+\end{figure*}
+\clearpage
+
+\begin{figure*}[h!]
+    \includegraphics[width=\textwidth]{{logMFeH}.png}
+    \caption{
+        This figure summarises above findings. TODO: write caption for 
+        paper.
+        \label{fig:todo6}
+    }
+\end{figure*}
+
+\clearpage
 
@@
 
-\newpage
 \bibliographystyle{../mnras}

### 2019-01-02 Partial/FeH_logM.tex
Mass-weighted Rgc binning v1.0 done

@@
     }
+
+    \includegraphics[width=0.32\textwidth]{{logMFeH_Au6}.png}
+    \includegraphics[width=0.32\textwidth]{{logMFeH_Au16}.png}
+    \includegraphics[width=0.32\textwidth]{{logMFeH_Au24}.png}
+    \caption{Same figure, but now colours indicate resolution: L3 green, L4 
+        orange, and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo
+        16. \emph{Right:} Auriga halo 24. For all three haloes we find marginal
+        increases in the mass normalization with increasing resolution level.
+        \label{fig:logMFeH_res}
+    }
 \end{figure*}
-
 \clearpage
 
+\afterpage{%
 \section{Distribution of Galactocentric radii R$_{\rm GC}$}
 \label{sec:Rgc}
+\thispagestyle{empty}
+\begin{figure*}[h!]
+    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_plot-all-trim}.png}
+    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_plot-errorbar-trim}.png}
+    \caption{
+        \emph{Left:} Mass-weighted R$_{\rm GC}$ distribution of 
+        all Auriga haloes (level 3, 4 and 5).
+        \emph{Right:} 
+        \label{fig:todo7}
+    }
+
+    \includegraphics[width=0.49\textwidth]
+        {{logMRgc_OldAccreted_plot-hist2d-with-mean}.png}
+    \includegraphics[width=0.49\textwidth]
+        {{logMRgc_OldInsitu_plot-hist2d-with-mean}.png}
+    \caption{
+        \emph{Left:} 
+        \emph{Right:}
+        \label{fig:todo8}
+    }
+\end{figure*}
+\clearpage
+}
+\clearpage
+\begin{figure*}[h!]
+    \includegraphics[width=\textwidth]{{logMRgc}.png}
+    \caption{
+        This figure summarises above findings. TODO: write caption for 
+        paper.
+        \label{fig:todo6}
+    }
+
+    \includegraphics[width=0.32\textwidth]{{logMRgc_Au6}.png}
+    \includegraphics[width=0.32\textwidth]{{logMRgc_Au16}.png}
+    \includegraphics[width=0.32\textwidth]{{logMRgc_Au24}.png}
+    \caption{Same figure, but now colours indicate resolution: L3 green, L4 
+        orange, and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo
+        16. \emph{Right:} Auriga halo 24. For all three haloes we find marginal
+        increases in the mass normalization with increasing resolution level.
+        \label{fig:logMFeH_res}
+    }
+\end{figure*}
+\clearpage
 

### 2019-01-05 Partial/FeH_logM.tex
Ran 2D FeH Rgc analysis

@@
     \caption{
-        \scriptsize \emph{Left:} Mass-weighted [Fe/H]-R$_{\rm GC}$ distribution of 
+        \scriptsize \emph{Left:} Mass-weighted [Fe/H] distribution of 
         all Auriga haloes (level 3, 4 and 5).
@@
         correlation, and find $a_2 = 0.00388$, $b_2 = 6.597$. Colours indicate 
-        resolution: L3 red, L4 green, and L5 blue.
+        resolution: L3 green, L4 orange, and L5 blue.
         \emph{Right:} Same `data', but MCMC fit. Red dotted line shows 
@@
 \section{Distribution of Galactocentric radii R$_{\rm GC}$}
+\label{sec:FeH}
+% \thispagestyle{empty}
+\begin{figure*}[h!]
+    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_plot-all-trim}.png}
+    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_normalization_fit0-trim}.png}
+    \caption{
+        \scriptsize \emph{Left:} Mass-weighted R$_{\rm GC}$ distribution of 
+        all Auriga haloes (level 3, 4 and 5).
+        \emph{Right:} We use linear regression to obtain log$_{10}$(mass
+        normalization) in the domain 0-100 kpc (i.e. we fit $ax+b$ with $a=0$)
+        \label{fig:todo1}
+    }
+
+    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_normalization_fit1}.png}
+    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_normalization_fit3}.png}
+    \caption{
+        \scriptsize \emph{Left:} Scatter plot of log$_{10}$(mass normalization)
+        [i.e. $b$ obtained above] against the virial mass M$_{200,c}$ of the 
+        Auriga haloes. We use linear regression to see whether there is a 
+        correlation, and find $a_2 = 0.005$, $b_2 = 8.716$. Colours indicate 
+        resolution: L3 green, L4 orange, and L5 blue.
+        \emph{Right:} Same `data', but MCMC fit. Red dotted line shows 
+        `central' x value; yellow region 1$\sigma$ interval; blue dashed lines 
+        intrinsic scatter. Fake Error bars (1\% of the obtained values).
+        \label{fig:todo2}
+    }
+
+    { \centering
+    \includegraphics[width=0.4\textwidth]{{logMRgc_OldStars_normalization_fit2}.png}
+    \caption{
+        \scriptsize TODO: corner plot of the MCMC. Conclusion: there is a positive 
+        correlation of the normalization of old stellar mass with the virial
+        mass $M_{200,c}.$
+        \label{fig:todo3}
+    }
+    }
+\end{figure*}
+\clearpage
+}
+\clearpage
+
+\afterpage{%
 \label{sec:Rgc}
-\thispagestyle{empty}
+% \thispagestyle{empty}
 \begin{figure*}[h!]
@@
 
+\afterpage{%
 \section{Distribution of [Fe/H]-R$_{\rm GC}$}
 \label{sec:FeH-Rgc}
+
+% \thispagestyle{empty}
+\begin{figure*}[h!]
+    { \centering
+    \includegraphics[width=0.49\textwidth]
+        {{MW_M31_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
+    \caption{
+        Repetition of Fig.~\ref{fig:MW-M31-Rgc-FeHRgc} (right) for (convenient)
+        comparison. Note that the limits on the color bar are different for the 
+        observations and the mean of all simulations below.
+        \label{fig:todo1}
+    }
+    }
+
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_istars_mean}.png}
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_iold_mean}.png}
+    \caption{
+        \emph{Left:} Mass-weighted R$_{\rm GC}$-[Fe/H] distribution of 
+        all Auriga haloes (level 3, 4 and 5). Here we consider all stars
+        in all simulations and color-code the \textbf{mean value} 
+        (of 40 Auriga haloes)
+        \emph{Right:} Same figure, but for old ($>$~10~Gyr) stars.
+        \label{fig:todo2}
+    }
+
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_insitu-old_mean}.png}
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_accreted-old_mean}.png}
+    \caption{
+        \emph{Left:} Same figure, but for old insitu stars.
+        \emph{Right:} Same figure, but for old accreted stars.
+        \label{fig:todo2}
+    }
+
+\end{figure*}
+\clearpage
+}
+\clearpage
+
+\afterpage{%
+\begin{figure*}[h!]
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_istars_std}.png}
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_iold_std}.png}
+    \caption{
+        \emph{Left:} Mass-weighted R$_{\rm GC}$-[Fe/H] distribution of 
+        all Auriga haloes (level 3, 4 and 5). Here we consider all stars
+        in all simulations and color-code the \textbf{standard deviation} 
+        (of 40 Auriga haloes)
+        \emph{Right:} Same figure, but for old ($>$~10~Gyr) stars.
+        \label{fig:todo2}
+    }
+
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_insitu-old_std}.png}
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_accreted-old_std}.png}
+    \caption{
+        \emph{Left:} Same figure, but for old insitu stars.
+        \emph{Right:} Same figure, but for old accreted stars.
+        \label{fig:todo2}
+    }
+
+    \includegraphics[width=0.32\textwidth]
+        {{Au3-23_RgcFeH_HistogramMassWeighted_iold_16bins_comparison}.png}
+    \includegraphics[width=0.32\textwidth]
+        {{Au3-23_RgcFeH_HistogramMassWeighted_insitu-old_16bins_comparison}.png}
+    \includegraphics[width=0.32\textwidth]
+        {{Au3-23_RgcFeH_HistogramMassWeighted_accreted-old_16bins_comparison}.png}
+    \caption{
+        Lazy comparison to check whether there is more (total) mass in the simulated
+        star particles than in the MW GCS. Green means yes; red means no. We
+        check this for all fourty haloes individually to answer the question
+        whether the star formation model implemented in the Auriga simulations
+        can produce 'stars in the right place'.
+        \emph{Left:} Au3-23, old stars.
+        \emph{Mid:} Au3-23: old insitu stars.
+        \emph{Right:} Au3-23: old accreted stars.
+        \label{fig:todo2}
+    }
+
+\end{figure*}
+\clearpage
+}
+\clearpage
+
+\appendix
+\section{MCMC}
+Bayesian  code  as  described  in  and  distributed  by \citet{2012A&A...547A.117A}
+and used in \citet{2014A&A...568A..23A} for analysing the determination 
+of the evolution of the richness-mass scaling. Code used is \textsc{jags} 
+\citep{plummer2003jags}, and the Python wrapper \textsc{pyjags}, and
+for laziness \textsc{corner} \citep{corner} for visual inspection.
+
+Text could be something like the following.
+Blabla ``we adopt this Bayesian approach.'', and blabla
+``We assume weak priors on slope, intercept, and intrinsic scatter and solve for 
+all variables at once. We used a computationally inexpensive 10 thousand long 
+Markov chain Monte Carlo, discarding the initial 3 thousand elements used for 
+burn-in. By running multiple chains, we checked that convergence is already 
+achieved with short chains.''
 

### 2019-01-08 AurigaGCS.tex
Fit ax+b to FeH-Rgc blob, weighted by pass.

@@
 \label{sec:harris}
-\citet[][2010 edition]{1996AJ....112.1487H} provides the most up-to-date and comprehensive catalog of the MW GCS that contains properties of 157 globular clusters.
+\citet[][2010 edition, H96]{1996AJ....112.1487H} provides the most up-to-date and comprehensive catalog of the MW GCS that contains properties of 157 globular clusters.
 The catalogue is believed to be roughly 90\% complete.
@@
 \label{sec:vandenberg}
-\citet{2013ApJ...775..134V} measured [Fe/H] and obtained age-estimates for 55 globular clusters in the MW GCS.
+\citet[][V13]{2013ApJ...775..134V} measured [Fe/H] and obtained age-estimates for 55 globular clusters in the MW GCS.
 
@@
 \label{sec:m31}
-\citep{2011AJ....141...61C}
+\citep[][C11]{2011AJ....141...61C}
 \citep{2014MNRAS.442.2165H, 2014MNRAS.442.2929V}
@@
 \label{sec:results}
-\citet{2013ApJ...775..134V} presents age measurements of 55 GCs in the MW. The
-mean age of GCs in the MW is $11.9$~Gyr with a dispersion of $0.8$~Gyr. 
-Therefore we select all star particles in the Auriga simulations that are older 
-than $10$~Gyr. Henceforth we will refer the this subset of star particles as the 
-`GC candidates'. Our approach is similar to the one taken by \citep{2017MNRAS.465.3622R},
-where we know we are oversampling the real GC population with the contribution
-of field stars in our subset. This will be further addressed in the discussion.
+\citet{2013ApJ...775..134V} presents observations of 55 GCs in the MW with age-estimates
+where the mean value is $11.9\pm0.1$~Gyr with a dispersion of $0.8$~Gyr. Therefore we
+investigate the subset of star particles in the Auriga simulations that formed before a
+lookback time of $10$~Gyr. Henceforth we will refer the this subset of star particles as
+`GC candidates'.
 
@@
 
+We investigate all star particles in the Auriga simulations that are older than 10~Gyr,
+an approach equal to the method of \citep{2017MNRAS.465.3622R}. This approach does not
+take the bound cluster fraction \citep[e.g.][]{2012MNRAS.426.3008K} into account. This
+means that our sub set, which is based on selection by age, comprises both stars in the
+field as well as globular clusters. We compare the total mass in the simulations in 
+metallicity ([Fe/H]), galactocentric radius $r_{\text{gc}}$, and [Fe/H]-$r_{\text{gal}}$ 
+bins to the total mass in the MW GCS (using the H96 data set). The mass excess in the
+simulations gives a maximum mass loss `budget' for the product of cluster formation 
+efficiency and dynamical evolution. We find fractions that vary with metallicity,
+radius and metallicity-and-radius.
+
+\todo{
+``The fraction of all star formation that occurs in bound stellar clusters (the cluster formation efficiency, hereafter CFE) follows by integration of these local clustering and survival properties over the full density spectrum of the ISM, and hence is set by galaxy-scale physics.
+We derive the CFE as a function of observable galaxy properties, and find that it increases with the gas surface density'' \citep{2012MNRAS.426.3008K}
+}
+
 \section{Summary and conclusions}

### 2019-01-08 Partial/FeH_logM.tex
Fit ax+b to FeH-Rgc blob, weighted by pass.

@@
     \caption{
-        \emph{Left:} Mass-weighted R$_{\rm GC}$ distribution of 156 GCs in the MW.
-        \emph{Right:} Mass-weighted [Fe/H]-R$_{\rm GC}$ distribution of
+        \emph{Left:} Mass-weighted r$_{\text{gc}}$ distribution of 156 GCs in the MW.
+        \emph{Right:} Mass-weighted [Fe/H]-r$_{\text{gc}}$ distribution of
         151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
@@
     \caption{
-        Mass-weighted [Fe/H]-R$_{\rm GC}$ distribution of
+        Mass-weighted [Fe/H]-r$_{\text{gc}}$ distribution of
         55 GCs in the Milky Way \citep[data from][]{2013ApJ...775..134V}, which
@@
 \afterpage{%
-\section{Distribution of Galactocentric radii R$_{\rm GC}$}
+\section{Distribution of Galactocentric radii r$_{\text{gc}}$}
 \label{sec:FeH}
@@
     \caption{
-        \scriptsize \emph{Left:} Mass-weighted R$_{\rm GC}$ distribution of 
+        \scriptsize \emph{Left:} Mass-weighted r$_{\text{gc}}$ distribution of 
         all Auriga haloes (level 3, 4 and 5).
@@
     \caption{
-        \emph{Left:} Mass-weighted R$_{\rm GC}$ distribution of 
+        \emph{Left:} Mass-weighted r$_{\text{gc}}$ distribution of 
         all Auriga haloes (level 3, 4 and 5).
@@
 \afterpage{%
-\section{Distribution of [Fe/H]-R$_{\rm GC}$}
+\section{Distribution of [Fe/H]-r$_{\text{gc}}$}
 \label{sec:FeH-Rgc}
@@
     \caption{
-        \emph{Left:} Mass-weighted R$_{\rm GC}$-[Fe/H] distribution of 
+        \emph{Left:} Mass-weighted [Fe/H]-r$_{\text{gc}}$ distribution of 
         all Auriga haloes (level 3, 4 and 5). Here we consider all stars
@@
 
+\afterpage{%
+\subsection{Distribution of [Fe/H]-r$_{\text{gc}}$: more bins / higher resolution}
+\label{sec:FeH-Rgc-4096}
+\begin{figure*}[h!]
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_istars_4096bins_mean}.png}
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_iold_4096bins_mean}.png}
+    \caption{
+        \emph{Left:} Mass-weighted [Fe/H]-r$_{\text{gc}}$ distribution of 
+        all Auriga haloes (level 3, 4 and 5). Here we consider all stars
+        in all simulations and color-code the \textbf{standard deviation} 
+        (of 40 Auriga haloes). Difference here is that we `crancked up' the
+        resolution, because we can and it's awesome. Note that the range is
+        somewhat larger. Observational bin edges are indicated by horizontal and
+        vertical lines for convenience.
+        \emph{Right:} Same figure, but for old ($>$~10~Gyr) stars.
+        The red line shows a linear fit to the metallicity-radius relation, 
+        weighted by mass. The best-fit parameters are indicated in the lower
+        left corner.
+        \label{fig:todo2}
+    }
+
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_insitu-old_4096bins_mean}.png}
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_accreted-old_4096bins_mean}.png}
+    \caption{
+        \emph{Left:} Same figure, but for old insitu stars.
+        \emph{Right:} Same figure, but for old accreted stars.
+        Our linear fit shows the slope of the metallicity profile ($a$), as well
+        as the zero crossing point at r$_{\text{gc}}$=1kpc. ($b$). We note that
+        the $b$ is $0.49$~dex lower for old star particles than for all star 
+        particles. The radial profile of the old \textbf{accreted} star particles
+        is 0.18 dex lower than that of the old \textbf{insitu} star particles.
+        The gradient $a$ of -0.48 and -0.37 is slightly higher than the findings
+        of Harris 1998 Fig.8 p.235, who reports 
+        $\Delta$[Fe/H]~/~$\Delta$log~R$_{\text{gc}}$~=~-0.30 for 
+        R$_{\text{gc}} \lesssim$~10~kpc.
+        \label{fig:todo2}
+    }
+\end{figure*}
+\clearpage
+}
+\clearpage
+
+\afterpage{%
+\begin{figure*}[h!]
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_istars_4096bins_std}.png}
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_iold_4096bins_std}.png}
+    \caption{
+        \emph{Left:} Mass-weighted [Fe/H]-r$_{\text{gc}}$ distribution of 
+        all Auriga haloes (level 3, 4 and 5). Here we consider all stars
+        in all simulations and color-code the \textbf{standard deviation} 
+        (of 40 Auriga haloes). 
+        \emph{Right:} Same figure, but for old ($>$~10~Gyr) stars.
+        \label{fig:todo2}
+    }
+
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_insitu-old_4096bins_std}.png}
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_accreted-old_4096bins_std}.png}
+    \caption{
+        \emph{Left:} Same figure, but for old insitu stars.
+        \emph{Right:} Same figure, but for old accreted stars.
+        \label{fig:todo2}
+    }
+\end{figure*}
+\clearpage
+}
+\clearpage
+
+\section{Properties of birth haloes of the accreted population}
+\label{sec:accreted-birth-haloes}
+
 \appendix

### 2019-01-08 AurigaGCS.tex
Improved figures. Placed figures in draft paper

@@
 $^{1}$ Max-Planck-Institut f\"ur Astrophysik, Postfach 1317, D-85741 Garching, Germany \\
-$^{2}$ Instituto de Investigaci\'{o}n Multidisciplinar en Ciencia yTecnolog\'{i}a, Universidad de La Serena, Ra\'{u}l Bitr\'{a}n 1305, La Serena, Chile \\
-$^{3}$ Departamento de F\'{i}sica y Astronom\'{i}a, Universidad de La Serena, Av. Juan Cisternas 1200 N, La Serena, Chile \\
-$^{4}$ Department of Physics, Kavli Institute for Astrophysics and Space Research, MIT, Cambridge, MA 02139, USA \\
-$^{5}$ Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA \\
+$^{2}$ Instituto de Investigaci\'{o}n Multidisciplinar en Ciencia yTecnolog\'{i}a, 
+    Universidad de La Serena, Ra\'{u}l Bitr\'{a}n 1305, La Serena, Chile \\
+$^{3}$ Departamento de F\'{i}sica y Astronom\'{i}a, Universidad de La Serena, Av.
+    Juan Cisternas 1200 N, La Serena, Chile \\
+$^{4}$ Department of Physics, Kavli Institute for Astrophysics and Space Research,
+    MIT, Cambridge, MA 02139, USA \\
+$^{5}$ Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge,
+    MA 02138, USA \\
 }
@@
 at radii and metallicities that are typical for the MW GCS, although we observe
-a varying mass-excess for the different $R_{\text{GC}}$-[Fe/H] bins. This implies
+a varying mass-excess for the different $r_{\text{gal}}$-[Fe/H] bins. This implies
 different values for the combined product of the bound cluster formation efficiency
@@
 \todo[inline]{Paper outline}
-We summarise the relevant characteristics of the Auriga simulations in section~\ref{sec:auriga}, followed by a summary of the observations of the Milky Way (MW) globular cluster system (GCS) in section~\ref{sec:observations} that we use to compare our simulations to in section~\ref{sec:results}.
-We discuss our findings in section~\ref{sec:discussion} to come to our conclusions in section~\ref{sec:conclusions}.
+We summarise the relevant characteristics of the Auriga simulations in 
+section~\ref{sec:auriga}, followed by a summary of the observations of the
+Milky Way (MW) globular cluster system (GCS) in section~\ref{sec:observations}
+that we use to compare our simulations to in section~\ref{sec:results}. We
+discuss our findings in section~\ref{sec:discussion} to come to our conclusions 
+in section~\ref{sec:conclusions}.
 
@@
 \label{sec:auriga}
-We use the Auriga \citep[][hereafter G17]{2017MNRAS.467..179G} simulations, a suite of high-resolution cosmological zoom simulations ran with a galaxy formation model that produces realistic Milky Way-like galaxies at redshift $z=0$.
-The simulations are performed with \textsc{arepo} \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} that solves the magnetohydrodynamical equations on a moving mesh.
-See G17 for further details; here we briefly summarise the relevant properties.
-\todo[inline]{Paragraph: Auriga boilerplate, paraphrased}
+We use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, a 
+suite of high-resolution cosmological zoom simulations ran with a galaxy
+formation model that produces realistic Milky Way-like galaxies at redshift
+$z=0$. The simulations are performed with the state-of-the art code \textsc{arepo}
+\citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} that solves the 
+magnetohydrodynamical equations on a moving mesh.
 
-``The simulations include a comprehensive model for galaxy formation physics which includes important baryonic processes, such as
+The interstellar medium is modelled using a sub-grid approach which implements
+the physical processes most relevant to galaxy formation and evolution. 
+This model was tailored to the \textsc{arepo} code and calibrated to reproduce
+key observables of galaxies, such as the history of the cosmic star formation rate 
+density, the stellar mass to halo mass relation, and galaxy luminosity functions.
 
-primordial and metal-line cooling \citep{2013MNRAS.436.3031V};
+The sub-grid includes primordial and metal-line cooling with self-shielding corrections.
+Reionization is completed at redshift six by a time-varying spatially uniform UV 
+background \citep{2009ApJ...703.1416F, 2013MNRAS.436.3031V}
+The interstellar medium is described by an equation of state for a two-phase medium
+in pressure equilibrium \citep{2003MNRAS.339..289S} with stochastic star formation
+in thermally unstable gas with a density threshold of $n = 0.13 \text{cm}^{-3}$,
+and consecutive stellar evolution is accounted for. Stars provide feedback by 
+stellar winds \citep{2014MNRAS.437.1750M, 2017MNRAS.467..179G}, and further 
+enrich the ISM with metals from SNIa, SNII, and AGB stars \citep{2013MNRAS.436.3031V}.
+The formation of black holes is modelled which results in feedback from active 
+galactic nuclei \citep{2005MNRAS.361..776S, 2014MNRAS.437.1750M, 2017MNRAS.467..179G}.
+Finally, the simulations follow the evolution of a magnetic field of $10^{-14}$
+(comoving)~G seeded at $z = 127$ \citep{2013MNRAS.432..176P, 2014ApJ...783L..20P}.
+See G17 for further details of the numerical setup as well as the galaxy formation
+model.
 
-a sub-grid model for the interstellar medium that utilises an equation of state representing a two-phase medium in pressure equilibrium \citep{2003MNRAS.339..289S}
-u
-a model for the star formation and stellar feedback that includes a phenomenological wind model \citep{2014MNRAS.437.1750M, 2017MNRAS.467..179G}
-
-and metal enrichment from SNII, SNIa and AGB stars \citep{2013MNRAS.436.3031V}
-
-black hole formation and active galactic nucleus feedback (\citep{2005MNRAS.361..776S, 2014MNRAS.437.1750M, 2017MNRAS.467..179G}
-
-a spatially uniform, time-varying UV background after reionization at redshift six \citep{2009ApJ...703.1416F, 2013MNRAS.436.3031V}
-
-and magnetic fields \citep{2013MNRAS.432..176P, 2014ApJ...783L..20P}
-
-The model was specifically developed for the \textsc{arepo} code and was calibrated to reproduce several observational results such as the stellar mass to halo mass relation, galaxy luminosity functions and the history of the cosmic star formation rate density.
-''
-
-\todo[inline]{What is the star formation density threshold?}
-``The gas is assumed to be star-forming and thermally unstable for densities higher than a threshold density that we derive from the parameters of the two gas phases and the desired star formation time-scale to be $n = 0.13 \text{cm}^{-3}$.'' - \citep{2017MNRAS.467..179G}
-
-\todo[inline]
-``The diversity in morphological properties of these simulated galaxies reflects the stochasticity inherent to the process of galaxy formation and evolution \citep[e.g.][]{2005ApJ...635..931B, 2010MNRAS.406..744C, 2010ApJ...708.1398T}.''
+\todo[inline]{
+``The diversity in morphological properties of these simulated galaxies reflects
+the stochasticity inherent to the process of galaxy formation and evolution 
+\citep[e.g.][]{2005ApJ...635..931B, 2010MNRAS.406..744C, 2010ApJ...708.1398T}.''
+}
 
@@
 
-\section{Relevant observational data for Local Group spirals}
-The Milky Way + M31 globular cluster system
+\section{Relevant observational data}
 \label{sec:observations}
+The galaxy formation model implemented for the Auriga simulations produces
+realistic spiral galaxies at redshift zero. Therefore we aim to compare the
+simulations to the globular cluster systems of the spiral galaxies in the 
+Local Group (i.e. the Milky Way and Andromeda galaxy or M31). Here we summarise 
+the relevant data available in the literature.
 
-\subsection{Harris catalogue}
+\subsection{Milky Way: Harris catalogue}
 \label{sec:harris}
-\citet[][2010 edition, H96]{1996AJ....112.1487H} provides the most up-to-date and comprehensive catalog of the MW GCS that contains properties of 157 globular clusters.
-The catalogue is believed to be roughly 90\% complete.
+\citet[][2010 edition; hereafter H96]{1996AJ....112.1487H} provides a fairly
+up-to-date, comprehensive catalogue of the Milky Way globular cluster system and
+contains properties of 157 globular clusters. The catalogue is believed to be 
+roughly 90\% complete. The relevant data fields that we use from H96 are the 
+metallicity [Fe/H], galactocentric radius $r_{\text{gal}}$, and absolute magnitude 
+in the V-band $M_V$. 
+\todo[inline]{
+We use the latter to calculate a mass-estimate by assuming
+$M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$ 
+(the mean for MW clusters McLaughlin \& van der Marel 2005). 
+}
 
-\subsection{Age estimates}
+In Fig.~\ref{fig:MW-RgcFeH} we show a two-dimensional mass-weighted distribution,
+splitting the data up in bins of both radius and metallicity. Later on we 
+investigate whether the star formation model implemented for the Auriga simulations 
+can produce a sufficient total mass in globular cluster candidates at the right
+values of radius, metallicity, and radius-metals, see Sec.~\ref{sec:RgcFeH}
+
+\begin{figure}
+    \includegraphics[width=\columnwidth]
+        {{MW_M31_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
+    \caption{
+        Mass-weighted r$_{\text{gc}}$-[Fe/H] distribution of
+        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
+        is 98.19 \% of the total MW GCS mass.
+        \label{fig:MW-RgcFeH}
+    }
+\end{figure}
+
+\subsection{Milky Way: VandenBerg catalogue}
 \label{sec:vandenberg}
-\citet[][V13]{2013ApJ...775..134V} measured [Fe/H] and obtained age-estimates for 55 globular clusters in the MW GCS.
+\citet[][hereafter V13]{2013ApJ...775..134V} used photometric data to obtain 
+[Fe/H] measurements and age-estimates for 55 globular clusters in the Milky Way.
+The mean value of the age-estimates in this data set is $11.9 \pm 0.1$ Gyr and the
+dispersion is 0.9 Gyr. Furthermore, only one of the 55 GC age-estimates is
+below 10 Gyr.
 
+\todo[inline]{
 How is this particular sample selected? What biases does this introduce?
-Is this sample drawn from the same underlying distribution as the Harris sample (plot distributions of FeH, compare mean/std, do t-test)
+Is this sample drawn from the same underlying distribution as the Harris sample 
+(plot distributions of FeH, compare mean/std, do t-test)
+}
 
-\subsection{M31}
-\todo[inline]{Get big dataset of M31 GCS}
+\subsection{Andromeda: Caldwell catalogue}
 \label{sec:m31}
-\citep[][C11]{2011AJ....141...61C}
-\citep{2014MNRAS.442.2165H, 2014MNRAS.442.2929V}
+\citet[][, hereafter C11]{2011AJ....141...61C} studied globular clusters in the
+Andromeda galaxy. The relevant fields in this data set are the age, metallicities,
+and absolute visual magnitude.
+\todo[inline]{
+`For M31 GC masses we combine the catalogues of Caldwell et al. (2011, using the 
+given masses) and Huxor et al. (2014, again assuming $M/L_V = 1.7$~M/L$_{\odot}$, 
+e.g. Strader, Caldwell \& Seth 2011).'
+}
+For M31 we find an age distribution with a mean value of 10.8$\pm 10.8$~Gyr and a 
+dispersion of 2.3~Gyr. Furthermore, 27 GCs have age-estimates below 10~Gyr, and
+the minimum age is 4.8~Gyr. Perhaps an age cut of 6~Gyr would would be more 
+appropriate for M31, see Fig.~\ref{fig:MW-M31-age}.
+
+\begin{figure}
+    \includegraphics[width=\columnwidth]{{MW_M31_Age_HistogramMassWeighted}.png}
+    \caption{
+        Mass-weighted age distribution of 55 GCs in the MW
+        \citep[data from][]{2013ApJ...775..134V} and 87 GCs
+        in M31 \citep[data from][]{2011AJ....141...61C}.
+        \label{fig:MW-M31-age}
+    }
+\end{figure}
+
+\todo[inline]{
+Furthermore, we supplement observational data of globular clusters in M31 with 
+\citet{2014MNRAS.442.2165H, 2014MNRAS.442.2929V}
+}
 
@@
 \label{sec:results}
-\citet{2013ApJ...775..134V} presents observations of 55 GCs in the MW with age-estimates
-where the mean value is $11.9\pm0.1$~Gyr with a dispersion of $0.8$~Gyr. Therefore we
-investigate the subset of star particles in the Auriga simulations that formed before a
-lookback time of $10$~Gyr. Henceforth we will refer the this subset of star particles as
-`GC candidates'.
+We investigate globular cluster candidates in the Auriga simulations using an age
+cut to select of stars that formed at a lookback time greater than $10$~Gyr. We 
+chose this particular value because the mean age-estimate of the $55$ in V13 is
+$11.9\pm0.1$~Gyr with a dispersion of $0.8$~Gyr, and only one observed globular 
+cluster falls below this selection criterion.
+
+In Sec.~\ref{sec:metallicity} we investigate the metallicity distribution of the
+GC candidates, in Sec.~\ref{sec:spatial} we show the distribution of galactocentric
+radii of the globular cluster candidates within the Auriga simulations, and we 
+combine both in Sec.~\ref{sec:RgcFeH}. We continue our analysis with a deeper 
+analysis of the properties of the proto-galaxies at times of birth of the accreted 
+globular cluster population in Sec.~\ref{sec:birth-properties-of-accreted-gc-candidates}
 
@@
 \label{sec:metallicity}
+\todo[inline]{
+Can the Auriga simulations produce star particles of $>10$~Gyr (GC candidates) 
+with a metallicity distribution that is consistent with the MW GCS?
+}
 
-Can the Auriga simulations produce star particles of $>10$~Gyr (GC candidates) with a metallicity distribution that is consistent with the MW GCS?
+In Fig.~\ref{fig:FeH} we show a mass-weighted metallicity distribution of star 
+particles in the Auriga simulations. We show the median value of all Auriga 
+haloes for all stars (orange dotted lines) and globular cluster candidates 
+orange solid). The latter sub set is further split up between stars that formed 
+in-situ (red solid), and those that were accreted (blue solid). The shaded regions 
+indicate the $1\sigma$ interval. The MW GCS is shown in purple and that of M31 
+in pink. We use the same bin sizes for the simulations as for the observations, 
+explicitly plotted for the observed profiles.
 
-Fig.~\ref{fig:FeH}
+\begin{figure}
+    \includegraphics[width=\columnwidth]{{logMFeH_noStepsMid-trim}.png}
+    \caption{
+        Mass-weighted metallicity distribution of star particles in the Auriga 
+        simulations. We show the median value of all Auriga haloes for all
+        stars (orange dotted) and globular cluster candidates (i.e. stars with 
+        age $>$~10~Gyr; orange solid). The latter sub set is further split up
+        between stars that formed in-situ (red solid), and those that were accreted
+        (blue solid). Shaded regions indicate the $1\sigma$ interval. The MW GCS
+        is shown in purple and that of M31 in pink. We use the same bin sizes
+        for the simulations as for the observations, explicitly plotted for the
+        observed profiles.
+        \label{fig:FeH}
+    }
+\end{figure}
 
-Split into insitu / accreted
+We find that the metallicity range $-3 <$ [Fe/H] $< -1$ is only populated by 
+star particles older than ten Gyr, while [Fe/H] $> -1$ is dominated by star 
+particles younger than 10~Gyr (with a difference of two orders of magnitude). 
+Furthermore, the old accreted star particles contribute most significantly to 
+the range $-3 <$ [Fe/H] $< -1$, and the contribution of the old in-situ star
+particles at these metallicities declines steeper with declining metallicity 
+than the old accreted population. The old in-situ population provides the 
+dominant contribution of the old population for [Fe/H] $> -1$.
 
-Conclusion: too many metal-rich star particles.
+We notice a scatter\footnote{Here scatter means the width of the 1$\sigma$ interval.
+The difference between the minimum and maximum values is $0.9$~dex.} in mass 
+normalization of $0.3$ dex between the different Auriga galaxies. We investigate 
+whether there is a correlation between the total stellar mass in (old) star particles
+and the virial mass\footnote{The virial mass is defined as the mass contained inside the
+radius $r_{200,c}$ at which the average (spherical) mass density equals two hundred 
+times the critical density of the Universe} $M_{200,c}$ of the host halo.
+We fit $a \cdot \left(\text{M}_{200,c}[1\text{e}10 \text{M\Sun}] - 140\right) + b$
+to log$_{10}\left(\Sigma_{i} m_i(\text{\scriptsize [Fe/H] = -3})\right)$.
+% \limits_{i, \text{if age(i) $>$ 10~Gyr}}
+Our fit thus provides the slope $a$ and normalization of (old) stellar mass $b$
+at [Fe/H]=-3 for $M_{200,c}$ at 140e10~M\Sun. We find $a = 0.00388$, $b = 6.597$
+and conclude that there is a small positive correlation of mass in (old) star 
+particles with the virial mass of the host halo.
 
-\begin{figure*}
-    \includegraphics[width=\columnwidth]{{logMFeH_OldStars}.png}
-    \includegraphics[width=\columnwidth]{{logMFeH}.png}
-\end{figure*}
-\begin{figure*}
-    \includegraphics[width=\columnwidth]{{logMFeH_OldInsitu}.png}
-    \includegraphics[width=\columnwidth]{{logMFeH_OldAccreted}.png}
-    \caption{Caption}
-    \label{fig:FeH}
-\end{figure*}
+\begin{figure}
+\includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_normalization_fit3}.png}
+    \caption{
+        Plot of log$_{10}$(mass normalization) [i.e. $b$ obtained above] against 
+        the virial mass M$_{200,c}$ of the Auriga haloes. We fit a linear relation 
+        to see whether there is a correlation, and find $a = 0.00388$, $b = 6.597$. 
+        % Colours indicate resolution: L3 green, L4 orange, and L5 blue.
+        The red dotted line shows the `central' value of M$_{200,c}$, the yellow 
+        region shows the 1$\sigma$ interval around the best-fit relation, and the
+        blue dashed lines shows the intrinsic scatter. The error bars show 1\% 
+        of the obtained values.
+        \label{fig:Mnorm-fit}
+    }
+\end{figure}
+
+Furthermore we compare the simulated metallicity distribution to observations
+of the Milky Way and M31.
+\todo[inline]{
+    yes/no bimodal
+
+    M31 slope between -3 and -1 consistent with old insitu?
+
+    MW above 0 no more GCs, but Auriga well populated (mostly insitu, but
+    also too many accreted.
+
+    should also comment on all vs old (Auriga simulation) btw
+
+}
+
+bla. Conclusion: too many metal-rich star particles.
 
@@
 
-\begin{figure*}
-    \includegraphics[width=\columnwidth]{{logMRgc_OldStars}.png}
-    \includegraphics[width=\columnwidth]{{logMRgc}.png}
-\end{figure*}
-\begin{figure*}
-    \includegraphics[width=\columnwidth]{{logMRgc_OldInsitu}.png}
-    \includegraphics[width=\columnwidth]{{logMRgc_OldAccreted}.png}
-    \caption{Caption}
+\begin{figure}
+    \includegraphics[width=\columnwidth]{{logMRgc_noStepsMid-trim}.png}
+    \caption{
+        Mass-weighted distribution of galactocentric radii at which star 
+        particles in the Auriga simulations are found.
         \label{fig:Rgc}
-\end{figure*}
+    }
+\end{figure}
+
+\subsection{Radius-metallicity distribution}
+\label{sec:RgcFeH}
+What age-metallicity distribution is produced by star formation events in the Auriga simulations?
+
+\begin{figure}
+    \includegraphics[width=\columnwidth]
+        {{logMRgcFeH_accreted-insitu-notitle}.png}
+    \caption{
+        OMG what a beautiful plot.
+        \label{fig:todo2}
+    }
+\end{figure}
+
+\section{Properties of birth haloes of the accreted population}
+\label{sec:birth-properties-of-accreted-gc-candidates}
 
@@
 
-How does the total stellar mass in $R_\textbf{GC}$-[Fe/H] bins compare to the MW GCS?
+How does the total stellar mass in $r_\textbf{gal}$-[Fe/H] bins compare to the MW GCS?
 
@@
 Can we distinguish between particles that have formed in-situ and those that have been accreted?
-Can we identify specific features in the age-metallicity plane, or in the $R_\textbf{GC}$-[Fe/H] plane, that result from one of both populations?
+Can we identify specific features in the age-metallicity plane, or in the $r_\textbf{gal}$-[Fe/H] plane, that result from one of both populations?
 How does this connect to proposed mechanisms for globular cluster formation in the literature?
@@
 Orbits: are the pericentres different? Look at velocity + specific angular momentum distribution in the different FeH/Rgc bins as proxy for the pericenter
-
-\subsection{Scatter for different Auriga haloes} 
-\label{sec:convergence}
-Are the properties of the Auriga globular cluster candidates converged for runs with different initial conditions but at the same resolution level?
-How much scatter do we observe in the properties of the globular cluster candidates across the full suite of Auriga haloes?
-
-\subsection{Numerical convergence (possibly in appendix)} 
-\label{sec:convergence}
-Are the properties of the Auriga globular cluster candidates converged for runs with the same initial conditions but at different resolution levels?
-
-\begin{figure*}
-    \includegraphics[width=0.31\textwidth]{{logMFeH_Au6}.png}
-    \includegraphics[width=0.31\textwidth]{{logMFeH_Au16}.png}
-    \includegraphics[width=0.31\textwidth]{{logMFeH_Au24}.png}
-    \caption{Caption}
-    \label{fig:FeH_l345}
-\end{figure*}
-\begin{figure*}
-    \includegraphics[width=0.31\textwidth]{{logMRgc_Au6}.png}
-    \includegraphics[width=0.31\textwidth]{{logMRgc_Au16}.png}
-    \includegraphics[width=0.31\textwidth]{{logMRgc_Au24}.png}
-    \caption{Caption}
-    \label{fig:Rgc_l345}
-\end{figure*}
-
-% \begin{figure*}
-%     \includegraphics[width=\textwidth]{{Au4-24_GCS_250_10}.pdf}
-%     \caption{TODO: combine upper left and mid left panel, remove upper right panel,
-%              remove lower panels (because mid right panel already shows the 
-%              relevant info). The point of this figure is to compare metallicity 
-%              distribution and radial distribution}
-%     \label{fig:FeH_Rcs_MWvsAu424_1D}
-% \end{figure*}
-% 
-% 
-% \begin{figure*}
-%     \includegraphics[width=\textwidth]{{Au4-24_FeH_vs_Rgc}.pdf}
-%     \caption{Comparison of [Fe/H] and galactocentric radius of the Milky Way GCS
-%              (red dots) with the star particles in Au4-24. TODO: only show the
-%              panel on the right-hand side. TODO: include details of exactly which
-%              star particles are shown. TODO: generate the same figure but color-coded
-%              by mass?}
-%     \label{fig:FeH_Rcs_MWvsAu424_2D}
-% \end{figure*}
-% 
-% 
-% \begin{figure*}
-%     \includegraphics[width=\columnwidth]{vandenBergh2013.png}
-%     \includegraphics[width=\columnwidth]{{Au4-24_Renaud2017_figure8}.png}
-%     \caption{TODO: add observed age-FeH data points \citep{2013ApJ...775..134V}
-%              to simulation plot, investigate starbursts by making pictures of
-%              these events, check if the observed data set shows a representative
-%              sample of the MW GCS, fix overlapping axes labels}
-%     \label{fig:bla}
-% \end{figure*}
-% \begin{figure}
-%     \includegraphics[width=\columnwidth]{{Au4-24_Renaud2017_figure6}.png}
-%     \caption{}
-%     \label{fig:bla}
-% \end{figure}
 
@@
 
-\todo{
+\todo[inline]{
 ``The fraction of all star formation that occurs in bound stellar clusters (the cluster formation efficiency, hereafter CFE) follows by integration of these local clustering and survival properties over the full density spectrum of the ISM, and hence is set by galaxy-scale physics.
@@
 %%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
+\clearpage
+\appendix
+\section{Scatter between individual Auriga haloes, and numerical convergence} 
+\label{sec:scatter-convergence}
+We check whether the properties of the Auriga globular cluster candidates 
+are well converged between the three different resolution levels used for the 
+Auriga simulations. Here we consider all three Auriga haloes for which simulation
+runs were performed at all three resolution levels: Au6, Au16, and Au24. Here
+we can investigate differences between individual haloes.
 
-\appendix
+Fig.~\ref{fig:logMFeH_res} shows the mass-weighted metallicity distribution, 
+Fig.~\ref{fig:logMRgc_res} shows the mass-weighted radial distribution, and
+Fig.~\ref{fig:logMRgcFeH_res}
 
-\section{Some extra material}
+\begin{figure*}
+    \includegraphics[width=0.31\textwidth]{{logMFeH_Au6}.png}
+    \includegraphics[width=0.31\textwidth]{{logMFeH_Au16}.png}
+    \includegraphics[width=0.31\textwidth]{{logMFeH_Au24}.png}
+    \caption{Same as Fig.~\ref{fig:FeH}, but here the colours indicate resolution
+        level: L3 green, L4 orange, and L5 blue. \emph{Left:} Auriga halo 6.
+        \emph{Mid:} Auriga halo 16. \emph{Right:} Auriga halo 24. For all three
+        haloes we find marginal increases in the mass normalization with increasing 
+        resolution level.
+        \label{fig:logMFeH_res}
+    }
 
-If you want to present additional material which would interrupt the flow of the main paper,
-it can be placed in an Appendix which appears after the list of references.
+\end{figure*}
+\begin{figure*}
+    \includegraphics[width=0.31\textwidth]{{logMRgc_Au6}.png}
+    \includegraphics[width=0.31\textwidth]{{logMRgc_Au16}.png}
+    \includegraphics[width=0.31\textwidth]{{logMRgc_Au24}.png}
+    \caption{Same as Fig.~\ref{fig:Rgc}, but here the colours indicate resolution
+        level: L3 green, L4 orange, and L5 blue. \emph{Left:} Auriga halo 6.
+        \emph{Mid:} Auriga halo 16. \emph{Right:} Auriga halo 24. For all three 
+        haloes we find marginal increases in the mass normalization with increasing 
+        resolution level.
+        \label{fig:logMRgc_res}
+    }
 
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-01-08 Partial/FeH_logM.tex
Improved figures. Placed figures in draft paper

@@
 \begin{figure*}[h!]
-    \includegraphics[width=\textwidth]{{logMFeH}.png}
+    \includegraphics[width=\textwidth]{{logMFeH_noStepsMid-trim}.png}
     \caption{
-        This figure summarises above findings. TODO: write caption for 
-        paper.
+        Mass-weighted metallicity distribution of star particles in the Auriga 
+        simulations. We show the median value of all Auriga haloes for all
+        stars (orange dotted) and globular cluster candidates (i.e. stars with 
+        age $>$~10~Gyr; orange solid). The latter sub set is further split up
+        between stars that formed insitu (red solid), and those that were accreted
+        (blue solid). Shaded regions indicate the $1\sigma$ interval. The MW GCS
+        is shown in purple and that of M31 in pink. We use the same bin sizes
+        for the simulations as for the observations, explicitly plotted for the
+        observed profiles.
         \label{fig:todo6}
@@
 \begin{figure*}[h!]
-    \includegraphics[width=\textwidth]{{logMRgc}.png}
+    \includegraphics[width=\textwidth]{{logMRgc_noStepsMid-trim}.png}
     \caption{
-        This figure summarises above findings. TODO: write caption for 
-        paper.
+        Mass-weighted distribution of galactocentric radii at which star 
+        particles in the Auriga simulations are found.
+        We show the median value of all Auriga haloes for all
+        stars (orange dotted) and globular cluster candidates (i.e. stars with 
+        age $>$~10~Gyr; orange solid). The latter sub set is further split up
+        between stars that formed insitu (red solid), and those that were accreted
+        (blue solid). Shaded regions indicate the $1\sigma$ interval. The MW GCS
+        is shown in purple and that of M31 in pink. We use the same bin sizes
+        for the simulations as for the observations, explicitly plotted for the
+        observed profiles.
         \label{fig:todo6}
@@
         increases in the mass normalization with increasing resolution level.
-        \label{fig:logMFeH_res}
+        \label{fig:logMRgc_res}
     }
@@
 
+\afterpage{%
+\begin{figure*}[h!]
+    \includegraphics[width=\textwidth]
+        {{logMRgcFeH_accreted-insitu}.png}
+    \caption{
+        OMG what a beautiful plot.
+        \label{fig:todo2}
+    }
+\end{figure*}
+\clearpage
+}
+\clearpage
+
 \section{Properties of birth haloes of the accreted population}

### 2019-01-10 AurigaGCS.tex
Generate Mauriga/Mmilkyway in each of the 25 FeHRgc bins

@@
     Timo L. R. Halbesma$^{1}$\thanks{E-mail: Halbesma@MPA-Garching.MPG.DE},
+    Philipp Busch$^{1}$,
     Wilma Trick$^{1}$,
@@
 
-Look into Pandromeda survey? Star counts, very wide angle survey
+\todo[inline]{
+Look into Pandromeda survey. Star counts, very wide angle survey
+}
 
@@
 What age-metallicity distribution is produced by star formation events in the Auriga simulations?
+?
+\begin{figure}
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_iold_mean}.png}
+    \caption{
+        Mass-weighted [Fe/H]-r$_{\text{gc}}$ distribution of all Auriga haloes 
+        (level 3, 4 and 5). Here we consider the old ($>$~10~Gyr) stars in all 
+        simulations and color-code the \textbf{mean value} (of 40 Auriga haloes)
+        \label{fig:Au-RgcFeH}
+    }
+\end{figure}
 
@@
     \caption{
-        OMG what a beautiful plot.
+        OMG what a beautiful plot - now only need 1$\sigma$ interval around both
+        relations, and need to know exactly what model I fit...
         \label{fig:todo2}
@@
 
-\section{Properties of birth haloes of the accreted population}
+\subsection{Properties of birth haloes of the accreted population}
 \label{sec:birth-properties-of-accreted-gc-candidates}

### 2019-02-11 AurigaGCS.tex
Added KS test figures

@@
     Timo L. R. Halbesma$^{1}$\thanks{E-mail: Halbesma@MPA-Garching.MPG.DE},
-    Philipp Busch$^{1}$,
-    Wilma Trick$^{1}$,
     Robert J. J. Grand$^{1}$, 
@@
     R\"{u}diger Pakmor$^{1}$, 
+    Wilma Trick$^{1}$,
+    Philipp Busch$^{1}$,
     Simon D. M. White$^{1}$
@@
 \begin{abstract}
+\todo[inline]{Ask SW whether I should ask Carlos Frenk and Adrian Jenkins for co-authorship}
 We investigate whether the galaxy formation model used for the Auriga simulations 
@@
 at radii and metallicities that are typical for the MW GCS, although we observe
-a varying mass-excess for the different $r_{\text{gal}}$-[Fe/H] bins. This implies
+a varying mass-excess for the different $R_{\text{GC}}$-[Fe/H] bins. This implies
 different values for the combined product of the bound cluster formation efficiency
@@
 
-\citet{2005MNRAS.364..367D}: ``The radial profile of the stellar halo and metal-poor globular
-clusters of the Milky Way suggest that these components formed in rare early peaks above $2.5 \sigma$ at redshift above 10. ''
+\begin{itemize}
+    \item \citet{2005MNRAS.364..367D}: ``The radial profile of the stellar halo
+    and metal-poor globular clusters of the Milky Way suggest that these components 
+    formed in rare early peaks above $2.5 \sigma$ at redshift above 10. ''
 
-\citet{2017MNRAS.465.3622R}: ``GCs among oldest astrophysical objects. GCs form in the early Universe in highest density peaks \citep[e.g.][]{2005MNRAS.364..367D, 2009ApJ...706L.192B}''
+    \item \citet{2017MNRAS.465.3622R}: ``GCs among oldest astrophysical objects.
+    GCs form in the early Universe in highest density peaks
+    \citep[e.g.][]{2005MNRAS.364..367D, 2009ApJ...706L.192B}''
 
+    \item ``Hence, they witness most of the formation and evolution processes
+    of galaxies, and can be used to probe them'' \citep{2006ARA&A..44..193B}
+\end{itemize}
+
+\todo[inline]{Paragraph: scientific context / state of the field: briefly summarise
+    previous work and references work of other groups}
 \begin{itemize}
-    \item ``Hence, they witness most of the formation and evolution processes of galaxies, and can be used to probe them'' \citep{2006ARA&A..44..193B}
+\item Origin of the Milky Way globular clusters \citep{2017MNRAS.465.3622R}
+\item GCs in FIRE \citep{2018MNRAS.474.4232K}
+\item EMOSAICS project \citep{2018MNRAS.475.4309P}
+\item GC-DMhalo connection \citep{2017MNRAS.472.3120B}
+\item Origin of GC bimodality? \citep{2018MNRAS.479..200F}
+\item \textit{GAIA} DR2: GC kinematics \citep{2018A&A...616A..12G}
+\item Dating GC Tidal Disruption \citep{2018ApJ...859L..13B}
+\item GC in N-body simulation \citep{2018ApJ...861...69C}
+\item (Role of GC mass evolution on stream properties \citep{2018MNRAS.474.2479B})
+\item GC formation from dwarfs to giants \citep{2018MNRAS.480.2343C}
+\item (GC contribution to EOR \citep{2018MNRAS.479..332B})
+\item Early Universe supermassive star / GC formation \citep{2018MNRAS.478.2461G}
+\item GC formation in cold filaments \citep{2018ApJ...861..148M}
+\item GC formation in high-redshift dwarf galaxies \citep{2018MNRAS.477..480Z}
+\item GCs in MW outer region \citep{2017arXiv170804542P}
+\item Impact of the Cutoff of the Cluster Initial Mass Function \citep{2018arXiv181001888C}
+\item Metallicity gradients in the globular cluster systems of early-type galaxies: in situ and accreted components \citep{2018MNRAS.479.4760F}
+\item Globular clusters in M31, Local Group, and external galaxies \citep{2016IAUS..317..120L}
+\item Globular Clusters Formed within Dark Halos I: present-day abundance, distribution and kinematics \citep{2019MNRAS.482..219C}
+\item (The mass of the Milky Way from satellite dynamics \citep{2018arXiv180810456C})
+\item Globular cluster formation and evolution in the context of cosmological galaxy assembly: open questions \citep{2018RSPSA.47470616F}
+\item The kinematics of globular clusters systems in the outer halos of the Aquarius simulations \citep{2016A&A...592A..55V}
+\item Star Cluster Formation in Cosmological Simulations \citep{2017ApJ...834...69L, 2018ApJ...861..107L, 2018arXiv181011036L}
+\item (A systematic analysis of star cluster disruption by tidal shocks - I. Controlled N-body simulations and a new theoretical model \citep{2018arXiv181200014W})
+\item Spatial mixing of binary stars in multiple-population globular clusters \citep{2018MNRAS.tmp.3147H}
+\item Star Clusters Across Cosmic Time \citep{2018arXiv181201615K}
+\item Kinematics of Subclusters in Star Cluster Complexes: Imprint of their Parental Molecular Clouds \citep{2018arXiv181201858F}
+\item Investigating the population of Galactic star formation regions and star clusters within a Wide-Fast-Deep Coverage of the Galactic Plane  \citep{2018arXiv181203025P}
+\item Globular cluster number density profiles using \textit{Gaia} DR2 \citep{2019arXiv190108072D}
+% TODO: last checked arXiv Jan 27, 2018
+\end{itemize}
+
+\todo[inline]{Paragraph, narrowing open questions in GC research down to formation,
+    possibly ``Bimodality suggests two formation mechanisms''. In-situ 
+    formation vs. accretion in hierarchical build-up of galaxies naturally produces 
+    two populations of globular cluster.}
+\begin{itemize}
     \item ``colour bimodality, blue and red clusters \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L, 2006ApJ...639...95P}
     \item ``blue metal-poor (with distribution peaking at [Fe/H] $\approx -1.5$ for the Milky Way), no sign of rotation as a population (..) more metal-rich (peak at [Fe/H] $\approx -0.5$ in the Milky  Way) more spatially concentrated and rotating with the galaxy.'' \citep{1996AJ....112.1487H}
-\end{itemize}
-
-\todo[inline]{Paragraph: ``Bimodality suggests two formation mechanisms''. In-situ vs. Accreted}
-\begin{itemize}
     \item ``Blue clusters from in early Universe in galaxies that merge later. In (wet) merger process starbursts generate red population \cite{1992ApJ...384...50A, 1987nngp.proc...18S}''
@@
 
-Dark Matter - GC connection
-
-\todo[inline]{Paragraph: scientific motivation}
+\todo[inline]{Paragraph: narrow the scientific motivation down to the scope of 
+    this particular work}
 \begin{itemize}
@@
 This is important because theoretical paradigms for globular cluster formation in the literature know two distinct classes of GCs that are separated by their exact formation sites: an in-situ versus an accreted population.
-Cosmological zoom simulations are uniquely allow for an investigation into globular cluster formation with particular focus on the in-situ and accreted populations.
+Cosmological zoom simulations uniquely allow for an investigation into globular cluster formation with particular focus on the in-situ and accreted populations.
 \end{itemize}
 
-\todo[inline]{Paragraph: previous work / work of other groups}
-This goes before the GC formation mechanism paragraph.
-\begin{itemize}
-\item Origin of the Milky Way globular clusters \citep{2017MNRAS.465.3622R}
-\item GCs in FIRE \citep{2018MNRAS.474.4232K}
-\item EMOSAICS project \citep{2018MNRAS.475.4309P}
-\item Origin of GC bimodality? \citep{2018MNRAS.479..200F}
-\item \textit{GAIA} DR2: GC kinematics \citep{2018A&A...616A..12G}, Dating GC Tidal Disruption \citep{2018ApJ...859L..13B}
-\item GC in N-body simulation \citep{2018ApJ...861...69C}
-\item Tangentially related? role of GC mass evolution on stream properties \citep{2018MNRAS.474.2479B}
-\item GC formation from dwarfs to giants \citep{2018MNRAS.480.2343C}
-\item GC contribution to EOR \citep{2018MNRAS.479..332B}
-\item Early Universe supermassive star / GC formation \citep{2018MNRAS.478.2461G}
-\item GC formation in cold filaments \citep{2018ApJ...861..148M}
-\item GC formation in high-redshift dwarf galaxies \citep{2018MNRAS.477..480Z}
-\item GCs in MW outer region \citep{2017arXiv170804542P}
-\item Impact of the Cutoff of the Cluster Initial Mass Function \citep{2018arXiv181001888C}
-\item Metallicity gradients in the globular cluster systems of early-type galaxies: in situ and accreted components \citep{2018MNRAS.479.4760F}
-\item Globular clusters in M31, Local Group, and external galaxies \citep{2016IAUS..317..120L}
-\item Globular Clusters Formed within Dark Halos I: present-day abundance, distribution and kinematics \citep{2019MNRAS.482..219C}
-\item The mass of the Milky Way from satellite dynamics \citep{2018arXiv180810456C}
-\item Globular cluster formation and evolution in the context of cosmological galaxy assembly: open questions \citep{2018RSPSA.47470616F}
-\item The kinematics of globular clusters systems in the outer halos of the Aquarius simulations \citep{2016A&A...592A..55V}
-\item Star Cluster Formation in Cosmological Simulations \citep{2017ApJ...834...69L, 2018ApJ...861..107L, 2018arXiv181011036L}
-\item A systematic analysis of star cluster disruption by tidal shocks -- I. Controlled N-body simulations and a new theoretical model \citep{2018arXiv181200014W}
-\item Spatial mixing of binary stars in multiple-population globular clusters \citep{2018MNRAS.tmp.3147H}
-\item Star Clusters Across Cosmic Time \citep{2018arXiv181201615K}
-\item Kinematics of Subclusters in Star Cluster Complexes: Imprint of their Parental Molecular Clouds \citep{2018arXiv181201858F}
-\item Investigating the population of Galactic star formation regions and star clusters within a Wide-Fast-Deep Coverage of the Galactic Plane  \citep{2018arXiv181203025P}
-% TODO: last checked arXiv Dec 15, 2018
-\end{itemize}
-
-\todo[inline]{Paper outline}
+\todo[inline]{Paragraph: Paper outline}
 We summarise the relevant characteristics of the Auriga simulations in 
@@
 \todo[inline]{
-``The diversity in morphological properties of these simulated galaxies reflects
+TODO: paraphrase ``The diversity in morphological properties of these simulated galaxies reflects
 the stochasticity inherent to the process of galaxy formation and evolution 
@@
 
-\subsection{Definition of stellar halo}
-\todo[inline]{Possibly also relevant here. See \citet{2018arXiv180407798M}.}
+\todo[inline]{Paragraph about Auriga's stellar haloes.
+``The Auriga Stellar Haloes: Connecting stellar population properties with
+accretion and merging history'' \citet{2018arXiv180407798M}
+}
 
-\subsection{Definition of accreted and in-situ component}
-\todo[inline]{Possibly also relevant here. See \citet{2018arXiv180407798M}.}
+% \subsection{Definition of stellar halo}
+% \todo[inline]{Possibly also relevant here. See \citet{2018arXiv180407798M}.}
+% 
+% 
+% \subsection{Definition of accreted and in-situ component}
+% \todo[inline]{Possibly also relevant here. See \citet{2018arXiv180407798M}.}
 
@@
 simulations to the globular cluster systems of the spiral galaxies in the 
-Local Group (i.e. the Milky Way and Andromeda galaxy or M31). Here we summarise 
+Local Group (i.e. the Milky Way and Andromeda galaxy, M31). Here we summarise 
 the relevant data available in the literature.
@@
 \citet[][2010 edition; hereafter H96]{1996AJ....112.1487H} provides a fairly
-up-to-date, comprehensive catalogue of the Milky Way globular cluster system and
-contains properties of 157 globular clusters. The catalogue is believed to be 
-roughly 90\% complete. The relevant data fields that we use from H96 are the 
-metallicity [Fe/H], galactocentric radius $r_{\text{gal}}$, and absolute magnitude 
-in the V-band $M_V$. 
-\todo[inline]{
-We use the latter to calculate a mass-estimate by assuming
-$M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$ 
-(the mean for MW clusters McLaughlin \& van der Marel 2005). 
-}
+up-to-date catalogue of the Milky Way globular cluster system containing the
+properties of 157 globular clusters. An additional 59 GCs have since been 
+discovered, 2 of which by \citet{2018ApJ...863L..38R}. The authors also provide 
+a comprehensive list of references to other discovery papers, and they predict 
+that the Milky Way GCS contains an additional 30 undiscovered GCs that are 
+obscured by the Galactic disk. Recently, \citet{2019arXiv190108574C} announced
+the discovery of three new GCs, totalling to the MW GCS to 218. This would make
+the Harris catalogue roughly 65\% complete. However, we do not use the properties 
+of the more recently discovered GCs in our analysis.
 
-In Fig.~\ref{fig:MW-RgcFeH} we show a two-dimensional mass-weighted distribution,
-splitting the data up in bins of both radius and metallicity. Later on we 
-investigate whether the star formation model implemented for the Auriga simulations 
-can produce a sufficient total mass in globular cluster candidates at the right
-values of radius, metallicity, and radius-metals, see Sec.~\ref{sec:RgcFeH}
+The relevant data fields that we use from H96 are the metallicity [Fe/H],
+galactocentric radius $R_{\text{GC}}$, and absolute magnitude in the V-band 
+$M_V$. We use the latter to calculate mass-estimates by assuming $M_{V,\odot}=4.83$
+and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$, the mean for MW clusters
+\citep{2005ApJS..161..304M}.
+
+\todo[inline]{Parse McLaughlin \& van der Marel data and calculate the mean $M/L_V$
+\url{http://vizier.cfa.harvard.edu/viz-bin/VizieR-3?-source=J/ApJS/161/304/clusters}}
+
+In Fig.~\ref{fig:MW-FeHRgc} we show the two-dimensional mass-weighted 
+metallicity-radial distribution of the MW GCS. In Sec.~\ref{sec:FeHRgc} 
+we investigate whether the star formation model implemented in the Auriga 
+simulations can produce sufficient total mass in GC candidates in the same bins.
 
@@
         151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
-        is 98.19 \% of the total MW GCS mass.
-        \label{fig:MW-RgcFeH}
+        is 98.19 \% of the total MW GCS mass in the Harris catalog.
+        \label{fig:MW-FeHRgc}
     }
@@
 [Fe/H] measurements and age-estimates for 55 globular clusters in the Milky Way.
-The mean value of the age-estimates in this data set is $11.9 \pm 0.1$ Gyr and the
-dispersion is 0.9 Gyr. Furthermore, only one of the 55 GC age-estimates is
-below 10 Gyr.
+The mean value of the age-estimates in this data set is $11.9 \pm 0.1$~Gyr and 
+the dispersion is 0.9~Gyr. Furthermore, only one of the 55 GC age-estimates is
+below 10~Gyr. Therefore we define GC candidates in the Auriga simulations as
+all star particles older than 10~Gyr in Sec.~\ref{sec:results}.
 
@@
 \citet[][, hereafter C11]{2011AJ....141...61C} studied globular clusters in the
-Andromeda galaxy. The relevant fields in this data set are the age, metallicities,
-and absolute visual magnitude.
+Andromeda (M31) galaxy. The relevant fields in this data set are the age, 
+metallicities, and absolute visual magnitude.
 \todo[inline]{
-`For M31 GC masses we combine the catalogues of Caldwell et al. (2011, using the 
+TODO: paraphrase ``For M31 GC masses we combine the catalogues of Caldwell et al. (2011, using the 
 given masses) and Huxor et al. (2014, again assuming $M/L_V = 1.7$~M/L$_{\odot}$, 
-e.g. Strader, Caldwell \& Seth 2011).'
+e.g. Strader, Caldwell \& Seth 2011).''
 }
@@
 dispersion of 2.3~Gyr. Furthermore, 27 GCs have age-estimates below 10~Gyr, and
-the minimum age is 4.8~Gyr. Perhaps an age cut of 6~Gyr would would be more 
+the minimum age is 4.8~Gyr.
+
+TODO: (in discussion) Perhaps an age cut of 6~Gyr would would be more 
 appropriate for M31, see Fig.~\ref{fig:MW-M31-age}.
@@
 \todo[inline]{
-Furthermore, we supplement observational data of globular clusters in M31 with 
-\citet{2014MNRAS.442.2165H, 2014MNRAS.442.2929V}
+TODO: paraphrase ``Furthermore, we supplement observational data of globular
+clusters in M31 with \citet{2014MNRAS.442.2165H, 2014MNRAS.442.2929V}'', and
+parse these data sets.
 }
+
+This text sits here just for debug purposes, just for now. We calculate the 
+projected and `inferred' galactocentric radius from the observed coordinates.
+\begin{align}
+    \cos \theta & = \sin \delta_1 \sin \delta_2 +
+        \cos \delta_1 \cos \delta_2 \cos \left( \alpha_1 - \alpha_2 \right),
+\end{align}
+where $(\alpha_1, \delta_1)$ are the right ascension and declination (in degrees,
+converted to radians) of the centroid of M31 and $(\alpha_2, \delta_2)$ are the
+observed coordinates of the globular cluster. The angle on the sky is converted
+to a physical distance in kpc using the small angle approximation, i.e. 
+$r_{\text{projected}} = \theta \cdot D_{\text{M31}}$. We adopt the values 
+$(\alpha_1, \delta_1) = (0^{\text{h}}42^{\text{m}}44.3^{\text{s}}, 
++41^{\circ}16'9")$ (TODO: reference), and  $D_{\text{M31}} = 778$~kpc 
+(TODO: reference).
+
+% TODO: Deprojection, assuming all GCs lie in the plane of the sky, inclination 
+% $12.5^{\circ}$
 
@@
 \label{sec:results}
-We investigate globular cluster candidates in the Auriga simulations using an age
-cut to select of stars that formed at a lookback time greater than $10$~Gyr. We 
-chose this particular value because the mean age-estimate of the $55$ in V13 is
-$11.9\pm0.1$~Gyr with a dispersion of $0.8$~Gyr, and only one observed globular 
-cluster falls below this selection criterion.
+Through out the analysis we use six sub sets of star particles: \emph{all stars}, 
+and \emph{old stars} (age $>10$~Gyr, GC candidates hereafter). Both sub sets are
+further split up in (old) star particles that have formed \emph{in-situ} 
+(bound to the most-massive halo/subhalo in the first snapshot that the star 
+particle was recorded), and (old) \emph{accreted} star particles (i.e. those that 
+have formed ex-situ and are bound to the most-massive halo/subhalo at $z=0$). 
+We use an age threshold of 10~Gyr for GC candidates because the mean 
+age-estimate of the $55$ MW GCs in V13 is $11.9\pm0.1$~Gyr with a dispersion of 
+$0.8$~Gyr, and only one observed GC lies outside this range.
 
 In Sec.~\ref{sec:metallicity} we investigate the metallicity distribution of the
-GC candidates, in Sec.~\ref{sec:spatial} we show the distribution of galactocentric
+GC candidates, in Sec.~\ref{sec:radial} we show the distribution of galactocentric
 radii of the globular cluster candidates within the Auriga simulations, and we 
-combine both in Sec.~\ref{sec:RgcFeH}. We continue our analysis with a deeper 
-analysis of the properties of the proto-galaxies at times of birth of the accreted 
-globular cluster population in Sec.~\ref{sec:birth-properties-of-accreted-gc-candidates}
+combine both in Sec.~\ref{sec:FeHRgc}. We continue our analysis with an investigation
+of the properties of the proto-galaxies at times of birth of the accreted globular 
+cluster population in Sec.~\ref{sec:birth-properties-of-accreted-gc-candidates}
 
@@
 \label{sec:metallicity}
-\todo[inline]{
-Can the Auriga simulations produce star particles of $>10$~Gyr (GC candidates) 
-with a metallicity distribution that is consistent with the MW GCS?
-}
-
-In Fig.~\ref{fig:FeH} we show a mass-weighted metallicity distribution of star 
-particles in the Auriga simulations. We show the median value of all Auriga 
-haloes for all stars (orange dotted lines) and globular cluster candidates 
-orange solid). The latter sub set is further split up between stars that formed 
-in-situ (red solid), and those that were accreted (blue solid). The shaded regions 
-indicate the $1\sigma$ interval. The MW GCS is shown in purple and that of M31 
-in pink. We use the same bin sizes for the simulations as for the observations, 
-explicitly plotted for the observed profiles.
+We investigate whether the star formation model implemented in the Auriga 
+simulations is capable of producing sufficient mass in old star particles in 
+each metallicity bin in comparison to the Milky Way and Andromeda globular 
+cluster systems. In Fig.~\ref{fig:FeH} we show a mass-weighted metallicity 
+distribution where the lines show the median value of all thirty Auriga level 4 
+haloes for \emph{all stars} (orange dotted), \emph{old stars / GC candidates} 
+(orange solid), \emph{old in-situ} stars (blue solid), and \emph{old accreted} stars
+(red solid). The shaded regions indicate the $1\sigma$ interval around the median 
+(i.e. the scatter between runs with different initial conditions and merger
+histories). The MW (M31) GCS is shown in purple (magenta). We use the 
+same bin sizes for the simulations as for the observations, explicitly shown for
+the observed profiles.
 
 \begin{figure}
-    \includegraphics[width=\columnwidth]{{logMFeH_noStepsMid-trim}.png}
+    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
     \caption{
@@
         age $>$~10~Gyr; orange solid). The latter sub set is further split up
-        between stars that formed in-situ (red solid), and those that were accreted
-        (blue solid). Shaded regions indicate the $1\sigma$ interval. The MW GCS
-        is shown in purple and that of M31 in pink. We use the same bin sizes
-        for the simulations as for the observations, explicitly plotted for the
-        observed profiles.
+        between stars that formed in-situ (blue solid), and those that were accreted
+        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
+        GCS is shown in purple (magenta). The middle (bottom) panel shows the
+        ratio of the simulated mass to the mass in the MW (M31) GCS.
         \label{fig:FeH}
@@
 
-We find that the metallicity range $-3 <$ [Fe/H] $< -1$ is only populated by 
-star particles older than ten Gyr, while [Fe/H] $> -1$ is dominated by star 
-particles younger than 10~Gyr (with a difference of two orders of magnitude). 
-Furthermore, the old accreted star particles contribute most significantly to 
-the range $-3 <$ [Fe/H] $< -1$, and the contribution of the old in-situ star
-particles at these metallicities declines steeper with declining metallicity 
-than the old accreted population. The old in-situ population provides the 
-dominant contribution of the old population for [Fe/H] $> -1$.
+The peak of the distribution shifts down from [Fe/H] $\thicksim 0.0$ to 
+$\thicksim -0.6$ for the \emph{old stars} compared to \emph{all stars} while the 
+mass at the peak lowers by roughly one dex. Moreover, we find that the 
+metallicity range $-3 <$ [Fe/H] $< -1$ is only populated by the GC candidates, 
+while [Fe/H] $> -1$ is dominated by star particles younger than 10~Gyr.
+Furthermore, the \emph{old accreted} sub set contributes most significantly to 
+the range $-3 <$ [Fe/H] $< -1$, and the contribution of the \emph{old in-situ}
+stars at these metallicities declines steeper with declining metallicity 
+than the \emph{old accreted} population. We note that the scatter between different
+Auriga haloes is much smaller than the difference between the MW and M31 GCSs.
+We conclude that old star particles in the Auriga simulation suite as a whole 
+cannot be consistent with both the Milky Way and the Andromeda globular cluster
+system.
 
-We notice a scatter\footnote{Here scatter means the width of the 1$\sigma$ interval.
-The difference between the minimum and maximum values is $0.9$~dex.} in mass 
-normalization of $0.3$ dex between the different Auriga galaxies. We investigate 
-whether there is a correlation between the total stellar mass in (old) star particles
-and the virial mass\footnote{The virial mass is defined as the mass contained inside the
-radius $r_{200,c}$ at which the average (spherical) mass density equals two hundred 
-times the critical density of the Universe} $M_{200,c}$ of the host halo.
-We fit $a \cdot \left(\text{M}_{200,c}[1\text{e}10 \text{M\Sun}] - 140\right) + b$
-to log$_{10}\left(\Sigma_{i} m_i(\text{\scriptsize [Fe/H] = -3})\right)$.
-% \limits_{i, \text{if age(i) $>$ 10~Gyr}}
-Our fit thus provides the slope $a$ and normalization of (old) stellar mass $b$
-at [Fe/H]=-3 for $M_{200,c}$ at 140e10~M\Sun. We find $a = 0.00388$, $b = 6.597$
-and conclude that there is a small positive correlation of mass in (old) star 
-particles with the virial mass of the host halo.
+The middle (bottom) panel shows the ratio of the simulated mass to the mass in
+the MW (M31) GCS. We observe an increasing trend with increasing metallicity 
+for the Milky Way over the entire range of the data, while the M31 GCS shows
+this increase only in the range [Fe/H]$>$-0.5 (although not for the \emph{old
+accreted} component.
 
-\begin{figure}
-\includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_normalization_fit3}.png}
-    \caption{
-        Plot of log$_{10}$(mass normalization) [i.e. $b$ obtained above] against 
-        the virial mass M$_{200,c}$ of the Auriga haloes. We fit a linear relation 
-        to see whether there is a correlation, and find $a = 0.00388$, $b = 6.597$. 
-        % Colours indicate resolution: L3 green, L4 orange, and L5 blue.
-        The red dotted line shows the `central' value of M$_{200,c}$, the yellow 
-        region shows the 1$\sigma$ interval around the best-fit relation, and the
-        blue dashed lines shows the intrinsic scatter. The error bars show 1\% 
-        of the obtained values.
-        \label{fig:Mnorm-fit}
-    }
-\end{figure}
+Furthermore we test the null hypothesis that the metallicity distribution of the
+MW (M31) GCS and the \emph{old}, \emph{old insitu}, and \emph{old accreted} star 
+particles in the Auriga simulations are drawn from the same underlying 
+distribution. We calculate the two-sample Kolmogorov-Smirnov test statistic for
+all thirty Auriga level 4 haloes and reject the null hypothesis for every halo, 
+for every sub set of star particles at least at the 99.99\% confidence level.
+In addition, the null hypothesis that the metallicity distributions of the MW 
+and M31 GCS are drawn from the same distribution is rejected at the 99.99997\%
+confidence level.
 
-Furthermore we compare the simulated metallicity distribution to observations
-of the Milky Way and M31.
-\todo[inline]{
-    yes/no bimodal
+% We notice a scatter\footnote{Here scatter means the width of the 1$\sigma$ interval.
+% The difference between the minimum and maximum values is $0.9$~dex.} in mass 
+% normalization of $0.3$ dex between the different Auriga galaxies. We investigate 
+% whether there is a correlation between the total stellar mass in (old) star particles
+% and the virial mass\footnote{The virial mass is defined as the mass contained 
+% inside the radius $r_{200,c}$ at which the average (spherical) mass density 
+% equals two hundred times the critical density of the Universe} $M_{200,c}$ of
+% the host halo. We fit $a \cdot \left(\text{M}_{200,c}[1\text{e}10 \text{M\Sun}]
+% - 140\right) + b$ to log$_{10}\left(\Sigma_{i} m_i(\text{\scriptsize [Fe/H] = 
+% -3})\right)$. % \limits_{i, \text{if age(i) $>$ 10~Gyr}}
+% Our fit thus provides the slope $a$ and normalization of (old) stellar mass $b$
+% at [Fe/H]=-3 for $M_{200,c}$ at 140e10~M\Sun. We find $a = 0.00388$, $b = 6.597$
+% and conclude that there is a small positive correlation of mass in (old) star 
+% particles with the virial mass of the host halo.
+% 
+% \begin{figure}
+% \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_normalization_fit3}.png}
+%     \caption{
+%         Plot of log$_{10}$(mass normalization) [i.e. $b$ obtained above] against 
+%         the virial mass M$_{200,c}$ of the Auriga haloes. We fit a linear relation 
+%         to see whether there is a correlation, and find $a = 0.00388$, $b = 6.597$. 
+%         % Colours indicate resolution: L3 green, L4 orange, and L5 blue.
+%         The red dotted line shows the `central' value of M$_{200,c}$, the yellow 
+%         region shows the 1$\sigma$ interval around the best-fit relation, and the
+%         blue dashed lines shows the intrinsic scatter. The error bars show 1\% 
+%         of the obtained values.
+%         \label{fig:Mnorm-fit}
+%     }
+% \end{figure}
 
-    M31 slope between -3 and -1 consistent with old insitu?
-
-    MW above 0 no more GCs, but Auriga well populated (mostly insitu, but
-    also too many accreted.
-
-    should also comment on all vs old (Auriga simulation) btw
-
-}
-
-bla. Conclusion: too many metal-rich star particles.
-
-\subsection{Spatial distribution}
-\label{sec:spatial}
+\subsection{Radial distribution}
+\label{sec:radial}
 Is the spatial distribution of the GC candidates in the Auriga simulations consistent with the MW GCS?
@@
 \begin{figure}
-    \includegraphics[width=\columnwidth]{{logMRgc_noStepsMid-trim}.png}
+    \includegraphics[width=\columnwidth]{{logMR2dgc_withRatios-trim}.png}
     \caption{
-        Mass-weighted distribution of galactocentric radii at which star 
-        particles in the Auriga simulations are found.
+        Mass-weighted distribution of (two-dimensional) galactocentric radii at 
+        which star particles in the Auriga simulations are found. For Andromeda 
+        we show the projected galactocentric radius, assuming its center is located
+        at $(0^{\text{h}}42^{\text{m}}44.3^{\text{s}}, +41^{\circ}16'9")$ at a 
+        distance of 778 kpc.
         \label{fig:Rgc}
@@
 
-\subsection{Radius-metallicity distribution}
-\label{sec:RgcFeH}
+\subsection{Metallicity-radial distribution}
+\label{sec:FeHRgc}
 What age-metallicity distribution is produced by star formation events in the Auriga simulations?
@@
     \caption{
-        Mass-weighted [Fe/H]-r$_{\text{gc}}$ distribution of all Auriga haloes 
+        Mass-weighted [Fe/H]-R$_{\text{GC}}$ distribution of all Auriga haloes 
         (level 3, 4 and 5). Here we consider the old ($>$~10~Gyr) stars in all 
         simulations and color-code the \textbf{mean value} (of 40 Auriga haloes)
-        \label{fig:Au-RgcFeH}
+        \label{fig:Au-FeHRgc}
     }
@@
 \begin{figure}
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_iold_36bins_mean-trim}.png}
+    \caption{
+        Ratio
+        \label{fig:Au-FeHRgc-ratio}
+    }
+\end{figure}
+
+\subsection{Metallicity-radial distribution: higher resolution}
+\todo[inline]{Do we even want this?}
+\label{sec:FeHRgc-morebins}
+\begin{figure}
     \includegraphics[width=\columnwidth]
@@
     \caption{
-        OMG what a beautiful plot - now only need 1$\sigma$ interval around both
-        relations, and need to know exactly what model I fit...
+        TODO: add 1$\sigma$ interval around both relations, and flip x and y.
         \label{fig:todo2}
@@
 
+\subsection{From star particles to globular clusters}
+\label{sec:star-to-gc}
+Star particles are not globular clusters. Many stars do form in clusters, but
+not all clusters end up gravitationally bound. Star particles in the
+Auriga simulations represent single-age stellar populations that have formed
+at the same location within the galaxy. Therefore one could assume a model
+for the star cluster formation efficiency $\Gamma$, which could be used to 
+`convert' star particles to bound star clusters e.g. Kruijssen (2012). This 
+model relies on the local birth properties of the star particles. However, 
+in our analysis we can retrieve the properties of the star particle in the 
+first snapshot it was recorded, but not the gas properties at times of birth.
+Therefore we are unable to model the formation of star clusters in more detail.
+
+Furthermore, we compare star particles to present-day globular clusters, thereby
+ignoring the effects of (dynamical) disruption of globular clusters over nearly
+a Hubble time. As shown by Pfeffer et al. (2018), a detailed model of the tidal
+history of star clusters requires a temporal resolution of order mega year. For
+the Auriga level 4 simulations we have 128 snapshots for the age of the Universe,
+thus, a far too coarse temporal resolution for meaningful calculations.
+
+Therefore we investigate the over-production of simulated mass in the metallicity
+and radial bins and use the term `efficiency' to refer to the combined product
+of bound cluster formation and globular cluster disruption. In Fig.~\ref{fig:todo} 
+we show the efficiencies that we find when we compare the simulations to the 
+globular cluster systems of the Milky Way as well as that of Andromeda (M31).
+
 \subsection{Properties of birth haloes of the accreted population}
 \label{sec:birth-properties-of-accreted-gc-candidates}
+
+Auriga galaxy /w 5 Myr snapshots.
 
@@
 What age-metallicity distribution is produced by star formation events in the Auriga simulations?
-
-\subsection{Mass budget} 
-\label{sec:mass}
-Does the star formation model implemented in the Auriga simulations produce sufficient mass in star particles with properties that are consistent with the MW GCS?
-
-What efficiencies could we afford if we would take into account the combined mass loss effect of converting from star particles to bound star clusters and globular cluster disruption?
-
-How does the total stellar mass in $r_\textbf{gal}$-[Fe/H] bins compare to the MW GCS?
 
@@
 Can we distinguish between particles that have formed in-situ and those that have been accreted?
-Can we identify specific features in the age-metallicity plane, or in the $r_\textbf{gal}$-[Fe/H] plane, that result from one of both populations?
+Can we identify specific features in the age-metallicity plane, or in the $R_\textbf{GC}$-[Fe/H] plane, that result from one of both populations?
 How does this connect to proposed mechanisms for globular cluster formation in the literature?
@@
 field as well as globular clusters. We compare the total mass in the simulations in 
-metallicity ([Fe/H]), galactocentric radius $r_{\text{gc}}$, and [Fe/H]-$r_{\text{gal}}$ 
+metallicity ([Fe/H]), galactocentric radius $R_{\text{GC}}$, and [Fe/H]-$R_{\text{GC}}$ 
 bins to the total mass in the MW GCS (using the H96 data set). The mass excess in the

### 2019-02-13 AurigaGCS.tex
Updates at ZoltaN

@@
 \item Globular cluster number density profiles using \textit{Gaia} DR2 \citep{2019arXiv190108072D}
-% TODO: last checked arXiv Jan 27, 2018
+\item Clustering Clusters: unsupervised learning on GC observations (of log $M$,
+    log \sigma_0, log $R_e$ , [Fe/H], log $|Z|$) to determine number of groups
+    $k=2$ (disk/halo) or $k=3$ (disk/inner-halo/outer-halo): the optimal number
+    of groups given the data is $k=3$. \citep{2019arXiv190105354P}.
+\item There is a well-known hypothesis that Open Stars Clusters (OSCs) could form as a result
+    of GCs crossing the disk. New kinematical data does not support
+    this claim for two particular OSC-GC pairs, and does seem consistent
+    with this scenario for six OSC-GC pairs \citep{2019arXiv190106481B}. (Note
+    that GC crossing the disk could also trigger formation of multiple OSCs!)
+% TODO: last checked arXiv Feb 13, 2019
 \end{itemize}
@@
 the minimum age is 4.8~Gyr.
-
-TODO: (in discussion) Perhaps an age cut of 6~Gyr would would be more 
-appropriate for M31, see Fig.~\ref{fig:MW-M31-age}.
 

### 2019-03-02 AurigaGCS.tex
Commented on MW and M31 GCS observations

@@
 \item Clustering Clusters: unsupervised learning on GC observations (of log $M$,
-    log \sigma_0, log $R_e$ , [Fe/H], log $|Z|$) to determine number of groups
+    log $\sigma_0$, log $R_e$ , [Fe/H], log $|Z|$) to determine number of groups
     $k=2$ (disk/halo) or $k=3$ (disk/inner-halo/outer-halo): the optimal number
@@
     that GC crossing the disk could also trigger formation of multiple OSCs!)
-% TODO: last checked arXiv Feb 13, 2019
+\item DM halo mass can be inferred from number of globular cluster in galaxy 
+    \citep{2019arXiv190100900B}
+\item GCs in M31 outer halo \citep{2019arXiv190111229W}
+% TODO: last checked arXiv Mar 2, 2019
 \end{itemize}
@@
 We use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, a 
-suite of high-resolution cosmological zoom simulations ran with a galaxy
-formation model that produces realistic Milky Way-like galaxies at redshift
-$z=0$. The simulations are performed with the state-of-the art code \textsc{arepo}
-\citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} that solves the 
-magnetohydrodynamical equations on a moving mesh.
+suite of high-resolution cosmological zoom simulations of Milky Way-mass 
+selected initial conditions. The simulations are performed with the 
+state-of-the art code \textsc{arepo} \citep{2010MNRAS.401..791S,
+2016MNRAS.455.1134P}, that solves the magnetohydrodynamical equations on a 
+moving mesh, and an elaborate galaxy formation model that produces realistic 
+spiral galaxies at redshift $z=0$.
 
@@
 
-The sub-grid includes primordial and metal-line cooling with self-shielding corrections.
-Reionization is completed at redshift six by a time-varying spatially uniform UV 
-background \citep{2009ApJ...703.1416F, 2013MNRAS.436.3031V}
+The sub-grid includes primordial and metal-line cooling with self-shielding 
+corrections. Reionization is completed at redshift six by a time-varying 
+spatially uniform UV background \citep{2009ApJ...703.1416F, 2013MNRAS.436.3031V}
 The interstellar medium is described by an equation of state for a two-phase medium
@@
 \todo[inline]{
-TODO: paraphrase ``The diversity in morphological properties of these simulated galaxies reflects
-the stochasticity inherent to the process of galaxy formation and evolution 
+TODO: paraphrase ``The diversity in morphological properties of these simulated 
+galaxies reflects the stochasticity inherent to the process of galaxy formation 
+and evolution 
 \citep[e.g.][]{2005ApJ...635..931B, 2010MNRAS.406..744C, 2010ApJ...708.1398T}.''
@@
 
-% \subsection{Definition of stellar halo}
-% \todo[inline]{Possibly also relevant here. See \citet{2018arXiv180407798M}.}
-% 
-% 
-% \subsection{Definition of accreted and in-situ component}
-% \todo[inline]{Possibly also relevant here. See \citet{2018arXiv180407798M}.}
-
 \section{Relevant observational data}
 \label{sec:observations}
-The galaxy formation model implemented for the Auriga simulations produces
-realistic spiral galaxies at redshift zero. Therefore we aim to compare the
-simulations to the globular cluster systems of the spiral galaxies in the 
-Local Group (i.e. the Milky Way and Andromeda galaxy, M31). Here we summarise 
-the relevant data available in the literature.
+We summarise relevant observations of the globular cluster system of the Milky 
+Way in Sec.~\ref{sec:milkyway}, and of Andromeda (M31) in Sec.~\ref{sec:andromeda}.
+In the remainder of the paper we compare observed (integrated) globular cluster
+properties to the Auriga simulations.
 
-\subsection{Milky Way: Harris catalogue}
-\label{sec:harris}
-\citet[][2010 edition; hereafter H96]{1996AJ....112.1487H} provides a fairly
-up-to-date catalogue of the Milky Way globular cluster system containing the
-properties of 157 globular clusters. An additional 59 GCs have since been 
-discovered, 2 of which by \citet{2018ApJ...863L..38R}. The authors also provide 
-a comprehensive list of references to other discovery papers, and they predict 
-that the Milky Way GCS contains an additional 30 undiscovered GCs that are 
-obscured by the Galactic disk. Recently, \citet{2019arXiv190108574C} announced
-the discovery of three new GCs, totalling to the MW GCS to 218. This would make
-the Harris catalogue roughly 65\% complete. However, we do not use the properties 
-of the more recently discovered GCs in our analysis.
+\subsection{Milky Way}
+\label{sec:milkyway}
+\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
+catalogue of the Milky Way globular cluster system that contains properties of 
+157 GCs. The authors initially estimated the size of the MW GCS to be 180~$\pm$~10,
+thus, their catalogue to be $\sim$85\% complete. However, an additional 59 GCs 
+have since been discovered by various authors. The total confirmed number of GCs 
+in the MW adds up to 216 with new estimates now anticipating an additional thirty 
+GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
 
-The relevant data fields that we use from H96 are the metallicity [Fe/H],
-galactocentric radius $R_{\text{GC}}$, and absolute magnitude in the V-band 
-$M_V$. We use the latter to calculate mass-estimates by assuming $M_{V,\odot}=4.83$
-and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$, the mean for MW clusters
-\citep{2005ApJS..161..304M}.
+\citet{2019AJ....157...12B} communicate the latest efforts to aggregate all
+available data, presented in their CatClu catalog. Amongst 10978 star clusters 
+and alike objects in the Milky Way, the catalog contains 200 GCs and 94 GC 
+candidates. Unfortunately a machine readable version of the catalog is unavailable
+at this point in time. Therefore we utilise the H96e10 dataset nonetheless, but
+we caution that the Harris catalogue is now believed to be (only) 53-72\% complete.
 
-\todo[inline]{Parse McLaughlin \& van der Marel data and calculate the mean $M/L_V$
-\url{http://vizier.cfa.harvard.edu/viz-bin/VizieR-3?-source=J/ApJS/161/304/clusters}}
+The relevant data fields that we use from H96e10 are the metallicity [Fe/H], the
+Galactic distance components $X$, $Y$, and $Z$ (in kpc)\footnote{In a Sun-centered 
+coordinate system where $X$ points toward Galactic center, $Y$ in direction of 
+Galactic rotation, and $Z$ toward the North Galactic Pole. We calculate the 
+galactocentric radius $R_{\text{GC}}=\sqrt{(X-R_\odot)^2 + Y^2 + Z^2}$, 
+assuming $R_\odot=8$~kpc.}, and absolute 
+magnitude in the V-band $M_V$. We use the latter to calculate mass-estimates by 
+assuming $M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$, 
+the mean for MW clusters \citep{2005ApJS..161..304M}.
 
+\subsubsection*{Age estimates}
+We supplement H96e10 with age-estimates from isochrone fits to stars
+near the main-sequence turnoff in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.
+The mean value of the age-estimates in this data set is $11.9 \pm 0.1$~Gyr and 
+the dispersion is 0.9~Gyr. Furthermore, only one of the 55 GC age-estimates is
+below 10~Gyr.
+
+\subsubsection*{Distribution of mass in metallicity-radial bins}
 In Fig.~\ref{fig:MW-FeHRgc} we show the two-dimensional mass-weighted 
@@
 
-\subsection{Milky Way: VandenBerg catalogue}
-\label{sec:vandenberg}
-\citet[][hereafter V13]{2013ApJ...775..134V} used photometric data to obtain 
-[Fe/H] measurements and age-estimates for 55 globular clusters in the Milky Way.
-The mean value of the age-estimates in this data set is $11.9 \pm 0.1$~Gyr and 
-the dispersion is 0.9~Gyr. Furthermore, only one of the 55 GC age-estimates is
-below 10~Gyr. Therefore we define GC candidates in the Auriga simulations as
-all star particles older than 10~Gyr in Sec.~\ref{sec:results}.
+\subsection{Andromeda}
+\label{sec:andromeda}
+The revised bologna catalogue \citep[][and references therein]{2004A&A...416..917G} 
+is the result compiling integrated properties of M31's GCS,
 
-\todo[inline]{
-How is this particular sample selected? What biases does this introduce?
-Is this sample drawn from the same underlying distribution as the Harris sample 
-(plot distributions of FeH, compare mean/std, do t-test)
-}
-
-\subsection{Andromeda: Caldwell catalogue}
-\label{sec:m31}
 \citet[][, hereafter C11]{2011AJ....141...61C} studied globular clusters in the
@@
 \label{sec:results}
-Through out the analysis we use six sub sets of star particles: \emph{all stars}, 
-and \emph{old stars} (age $>10$~Gyr, GC candidates hereafter). Both sub sets are
-further split up in (old) star particles that have formed \emph{in-situ} 
-(bound to the most-massive halo/subhalo in the first snapshot that the star 
-particle was recorded), and (old) \emph{accreted} star particles (i.e. those that 
-have formed ex-situ and are bound to the most-massive halo/subhalo at $z=0$). 
-We use an age threshold of 10~Gyr for GC candidates because the mean 
-age-estimate of the $55$ MW GCs in V13 is $11.9\pm0.1$~Gyr with a dispersion of 
-$0.8$~Gyr, and only one observed GC lies outside this range.
+We define GC candidates in the Auriga simulations as all star particles older 
+than $10$~Gyr. The mean age-estimate of the $55$ MW GCs in V13 is $11.9\pm0.1$~Gyr
+with a dispersion of $0.8$~Gyr, and the age-estimate for only one observed GC is 
+smaller than $10$~Gyr.
+
+Through out the analysis we use six sub sets of star particles: 
+\emph{all stars}, and \emph{old stars} (age $>10$~Gyr, GC candidates hereafter). 
+Both sub sets are further split up in (old) star particles that have formed 
+\emph{in-situ} (bound to the most-massive halo/subhalo in the first snapshot that 
+the star particle was recorded), and (old) \emph{accreted} star particles (i.e. 
+those that have formed ex-situ and are bound to the most-massive halo/subhalo
+at $z=0$).
 
@@
 \label{sec:radial}
+
+Somewhat arbitrarily, I will take the region $r_p > 3$ kpc (containing 75 clusters) as the fiducial Mikly Way sample.
+If we were to view the Mikly Way at the same inclination angle to the disk as we see M31, this cutoff in projected distance would correspond roughly to the inner distance limits in the M31 halo sample.
+
 Is the spatial distribution of the GC candidates in the Auriga simulations consistent with the MW GCS?
@@
 metallicity ([Fe/H]), galactocentric radius $R_{\text{GC}}$, and [Fe/H]-$R_{\text{GC}}$ 
-bins to the total mass in the MW GCS (using the H96 data set). The mass excess in the
+bins to the total mass in the MW GCS (using the H96e10 data set). The mass excess in the
 simulations gives a maximum mass loss `budget' for the product of cluster formation 
@@
 }
+
+\subsection{Age cut}
+Although the age distribution of M31 Perhaps an age cut of 6~Gyr would would be more 
+appropriate for M31, see Fig.~\ref{fig:MW-M31-age}.
 

### 2019-03-03 AurigaGCS.tex
Commented some more on MW and M31 GCS observations.

@@
 
-\citet{2019AJ....157...12B} communicate the latest efforts to aggregate all
+\citet{2019AJ....157...12B} communicate the latest efforts to aggregate the
 available data, presented in their CatClu catalog. Amongst 10978 star clusters 
@@
 Galactic distance components $X$, $Y$, and $Z$ (in kpc)\footnote{In a Sun-centered 
-coordinate system where $X$ points toward Galactic center, $Y$ in direction of 
+coordinate system: $X$ points toward Galactic center, $Y$ in direction of 
 Galactic rotation, and $Z$ toward the North Galactic Pole. We calculate the 
 galactocentric radius $R_{\text{GC}}=\sqrt{(X-R_\odot)^2 + Y^2 + Z^2}$, 
-assuming $R_\odot=8$~kpc.}, and absolute 
+assuming the solar radius $R_\odot=8$~kpc.}, and absolute 
 magnitude in the V-band $M_V$. We use the latter to calculate mass-estimates by 
@@
 
-\subsubsection*{Distribution of mass in metallicity-radial bins}
+\subsubsection*{Distribution of total GC mass in metallicity-radial bins}
 In Fig.~\ref{fig:MW-FeHRgc} we show the two-dimensional mass-weighted 
@@
 \label{sec:andromeda}
-The revised bologna catalogue \citep[][and references therein]{2004A&A...416..917G} 
-is the result compiling integrated properties of M31's GCS,
+The fifth revision of the revised bologna catalogue (RBC~5, last updated 
+August, 2012) is the latest edition of three decades of systematically 
+collecting integrated properties of the globular cluster system of the 
+Andromeda galaxy \citep[][and references therein]{2004A&A...416..917G}. One
+contribution to RBC~5 is the work by \citet[][hereafter C11]{2011AJ....141...61C}. 
+C11 delivers a uniform set of spectroscopic observations $316$ out of the 
+$339$ GCs in the inner $1^\circ.6 (\sim 21)$~kpc, calibrated using the Milky 
+Way GCS.
 
-\citet[][, hereafter C11]{2011AJ....141...61C} studied globular clusters in the
-Andromeda (M31) galaxy. The relevant fields in this data set are the age, 
-metallicities, and absolute visual magnitude.
+Globular clusters in the outer halo of M31, up to projected radii 
+$R_{\text{proj}}\sim150$~kpc, are observed in the Pan-Andromeda Archaeological 
+Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H}, see also
+\citet{2014MNRAS.442.2929V, 2019MNRAS.484.1756M}. H14 presents the
+discovery of 59 new GCs and publishes updates to RBC~5. The work of H14 is
+incorporated in the latest version\footnote{dated 23 Sep 2015; retrieved
+from \url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}} 
+of the C11 dataset. It seems that the 2015 edition of C11 is the most recent 
+aggregated dataset M31's GCS and we will therefore use this troughout the 
+remainder of this work.
+
+The relevant fields in the C11 dataset are the age, metallicities, and 
+absolute visual magnitude.
 \todo[inline]{
@@
 }
+
 For M31 we find an age distribution with a mean value of 10.8$\pm 10.8$~Gyr and a 
@@
 
-\todo[inline]{
-TODO: paraphrase ``Furthermore, we supplement observational data of globular
-clusters in M31 with \citet{2014MNRAS.442.2165H, 2014MNRAS.442.2929V}'', and
-parse these data sets.
-}
-
-This text sits here just for debug purposes, just for now. We calculate the 
-projected and `inferred' galactocentric radius from the observed coordinates.
 \begin{align}
-    \cos \theta & = \sin \delta_1 \sin \delta_2 +
-        \cos \delta_1 \cos \delta_2 \cos \left( \alpha_1 - \alpha_2 \right),
 \end{align}
 where $(\alpha_1, \delta_1)$ are the right ascension and declination (in degrees,
-converted to radians) of the centroid of M31 and $(\alpha_2, \delta_2)$ are the
-observed coordinates of the globular cluster. The angle on the sky is converted
-to a physical distance in kpc using the small angle approximation, i.e. 
-$r_{\text{projected}} = \theta \cdot D_{\text{M31}}$. We adopt the values 
-$(\alpha_1, \delta_1) = (0^{\text{h}}42^{\text{m}}44.3^{\text{s}}, 
-+41^{\circ}16'9")$ (TODO: reference), and  $D_{\text{M31}} = 778$~kpc 
+We adopt the values 
+$(\alpha_0, \delta_0) = (0^{\text{h}}42^{\text{m}}44.3^{\text{s}}, 
++41^{\circ}16'9")$\footnote{See \url{https://ned.ipac.caltech.edu/}} , and  $D_{\text{M31}} = 778$~kpc 
 (TODO: reference).

### 2019-03-04 AurigaGCS.tex
Should now be done with describing observations. Moving on to results. Also commented out list of papers to read in introduction.

@@
 
-\begin{itemize}
-    \item \citet{2005MNRAS.364..367D}: ``The radial profile of the stellar halo
-    and metal-poor globular clusters of the Milky Way suggest that these components 
-    formed in rare early peaks above $2.5 \sigma$ at redshift above 10. ''
-
-    \item \citet{2017MNRAS.465.3622R}: ``GCs among oldest astrophysical objects.
-    GCs form in the early Universe in highest density peaks
-    \citep[e.g.][]{2005MNRAS.364..367D, 2009ApJ...706L.192B}''
-
-    \item ``Hence, they witness most of the formation and evolution processes
-    of galaxies, and can be used to probe them'' \citep{2006ARA&A..44..193B}
-\end{itemize}
+% \begin{itemize}
+%     \item \citet{2005MNRAS.364..367D}: ``The radial profile of the stellar halo
+%     and metal-poor globular clusters of the Milky Way suggest that these components 
+%     formed in rare early peaks above $2.5 \sigma$ at redshift above 10. ''
+% 
+%     \item \citet{2017MNRAS.465.3622R}: ``GCs among oldest astrophysical objects.
+%     GCs form in the early Universe in highest density peaks
+%     \citep[e.g.][]{2005MNRAS.364..367D, 2009ApJ...706L.192B}''
+% 
+%     \item ``Hence, they witness most of the formation and evolution processes
+%     of galaxies, and can be used to probe them'' \citep{2006ARA&A..44..193B}
+% \end{itemize}
 
@@
     previous work and references work of other groups}
-\begin{itemize}
-\item Origin of the Milky Way globular clusters \citep{2017MNRAS.465.3622R}
-\item GCs in FIRE \citep{2018MNRAS.474.4232K}
-\item EMOSAICS project \citep{2018MNRAS.475.4309P}
-\item GC-DMhalo connection \citep{2017MNRAS.472.3120B}
-\item Origin of GC bimodality? \citep{2018MNRAS.479..200F}
-\item \textit{GAIA} DR2: GC kinematics \citep{2018A&A...616A..12G}
-\item Dating GC Tidal Disruption \citep{2018ApJ...859L..13B}
-\item GC in N-body simulation \citep{2018ApJ...861...69C}
-\item (Role of GC mass evolution on stream properties \citep{2018MNRAS.474.2479B})
-\item GC formation from dwarfs to giants \citep{2018MNRAS.480.2343C}
-\item (GC contribution to EOR \citep{2018MNRAS.479..332B})
-\item Early Universe supermassive star / GC formation \citep{2018MNRAS.478.2461G}
-\item GC formation in cold filaments \citep{2018ApJ...861..148M}
-\item GC formation in high-redshift dwarf galaxies \citep{2018MNRAS.477..480Z}
-\item GCs in MW outer region \citep{2017arXiv170804542P}
-\item Impact of the Cutoff of the Cluster Initial Mass Function \citep{2018arXiv181001888C}
-\item Metallicity gradients in the globular cluster systems of early-type galaxies: in situ and accreted components \citep{2018MNRAS.479.4760F}
-\item Globular clusters in M31, Local Group, and external galaxies \citep{2016IAUS..317..120L}
-\item Globular Clusters Formed within Dark Halos I: present-day abundance, distribution and kinematics \citep{2019MNRAS.482..219C}
-\item (The mass of the Milky Way from satellite dynamics \citep{2018arXiv180810456C})
-\item Globular cluster formation and evolution in the context of cosmological galaxy assembly: open questions \citep{2018RSPSA.47470616F}
-\item The kinematics of globular clusters systems in the outer halos of the Aquarius simulations \citep{2016A&A...592A..55V}
-\item Star Cluster Formation in Cosmological Simulations \citep{2017ApJ...834...69L, 2018ApJ...861..107L, 2018arXiv181011036L}
-\item (A systematic analysis of star cluster disruption by tidal shocks - I. Controlled N-body simulations and a new theoretical model \citep{2018arXiv181200014W})
-\item Spatial mixing of binary stars in multiple-population globular clusters \citep{2018MNRAS.tmp.3147H}
-\item Star Clusters Across Cosmic Time \citep{2018arXiv181201615K}
-\item Kinematics of Subclusters in Star Cluster Complexes: Imprint of their Parental Molecular Clouds \citep{2018arXiv181201858F}
-\item Investigating the population of Galactic star formation regions and star clusters within a Wide-Fast-Deep Coverage of the Galactic Plane  \citep{2018arXiv181203025P}
-\item Globular cluster number density profiles using \textit{Gaia} DR2 \citep{2019arXiv190108072D}
-\item Clustering Clusters: unsupervised learning on GC observations (of log $M$,
-    log $\sigma_0$, log $R_e$ , [Fe/H], log $|Z|$) to determine number of groups
-    $k=2$ (disk/halo) or $k=3$ (disk/inner-halo/outer-halo): the optimal number
-    of groups given the data is $k=3$. \citep{2019arXiv190105354P}.
-\item There is a well-known hypothesis that Open Stars Clusters (OSCs) could form as a result
-    of GCs crossing the disk. New kinematical data does not support
-    this claim for two particular OSC-GC pairs, and does seem consistent
-    with this scenario for six OSC-GC pairs \citep{2019arXiv190106481B}. (Note
-    that GC crossing the disk could also trigger formation of multiple OSCs!)
-\item DM halo mass can be inferred from number of globular cluster in galaxy 
-    \citep{2019arXiv190100900B}
-\item GCs in M31 outer halo \citep{2019arXiv190111229W}
-% TODO: last checked arXiv Mar 2, 2019
-\end{itemize}
+% \begin{itemize}
+% \item Origin of the Milky Way globular clusters \citep{2017MNRAS.465.3622R}
+% \item GCs in FIRE \citep{2018MNRAS.474.4232K}
+% \item EMOSAICS project \citep{2018MNRAS.475.4309P}
+% \item GC-DMhalo connection \citep{2017MNRAS.472.3120B}
+% \item Origin of GC bimodality? \citep{2018MNRAS.479..200F}
+% \item \textit{GAIA} DR2: GC kinematics \citep{2018A&A...616A..12G}
+% \item Dating GC Tidal Disruption \citep{2018ApJ...859L..13B}
+% \item GC in N-body simulation \citep{2018ApJ...861...69C}
+% \item (Role of GC mass evolution on stream properties \citep{2018MNRAS.474.2479B})
+% \item GC formation from dwarfs to giants \citep{2018MNRAS.480.2343C}
+% \item (GC contribution to EOR \citep{2018MNRAS.479..332B})
+% \item Early Universe supermassive star / GC formation \citep{2018MNRAS.478.2461G}
+% \item GC formation in cold filaments \citep{2018ApJ...861..148M}
+% \item GC formation in high-redshift dwarf galaxies \citep{2018MNRAS.477..480Z}
+% \item GCs in MW outer region \citep{2017arXiv170804542P}
+% \item Impact of the Cutoff of the Cluster Initial Mass Function \citep{2018arXiv181001888C}
+% \item Metallicity gradients in the globular cluster systems of early-type galaxies: in situ and accreted components \citep{2018MNRAS.479.4760F}
+% \item Globular clusters in M31, Local Group, and external galaxies \citep{2016IAUS..317..120L}
+% \item Globular Clusters Formed within Dark Halos I: present-day abundance, distribution and kinematics \citep{2019MNRAS.482..219C}
+% \item (The mass of the Milky Way from satellite dynamics \citep{2018arXiv180810456C})
+% \item Globular cluster formation and evolution in the context of cosmological galaxy assembly: open questions \citep{2018RSPSA.47470616F}
+% \item The kinematics of globular clusters systems in the outer halos of the Aquarius simulations \citep{2016A&A...592A..55V}
+% \item Star Cluster Formation in Cosmological Simulations \citep{2017ApJ...834...69L, 2018ApJ...861..107L, 2018arXiv181011036L}
+% \item (A systematic analysis of star cluster disruption by tidal shocks - I. Controlled N-body simulations and a new theoretical model \citep{2018arXiv181200014W})
+% \item Spatial mixing of binary stars in multiple-population globular clusters \citep{2018MNRAS.tmp.3147H}
+% \item Star Clusters Across Cosmic Time \citep{2018arXiv181201615K}
+% \item Kinematics of Subclusters in Star Cluster Complexes: Imprint of their Parental Molecular Clouds \citep{2018arXiv181201858F}
+% \item Investigating the population of Galactic star formation regions and star clusters within a Wide-Fast-Deep Coverage of the Galactic Plane  \citep{2018arXiv181203025P}
+% \item Globular cluster number density profiles using \textit{Gaia} DR2 \citep{2019arXiv190108072D}
+% \item Clustering Clusters: unsupervised learning on GC observations (of log $M$,
+%     log $\sigma_0$, log $R_e$ , [Fe/H], log $|Z|$) to determine number of groups
+%     $k=2$ (disk/halo) or $k=3$ (disk/inner-halo/outer-halo): the optimal number
+%     of groups given the data is $k=3$. \citep{2019arXiv190105354P}.
+% \item There is a well-known hypothesis that Open Stars Clusters (OSCs) could form as a result
+%     of GCs crossing the disk. New kinematical data does not support
+%     this claim for two particular OSC-GC pairs, and does seem consistent
+%     with this scenario for six OSC-GC pairs \citep{2019arXiv190106481B}. (Note
+%     that GC crossing the disk could also trigger formation of multiple OSCs!)
+% \item DM halo mass can be inferred from number of globular cluster in galaxy 
+%     \citep{2019arXiv190100900B}
+% \item GCs in M31 outer halo \citep{2019arXiv190111229W}
+% % TODO: last checked arXiv Mar 2, 2019
+% \end{itemize}
 
@@
     two populations of globular cluster.}
-\begin{itemize}
-    \item ``colour bimodality, blue and red clusters \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L, 2006ApJ...639...95P}
-    \item ``blue metal-poor (with distribution peaking at [Fe/H] $\approx -1.5$ for the Milky Way), no sign of rotation as a population (..) more metal-rich (peak at [Fe/H] $\approx -0.5$ in the Milky  Way) more spatially concentrated and rotating with the galaxy.'' \citep{1996AJ....112.1487H}
-    \item ``Blue clusters from in early Universe in galaxies that merge later. In (wet) merger process starbursts generate red population \cite{1992ApJ...384...50A, 1987nngp.proc...18S}''
-    \item ``\citet{1997AJ....113.1652F} propose instead that blue globulars form when the protogalaxy itself collapses, in a metal-poor and turbulence media.
+% \begin{itemize}
+%     \item ``colour bimodality, blue and red clusters \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L, 2006ApJ...639...95P}
+%     \item ``blue metal-poor (with distribution peaking at [Fe/H] $\approx -1.5$ for the Milky Way), no sign of rotation as a population (..) more metal-rich (peak at [Fe/H] $\approx -0.5$ in the Milky  Way) more spatially concentrated and rotating with the galaxy.'' \citep{1996AJ....112.1487H}
+%     \item ``Blue clusters from in early Universe in galaxies that merge later. In (wet) merger process starbursts generate red population \cite{1992ApJ...384...50A, 1987nngp.proc...18S}''
+%     \item ``\citet{1997AJ....113.1652F} propose instead that blue globulars form when the protogalaxy itself collapses, in a metal-poor and turbulence media.
 The red population would form later, once the galactic disc has settled.
 The formation of globular clusters would then be a multiphase process, with the first phase being interrupted possibly by cosmic reionization \citep{2002MNRAS.333..383B}.''
-    \item ``\citet{2005ApJ...623..650K, 2014ApJ...796...10L} advocate
-that major mergers are at the origin of both sub-populations: blue
-clusters form during early mergers (z > 4) while the red ones appear
-in mergers at lower redshifts (even after z = 1). Although, this
-scenario, combined with star formation enhancement in mergers,
-seems appropriate in dense galactic environment leading to the
-assembly of massive elliptical galaxies, like in the Virgo Cluster
-as tested by \citet{2014ApJ...796...10L}, it does not apply to Milky Way-
-like systems where no recent major merger took place (Wyse 2001;
-Deason et al. 2013; Ruchti et al. 2014, 2015).
-\item ``\citet{1998ApJ...501..554C} argue that red clusters form in situ while the blue ones are accreted, either via merging satellite galaxies, or by tidal capture of the clusters themselves \citep[see also][]{2013ApJ...762...39T}.''
-\end{itemize}
+%     \item ``\citet{2005ApJ...623..650K, 2014ApJ...796...10L} advocate
+% that major mergers are at the origin of both sub-populations: blue
+% clusters form during early mergers (z > 4) while the red ones appear
+% in mergers at lower redshifts (even after z = 1). Although, this
+% scenario, combined with star formation enhancement in mergers,
+% seems appropriate in dense galactic environment leading to the
+% assembly of massive elliptical galaxies, like in the Virgo Cluster
+% as tested by \citet{2014ApJ...796...10L}, it does not apply to Milky Way-
+% like systems where no recent major merger took place (Wyse 2001;
+% Deason et al. 2013; Ruchti et al. 2014, 2015).
+% \item ``\citet{1998ApJ...501..554C} argue that red clusters form in situ while the blue ones are accreted, either via merging satellite galaxies, or by tidal capture of the clusters themselves \citep[see also][]{2013ApJ...762...39T}.''
+% \end{itemize}
 
@@
     \item The star formation model implemented in the Auriga simulations is capable of producing a suite/population of realistic Milky Way-like galaxies at redshift zero.
-    \item (However) State of the art simulations still face numerical restrictions that requires a subgrid approach to star formation and feedback because individual stars (and their evolution) cannot yet be accounted for.
-Star formation thus occurs in a heuristic/probabilistic fashion for gas cells that fulfill some star formation criterion.
-The star particles enrich the gas with metals and energy, both according to pre-defined/pre-calculated yields for specific feedback processes (supernova type I and II, strong stellar winds of asymptotic giant branch stars, ).
-In addition, black holes are seeded in eligible haloes to account for feedback associated with an active galactic nucleus.
-    \item The end-result of the star formation model is the production of simulated Milky Way-like galaxies.
-Therefore the question naturally arises whether or not the Auriga simulations are also capable of faithfully producing a globular cluster population as observed in the Milky Way.
+    \item Therefore the question naturally arises whether or not the Auriga simulations are also capable of faithfully producing a globular cluster population as observed in the Milky Way (or Andromeda).
     \item Globular cluster formation in cosmological zoom simulations is very interesting for two reasons.
@@
 Way in Sec.~\ref{sec:milkyway}, and of Andromeda (M31) in Sec.~\ref{sec:andromeda}.
-In the remainder of the paper we compare observed (integrated) globular cluster
-properties to the Auriga simulations.
 
@@
 \citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
-catalogue of the Milky Way globular cluster system that contains properties of 
+catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}} 
+of the Milky Way globular cluster system that contains properties of 
 157 GCs. The authors initially estimated the size of the MW GCS to be 180~$\pm$~10,
@@
 and alike objects in the Milky Way, the catalog contains 200 GCs and 94 GC 
-candidates. Unfortunately a machine readable version of the catalog is unavailable
-at this point in time. Therefore we utilise the H96e10 dataset nonetheless, but
-we caution that the Harris catalogue is now believed to be (only) 53-72\% complete.
+candidates. The CatClu catalog contains reference papers, positions, distances,
+and total absolute V magnitude. Therefore we rely on the H96e10 dataset for all
+other quantities, but we caution that the Harris catalogue is now believed to be (only) 53-72\% complete.
 
-The relevant data fields that we use from H96e10 are the metallicity [Fe/H], the
-Galactic distance components $X$, $Y$, and $Z$ (in kpc)\footnote{In a Sun-centered 
-coordinate system: $X$ points toward Galactic center, $Y$ in direction of 
-Galactic rotation, and $Z$ toward the North Galactic Pole. We calculate the 
-galactocentric radius $R_{\text{GC}}=\sqrt{(X-R_\odot)^2 + Y^2 + Z^2}$, 
-assuming the solar radius $R_\odot=8$~kpc.}, and absolute 
+Specifically, the relevant data fields that we use from H96e10 are the 
+metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in 
+kpc)\footnote{In a Sun-centered coordinate system: $X$ points toward Galactic 
+center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic 
+Pole. We calculate the galactocentric radius $R_{\text{GC}}=\sqrt{(X-R_\odot)^2
++ Y^2 + Z^2}$, assuming the solar radius $R_\odot=8$~kpc.}, and absolute 
 magnitude in the V-band $M_V$. We use the latter to calculate mass-estimates by 
@@
 Andromeda galaxy \citep[][and references therein]{2004A&A...416..917G}. One
-contribution to RBC~5 is the work by \citet[][hereafter C11]{2011AJ....141...61C}. 
-C11 delivers a uniform set of spectroscopic observations $316$ out of the 
-$339$ GCs in the inner $1^\circ.6 (\sim 21)$~kpc, calibrated using the Milky 
-Way GCS.
+contribution to RBC~5 is the work by \citet[][hereafter C11]{2011AJ....141...61C},
+subsequently updated by \citet[][hereafter CR16]{2016ApJ...824...42C}.
 
-Globular clusters in the outer halo of M31, up to projected radii 
+C11 and CR16 present a uniform set of spectroscopic observations calibrated 
+on the Milky Way GCS of the inner $1.6^\circ~(\sim21)$~kpc that 
+is believed to be 94\% complete. GCs in the outer stellar halo, up to 
 $R_{\text{proj}}\sim150$~kpc, are observed in the Pan-Andromeda Archaeological
-Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H}, see also
-\citet{2014MNRAS.442.2929V, 2019MNRAS.484.1756M}. H14 presents the
+Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H}, but see also
+\citet{2014MNRAS.442.2929V} and \citet{2019MNRAS.484.1756M}. H14 presents the
 discovery of 59 new GCs and publishes updates to RBC~5. The work of H14 is
-incorporated in the latest version\footnote{dated 23 Sep 2015; retrieved
-from \url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}} 
-of the C11 dataset. It seems that the 2015 edition of C11 is the most recent 
-aggregated dataset M31's GCS and we will therefore use this troughout the 
-remainder of this work.
+incorporated in the latest public release\footnote{Last revised 23 Sep 2015, see
+\url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}} 
+of the C11 dataset, further revised by CR16. It seems that CR16 is the most 
+recent aggregated dataset of M31's GCS that contains properties of interest
+for our study as it contains GCs in the inner region and in the outer halo. The 
+relevant fields in the CR16 dataset that we use are the age, metallicity, and the 
+mass-estimate\footnote{The authors assumed $M/L_V = 2$ (independent of [Fe/H])}.
 
-The relevant fields in the C11 dataset are the age, metallicities, and 
-absolute visual magnitude.
-\todo[inline]{
-TODO: paraphrase ``For M31 GC masses we combine the catalogues of Caldwell et al. (2011, using the 
-given masses) and Huxor et al. (2014, again assuming $M/L_V = 1.7$~M/L$_{\odot}$, 
-e.g. Strader, Caldwell \& Seth 2011).''
-}
+% \todo[inline]{
+% ``For M31 GC masses we combine the catalogues of Caldwell et al. (2011, using the 
+% given masses) and Huxor et al. (2014, again assuming $M/L_V = 1.7$~M/L$_{\odot}$, 
+% e.g. Strader, Caldwell \& Seth 2011).''
+% }
 
+\subsubsection*{Age estimates}
 For M31 we find an age distribution with a mean value of 10.8$\pm 10.8$~Gyr and a 
@@
 the minimum age is 4.8~Gyr.
+
+We present a mass-weighted histogram of the age-estimates of the 55 MW GCs in V13
+and 85 GCs in M31 for which age-estimates are available in CR16, see 
+Fig.~\ref{fig:MW-M31-age}.
 
@@
         Mass-weighted age distribution of 55 GCs in the MW
-        \citep[data from][]{2013ApJ...775..134V} and 87 GCs
-        in M31 \citep[data from][]{2011AJ....141...61C}.
+        \citep[data from][]{2013ApJ...775..134V} and 85 GCs
+        in M31 \citep[data from][]{2016ApJ...824...42C}.
         \label{fig:MW-M31-age}
@@
 
+\subsubsection*{Calculation of galactocentric radius}
+The projected galacocentric radius $R_{\text{proj}}$ is calculated following
+\citet[][Sec.~4.1, eq.~4]{2019arXiv190111229W}. Specifically,
 \begin{align}
+    X &= A \sin{(\text{PA})} + B \cos{(\text{PA})} \nonumber \quad \text{and} \\
+    Y &= - A \cos{(\text{PA})} + B \sin{(\text{PA})} \text{,}
 \end{align}
-where $(\alpha_1, \delta_1)$ are the right ascension and declination (in degrees,
-We adopt the values 
-$(\alpha_0, \delta_0) = (0^{\text{h}}42^{\text{m}}44.3^{\text{s}}, 
-+41^{\circ}16'9")$\footnote{See \url{https://ned.ipac.caltech.edu/}} , and  $D_{\text{M31}} = 778$~kpc 
-(TODO: reference).
-
-% TODO: Deprojection, assuming all GCs lie in the plane of the sky, inclination 
-% $12.5^{\circ}$
+where $A = \sin{(\alpha - \alpha_0)} \cos{\delta}$ and
+$B = \sin\delta \cos\delta_0 - \cos{(\alpha - \alpha_0)} \cos\delta \sin\delta_0$
+for the right ascension $\alpha$ (hourangle) and declination $\delta$ (degree) 
+of the GCs. For the central position of M31 we take the preferred position 
+from the NASA Extragalactic Database\footnote{\url{https://ned.ipac.caltech.edu/}}
+entry of M31: $(\alpha_0, \, \delta_0) = 
+(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$.
+The projected galactocentrid radius is calculated as $R_\text{proj} = 
+\sqrt{X^2 + Y^2}$ (for $X$ and $Y$ in arcsec), and using the small angle 
+approximation with a distance of $D_{\text{M31}} = 778$~kpc to convert to kpc.
+TODO: McConnachie et al. 2005; Conn  et  al. 2012. Finally, we convert the 
+projected distance ($R_{\text{proj}}$) to an `average deprojected distance` 
+via the relationship $R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$.
 
@@
 We define GC candidates in the Auriga simulations as all star particles older 
-than $10$~Gyr. The mean age-estimate of the $55$ MW GCs in V13 is $11.9\pm0.1$~Gyr
-with a dispersion of $0.8$~Gyr, and the age-estimate for only one observed GC is 
-smaller than $10$~Gyr.
+than $10$~Gyr based on the age distribution of the MW GCS in 
+Fig.~\ref{fig:MW-M31-age} and following \citet{2017MNRAS.465.3622R}.
 
@@
 radii of the globular cluster candidates within the Auriga simulations, and we 
-combine both in Sec.~\ref{sec:FeHRgc}. We continue our analysis with an investigation
-of the properties of the proto-galaxies at times of birth of the accreted globular 
-cluster population in Sec.~\ref{sec:birth-properties-of-accreted-gc-candidates}
+combine both in Sec.~\ref{sec:FeHRgc}. 
+% We continue our analysis with an investigation
+% of the properties of the proto-galaxies at times of birth of the accreted globular 
+% cluster population in Sec.~\ref{sec:birth-properties-of-accreted-gc-candidates}
 
@@
 Is the spatial distribution of the GC candidates in the Auriga simulations consistent with the MW GCS?
-
-\todo[inline]{
-Look into Pandromeda survey. Star counts, very wide angle survey
-}
 
@@
 
+\todo[inline]{
+\citet{2016ApJ...824...42C} writes:
+``there are two broad, well-established differences:
+(1) the M31 GC system is more populous than the MW system, by a factor of
+$\sim$2-3, and (2) it does not exhibit the same obvious bimodality in
+metallicity \citep{2000AJ....119..727B, 2009A&A...508.1285G, 2011AJ....141...61C, 
+2013A&A...549A..60C}. Both of these aspects may be reflections of dramatic 
+differences discovered in these galaxies stellar halos, where the M31 halo 
+appears much more metal-enriched, with massive substructures suggesting a more 
+active satellite accretion history \citep[e.g.][]{2009Natur.461...66M}''
+}
+
 \section{Summary and conclusions}

### 2019-03-05 AurigaGCS.tex
Minor updates to abstract

@@
 } \vspace{10pt} \\
-$^{1}$ Max-Planck-Institut f\"ur Astrophysik, Postfach 1317, D-85741 Garching, Germany \\
+$^{1}$ Max-Planck-Institut f\"ur Astrophysik, Karl-Schwarzschild-Str. 1,
+    85741 Garching, Germany \\
 $^{2}$ Instituto de Investigaci\'{o}n Multidisciplinar en Ciencia yTecnolog\'{i}a, 
@@
 \begin{abstract}
-\todo[inline]{Ask SW whether I should ask Carlos Frenk and Adrian Jenkins for co-authorship}
+\todo[inline]{Rob Grand: `for many Auriga papers Carlos Frenk and Adrian Jenkins 
+are offered co-authorship. Perhaps you could ask Simon about this.'}
 We investigate whether the galaxy formation model used for the Auriga simulations 
@@
 catalogues of observations of the Milky Way globular cluster population available
-in the literature. We find that the Auriga simulations produce sufficient mass
+in the literature. We find that the Auriga simulations do produce sufficient mass
 at radii and metallicities that are typical for the MW GCS, although we observe
@@
 and the globular cluster disruption rate. We investigate wether these differences
-could result from formation insitu vs. accreted star particles. We find ...
+could result from formation insitu vs. accreted star particles. We find ... TODO.
+Furthermore we test whether any of the Auriga galaxies has a metallicity and radial
+distribution that is consistent with the MW (M31) GCS. For all of the Auriga haloes
+we reject the null hypothesis that the simulated and observed metallicities are 
+drawn from the same distribution at the 99.99\% confidence level, for the GCS
+of the Milky Way as well as that of the Andromeda galaxy. The same holds true for
+the distribution of galactocentric radius.
 \end{abstract}

### 2019-03-06 AurigaGCS.tex
Updated the updated figures in the draft

@@
     \includegraphics[width=\columnwidth]
-        {{MW_M31_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
+        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
+    \includegraphics[width=\columnwidth]
+        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data}.png}
     \caption{
-        Mass-weighted r$_{\text{gc}}$-[Fe/H] distribution of
+        \emph{Top}: Mass-weighted r$_{\text{gc}}$-[Fe/H] distribution of
         151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
         is 98.19 \% of the total MW GCS mass in the Harris catalog.
+        \emph{Bottom}: Same for M31, showing 366 GCs and 88.38 \% of the total 
+        mass in CR16 \citep[data from][]{2016ApJ...824...42C}.
         \label{fig:MW-FeHRgc}
@@
 
-Somewhat arbitrarily, I will take the region $r_p > 3$ kpc (containing 75 clusters) as the fiducial Mikly Way sample.
-If we were to view the Mikly Way at the same inclination angle to the disk as we see M31, this cutoff in projected distance would correspond roughly to the inner distance limits in the M31 halo sample.
-
-Is the spatial distribution of the GC candidates in the Auriga simulations consistent with the MW GCS?
-
 \begin{figure}
-    \includegraphics[width=\columnwidth]{{logMR2dgc_withRatios-trim}.png}
+    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
     \caption{
-        Mass-weighted distribution of (two-dimensional) galactocentric radii at 
-        which star particles in the Auriga simulations are found. For Andromeda 
-        we show the projected galactocentric radius, assuming its center is located
-        at $(0^{\text{h}}42^{\text{m}}44.3^{\text{s}}, +41^{\circ}16'9")$ at a 
-        distance of 778 kpc.
+        Mass-weighted radial distribution of star particles in the Auriga 
+        simulations. We show the median value of all Auriga haloes for all
+        stars (orange dotted) and globular cluster candidates (i.e. stars with 
+        age $>$~10~Gyr; orange solid). The latter sub set is further split up
+        between stars that formed in-situ (blue solid), and those that were accreted
+        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
+        GCS is shown in purple (magenta). The middle (bottom) panel shows the
+        ratio of the simulated mass to the mass in the MW (M31) GCS.
         \label{fig:Rgc}
@@
 \end{figure}
+
+\todo[inline]{
+    Harris: `Somewhat arbitrarily, I will take the region $r_p > 3$ kpc 
+    (containing 75 clusters) as the fiducial Milky Way sample. If we were to
+    view the Milky Way at the same inclination angle to the disk as we see 
+    M31, this cutoff in projected distance would correspond roughly to the 
+    inner distance limits in the M31 halo sample.'
+}
+
+Is the spatial distribution of the GC candidates in the Auriga simulations consistent with the MW GCS?
 

### 2019-03-22 AurigaGCS.tex
Working on paragraph 0 of introduction: general introduction of GCs

@@
 \todo[inline]{Paragraph: General introduction of GCs}
+Globular clusters (GCs) are old, ubiquitous, and bright. 
+GC ages range from $6-14$~Gyr, although observational age-estimates can be 
+uncertain and a definitive age threshold to classify star clusters as `globular' 
+remains topic of debate.
+GCs are observed at scales ranging from clusters of galaxies down to 
+dwarf galaxies 
+The globular cluster system (GCS) of galaxy clusters can comprise 
+a few hundred thousand GCs (citation needed), 
+brightest cluster galaxies a few ten thousand (citation needed), 
+spiral galaxies a few hundred (citation needed), 
+and a handful GCs are expected to be present in dwarf galaxies with masses as low 
+as $\sim10^{8}$~M\Sun (citation needed).
+
+\todo[inline]{
+    `The population of galaxies bound to a rich galaxy cluster can host 
+    hundreds of thousands of GCs \citep{2013ApJ...775...20A}'
+    \citep[stolen from][]{2018MNRAS.475.4309P}
+}
+\todo[inline]{
+    `brightest cluster galaxies can host tens of thousands 
+    \citep{2008ApJ...681..197P, 2017ApJ...835..101H}'
+    \citep[stolen from][]{2018MNRAS.475.4309P}
+}
+\todo[inline]{
+    \citep[for recent reviews, see e.g.][]{2006ARA&A..44..193B, 2014CQGra..31x4006K}
+}
+\todo[inline]{
+    `the Milky Way (MW) and M31 are known to host a few hundred
+    \citep{1991ARA&A..29..543H}'
+    \citep[stolen from][]{2018MNRAS.475.4309P}
+}
+\todo[inline]{
+    `Even at masses as low as $10^{8}$~M\Sun, the majority of galaxies still
+    contain at least one GC \citep[e.g.][]{2010MNRAS.406.1967G}' 
+    \citep[stolen from][]{2018MNRAS.475.4309P}
+}
+
+The properties of the GCs themselves are correlated with those of their host
+galaxies, in particular their metallicities. 
+\todo[inline]{
+    `The mean metallicities of GC systems have long been 
+    known to scale with the metallicity of their host (van den Bergh
+    1975; Brodie \& Huchra 1991)' \citep[from][]{2008ApJ...681..197P}
+}
 
@@
 The mean value of the age-estimates in this data set is $11.9 \pm 0.1$~Gyr and 
-the dispersion is 0.9~Gyr. Furthermore, only one of the 55 GC age-estimates is
-below 10~Gyr.
+the dispersion is $0.8$~Gyr. Furthermore, only one of the 55 GC age-estimates is
+below $10$~Gyr.
 
@@
 \subsubsection*{Age estimates}
-For M31 we find an age distribution with a mean value of 10.8$\pm 10.8$~Gyr and a 
-dispersion of 2.3~Gyr. Furthermore, 27 GCs have age-estimates below 10~Gyr, and
-the minimum age is 4.8~Gyr.
+For M31 we find an age distribution with a mean value of 11.0$\pm 0.2$~Gyr and a 
+dispersion of $2.2$~Gyr. Furthermore, $24$ GCs have age-estimates below $10$~Gyr, and
+the minimum age is $4.8$~Gyr.
 
-We present a mass-weighted histogram of the age-estimates of the 55 MW GCs in V13
-and 85 GCs in M31 for which age-estimates are available in CR16, see 
+We present a mass-weighted histogram of the age-estimates of the $55$ MW GCs in V13
+and $85$ GCs in M31 for which age-estimates are available in CR16, see 
 Fig.~\ref{fig:MW-M31-age}.

### 2019-03-22 AurigaGCS.tex
Bulletpointoutline of paragraph 0 of introduction

@@
 \todo[inline]{Paragraph: General introduction of GCs}
+\begin{itemize}
+    \item old, ubiquitous, bright, `simple' single-age stellar populations
+    \item properties (particularly metallicity) correlate with the host galaxy
+    \item GCs can be used to understand galform, if GCform understood
+\end{itemize}
 Globular clusters (GCs) are old, ubiquitous, and bright. 
@@
 dwarf galaxies 
-The globular cluster system (GCS) of galaxy clusters can comprise 
-a few hundred thousand GCs (citation needed), 
-brightest cluster galaxies a few ten thousand (citation needed), 
-spiral galaxies a few hundred (citation needed), 
-and a handful GCs are expected to be present in dwarf galaxies with masses as low 
-as $\sim10^{8}$~M\Sun (citation needed).
-
-\todo[inline]{
-    `The population of galaxies bound to a rich galaxy cluster can host 
-    hundreds of thousands of GCs \citep{2013ApJ...775...20A}'
-    \citep[stolen from][]{2018MNRAS.475.4309P}
-}
-\todo[inline]{
-    `brightest cluster galaxies can host tens of thousands 
-    \citep{2008ApJ...681..197P, 2017ApJ...835..101H}'
-    \citep[stolen from][]{2018MNRAS.475.4309P}
-}
 \todo[inline]{
     \citep[for recent reviews, see e.g.][]{2006ARA&A..44..193B, 2014CQGra..31x4006K}
-}
-\todo[inline]{
-    `the Milky Way (MW) and M31 are known to host a few hundred
-    \citep{1991ARA&A..29..543H}'
-    \citep[stolen from][]{2018MNRAS.475.4309P}
-}
-\todo[inline]{
-    `Even at masses as low as $10^{8}$~M\Sun, the majority of galaxies still
-    contain at least one GC \citep[e.g.][]{2010MNRAS.406.1967G}' 
-    \citep[stolen from][]{2018MNRAS.475.4309P}
 }

### 2019-03-22 AurigaGCS.tex
Bullet point outline of the paragraphs included in the introduction

@@
 \begin{itemize}
-    \item old, ubiquitous, bright, `simple' single-age stellar populations
-    \item properties (particularly metallicity) correlate with the host galaxy
-    \item GCs can be used to understand galform, if GCform understood
+    \item GCs are old, ubiquitous, bright, `simple' single-age stellar populations
+    \item GC properties (particularly metallicity) set by birth gas properties, 
+        GC properties correlate with their host galaxy properties.
+    \item The above makes GCs excellent proxies to study galform
+    \item But first GCform should be understood
 \end{itemize}
-Globular clusters (GCs) are old, ubiquitous, and bright. 
-GC ages range from $6-14$~Gyr, although observational age-estimates can be 
-uncertain and a definitive age threshold to classify star clusters as `globular' 
-remains topic of debate.
-GCs are observed at scales ranging from clusters of galaxies down to 
-dwarf galaxies 
-\todo[inline]{
-    \citep[for recent reviews, see e.g.][]{2006ARA&A..44..193B, 2014CQGra..31x4006K}
-}
+% Globular clusters (GCs) are old, ubiquitous, and bright. 
+% GC ages range from $6-14$~Gyr, although observational age-estimates can be 
+% uncertain and a definitive age threshold to classify star clusters as `globular' 
+% remains topic of debate.
+% GCs are observed at scales ranging from clusters of galaxies down to 
+% dwarf galaxies 
+% \todo[inline]{
+%     \citep[for recent reviews, see e.g.][]{2006ARA&A..44..193B, 2014CQGra..31x4006K}
+% }
+% 
+% The properties of the GCs themselves are correlated with those of their host
+% galaxies, in particular their metallicities. 
+% \todo[inline]{
+%     `The mean metallicities of GC systems have long been 
+%     known to scale with the metallicity of their host (van den Bergh
+%     1975; Brodie \& Huchra 1991)' \citep[from][]{2008ApJ...681..197P}
+% }
 
-The properties of the GCs themselves are correlated with those of their host
-galaxies, in particular their metallicities. 
-\todo[inline]{
-    `The mean metallicities of GC systems have long been 
-    known to scale with the metallicity of their host (van den Bergh
-    1975; Brodie \& Huchra 1991)' \citep[from][]{2008ApJ...681..197P}
-}
+\todo[inline]{Paragraph: Theories of GC formation}
+\begin{itemize}
+    \item Special conditions in early Universe?
+    \item Formation in collapsing proto-galaxies (in-situ-ish?)
+    \item Formation as a result of (wet) mergers?
+    \item Formation in satellites that are later accreted?
+    \item No special conditions at high z, but connection between low-z YMC-
+        and high-z GC-formation where differences could result from Hubble time
+        of evolution?
+    \item This means that in order to test formation models against observations,
+        one not only needs needs to model GC formation, but also include the full 
+        evolution over their lifetime in a cosmological tidal field.
+\end{itemize}
+
+\todo[inline]{Paragraph: ingredients for numerical studies}
+\begin{itemize}
+    \item High resolution in the ISM
+    \item Full cosmological evolution
+\end{itemize}
 
@@
 
-\todo[inline]{Paragraph: scientific context / state of the field: briefly summarise
-    previous work and references work of other groups}
+% \todo[inline]{Paragraph: scientific context / state of the field: briefly summarise
+%     previous work and references work of other groups}
 % \begin{itemize}
@@
 
-\todo[inline]{Paragraph, narrowing open questions in GC research down to formation,
-    possibly ``Bimodality suggests two formation mechanisms''. In-situ 
-    formation vs. accretion in hierarchical build-up of galaxies naturally produces 
-    two populations of globular cluster.}
+% \todo[inline]{Paragraph, narrowing open questions in GC research down to formation,
+%     possibly ``Bimodality suggests two formation mechanisms''. In-situ 
+%     formation vs. accretion in hierarchical build-up of galaxies naturally produces 
+%     two populations of globular cluster.}
 % \begin{itemize}
@@
 
-\todo[inline]{Paragraph: narrow the scientific motivation down to the scope of 
-    this particular work}
+\todo[inline]{Paragraph: narrow down to this work}
 \begin{itemize}

### 2019-03-24 AurigaGCS.tex
Wrote paragraph0 of the introduction

@@
 \section{Introduction}
-\todo[inline]{Paragraph: General introduction of GCs}
-\begin{itemize}
-    \item GCs are old, ubiquitous, bright, `simple' single-age stellar populations
-    \item GC properties (particularly metallicity) set by birth gas properties, 
-        GC properties correlate with their host galaxy properties.
-    \item The above makes GCs excellent proxies to study galform
-    \item But first GCform should be understood
-\end{itemize}
-% Globular clusters (GCs) are old, ubiquitous, and bright. 
-% GC ages range from $6-14$~Gyr, although observational age-estimates can be 
-% uncertain and a definitive age threshold to classify star clusters as `globular' 
-% remains topic of debate.
-% GCs are observed at scales ranging from clusters of galaxies down to 
-% dwarf galaxies 
-% \todo[inline]{
-%     \citep[for recent reviews, see e.g.][]{2006ARA&A..44..193B, 2014CQGra..31x4006K}
-% }
-% 
-% The properties of the GCs themselves are correlated with those of their host
-% galaxies, in particular their metallicities. 
-% \todo[inline]{
-%     `The mean metallicities of GC systems have long been 
-%     known to scale with the metallicity of their host (van den Bergh
-%     1975; Brodie \& Huchra 1991)' \citep[from][]{2008ApJ...681..197P}
-% }
+Globular clusters (GCs) are old, ubiquitous, bright, and amongst the simplest
+stellar configurations in the Universe. They inherit properties from their natal
+gas, and the properties of globular cluster systems correlate with those of
+(the field stars in) their host galaxies. In theory, this means that GC systems 
+are excellent tracers of the formation and evolution of their host galaxies, if 
+the formation of the GCs themselves is well-understood.
 
 \todo[inline]{Paragraph: Theories of GC formation}
+
+% \begin{itemize}
+%     \item \citet{2005MNRAS.364..367D}: ``The radial profile of the stellar halo
+%     and metal-poor globular clusters of the Milky Way suggest that these components 
+%     formed in rare early peaks above $2.5 \sigma$ at redshift above 10. ''
+% 
+%     \item \citet{2017MNRAS.465.3622R}: ``GCs among oldest astrophysical objects.
+%     GCs form in the early Universe in highest density peaks
+%     \citep[e.g.][]{2005MNRAS.364..367D, 2009ApJ...706L.192B}''
+% 
+%     \item ``Hence, they witness most of the formation and evolution processes
+%     of galaxies, and can be used to probe them'' \citep{2006ARA&A..44..193B}
+% \end{itemize}
+
 \begin{itemize}
@@
 \end{itemize}
-
-% \begin{itemize}
-%     \item \citet{2005MNRAS.364..367D}: ``The radial profile of the stellar halo
-%     and metal-poor globular clusters of the Milky Way suggest that these components 
-%     formed in rare early peaks above $2.5 \sigma$ at redshift above 10. ''
-% 
-%     \item \citet{2017MNRAS.465.3622R}: ``GCs among oldest astrophysical objects.
-%     GCs form in the early Universe in highest density peaks
-%     \citep[e.g.][]{2005MNRAS.364..367D, 2009ApJ...706L.192B}''
-% 
-%     \item ``Hence, they witness most of the formation and evolution processes
-%     of galaxies, and can be used to probe them'' \citep{2006ARA&A..44..193B}
-% \end{itemize}
 

### 2019-03-24 tmp.tex
Wrote paragraph0 of the introduction

Introduction: GC properties correlate with those of their host galaxies,
particularly the metallicities.

In the local universe, we see massive star clusters forming wherever
there are high star formation rate (SFR) surface densities
( Larsen \& Richtler 2000), providing a connection that suggests
that the properties of star cluster populations (age, metallicity,
mass) should scale quite closely with field stars formed in the same
events. The properties of globular cluster systems do in fact correlate
strongly with the properties of the field stars of their host
galaxies. The mean metallicities of GC systems have long been
known to scale with the metallicity of their host (van den Bergh
1975; Brodie \& Huchra 1991), and the mean metallicities of both
the metal-rich and metal-poor subpopulations also correlate with
the luminosity and mass of the host galaxy (Larsen et al. 2001;
Peng et al. 2006a, hereafter Paper IX, and references therein).
However, if GC systems directly followed the underlying field
light in every way, they might be less interesting. For instance,
although the metallicities of GC systems may track those of galaxies, 
they are consistently offset to lower values by 0.5–0.8 dex
in [Fe/H] (e.g., Jordan et al. 2004a; Lotz et al. 2004). Most conspicuously,
even the most massive and metal-rich galaxies have
GC systems dominated by metal-poor star clusters ([Fe/H] >= 1).
This suggests a disconnect between the formation of ``halo'' stellar
populations and the bulk of the galaxy.
\citep[from][]{2008ApJ...681..197P}

### 2019-03-24 AurigaGCS.tex
Second paragraph of introduction: two GC subpopulations

@@
 \section{Introduction}
-Globular clusters (GCs) are old, ubiquitous, bright, and amongst the simplest
-stellar configurations in the Universe. They inherit properties from their natal
-gas, and the properties of globular cluster systems correlate with those of
-(the field stars in) their host galaxies. In theory, this means that GC systems 
-are excellent tracers of the formation and evolution of their host galaxies, if 
-the formation of the GCs themselves is well-understood.
+Globular clusters (GC)s are omnipresent, bright, old, and amongst the simplest
+stellar configurations in the Universe. Their visbility and ubiquity make it 
+possible to obtain integrated GC quantities of galaxies in the Local Group. 
+Moreover, GCs inherit characteristics from their natal gas and GC systems show 
+correlations with properties of (the field stars in) their host galaxies. For 
+example, the mean metallicity of GC systems in early-type galaxies correlates with 
+the galactic metallicity (van den Bergh 1975, Brodie \& Huchra 1991) as well as 
+with the luminosity and possibly the mass (Larsen 2001; Peng 2006). The old ages
+are consistent with formation before, during, or shortly after the initial
+collapse of the proto-galaxy. In theory, all of these characteristics make GC
+systems excellent tracers of the formation and evolution of their parent galaxies,
+if the formation of GCs themselves is well-understood.
 
-\todo[inline]{Paragraph: Theories of GC formation}
+Most galaxies host GC systems with a bimodal colour distribution, indicative of
+a bimodal metallicity distribution. The Milky Way (MW) GC system (GCS) can be
+split up in a metal-rich (red) and metal-poor (blue) subpopulation divided at
+[Fe/H]~$=-1$ \citep[e.g.][]{Harris2001}, although slightly different values can
+also be found in the literature. The two subpopulations are believed to be
+associated to the galactic disk, respectively the stellar halo 
+\citep{1985ApJ...293..424Z}. The latter is supported by observed similarities 
+between the spatial distribution and chemical signature of the `blue' GCs show 
+and stars in the stellar halo \citep{2008A&ARv..15..145H}. Moreover, relative 
+age-estimates show an offset of $1.5$~Gyr between both subpopulations 
+\citep{2005AJ....130..116D}.
+
+\citet{2006ARA&A..44..193B} review extragalactic GCs and galaxy 
+formation, and argue that the observed metal-rich and metal-poor
 

### 2019-03-25 AurigaGCS.tex
Added plot of mean vs stdev of FeH and Rgc distributions

@@
 stellar configurations in the Universe. Their visbility and ubiquity make it 
-possible to obtain integrated GC quantities of galaxies in the Local Group. 
+possible to obtain integrated GC quantities within the Virgo Supercluster.
 Moreover, GCs inherit characteristics from their natal gas and GC systems show 
-correlations with properties of (the field stars in) their host galaxies. For 
-example, the mean metallicity of GC systems in early-type galaxies correlates with 
-the galactic metallicity (van den Bergh 1975, Brodie \& Huchra 1991) as well as 
-with the luminosity and possibly the mass (Larsen 2001; Peng 2006). The old ages
+correlations with properties of (the field stars in) their host galaxies.
+% For 
+% example, the mean metallicity of GC systems in early-type galaxies correlates with 
+% the galactic metallicity (van den Bergh 1975, Brodie \& Huchra 1991) as well as 
+% with the luminosity, and possibly the mass (Larsen 2001; Peng 2006).
+The old ages
 are consistent with formation before, during, or shortly after the initial
-collapse of the proto-galaxy. In theory, all of these characteristics make GC
-systems excellent tracers of the formation and evolution of their parent galaxies,
-if the formation of GCs themselves is well-understood.
+collapse of the proto-galaxy and GCs have been present within galaxies for nearly
+a Hubble time. In theory, all of these characteristics make GC systems excellent
+tracers of the formation and evolution of their parent galaxies, if the formation 
+of GCs themselves is well-understood.
 
@@
 associated to the galactic disk, respectively the stellar halo 
-\citep{1985ApJ...293..424Z}. The latter is supported by observed similarities 
+\citep[e.g.][]{1985ApJ...293..424Z}. The latter is supported by observed similarities 
 between the spatial distribution and chemical signature of the `blue' GCs show 
 and stars in the stellar halo \citep{2008A&ARv..15..145H}. Moreover, relative 
-age-estimates show an offset of $1.5$~Gyr between both subpopulations 
-\citep{2005AJ....130..116D}.
+age-estimates indicate that the metal-poor subpopulation may be $1.5$~Gyr younger 
+than the metal-rich counterpart \citep{2005AJ....130..116D}.
 
-\citet{2006ARA&A..44..193B} review extragalactic GCs and galaxy 
-formation, and argue that the observed metal-rich and metal-poor
+Several formation scenarios could explain the observed bimodality, see 
+\citet{2006ARA&A..44..193B} for a review of extragalactic GCs and galaxy 
+formation. The authors argue that the observed metal-rich and metal-poor
 
@@
 \subsubsection*{Distribution of total GC mass in metallicity-radial bins}
-In Fig.~\ref{fig:MW-FeHRgc} we show the two-dimensional mass-weighted 
+In Figure~\ref{fig:MW-FeHRgc} we show the two-dimensional mass-weighted 
 metallicity-radial distribution of the MW GCS. In Sec.~\ref{sec:FeHRgc} 
@@
 and $85$ GCs in M31 for which age-estimates are available in CR16, see 
-Fig.~\ref{fig:MW-M31-age}.
+Figure~\ref{fig:MW-M31-age}.
 
 \begin{figure}
-    \includegraphics[width=\columnwidth]{{MW_M31_Age_HistogramMassWeighted}.png}
+    \includegraphics[width=\columnwidth]{{MW_M31_Age_HistogramMassWeighted_Msun}.png}
     \caption{
@@
 We define GC candidates in the Auriga simulations as all star particles older 
-than $10$~Gyr based on the age distribution of the MW GCS in 
-Fig.~\ref{fig:MW-M31-age} and following \citet{2017MNRAS.465.3622R}.
+than $10$~Gyr based on the MW GCS age distribution (Figure~\ref{fig:MW-M31-age}),
+and following \citet{2017MNRAS.465.3622R}.
 
-Through out the analysis we use six sub sets of star particles: 
-\emph{all stars}, and \emph{old stars} (age $>10$~Gyr, GC candidates hereafter). 
-Both sub sets are further split up in (old) star particles that have formed 
-\emph{in-situ} (bound to the most-massive halo/subhalo in the first snapshot that 
-the star particle was recorded), and (old) \emph{accreted} star particles (i.e. 
-those that have formed ex-situ and are bound to the most-massive halo/subhalo
-at $z=0$).
+Trough out the analysis we mainly use three subsets of star particles, the 
+\emph{old stars} (age $>10$~Gyr, or GC candidates), the \emph{old insitu} stars
+(defined as those bound to the most-massive halo/subhalo in the first snapshot 
+that the particle was recorded), and the \emph{old accreted} star particles
+(i.e. those that have formed ex-situ and are bound to the most-massive halo/subhalo 
+at $z=0$). In addition, we include \emph{all stars} (no selection criterion) to 
+examine the result of (not) applying an age cut to our selection functions.
 
-In Sec.~\ref{sec:metallicity} we investigate the metallicity distribution of the
-GC candidates, in Sec.~\ref{sec:radial} we show the distribution of galactocentric
-radii of the globular cluster candidates within the Auriga simulations, and we 
-combine both in Sec.~\ref{sec:FeHRgc}. 
-% We continue our analysis with an investigation
-% of the properties of the proto-galaxies at times of birth of the accreted globular 
-% cluster population in Sec.~\ref{sec:birth-properties-of-accreted-gc-candidates}
+We consider the metallicity distribution in Sec.~\ref{sec:metallicity} 
+the distribution of galactocentric radii in Sec.~\ref{sec:radial}, and the
+combination of both in Sec.~\ref{sec:FeHRgc}.
 
@@
 We investigate whether the star formation model implemented in the Auriga 
-simulations is capable of producing sufficient mass in old star particles in 
-each metallicity bin in comparison to the Milky Way and Andromeda globular 
-cluster systems. In Fig.~\ref{fig:FeH} we show a mass-weighted metallicity 
+simulations is capable of i) producing a metallicity distribution that is 
+consistent with the GCS observed in the MW (M31), and ii) generating sufficient 
+mass over the full domain of the observations.
+
+In Figure~\ref{fig:FeH} we show a mass-weighted metallicity 
 distribution where the lines show the median value of all thirty Auriga level 4 
@@
 the observed profiles.
+
+\begin{figure}
+    \includegraphics[width=\columnwidth]{{FeH_mu_sigma}.png}
+    \caption{
+        \label{fig:FeH_mu_sigma}
+    }
+\end{figure}
 
@@
 \label{sec:radial}
+
+\begin{figure}
+    \includegraphics[width=\columnwidth]{{Rgc_mu_sigma}.png}
+    \caption{
+        \label{fig:Rgc_mu_sigma}
+    }
+\end{figure}
 
@@
 and radial bins and use the term `efficiency' to refer to the combined product
-of bound cluster formation and globular cluster disruption. In Fig.~\ref{fig:todo} 
+of bound cluster formation and globular cluster disruption. In Figure~\ref{fig:todo} 
 we show the efficiencies that we find when we compare the simulations to the 
@@
 Although the age distribution of M31 Perhaps an age cut of 6~Gyr would would be more 
-appropriate for M31, see Fig.~\ref{fig:MW-M31-age}.
+appropriate for M31, see Figure~\ref{fig:MW-M31-age}.
 
@@
 
-Fig.~\ref{fig:logMFeH_res} shows the mass-weighted metallicity distribution, 
-Fig.~\ref{fig:logMRgc_res} shows the mass-weighted radial distribution, and
-Fig.~\ref{fig:logMRgcFeH_res}
+Figure~\ref{fig:logMFeH_res} shows the mass-weighted metallicity distribution, 
+Figure~\ref{fig:logMRgc_res} shows the mass-weighted radial distribution, and
+Figure~\ref{fig:logMRgcFeH_res}
 
@@
     \includegraphics[width=0.31\textwidth]{{logMFeH_Au24}.png}
-    \caption{Same as Fig.~\ref{fig:FeH}, but here the colours indicate resolution
+    \caption{Same as Figure~\ref{fig:FeH}, but here the colours indicate resolution
         level: L3 green, L4 orange, and L5 blue. \emph{Left:} Auriga halo 6.
@@
     \includegraphics[width=0.31\textwidth]{{logMRgc_Au24}.png}
-    \caption{Same as Fig.~\ref{fig:Rgc}, but here the colours indicate resolution
+    \caption{Same as Figure~\ref{fig:Rgc}, but here the colours indicate resolution
         level: L3 green, L4 orange, and L5 blue. \emph{Left:} Auriga halo 6.

### 2019-03-26 AurigaGCS.tex
Mass-weighted Rgc-FeH plot of MW and M31 without scattering the observed points

@@
 
-\todo[inline]{
-TODO: paraphrase ``The diversity in morphological properties of these simulated 
-galaxies reflects the stochasticity inherent to the process of galaxy formation 
-and evolution 
-\citep[e.g.][]{2005ApJ...635..931B, 2010MNRAS.406..744C, 2010ApJ...708.1398T}.''
-}
+The Auriga suite has a fiducial resolution level L4, accompanied by the lower 
+(higher) level L5 (L3) that is available for selected initial condition runs.
+The baryonic mass resolution in order of increasing level is $m_b$~=~[$4 \times 10^5$,
+$5 \times 10^4$, $6 \times 10^3$]~M\Sun \, with gravitational softening of 
+collissionless particles $\epsilon$~=~[$738, 369, 184$]~pc.
 
-\todo[inline]{Paragraph about Auriga's stellar haloes.
-``The Auriga Stellar Haloes: Connecting stellar population properties with
-accretion and merging history'' \citet{2018arXiv180407798M}
-}
+% \todo[inline]{
+% TODO: paraphrase ``The diversity in morphological properties of these simulated 
+% galaxies reflects the stochasticity inherent to the process of galaxy formation 
+% and evolution 
+% \citep[e.g.][]{2005ApJ...635..931B, 2010MNRAS.406..744C, 2010ApJ...708.1398T}.''
+% }
+% 
+% \todo[inline]{Paragraph about Auriga's stellar haloes.
+% ``The Auriga Stellar Haloes: Connecting stellar population properties with
+% accretion and merging history'' \citet{2018arXiv180407798M}
+% }
 
@@
     \caption{
-        \emph{Top}: Mass-weighted r$_{\text{gc}}$-[Fe/H] distribution of
+        \emph{Top}: Mass-weighted R$_{\text{GC}}$-[Fe/H] distribution of
         151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
@@
         \emph{Bottom}: Same for M31, showing 366 GCs and 88.38 \% of the total 
-        mass in CR16 \citep[data from][]{2016ApJ...824...42C}.
+        mass in CR16 \citep[data from][]{2016ApJ...824...42C}. Note that the
+        range of the colourmap differs in both figures.
         \label{fig:MW-FeHRgc}
@@
 consistent with the GCS observed in the MW (M31), and ii) generating sufficient 
-mass over the full domain of the observations.
-
-In Figure~\ref{fig:FeH} we show a mass-weighted metallicity 
-distribution where the lines show the median value of all thirty Auriga level 4 
-haloes for \emph{all stars} (orange dotted), \emph{old stars / GC candidates} 
-(orange solid), \emph{old in-situ} stars (blue solid), and \emph{old accreted} stars
-(red solid). The shaded regions indicate the $1\sigma$ interval around the median 
-(i.e. the scatter between runs with different initial conditions and merger
-histories). The MW (M31) GCS is shown in purple (magenta). We use the 
-same bin sizes for the simulations as for the observations, explicitly shown for
-the observed profiles.
+mass over the domain of the observations.
 
@@
 \end{figure}
+
+Figure~\ref{fig:FeH} shows a mass-weighted metallicity distribution of the
+Auriga L4 median
+for \emph{all stars} (orange dotted), \emph{old stars / GC candidates} 
+(orange solid), \emph{old in-situ} stars (blue solid), and \emph{old accreted} stars
+(red solid). The shaded regions indicate the $1\sigma$ interval around the median 
+(i.e. the scatter between runs with different initial conditions and merger
+histories). The MW (M31) GCS is shown in purple (magenta). We use the 
+same bin sizes for the simulations as for the observations, explicitly shown for
+the observed profiles.
 

### 2019-03-26 AurigaGCS.tex
Some fixes for data section, and split what we see (results) from what we interprete (discussion)

@@
 
-\section{Relevant observational data}
+\section{Observational data}
 \label{sec:observations}
@@
 
-\subsubsection*{Age estimates}
+\subsubsection{Age estimates}
 We supplement H96e10 with age-estimates from isochrone fits to stars
@@
 below $10$~Gyr.
-
-\subsubsection*{Distribution of total GC mass in metallicity-radial bins}
-In Figure~\ref{fig:MW-FeHRgc} we show the two-dimensional mass-weighted 
-metallicity-radial distribution of the MW GCS. In Sec.~\ref{sec:FeHRgc} 
-we investigate whether the star formation model implemented in the Auriga 
-simulations can produce sufficient total mass in GC candidates in the same bins.
-
-\begin{figure}
-    \includegraphics[width=\columnwidth]
-        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
-    \includegraphics[width=\columnwidth]
-        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data}.png}
-    \caption{
-        \emph{Top}: Mass-weighted R$_{\text{GC}}$-[Fe/H] distribution of
-        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
-        is 98.19 \% of the total MW GCS mass in the Harris catalog.
-        \emph{Bottom}: Same for M31, showing 366 GCs and 88.38 \% of the total 
-        mass in CR16 \citep[data from][]{2016ApJ...824...42C}. Note that the
-        range of the colourmap differs in both figures.
-        \label{fig:MW-FeHRgc}
-    }
-\end{figure}
 
@@
 relevant fields in the CR16 dataset that we use are the age, metallicity, and the 
-mass-estimate\footnote{The authors assumed $M/L_V = 2$ (independent of [Fe/H])}.
+mass-estimate\footnote{The authors assumed $M/L_V = 2$ independent of [Fe/H]}.
 
@@
 
-\subsubsection*{Age estimates}
+\subsubsection{Age estimates}
 For M31 we find an age distribution with a mean value of 11.0$\pm 0.2$~Gyr and a 
@@
 
-\subsubsection*{Calculation of galactocentric radius}
-The projected galacocentric radius $R_{\text{proj}}$ is calculated following
-\citet[][Sec.~4.1, eq.~4]{2019arXiv190111229W}. Specifically,
-\begin{align}
-    X &= A \sin{(\text{PA})} + B \cos{(\text{PA})} \nonumber \quad \text{and} \\
-    Y &= - A \cos{(\text{PA})} + B \sin{(\text{PA})} \text{,}
-\end{align}
-where $A = \sin{(\alpha - \alpha_0)} \cos{\delta}$ and
-$B = \sin\delta \cos\delta_0 - \cos{(\alpha - \alpha_0)} \cos\delta \sin\delta_0$
-for the right ascension $\alpha$ (hourangle) and declination $\delta$ (degree) 
-of the GCs. For the central position of M31 we take the preferred position 
+\subsection{Total GC mass in metallicity-radial space}
+\label{sec:observations_FeHRgc}
+We show the two-dimensional mass-weighted metallicity-radial distribution of the 
+MW (M31) GCS in the top (bottom) panel of Figure~\ref{fig:observations_FeHRgc}. Both
+quantities are readily available in H96e10, but the galactocentric radius
+of GCs in M31 is not available in CR16. Therefore we follow 
+\citet[][Sec.~4.1]{2019arXiv190111229W} to calculate the projected radius 
+$R_{\text{proj}}$ from the observed positions, adopting M31's central position
 from the NASA Extragalactic Database\footnote{\url{https://ned.ipac.caltech.edu/}} 
-entry of M31: $(\alpha_0, \, \delta_0) = 
-(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$.
-The projected galactocentrid radius is calculated as $R_\text{proj} = 
-\sqrt{X^2 + Y^2}$ (for $X$ and $Y$ in arcsec), and using the small angle 
-approximation with a distance of $D_{\text{M31}} = 778$~kpc to convert to kpc.
-TODO: McConnachie et al. 2005; Conn  et  al. 2012. Finally, we convert the 
-projected distance ($R_{\text{proj}}$) to an `average deprojected distance` 
-via the relationship $R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$.
+$(\alpha_0, \, \delta_0) = 
+(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$ 
+and distance $D_{\text{M31}} = 778$~kpc (McConnachie et al. 2005; Conn  et  al. 2012).
+We calculate $R_{\text{GC}}$ as `average deprojected distance`
+$R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$.
+We compare these observations to the Auriga simulations later on in 
+Section~\ref{sec:discussion_FeHRgc},
+
+\begin{figure}
+    \includegraphics[width=\columnwidth]
+        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
+    \includegraphics[width=\columnwidth]
+        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data}.png}
+    \caption{
+        \emph{Top}: Mass-weighted R$_{\text{GC}}$-[Fe/H] distribution of
+        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
+        is 98.19 \% of the total MW GCS mass in the Harris catalog.
+        \emph{Bottom}: Same for M31, showing 366 GCs and 88.38 \% of the total 
+        mass in CR16 \citep[data from][]{2016ApJ...824...42C}. Note that the
+        range of the colourmap differs in both figures.
+        \label{fig:observations_FeHRgc}
+    }
+\end{figure}
 
@@
 
-We consider the metallicity distribution in Sec.~\ref{sec:metallicity} 
-the distribution of galactocentric radii in Sec.~\ref{sec:radial}, and the
+We consider the metallicity distribution in Sec.~\ref{sec:results_FeH} 
+the distribution of galactocentric radii in Sec.~\ref{sec:results_Rgc}, and the
 combination of both in Sec.~\ref{sec:FeHRgc}.
@@
 \subsection{Metallicity distribution}
-\label{sec:metallicity}
+\label{sec:results_FeH}
 We investigate whether the star formation model implemented in the Auriga 
@@
     \caption{
+        Mean and standard deviation of the metallicity distribution of star
+        particles in our Auriga subsets compared to the MW (M31) GCS shown in
+        purple (magenta). The black solid (open) dot shows values of the 
+        metal-rich (metal-poor) component of the MW GCS as quoted by
+        \citep[][p. 38]{1998gcs..book.....A}.
         \label{fig:FeH_mu_sigma}
@@
 
-Figure~\ref{fig:FeH} shows a mass-weighted metallicity distribution of the
-Auriga L4 median
-for \emph{all stars} (orange dotted), \emph{old stars / GC candidates} 
+Figure~\ref{fig:FeH_mu_sigma} shows the mean and standard deviation of the
+[Fe/H] distribution of star particles in the Auriga simulations. The mean
+metallicity of old star particles lies in the range $-1.0$ to $-0.5$ and the
+dispersion increases with decreasing metallicity. For comparison, the mean
+of all star particles populates the range $-0.25$ to $0$ with a near-constant
+dispersion a bit above $0.5$. Old accreted stars in the Auriga haloes reach
+mean metallicities between $-1.5$ and $-1.0$, which is considerably lower than 
+the old- and old insitu populations. Most Auriga L4 haloes have old insitu 
+populations with mean metallicities around $-0.5$. The old accreted populations 
+follow the trent of increasing dispersion with decreasing mean metallicity, but 
+notably the old insitu populations all have a constant dispersion of roughly
+$0.45$. We show the values calculated using all MW (M31) GCs in purple (magenta),
+and literature values of the metal-rich (metal-poor) component of the MW GCS
+as black solid (open) dots.
+
+Figure~\ref{fig:FeH} shows the mass-weighted metallicity distribution of the
+Auriga L4 haloes. Lines show the median value and the shaded regions indicate 
+the $1\sigma$ interval (i.e. scatter between runs with different initial 
+conditions which thus have unique merger histories). We notice once more that
+the peak metallicity shifts from $0$ to $-0.5$ for old stars (orange solid)
+compared to all stars (orange dotted).
 (orange solid), \emph{old in-situ} stars (blue solid), and \emph{old accreted} stars
-(red solid). The shaded regions indicate the $1\sigma$ interval around the median 
-(i.e. the scatter between runs with different initial conditions and merger
-histories). The MW (M31) GCS is shown in purple (magenta). We use the 
+(red solid). 
+of \emph{all stars} (orange dotted),
+
+The MW (M31) GCS is shown in purple (magenta). We use the 
 same bin sizes for the simulations as for the observations, explicitly shown for
@@
 
-Furthermore we test the null hypothesis that the metallicity distribution of the
-MW (M31) GCS and the \emph{old}, \emph{old insitu}, and \emph{old accreted} star 
-particles in the Auriga simulations are drawn from the same underlying 
-distribution. We calculate the two-sample Kolmogorov-Smirnov test statistic for
-all thirty Auriga level 4 haloes and reject the null hypothesis for every halo, 
-for every sub set of star particles at least at the 99.99\% confidence level.
-In addition, the null hypothesis that the metallicity distributions of the MW 
-and M31 GCS are drawn from the same distribution is rejected at the 99.99997\%
-confidence level.
-
 % We notice a scatter\footnote{Here scatter means the width of the 1$\sigma$ interval.
@@
 \subsection{Radial distribution}
-\label{sec:radial}
+\label{sec:results_Rgc}
 
@@
 
-Is the spatial distribution of the GC candidates in the Auriga simulations consistent with the MW GCS?
-
-\subsection{Metallicity-radial distribution}
-\label{sec:FeHRgc}
-What age-metallicity distribution is produced by star formation events in the Auriga simulations?
-?
 \begin{figure}
@@
 
+\subsection{Total mass in metallicity-radial space}
+\label{sec:results_FeHRgc}
 \begin{figure}
@@
 
-\subsection{Metallicity-radial distribution: higher resolution}
-\todo[inline]{Do we even want this?}
-\label{sec:FeHRgc-morebins}
-\begin{figure}
-    \includegraphics[width=\columnwidth]
-        {{logMRgcFeH_accreted-insitu-notitle}.png}
-    \caption{
-        TODO: add 1$\sigma$ interval around both relations, and flip x and y.
-        \label{fig:todo2}
+\section{Discussion}
+\label{sec:discussion}
+\subsection{Metallicity distribution}
+\label{sec:discussion_FeH}
+\citet[][p. 234]{1998gcs..book.....A} and \citet[][p. 38]{Harris2001} describe
+the bimodal [Fe/H] distribution of the MW GCS. The latter fits a double
+Gaussian that peaks at [Fe/H] = $-1.59$ (metal-poor) and $-0.51$ (metal-rich)
+with dispersions of $0.34$ and $0.23$. T
+KMM mixture-modeling
+
+Furthermore we test the null hypothesis that the metallicity distribution of the
+MW (M31) GCS and the \emph{old}, \emph{old insitu}, and \emph{old accreted} star 
+particles in the Auriga simulations are drawn from the same underlying 
+distribution. We calculate the two-sample Kolmogorov-Smirnov test statistic for
+all thirty Auriga level 4 haloes and reject the null hypothesis for every halo, 
+for every sub set of star particles at least at the 99.99\% confidence level.
+In addition, the null hypothesis that the metallicity distributions of the MW 
+and M31 GCS are drawn from the same distribution is rejected at the 99.99997\%
+confidence level.
+
+\subsection{Radial distribution}
+\label{sec:discussion_Rgc}
+
+\subsection{Metallicity-radial space}
+\label{sec:discussion_FeHRgc}
+See Figure~\ref{fig:observations_FeHRgc} in Section~\ref{sec:observations_FeHRgc}.
+
+\todo[inline]{
+``The fraction of all star formation that occurs in bound stellar clusters (the cluster formation efficiency, hereafter CFE) follows by integration of these local clustering and survival properties over the full density spectrum of the ISM, and hence is set by galaxy-scale physics.
+We derive the CFE as a function of observable galaxy properties, and find that it increases with the gas surface density'' \citep{2012MNRAS.426.3008K}
 }
-\end{figure}
+
+\subsection{Age cut}
+Although the age distribution of M31 Perhaps an age cut of 6~Gyr would would be more 
+appropriate for M31, see Figure~\ref{fig:MW-M31-age}.
+
+\todo[inline]{
+\citet{2016ApJ...824...42C} writes:
+``there are two broad, well-established differences:
+(1) the M31 GC system is more populous than the MW system, by a factor of
+$\sim$2-3, and (2) it does not exhibit the same obvious bimodality in
+metallicity \citep{2000AJ....119..727B, 2009A&A...508.1285G, 2011AJ....141...61C, 
+2013A&A...549A..60C}. Both of these aspects may be reflections of dramatic 
+differences discovered in these galaxies stellar halos, where the M31 halo 
+appears much more metal-enriched, with massive substructures suggesting a more 
+active satellite accretion history \citep[e.g.][]{2009Natur.461...66M}''
+}
 
@@
 globular cluster systems of the Milky Way as well as that of Andromeda (M31).
-
-\subsection{Properties of birth haloes of the accreted population}
-\label{sec:birth-properties-of-accreted-gc-candidates}
-
-Auriga galaxy /w 5 Myr snapshots.
-
-\subsection{Age-metallicity distribution}
-\label{sec:agemetallicity}
-What age-metallicity distribution is produced by star formation events in the Auriga simulations?
-
-\subsection{Formation history} 
-\label{sec:history}
-Can we identify particular star formation events that generate GC candidates with the correct age, metallicity, and radial properties as expected or the MW GCS?
-
-Can we distinguish between particles that have formed in-situ and those that have been accreted?
-Can we identify specific features in the age-metallicity plane, or in the $R_\textbf{GC}$-[Fe/H] plane, that result from one of both populations?
-How does this connect to proposed mechanisms for globular cluster formation in the literature?
-
-Orbits: are the pericentres different? Look at velocity + specific angular momentum distribution in the different FeH/Rgc bins as proxy for the pericenter
-
-\section{Discussion}
-\label{sec:discussion}
-
-We investigate all star particles in the Auriga simulations that are older than 10~Gyr,
-an approach equal to the method of \citep{2017MNRAS.465.3622R}. This approach does not
-take the bound cluster fraction \citep[e.g.][]{2012MNRAS.426.3008K} into account. This
-means that our sub set, which is based on selection by age, comprises both stars in the
-field as well as globular clusters. We compare the total mass in the simulations in 
-metallicity ([Fe/H]), galactocentric radius $R_{\text{GC}}$, and [Fe/H]-$R_{\text{GC}}$ 
-bins to the total mass in the MW GCS (using the H96e10 data set). The mass excess in the
-simulations gives a maximum mass loss `budget' for the product of cluster formation 
-efficiency and dynamical evolution. We find fractions that vary with metallicity,
-radius and metallicity-and-radius.
-
-\todo[inline]{
-``The fraction of all star formation that occurs in bound stellar clusters (the cluster formation efficiency, hereafter CFE) follows by integration of these local clustering and survival properties over the full density spectrum of the ISM, and hence is set by galaxy-scale physics.
-We derive the CFE as a function of observable galaxy properties, and find that it increases with the gas surface density'' \citep{2012MNRAS.426.3008K}
-}
-
-\subsection{Age cut}
-Although the age distribution of M31 Perhaps an age cut of 6~Gyr would would be more 
-appropriate for M31, see Figure~\ref{fig:MW-M31-age}.
-
-\todo[inline]{
-\citet{2016ApJ...824...42C} writes:
-``there are two broad, well-established differences:
-(1) the M31 GC system is more populous than the MW system, by a factor of
-$\sim$2-3, and (2) it does not exhibit the same obvious bimodality in
-metallicity \citep{2000AJ....119..727B, 2009A&A...508.1285G, 2011AJ....141...61C, 
-2013A&A...549A..60C}. Both of these aspects may be reflections of dramatic 
-differences discovered in these galaxies stellar halos, where the M31 halo 
-appears much more metal-enriched, with massive substructures suggesting a more 
-active satellite accretion history \citep[e.g.][]{2009Natur.461...66M}''
-}
 

### 2019-03-26 AurigaGCS.tex
Implemented Sec. 4.1 Results / Metallicity distribution

@@
 We compare these observations to the Auriga simulations later on in
-Section~\ref{sec:discussion_FeHRgc},
+Sec.~\ref{sec:discussion_FeHRgc},
 
@@
 the distribution of galactocentric radii in Sec.~\ref{sec:results_Rgc}, and the
-combination of both in Sec.~\ref{sec:FeHRgc}.
+combination of both in Sec.~\ref{sec:results_FeHRgc}.
 
@@
 and literature values of the metal-rich (metal-poor) component of the MW GCS
-as black solid (open) dots.
+as black solid (open) dots. We further discuss the comparison between the
+simulations and the observations in Sec.~\ref{sec:discussion_FeH}
 
@@
 Auriga L4 haloes. Lines show the median value and the shaded regions indicate
-the $1\sigma$ interval (i.e. scatter between runs with different initial 
-conditions which thus have unique merger histories). We notice once more that
-the peak metallicity shifts from $0$ to $-0.5$ for old stars (orange solid)
-compared to all stars (orange dotted).
-(orange solid), \emph{old in-situ} stars (blue solid), and \emph{old accreted} stars
-(red solid). 
-of \emph{all stars} (orange dotted),
-
-The MW (M31) GCS is shown in purple (magenta). We use the 
-same bin sizes for the simulations as for the observations, explicitly shown for
-the observed profiles.
+the $1\sigma$ interval around it (i.e. scatter between runs with different initial
+conditions which thus have unique merger histories). We notice again that
+the peak metallicity shifts down from $0$ to $-0.5$ for old stars (orange solid)
+compared to all stars (orange dotted) while the mass at the peak lowers by 
+roughly one dex. The mass budget of the old stars is
+dominated by the old insitu population (blue solid) below [Fe/H]=$-1$, and by
+the old accreted stars (red solid) above this value. We show the MW (M31) GCS 
+in purple (magenta) and we show the ratio of the simulated to the observed 
+profiles in the middle (bottom) panel. This mass excess can be thought of as a
+combination of the bound cluster formation efficiency and disruptive processes,
+further discussed in Sec.~\ref{sec:discussion_mass_excess}.
 
@@
 \end{figure}
-
-The peak of the distribution shifts down from [Fe/H] $\thicksim 0.0$ to 
-$\thicksim -0.6$ for the \emph{old stars} compared to \emph{all stars} while the 
-mass at the peak lowers by roughly one dex. Moreover, we find that the 
-metallicity range $-3 <$ [Fe/H] $< -1$ is only populated by the GC candidates, 
-while [Fe/H] $> -1$ is dominated by star particles younger than 10~Gyr.
-Furthermore, the \emph{old accreted} sub set contributes most significantly to 
-the range $-3 <$ [Fe/H] $< -1$, and the contribution of the \emph{old in-situ}
-stars at these metallicities declines steeper with declining metallicity 
-than the \emph{old accreted} population. We note that the scatter between different
-Auriga haloes is much smaller than the difference between the MW and M31 GCSs.
-We conclude that old star particles in the Auriga simulation suite as a whole 
-cannot be consistent with both the Milky Way and the Andromeda globular cluster
-system.
-
-The middle (bottom) panel shows the ratio of the simulated mass to the mass in
-the MW (M31) GCS. We observe an increasing trend with increasing metallicity 
-for the Milky Way over the entire range of the data, while the M31 GCS shows
-this increase only in the range [Fe/H]$>$-0.5 (although not for the \emph{old
-accreted} component.
 
@@
 
+Furthermore, 
+We note that the scatter between different
+Auriga haloes is much smaller than the difference between the MW and M31 GCSs.
+We conclude that old star particles in the Auriga simulation suite as a whole
+cannot be consistent with both the Milky Way and the Andromeda globular cluster
+system.
+
+We observe an increasing trend with increasing metallicity
+for the Milky Way over the entire range of the data, while the M31 GCS shows
+this increase only in the range [Fe/H]$>$-0.5 (although not for the \emph{old
+accreted} component.
+
 Furthermore we test the null hypothesis that the metallicity distribution of the
@@
 \label{sec:discussion_FeHRgc}
-See Figure~\ref{fig:observations_FeHRgc} in Section~\ref{sec:observations_FeHRgc}.
+See Figure~\ref{fig:observations_FeHRgc} in Sec.~\ref{sec:observations_FeHRgc}.
 
@@
 \subsection{From star particles to globular clusters}
-\label{sec:star-to-gc}
+\label{sec:discussion_mass_excess}
 Star particles are not globular clusters. Many stars do form in clusters, but

### 2019-03-26 AurigaGCS.tex
Implemented v0.01 of Sec. 4.2, now moving on

@@
         Mean and standard deviation of the metallicity distribution of star
-        particles in our Auriga subsets compared to the MW (M31) GCS shown in
-        purple (magenta). The black solid (open) dot shows values of the
-        metal-rich (metal-poor) component of the MW GCS as quoted by
-        \citep[][p. 38]{1998gcs..book.....A}.
+        particles in each of the thirty Auriga L4 haloes. Orange dots show 
+        the subset of old star particles, and blue (red) dots show the old 
+        insitu (accreted) component. These Auriga subsets can be compared to 
+        the MW (M31) GCS shown in purple (magenta), and to the metal-rich 
+        (metal-poor) component of the MW GCS indicated by the black solid (open) 
+        dots \citep[values from][p. 38]{1998gcs..book.....A}.
         \label{fig:FeH_mu_sigma}
@@
 \end{figure}
-
 Figure~\ref{fig:FeH_mu_sigma} shows the mean and standard deviation of the
-[Fe/H] distribution of star particles in the Auriga simulations. The mean
+[Fe/H] distribution of star particles in all Auriga L4 simulations. The mean
 metallicity of old star particles lies in the range $-1.0$ to $-0.5$ and the
@@
 and literature values of the metal-rich (metal-poor) component of the MW GCS
-as black solid (open) dots. We further discuss the comparison between the
+as black solid (open) dots. We further discuss our comparison between the
 simulations and the observations in Sec.~\ref{sec:discussion_FeH}
-
-Figure~\ref{fig:FeH} shows the mass-weighted metallicity distribution of the
-Auriga L4 haloes. Lines show the median value and the shaded regions indicate
-the $1\sigma$ interval around it (i.e. scatter between runs with different initial
-conditions which thus have unique merger histories). We notice again that
-the peak metallicity shifts down from $0$ to $-0.5$ for old stars (orange solid)
-compared to all stars (orange dotted) while the mass at the peak lowers by 
-roughly one dex. The mass budget of the old stars is
-dominated by the old insitu population (blue solid) below [Fe/H]=$-1$, and by
-the old accreted stars (red solid) above this value. We show the MW (M31) GCS 
-in purple (magenta) and we show the ratio of the simulated to the observed 
-profiles in the middle (bottom) panel. This mass excess can be thought of as a
-combination of the bound cluster formation efficiency and disruptive processes,
-further discussed in Sec.~\ref{sec:discussion_mass_excess}.
 
@@
 \end{figure}
-
-% We notice a scatter\footnote{Here scatter means the width of the 1$\sigma$ interval.
-% The difference between the minimum and maximum values is $0.9$~dex.} in mass
-% normalization of $0.3$ dex between the different Auriga galaxies. We investigate
-% whether there is a correlation between the total stellar mass in (old) star particles
-% and the virial mass\footnote{The virial mass is defined as the mass contained
-% inside the radius $r_{200,c}$ at which the average (spherical) mass density
-% equals two hundred times the critical density of the Universe} $M_{200,c}$ of
-% the host halo. We fit $a \cdot \left(\text{M}_{200,c}[1\text{e}10 \text{M\Sun}]
-% - 140\right) + b$ to log$_{10}\left(\Sigma_{i} m_i(\text{\scriptsize [Fe/H] =
-% -3})\right)$. % \limits_{i, \text{if age(i) $>$ 10~Gyr}}
-% Our fit thus provides the slope $a$ and normalization of (old) stellar mass $b$
-% at [Fe/H]=-3 for $M_{200,c}$ at 140e10~M\Sun. We find $a = 0.00388$, $b = 6.597$
-% and conclude that there is a small positive correlation of mass in (old) star
-% particles with the virial mass of the host halo.
-%
-% \begin{figure}
-% \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_normalization_fit3}.png}
-%     \caption{
-%         Plot of log$_{10}$(mass normalization) [i.e. $b$ obtained above] against
-%         the virial mass M$_{200,c}$ of the Auriga haloes. We fit a linear relation
-%         to see whether there is a correlation, and find $a = 0.00388$, $b = 6.597$.
-%         % Colours indicate resolution: L3 green, L4 orange, and L5 blue.
-%         The red dotted line shows the `central' value of M$_{200,c}$, the yellow
-%         region shows the 1$\sigma$ interval around the best-fit relation, and the
-%         blue dashed lines shows the intrinsic scatter. The error bars show 1\%
-%         of the obtained values.
-%         \label{fig:Mnorm-fit}
-%     }
-% \end{figure}
+Figure~\ref{fig:FeH} shows the mass-weighted metallicity distribution of the
+Auriga L4 haloes. Lines show the median value and the shaded regions indicate
+the $1\sigma$ interval around it (i.e. scatter between runs with different initial
+conditions which thus have unique merger histories). We notice again that
+the peak metallicity shifts down from $0$ to $-0.5$ for old stars (orange solid)
+compared to all stars (orange dotted) while the mass at the peak lowers by 
+roughly one dex. The mass budget of the old stars is
+dominated by the old insitu population (blue solid) below [Fe/H]=$-1$, and by
+the old accreted stars (red solid) above this value. We show the MW (M31) GCS 
+in purple (magenta) and we show the ratio of the simulated to the observed 
+profiles in the middle (bottom) panel. This mass excess can be thought of as a
+combination of the bound cluster formation efficiency and disruptive processes,
+further discussed in Sec.~\ref{sec:discussion_mass_excess}.
 
@@
     \caption{
+        Mean and standard deviation of the radial distribution of star particles
+        in each of the thirty Auriga L4 haloes compared to the MW (M31) GCS 
+        shown in purple (magenta).
         \label{fig:Rgc_mu_sigma}
@@
 \end{figure}
+Figure~\ref{fig:Rgc_mu_sigma} shows the mean and standard deviation of the
+radial distribution of star particles in all Auriga L4 simulations. We notice 
+that the old insitu populations are much more centrally distributed, whereas
+the old accreted component has a larger radial extent. Moreover, the dispersion
+increases with increasing mean value of the radial distribution.
 
@@
 \end{figure}
-
-\todo[inline]{
-    Harris: `Somewhat arbitrarily, I will take the region $r_p > 3$ kpc
-    (containing 75 clusters) as the fiducial Milky Way sample. If we were to
-    view the Milky Way at the same inclination angle to the disk as we see
-    M31, this cutoff in projected distance would correspond roughly to the
-    inner distance limits in the M31 halo sample.'
-}
+Figure~\ref{fig:Rgc} shows the mass-weighted radial distribution of the
+Auriga L4 haloes. We notice a subtle peak around $10$~kpc for all star
+particles that is not present for the old star particles, indicating that the
+stellar disc is no longer present when applying the latter selection criterion.
+Furtermore, we find that the dominant contribution to the total mass in old
+stars changes from those formed insitu to the accreted population around 
+$10$~kpc. We further discuss our comparison between the simulations and the 
+observations in Sec.~\ref{sec:discussion_Rgc}.
 
@@
 \subsection{Total mass in metallicity-radial space}
+We investigate whether the Auriga simulations still produce sufficient mass in 
+old star particles to be consistent with the MW (M31) GCS when two-dimensionally 
+binned in both [Fe/H] and $R_\text{GC}$. We sum the total simulated mass in 
+each bin and then divide it by the total mass in the MW (M31) GCS. We show this
+mass excess in Figure~\ref{}, respectively Figure~\ref{}
 \label{sec:results_FeHRgc}
@@
 \label{sec:discussion_Rgc}
+
+\todo[inline]{
+    Harris: `Somewhat arbitrarily, I will take the region $r_p > 3$ kpc
+    (containing 75 clusters) as the fiducial Milky Way sample. If we were to
+    view the Milky Way at the same inclination angle to the disk as we see
+    M31, this cutoff in projected distance would correspond roughly to the
+    inner distance limits in the M31 halo sample.'
+}
 

### 2019-03-26 AurigaGCS.tex
R of radius wrapped in LaTeX math

@@
     \caption{
-        \emph{Top}: Mass-weighted R$_{\text{GC}}$-[Fe/H] distribution of
+        \emph{Top}: Mass-weighted $R_{\text{GC}}$-[Fe/H] distribution of
         151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
@@
     \caption{
-        Mass-weighted [Fe/H]-R$_{\text{GC}}$ distribution of all Auriga haloes
+        Mass-weighted [Fe/H]-$R_{\text{GC}}$ distribution of all Auriga haloes
         (level 3, 4 and 5). Here we consider the old ($>$~10~Gyr) stars in all

### 2019-03-27 AurigaGCS.tex
Images for Sec. 4.3 v0.1

@@
 
+\subsection{Total mass in metallicity-radial space}
+\label{sec:results_FeHRgc}
+
+We investigate whether the Auriga simulations still produce sufficient mass in 
+old star particles to be consistent with the MW (M31) GCS when two-dimensionally 
+binned in both [Fe/H] and $R_\text{GC}$. We sum the total simulated mass in 
+each bin and then divide it by the total mass in the MW (M31) GCS. We show this
+mass excess in Figure~\ref{}, respectively Figure~\ref{}
 \begin{figure}
     \includegraphics[width=0.49\textwidth]
-        {{Au-all_RgcFeH_HistogramMassWeighted_iold_mean}.png}
+        {{Au-all_RgcFeH_HistogramMassWeighted_iold_36bins_mean}.png}
     \caption{
@@
 
-\subsection{Total mass in metallicity-radial space}
-We investigate whether the Auriga simulations still produce sufficient mass in 
-old star particles to be consistent with the MW (M31) GCS when two-dimensionally 
-binned in both [Fe/H] and $R_\text{GC}$. We sum the total simulated mass in 
-each bin and then divide it by the total mass in the MW (M31) GCS. We show this
-mass excess in Figure~\ref{}, respectively Figure~\ref{}
-\label{sec:results_FeHRgc}
 \begin{figure}
     \includegraphics[width=0.49\textwidth]
-        {{Au-all_RgcFeH_HistogramMassWeighted_iold_36bins_mean-trim}.png}
+        {{Au-all_RgcFeH_HistogramMassWeighted_MW_iold_36bins_mean}.png}
+    \includegraphics[width=0.49\textwidth]
+        {{Au-all_RgcFeH_HistogramMassWeighted_M31_iold_36bins_mean}.png}
     \caption{
-        Ratio
+        Caption
         \label{fig:Au-FeHRgc-ratio}

### 2019-04-25 AurigaGCS.tex
Wrote four paragraphs for the introduction (deliberately w/o references)

@@
 Globular clusters (GC)s are omnipresent, bright, old, and amongst the simplest
-stellar configurations in the Universe. Their visbility and ubiquity make it
-possible to obtain integrated GC quantities within the Virgo Supercluster.
-Moreover, GCs inherit characteristics from their natal gas and GC systems show
-correlations with properties of (the field stars in) their host galaxies.
-% For
-% example, the mean metallicity of GC systems in early-type galaxies correlates with
-% the galactic metallicity (van den Bergh 1975, Brodie \& Huchra 1991) as well as
-% with the luminosity, and possibly the mass (Larsen 2001; Peng 2006).
-The old ages
-are consistent with formation before, during, or shortly after the initial
-collapse of the proto-galaxy and GCs have been present within galaxies for nearly
-a Hubble time. In theory, all of these characteristics make GC systems excellent
-tracers of the formation and evolution of their parent galaxies, if the formation
-of GCs themselves is well-understood.
+stellar configurations in the Universe. The globular cluster systems (GCS) of
+the Milky Way (MW) and the Andromeda galaxy (M31) have been studied extensively 
+over the last decades. More recent analyses of the Gaia data shed new light on the 
+chemical- and structural properties, and on the phase-space distribution 
+of the MW GC system.
+% https://arxiv.org/abs/1805.01408
+% https://arxiv.org/abs/1807.09775
+% https://www.aanda.org/articles/aa/abs/2018/08/aa32698-18/aa32698-18.html
+Moreover, the visbility and ubiquity of GCs makes it possible to obtain integrated 
+properties of GCs within the Local Group with reasonable certainty, and even of 
+those that are located further away within the Virgo Supercluster.
 
-Most galaxies host GC systems with a bimodal colour distribution, indicative of
-a bimodal metallicity distribution. The Milky Way (MW) GC system (GCS) can be
+The natal gas regions in which globular clusters form inherit key characteristics 
+from their parent (proto-)galaxies. GC populations, in turn, will therefore retain 
+a record of these properties and offer a unique insight into the detailed chemical 
+and dynamical evolution history of their host galaxies. In theory, this information 
+should be readily available and easily observable in the low redshift Universe, given 
+that GCs survive nearly a Hubble time of evolution within the violent galactic 
+environments they live in. However, a prerequisite to infer galactic histories
+from observations of GC systems is to understand the subtleties of the GC formation
+and evolution itself.
+
+Several formation scenerarios are consistent with the observations of globular 
+cluster populations. One important constraint comes from bimodality in the 
+colour distribution, which is indicative of a bimodality in the underlying 
+metallicity distribution of GC systems. For example, GCs in the MW are typically
 split up in a metal-rich (red) and metal-poor (blue) subpopulation divided at
@@
 
-Several formation scenarios could explain the observed bimodality, see
 \citet{2006ARA&A..44..193B} for a review of extragalactic GCs and galaxy
 formation. The authors argue that the observed metal-rich and metal-poor
+
+In a recent study Chiou et al. speculate that GCs may form in supersonically
+induced gasseous objects at high redshifts. These objects are free of dark matter 
+and populate a mass range consistent with the typical mass scale of GCs. 
+Interestingly, the authors find present-day absolute visual magnitude and 
+characteristic scales consistent with GCs in the Local group, based on a 
+rudimentary star formation model.
 

### 2019-04-26 AurigaGCS.tex
Some sentences on GC formation, and some sentences on FeH distribution

@@
 from their parent (proto-)galaxies. GC populations, in turn, will therefore retain 
-a record of these properties and offer a unique insight into the detailed chemical 
+a record of these properties and offer unique insight into the detailed chemical 
 and dynamical evolution history of their host galaxies. In theory, this information 
@@
 that GCs survive nearly a Hubble time of evolution within the violent galactic 
-environments they live in. However, a prerequisite to infer galactic histories
-from observations of GC systems is to understand the subtleties of the GC formation
-and evolution itself.
+environments they live in. However, these long and complex evolution histories
+themselves imposes their imprints onto the GCs observables. Thus, a prerequisite to 
+infer galactic histories from studies of GC systems is to understand the 
+subtleties of the GC formation and evolution itself.
 
-Several formation scenerarios are consistent with the observations of globular 
-cluster populations. One important constraint comes from bimodality in the 
-colour distribution, which is indicative of a bimodality in the underlying 
-metallicity distribution of GC systems. For example, GCs in the MW are typically
-split up in a metal-rich (red) and metal-poor (blue) subpopulation divided at
-[Fe/H]~$=-1$ \citep[e.g.][]{Harris2001}, although slightly different values can
-also be found in the literature. The two subpopulations are believed to be
-associated to the galactic disk, respectively the stellar halo
-\citep[e.g.][]{1985ApJ...293..424Z}. The latter is supported by observed similarities
-between the spatial distribution and chemical signature of the `blue' GCs show
-and stars in the stellar halo \citep{2008A&ARv..15..145H}. Moreover, relative
-age-estimates indicate that the metal-poor subpopulation may be $1.5$~Gyr younger
-than the metal-rich counterpart \citep{2005AJ....130..116D}.
+The literature offers several formation scenerarios that are consistent with the 
+data. One important constraint comes from bimodality in the colour distribution, 
+which is indicative of a bimodality in the underlying metallicity distribution 
+of GC systems. For example, GCs in the MW are typically split up in a metal-rich 
+(red) and metal-poor (blue) subpopulation divided at [Fe/H]~$=-1$ 
+\citep[e.g.][]{Harris2001}. These two subpopulations could be associated to the 
+galactic disk, respectively to the stellar halo \citep[e.g.][]{1985ApJ...293..424Z}. 
+The latter is supported by observed similarities between the spatial distribution
+and chemical signature of the `blue' GCs and the Galactic stellar halo 
+\citep{2008A&ARv..15..145H}. Moreover, relative age-estimates indicate that the 
+metal-poor subpopulation may be $1.5$~Gyr younger than the metal-rich counterpart 
+\citep{2005AJ....130..116D}, providing futher support that the GC population indeed
+consists of two distinct classes.
 
-\citet{2006ARA&A..44..193B} for a review of extragalactic GCs and galaxy
-formation. The authors argue that the observed metal-rich and metal-poor
+People postulate that the frequent mergers that occur during hierarchical build-up 
+of galaxies naturally produce (sub)populations of GCs from enriched gas on tight 
+orbits, if the mass ratios and gas fractions of the mergers are sufficiently high.
 
-In a recent study Chiou et al. speculate that GCs may form in supersonically
+Boylan-Kolchin: the blue population could form in high density regions along the 
+cosmic filament before or during the collapse of the proto-galaxy itself.
+This formation scenario would explain the presence of the oldest GCs with 
+primordial metallicities in the (outer) haloes of galaxies as the GCs are
+accreted over time. Moreover, the tidal fields experienced by GCs at (outer) halo
+orbits is significantly lower than by GCs in the inner galaxy, thus such GCs
+are expected to be long-lived.
+
+In a recent study, Chiou et al. speculate that GCs may form in supersonically
 induced gasseous objects at high redshifts. These objects are free of dark matter 
@@
 rudimentary star formation model.
+
+An alternative paradigm is that GC formation does not rely on special conditions
+at high redshifts. Rather, the same physics that governs the formation of young 
+massive clusters (YMCs) in the Local Group can be applied to the high redshift
+Universe. The observed differences between YMCs and GCs, in this scenario, arise
+naturally as the result intrinsic GC evolution within galactic tidal fields over
+a Hubble time. This interesting hypothesis is tested numerically by the E-MOSAICS
+people.
+
+\citet{2006ARA&A..44..193B} for a review of extragalactic GCs and galaxy
+formation.
 
@@
 We define GC candidates in the Auriga simulations as all star particles older
-than $10$~Gyr based on the MW GCS age distribution (Figure~\ref{fig:MW-M31-age}),
-and following \citet{2017MNRAS.465.3622R}.
+than $10$~Gyr based on the age distribution of the MW GCS (Figure~\ref{fig:MW-M31-age}),
+and following the analysis of \citet{2017MNRAS.465.3622R}.
 
-Trough out the analysis we mainly use three subsets of star particles, the
-\emph{old stars} (age $>10$~Gyr, or GC candidates), the \emph{old insitu} stars
-(defined as those bound to the most-massive halo/subhalo in the first snapshot
-that the particle was recorded), and the \emph{old accreted} star particles
-(i.e. those that have formed ex-situ and are bound to the most-massive halo/subhalo
-at $z=0$). In addition, we include \emph{all stars} (no selection criterion) to
-examine the result of (not) applying an age cut to our selection functions.
-
-We consider the metallicity distribution in Sec.~\ref{sec:results_FeH}
-the distribution of galactocentric radii in Sec.~\ref{sec:results_Rgc}, and the
-combination of both in Sec.~\ref{sec:results_FeHRgc}.
+Trough out our analysis we compare the distributions of three subsets of star 
+particles: \emph{old stars} (age $>10$~Gyr, or GC candidates), \emph{old insitu} 
+stars (defined as those bound to the most-massive halo/subhalo in the first
+snapshot that the particle was recorded), and \emph{old accreted} star particles 
+(those that have formed ex-situ and are bound to the most-massive halo/subhalo
+at $z=0$). For comparison we also include the results for \emph{all stars} (when
+no additional selection criterion is applied to the star particles). We consider 
+the metallicity distribution in Sec.~\ref{sec:results_FeH}, the distribution of 
+galactocentric radii in Sec.~\ref{sec:results_Rgc}, and the combination of both 
+in Sec.~\ref{sec:results_FeHRgc}.
 
@@
 \label{sec:results_FeH}
-We investigate whether the star formation model implemented in the Auriga
-simulations is capable of i) producing a metallicity distribution that is
-consistent with the GCS observed in the MW (M31), and ii) generating sufficient
-mass over the domain of the observations.
+We investigate whether the star formation model implemented in Auriga produces 
+metallicity distributions consistent with the MW (M31) GC system, and whether 
+the subgrid generates sufficient total mass to account for the bound cluster 
+formation efficiency and evolutionary mass loss.
 
@@
     \caption{
-        Mean and standard deviation of the metallicity distribution of star
-        particles in each of the thirty Auriga L4 haloes. Orange dots show 
-        the subset of old star particles, and blue (red) dots show the old 
-        insitu (accreted) component. These Auriga subsets can be compared to 
-        the MW (M31) GCS shown in purple (magenta), and to the metal-rich 
-        (metal-poor) component of the MW GCS indicated by the black solid (open) 
-        dots \citep[values from][p. 38]{1998gcs..book.....A}.
+        First vs second central moment of the Auriga L4 metallicity distributions.
+        Each dot represents one simulation for a given colour. The orange (blue) 
+        [red] dots shows the values calculated using the old (old insitu) 
+        [old accreted] star particles. Orange triangles indicate that all stars 
+        were used. The purple (magenta) cross denotes our calculation using all 
+        MW (M31) observations (i.e. asuming a unimodal distribution). The black 
+        solid (open) dots indicate the literature values of a bimodal Gaussian 
+        fit to the data \citep[values from][p. 38]{1998gcs..book.....A},
+        showing the the metal-rich (metal-poor) component of the MW.
         \label{fig:FeH_mu_sigma}
@@
 Figure~\ref{fig:FeH_mu_sigma} shows the mean and standard deviation of the
-[Fe/H] distribution of star particles in all Auriga L4 simulations. The mean
-metallicity of old star particles lies in the range $-1.0$ to $-0.5$ and the
-dispersion increases with decreasing metallicity. For comparison, the mean
-of all star particles populates the range $-0.25$ to $0$ with a near-constant
-dispersion a bit above $0.5$. Old accreted stars in the Auriga haloes reach
-mean metallicities between $-1.5$ and $-1.0$, which is considerably lower than
-the old- and old insitu populations. Most Auriga L4 haloes have old insitu
-populations with mean metallicities around $-0.5$. The old accreted populations
-follow the trent of increasing dispersion with decreasing mean metallicity, but
-notably the old insitu populations all have a constant dispersion of roughly
-$0.45$. We show the values calculated using all MW (M31) GCs in purple (magenta),
-and literature values of the metal-rich (metal-poor) component of the MW GCS
-as black solid (open) dots. We further discuss our comparison between the
-simulations and the observations in Sec.~\ref{sec:discussion_FeH}
+[Fe/H] distribution of star particles in the Auriga L4 simulations. One dot 
+of a given colour shows one particular simulation (thirty in total). The 
+orange (blue) [red] dots represent the distributions of old (old insitu) 
+[old accreted] star particles, and orange triangles indicate that all stars
+were used. The mean metallicities of all GC candidates (orange dots) lie in the 
+range $-0.95$ to $-0.4$, which is lower than when we include all star particles 
+(orange triangles, centred around $\mu \sim 0$). Furthermore we find that the 
+distributions of the accreted (insitu) GC candidates shift to slightly lower 
+(higher) values and seem to be roughly centred around $\mu \sim -0.5$ ($-0.8$)
+We find this trent that the distribution is more metal-poor (metal-rich)
+when splitting the GC candidates into accreted (insitu) populations for the
+majority of the Auriga simulations. The only exceptions are Au4-1 where this 
+trent is reversed, and Au4-7 where all three (sub)populations have $\mu \sim -0.82$
+
+The purple (magenta) cross shows the values calculated using all MW (M31) GC
+observations (i.e. assuming a unimodal distribution). The black solid (open) dots
+mark the literature values of a bimodal Gaussian fit to the MW data, indicating
+the metal-rich (metal-poor) subpopulation. Overall we find that the Auriga 
+simulations produce (sub)populations of GC candidates that are more metal-rich 
+than the MW and M31 GC systems. The only exception is Au4-1 with $\mu \approx -1.51$
+and $\sigma \approx 0.54$, close to the mean of the blue/metal-poor population
+of the MW GCS. However, the insitu GC candidates in Au4-1 consists 30 times
+less star particles than any of the other (sub)population. Finally, we find that
+the populations of GC candidates that have formed insitu have mean values that 
+are similar the that of the red/metal-rich subpopulation of Milky Way GCs.
+
+(sub)populations of GC candidates in the Auriga simulations has a metallicity
+distribution with sufficiently low
 

### 2019-04-28 AurigaGCS.tex
Added a paragraph to describe FeH distribution of Au4-24

@@
 
+\begin{figure*}
+    \includegraphics[width=\columnwidth]{{Au4-24_FeH_cleaner-trim}.png}
+    \includegraphics[width=\columnwidth]{{Au4-24_FeH_mass-trim}.png}
+    \caption{
+        \emph{Left:} Metallicity distribution of Au4-24 (bottom panel). We show 
+        the the GG candicates in orange. We split the GC candidates into two 
+        subpopulations, those that have formed insitu (blue), and those that have 
+        been accreted (red). The thin orange line shows all star particles.
+        The solid purple (magenta) line in the top panel shows the GC system 
+        of the MW (M31). \emph{Right:} Total mass in each metallicity bin.
+        \label{fig:Au4-24_FeH}
+    }
+\end{figure*}
+Figure~\ref{fig:Au4-24_FeH} shows the metallicity distribution of 
+Au4-24\footnote{The nomenclature is `Au' for Auriga, followed by the resolution 
+level (4) and halo number (24 - indicating which set of initial conditions was used 
+the run).} as one particular example of an Auriga galaxy. The panel on the left
+shows the distribution normalized by the number of particles, showing the GC
+candidates in orange. The accreted GC candidates are shown in red, and the insitu
+subpopulation is shown in blue. The top panel shows the MW (M31) GC system in
+purple (magenta). We overplot two Gaussian curves (the purple dashed lines) using
+literature values of the mean $\mu$ and standard deviation $\sigma$ of the 
+metal-rich and metal-poor populations of the MW GCS \citep[][p. 38]{Harris2001}.
+However, we use arbitrary normalizations to produce aesthetically pleasing curves.
+The panel on the right shows the metallicity distribution weighted by the total
+mass of the particles (observations) in that bin.
+
+We find that the metallicity distribution of the Auriga simulations blabla.
+
 \begin{figure}
@@
 \end{figure}
+
 Figure~\ref{fig:FeH_mu_sigma} shows the mean and standard deviation of the

### 2019-05-09 AurigaGCS.tex
Updates for 4.1

--- 2019-04-26 AurigaGCS.tex
@@
 metallicity distributions consistent with the MW (M31) GC system, and whether 
-the subgrid generates sufficient total mass to account for the bound cluster 
-formation efficiency and evolutionary mass loss.
+the subgrid generates sufficient total mass at metallicities (and radii) typical
+for the MW (M31) GCS.
+
+\begin{figure*}
+    \includegraphics[width=\columnwidth]{{Au4-10_FeH_cleaner-trim}.png}
+    \includegraphics[width=\columnwidth]{{Au4-21_FeH_cleaner-trim}.png}
+    \caption{
+        \emph{Left:} Metallicity distribution of Au4-10 (bottom panel). We show 
+        the the GG candicates in green. We split the GC candidates into two 
+        subpopulations, those that have formed insitu (blue), and those that have 
+        been accreted (red). The thin green line shows all star particles.
+        The solid purple (magenta) line in the top panel shows the GC system 
+        of the MW (M31). \emph{Right:} Total mass in each metallicity bin.
+        \label{fig:Au4-10and21_FeH}
+    }
+\end{figure*}
+Figure~\ref{fig:Au4-10and21_FeH} shows the normalized metallicity distribution 
+of Au4-10\footnote{The nomenclature is `Au' for Auriga, followed by the resolution 
+level (4) and halo number (10 - indicating which set of initial conditions was 
+used the run).} and Au4-21, showing the GC candidates in green. The accreted GC 
+candidates are shown in red, and the insitu subpopulation in blue. The top panels 
+show the MW (M31) GC system in purple (magenta). We overplot a double Gaussian 
+for the MW GCS (the purple dashed lines), adopting literature values of the 
+mean $\mu$ and standard deviation $\sigma$ of the metal-rich and metal-poor 
+populations \citep[][p. 38]{Harris2001}.
+
+We find that the age cut lowers the mean metallicity from $\sim 0.0$ to $\sim -0.6$.
+Furthermore, the old accreted stars generally have lower metallicities than the
+old insitu stars. The difference between the mean metalicity of the old insitu 
+and old accreted stars for the majority of the simulations is $\sim 0.3$ (e.g.
+Au4-21), and $\sim 0.5$ dex for Au4-10, Au4-16, Au4-17, Au4-18 and Au4-22.
+This trent is only reversed for Au4-1 and Au4-4, for which the old insitu population
+has a lower mean metallicity instead. For Au4-1 we find $\mu = -1.51$ (-0.74) 
+for the old insitu (accreted), but the former consists of only 1019 particles 
+(with a total mass of 5e7 M\Sun). Overall we find that the simulations produce 
+(sub)populations of GC candidates that are more metal-rich than the MW and M31 
+GC systems. Moreover, none of the simulations has a population of GC candidates 
+with a bimodal metallicity distribution (the green curves).
 
 \begin{figure}
-    \includegraphics[width=\columnwidth]{{FeH_mu_sigma}.png}
+    \includegraphics[width=\columnwidth]{{FeH_mu_sigma-trim}.png}
     \caption{
         First vs second central moment of the Auriga L4 metallicity distributions.
-        Each dot represents one simulation for a given colour. The orange (blue) 
-        [red] dots shows the values calculated using the old (old insitu) 
-        [old accreted] star particles. Orange triangles indicate that all stars 
+        Each cross represents one simulation for a given colour. The green (blue) 
+        [red] crosses show the values calculated using the old (old insitu) 
+        [old accreted] star particles. Green triangles indicate that all stars 
         were used. The purple (magenta) cross denotes our calculation using all 
@@
 \end{figure}
-Figure~\ref{fig:FeH_mu_sigma} shows the mean and standard deviation of the
-[Fe/H] distribution of star particles in the Auriga L4 simulations. One dot 
-of a given colour shows one particular simulation (thirty in total). The 
-orange (blue) [red] dots represent the distributions of old (old insitu) 
-[old accreted] star particles, and orange triangles indicate that all stars
-were used. The mean metallicities of all GC candidates (orange dots) lie in the 
-range $-0.95$ to $-0.4$, which is lower than when we include all star particles 
-(orange triangles, centred around $\mu \sim 0$). Furthermore we find that the 
-distributions of the accreted (insitu) GC candidates shift to slightly lower 
-(higher) values and seem to be roughly centred around $\mu \sim -0.5$ ($-0.8$)
-We find this trent that the distribution is more metal-poor (metal-rich)
-when splitting the GC candidates into accreted (insitu) populations for the
-majority of the Auriga simulations. The only exceptions are Au4-1 where this 
-trent is reversed, and Au4-7 where all three (sub)populations have $\mu \sim -0.82$
 
-The purple (magenta) cross shows the values calculated using all MW (M31) GC
-observations (i.e. assuming a unimodal distribution). The black solid (open) dots
-mark the literature values of a bimodal Gaussian fit to the MW data, indicating
-the metal-rich (metal-poor) subpopulation. Overall we find that the Auriga 
-simulations produce (sub)populations of GC candidates that are more metal-rich 
-than the MW and M31 GC systems. The only exception is Au4-1 with $\mu \approx -1.51$
-and $\sigma \approx 0.54$, close to the mean of the blue/metal-poor population
-of the MW GCS. However, the insitu GC candidates in Au4-1 consists 30 times
-less star particles than any of the other (sub)population. Finally, we find that
-the populations of GC candidates that have formed insitu have mean values that 
-are similar the that of the red/metal-rich subpopulation of Milky Way GCs.
+We show the mean metallicity and standard deviation of all thirty Auriga L4 haloes
+in Figure~\ref{fig:FeH_mu_sigma}. The green crosses are to be compared to the 
+purple (magenta) cross, which shows the mean value of all MW (M31) GCs. 
+We test the null hypothesis that MW (M31) and the GC candidates (all, insitu, and
+accreted) are drawn from the same underlying distribution by calculating the KS
+test statistic (i.e. six KS tests per simulation). We reject $H_0$ at the 100.00~\%
+confidence level for virtually all subsets of all simulations, both for MW and M31,
+except when comparing the old accreted stars of Au4-10 to the MW GCS. In this 
+case we still reject $H_0$ with, but with $\leq 98.68$~\% confidence. When comparing
+to the M31 GCS, the `best' matches are the old accreted subpopulations of Au4-13,
+Au4-15, and Au4-17 ($H_0$ rejected with $\leq$ 99.82~\% confidence, 99.95~\%, 
+and 98.32~\%). Here we find that the cumulative distributions are more or less 
+similar up to [Fe/H]~$\sim$~-0.5, above which the simulations yield higher number 
+counts which drives the KS test statistic over the critical values. This affirms
+our finding that the simulations produce GC candidates that are more metal-rich 
+than the MW (M31) GCS because under-production of old stars with [Fe/H]~$\leq$~-1.5,
+and over-production of stars with [Fe/H]$\geq$~-0.5, are the main reason reasons
+that $H_0$ is rejected with such high confidence.
 
-(sub)populations of GC candidates in the Auriga simulations has a metallicity
-distribution with sufficiently low
+In addition, we show the metal-rich (metal-poor) population of the MW GCS using 
+a solid (open) dot. The mean metallicities of the old insitu populations appear
+roughly consistent with that of the metal-rich population of the MW, but the 
+simulations show larger dispersions.
 
@@
         simulations. We show the median value of all Auriga haloes for all
-        stars (orange dotted) and globular cluster candidates (i.e. stars with
-        age $>$~10~Gyr; orange solid). The latter sub set is further split up
+        stars (green dotted) and globular cluster candidates (i.e. stars with
+        age $>$~10~Gyr; green solid). The latter sub set is further split up
         between stars that formed in-situ (blue solid), and those that were accreted
@@
 conditions which thus have unique merger histories). We notice again that
-the peak metallicity shifts down from $0$ to $-0.5$ for old stars (orange solid)
-compared to all stars (orange dotted) while the mass at the peak lowers by 
+the peak metallicity shifts down from $0$ to $-0.5$ for old stars (green solid)
+compared to all stars (green dotted) while the mass at the peak lowers by 
 roughly one dex. The mass budget of the old stars is

### 2019-05-12 AurigaGCS.tex
Minor revisions to Sec. 3 (switched to non-mass-weigthed age distribution of MW/M31 GCS). Finished 4.1, near-finished 4.2, and some progress on 4.3

@@
 different values for the combined product of the bound cluster formation efficiency
-and the globular cluster disruption rate. We investigate wether these differences
+and the globular cluster disruption rate. We investigate whether these differences
 could result from formation insitu vs. accreted star particles. We find ... TODO.
@@
 we reject the null hypothesis that the simulated and observed metallicities are
-drawn from the same distribution at the 99.99\% confidence level, for the GCS
+drawn from the same distribution at $\geq98.32$~\% confidence level, for the GCS
 of the Milky Way as well as that of the Andromeda galaxy. The same holds true for
@@
 \label{sec:observations}
-We summarise relevant observations of the globular cluster system of the Milky
-Way in Sec.~\ref{sec:milkyway}, and of Andromeda (M31) in Sec.~\ref{sec:andromeda}.
+We describe the observations of the MW GCS in Sec.~\ref{sec:milkyway}, 
+and of the Andromeda (M31) GCS in Sec.~\ref{sec:andromeda}
 
@@
 GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
-
-\citet{2019AJ....157...12B} communicate the latest efforts to aggregate the
-available data, presented in their CatClu catalog. Amongst 10978 star clusters
-and alike objects in the Milky Way, the catalog contains 200 GCs and 94 GC
-candidates. The CatClu catalog contains reference papers, positions, distances,
-and total absolute V magnitude. Therefore we rely on the H96e10 dataset for all
-other quantities, but we caution that the Harris catalogue is now believed to be (only) 53-72\% complete.
-
-Specifically, the relevant data fields that we use from H96e10 are the
-metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in
+We still use data from the Harris catalogue, but caution that it may (only) be 
+53-72\% complete. Specifically, the relevant data fields that we use from H96e10 
+are the metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in
 kpc)\footnote{In a Sun-centered coordinate system: $X$ points toward Galactic
@@
 
-\subsubsection{Age estimates}
-We supplement H96e10 with age-estimates from isochrone fits to stars
+% \citet{2019AJ....157...12B} communicate the latest efforts to aggregate the
+% available data, presented in their CatClu catalog. Amongst 10978 star clusters
+% and alike objects in the Milky Way, the catalog contains 200 GCs and 94 GC
+% candidates. The CatClu catalog contains reference papers, positions, distances,
+% and total absolute V magnitude. Therefore we rely on the H96e10 dataset for all
+% other quantities, but
+
+We supplement the catalogue with age-estimates from isochrone fits to stars
 near the main-sequence turnoff in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.
@@
 
-% \todo[inline]{
-% ``For M31 GC masses we combine the catalogues of Caldwell et al. (2011, using the
-% given masses) and Huxor et al. (2014, again assuming $M/L_V = 1.7$~M/L$_{\odot}$,
-% e.g. Strader, Caldwell \& Seth 2011).''
-% }
-
-\subsubsection{Age estimates}
-For M31 we find an age distribution with a mean value of 11.0$\pm 0.2$~Gyr and a
-dispersion of $2.2$~Gyr. Furthermore, $24$ GCs have age-estimates below $10$~Gyr, and
-the minimum age is $4.8$~Gyr.
-
-We present a mass-weighted histogram of the age-estimates of the $55$ MW GCs in V13
-and $85$ GCs in M31 for which age-estimates are available in CR16, see
-Figure~\ref{fig:MW-M31-age}.
+The M31 GCS has a mean age of $11.0 \pm 0.2$~Gyr with a dispersion of $2.2$~Gyr,
+and $24$ GCs have age-estimates below $10$~Gyr with a minimum age of $4.8$~Gyr. 
+We show a histogram of the age-estimates of the $55$ MW GCs in V13 and $88$ GCs
+in M31 for which age-estimates are available in CR16, see Figure~\ref{fig:MW-M31-age}.
 
 \begin{figure}
-    \includegraphics[width=\columnwidth]{{MW_M31_Age_HistogramMassWeighted_Msun}.png}
+    \includegraphics[width=\columnwidth]{{MW_M31_Age_Histogram-trim}.png}
     \caption{
-        Mass-weighted age distribution of 55 GCs in the MW
-        \citep[data from][]{2013ApJ...775..134V} and 85 GCs
+        Age distribution of 55 GCs in the MW
+        \citep[data from][]{2013ApJ...775..134V} and 88 GCs
         in M31 \citep[data from][]{2016ApJ...824...42C}.
@@
 \end{figure}
+% \begin{figure}
+%     \includegraphics[width=\columnwidth]{{MW_M31_Age_HistogramMassWeighted_Msun}.png}
+%     \caption{
+%         Mass-weighted age distribution of 55 GCs in the MW
+%         \citep[data from][]{2013ApJ...775..134V} and 85 GCs
+%         in M31 \citep[data from][]{2016ApJ...824...42C}.
+%         \label{fig:MW-M31-age}
+%     }
+% \end{figure}
 
@@
 MW (M31) GCS in the top (bottom) panel of Figure~\ref{fig:observations_FeHRgc}. Both
-quantities are readily available in H96e10, but the galactocentric radius
-of GCs in M31 is not available in CR16. Therefore we follow
-\citet[][Sec.~4.1]{2019arXiv190111229W} to calculate the projected radius
+quantities are readily available in H96e10 (assuming $R_{\odot}=8.0$~kpc), but 
+the galactocentric radius of GCs in M31 is not available in CR16. Therefore we 
+follow \citet[][Sec.~4.1]{2019arXiv190111229W} to calculate the projected radius
 $R_{\text{proj}}$ from the observed positions, adopting M31's central position
@@
 We calculate $R_{\text{GC}}$ as `average deprojected distance`
-$R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$.
-We compare these observations to the Auriga simulations later on in
-Sec.~\ref{sec:discussion_FeHRgc},
+$R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$. The observations indicate that 
+no GCs with high metallicities are to be expected at large radii (the three bins 
+in the upper right corner, both for MW and M31), and relatively few GCs at large 
+radii in general ($R_{\text{GC}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
+the MW and $17$ or 4.6\% in M31). We compare these observations to the Auriga
+simulations later on in Sec.~\ref{sec:results_FeHRgc}.
 
@@
 metallicity distributions consistent with the MW (M31) GC system, and whether 
-the subgrid generates sufficient total mass at metallicities (and radii) typical
-for the MW (M31) GCS.
+the subgrid generates sufficient total mass at metallicities typical for the 
+MW (M31) GCS.
 
@@
     \includegraphics[width=\columnwidth]{{Au4-10_FeH_cleaner-trim}.png}
-    \includegraphics[width=\columnwidth]{{Au4-21_FeH_cleaner-trim}.png}
+    \includegraphics[width=\columnwidth]{{Au4-4_and_Au4_21_FeH-trim}.png}
     \caption{
         \emph{Left:} Metallicity distribution of Au4-10 (bottom panel). We show 
-        the the GG candicates in green. We split the GC candidates into two 
+        the GG candicates in green. We split the GC candidates into two 
         subpopulations, those that have formed insitu (blue), and those that have 
-        been accreted (red). The thin green line shows all star particles.
+        been accreted (red). The dotted green line shows all star particles.
         The solid purple (magenta) line in the top panel shows the GC system 
-        of the MW (M31). \emph{Right:} Total mass in each metallicity bin.
+        of the MW (M31). \emph{Right:} Au4-4 (bottom), and Au4-21 (top).
         \label{fig:Au4-10and21_FeH}
@@
 Figure~\ref{fig:Au4-10and21_FeH} shows the normalized metallicity distribution 
-of Au4-10\footnote{The nomenclature is `Au' for Auriga, followed by the resolution 
+of \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the resolution 
 level (4) and halo number (10 - indicating which set of initial conditions was 
-used the run).} and Au4-21, showing the GC candidates in green. The accreted GC 
+used the run).} and \mbox{Au4-21}, showing the GC candidates in green. The accreted GC 
 candidates are shown in red, and the insitu subpopulation in blue. The top panels 
@@
 
-We find that the age cut lowers the mean metallicity from $\sim 0.0$ to $\sim -0.6$.
+We find that the age cut lowers the mean metallicity from \textasciitilde{}$0.0$
+to \textasciitilde{}$-0.6$.
 Furthermore, the old accreted stars generally have lower metallicities than the
-old insitu stars. The difference between the mean metalicity of the old insitu 
-and old accreted stars for the majority of the simulations is $\sim 0.3$ (e.g.
-Au4-21), and $\sim 0.5$ dex for Au4-10, Au4-16, Au4-17, Au4-18 and Au4-22.
-This trent is only reversed for Au4-1 and Au4-4, for which the old insitu population
-has a lower mean metallicity instead. For Au4-1 we find $\mu = -1.51$ (-0.74) 
-for the old insitu (accreted), but the former consists of only 1019 particles 
-(with a total mass of 5e7 M\Sun). Overall we find that the simulations produce 
-(sub)populations of GC candidates that are more metal-rich than the MW and M31 
-GC systems. Moreover, none of the simulations has a population of GC candidates 
-with a bimodal metallicity distribution (the green curves).
+old insitu stars. The difference between the mean metallicity of the old insitu 
+and old accreted stars for the majority of the simulations is \textasciitilde{}$0.3$ (e.g.
+\mbox{Au4-21}), and \textasciitilde{}$0.5$ dex for \mbox{Au4-10}, \mbox{Au4-16}, \mbox{Au4-17},
+\mbox{Au4-18} and \mbox{Au4-22}. This trend is only reversed for \mbox{Au4-1}
+and \mbox{Au4-4}, for which the old insitu population has a lower mean metallicity 
+instead. For \mbox{Au4-1} we find $\mu = -1.51$ (-0.74) for the old insitu (accreted), 
+but the former consists of only $1019$ particles ($1.3$\% of all GC candidates, and 
+with a total mass of 5e7 M\Sun) thus we believe our classification of insitu is 
+flawed for this halo due to misclassification of the primary halo in the merger
+tree by subfind. For \mbox{Au4-4}, $10.8$ \% of the GC candidates is classified 
+as insitu (compared to insitu fractions of $40-80$\% for other haloes). Overall
+we find that the simulations produce (sub)populations of GC candidates that are
+more metal-rich than the MW and M31 GC systems. Moreover, none of the simulations
+has a population of GC candidates with a bimodal metallicity distribution
+(the green curves).
 
@@
         First vs second central moment of the Auriga L4 metallicity distributions.
-        Each cross represents one simulation for a given colour. The green (blue) 
+        Each cross (for a given colour) represents one simulation. The green (blue) 
         [red] crosses show the values calculated using the old (old insitu) 
@@
         were used. The purple (magenta) cross denotes our calculation using all 
-        MW (M31) observations (i.e. asuming a unimodal distribution). The black 
-        solid (open) dots indicate the literature values of a bimodal Gaussian 
-        fit to the data \citep[values from][p. 38]{1998gcs..book.....A},
-        showing the the metal-rich (metal-poor) component of the MW.
+        MW (M31) observations (which would be appropriate for a unimodal 
+        distribution). The black solid (open) dots indicate the literature values
+        of a bimodal Gaussian fit to the data \citep[values from][p. 38]{1998gcs..book.....A},
+        showing the metal-rich (metal-poor) component of the MW.
         \label{fig:FeH_mu_sigma}
@@
 confidence level for virtually all subsets of all simulations, both for MW and M31,
-except when comparing the old accreted stars of Au4-10 to the MW GCS. In this 
+except when comparing the old accreted stars of \mbox{Au4-10} to the MW GCS. In this 
 case we still reject $H_0$ with, but with $\leq 98.68$~\% confidence. When comparing
-to the M31 GCS, the `best' matches are the old accreted subpopulations of Au4-13,
-Au4-15, and Au4-17 ($H_0$ rejected with $\leq$ 99.82~\% confidence, 99.95~\%, 
+to the M31 GCS, the `best' matches are the old accreted subpopulations of \mbox{Au4-13},
+\mbox{Au4-15}, and \mbox{Au4-17} ($H_0$ rejected with $\leq$ 99.82~\% confidence, 99.95~\%, 
 and 98.32~\%). Here we find that the cumulative distributions are more or less 
-similar up to [Fe/H]~$\sim$~-0.5, above which the simulations yield higher number 
+similar up to [Fe/H]~\textasciitilde{}$-0.5$, above which the simulations yield higher number 
 counts which drives the KS test statistic over the critical values. This affirms
 our finding that the simulations produce GC candidates that are more metal-rich 
-than the MW (M31) GCS because under-production of old stars with [Fe/H]~$\leq$~-1.5,
-and over-production of stars with [Fe/H]$\geq$~-0.5, are the main reason reasons
-that $H_0$ is rejected with such high confidence.
+than the MW (M31) GCS. The main reason reasons that $H_0$ is rejected with such 
+high confidence are under-production of old stars with [Fe/H]~$\leq$~-1.5,
+and over-production of stars with [Fe/H]$\geq$~-0.5.
 
@@
 roughly consistent with that of the metal-rich population of the MW, but the 
-simulations show larger dispersions.
+simulations show larger dispersions. We are uncertain whether definitive consensus 
+is reached concerning uni- or bimodality in the [Fe/H] distribution of M31, but
+CR16 argues that the data, after removal of younger objects due to improved age
+classification, leans towards unimodality. Therefore we do not show two data
+points for the M31 GCS.
 
@@
 \end{figure}
-Figure~\ref{fig:FeH} shows the mass-weighted metallicity distribution of the
-Auriga L4 haloes. Lines show the median value and the shaded regions indicate
-the $1\sigma$ interval around it (i.e. scatter between runs with different initial
-conditions which thus have unique merger histories). We notice again that
-the peak metallicity shifts down from $0$ to $-0.5$ for old stars (green solid)
-compared to all stars (green dotted) while the mass at the peak lowers by 
-roughly one dex. The mass budget of the old stars is
-dominated by the old insitu population (blue solid) below [Fe/H]=$-1$, and by
-the old accreted stars (red solid) above this value. We show the MW (M31) GCS 
-in purple (magenta) and we show the ratio of the simulated to the observed 
-profiles in the middle (bottom) panel. This mass excess can be thought of as a
-combination of the bound cluster formation efficiency and disruptive processes,
-further discussed in Sec.~\ref{sec:discussion_mass_excess}.
+We now turn to the total mass in GC candidates produced by the Auriga simulations. 
+We show the median (coloured lines) for all thirty Auriga L4 haloes with the 
+$1\sigma$ interval around it (shaded regions, which shows the scatter between 
+runs that have different initial conditions, thus, have unique merger histories). 
+We chose to aggregate the data to indicate a general trend that we find when the
+GC candidates are split up according to birth location, rather than selecting 
+typical examples of individual galaxies. Figure~\ref{fig:FeH} shows the mass-weighted
+metallicity distribution of all Auriga L4 galaxies. Once again we notice that the 
+peak metallicity shifts down from $0$ to $-0.5$ for old stars (green solid)
+compared to all stars (green dotted), and we learn that the mass at the peak 
+lowers by roughly one dex. The mass budget of the old stars is dominated by the 
+old insitu population (blue solid) below [Fe/H]~=~$-1$, and by the old accreted 
+stars (red solid) above this value. We show the MW (M31) GCS in purple (magenta) 
+and we show the ratio of the simulated to the observed profiles in the middle 
+(bottom) panel. This mass excess can be thought of the `mass budget' that the
+Auriga GC candidates can `afford to lose' due to a combination of smaller than
+unity bound cluster formation efficiencies combined with a Hubble time of dynamical 
+evolution, while still producing a GC system with sufficient mass to be consistent
+with the MW (M31) GCS. The cluster formation efficiency would have to linearly
+decrease with decreasing metallicity for Auriga GC candidates to produce a population
+of GC candidates that is consistent with the MW. For the GC candidates in M31
+we find a constant mass excess up to \textasciitilde{}$-0.9$, above which the 
+simulations produce a higher mass excess with increasing metallicity. If dynamical
+evolution is not expected to more efficiently disrupt GCs of higher metallicity,
+then we would find that the efficiency to form bound star clusters would have to
+decrease with increasing metallicity.
 
@@
 \begin{figure}
-    \includegraphics[width=\columnwidth]{{Rgc_mu_sigma}.png}
+    \includegraphics[width=\columnwidth]{{Rgc_mu_sigma-trim}.png}
     \caption{
@@
 the old accreted component has a larger radial extent. Moreover, the dispersion
-increases with increasing mean value of the radial distribution.
+increases with increasing mean value of the radial distribution as may be expected
+for a quantity that cannot have negative values.
 
@@
 Auriga L4 haloes. We notice a subtle peak around $10$~kpc for all star
-particles that is not present for the old star particles, indicating that the
+particles that is not present for the GC candidates, indicating that the
 stellar disc is no longer present when applying the latter selection criterion.
-Furtermore, we find that the dominant contribution to the total mass in old
-stars changes from those formed insitu to the accreted population around 
-$10$~kpc. We further discuss our comparison between the simulations and the 
-observations in Sec.~\ref{sec:discussion_Rgc}.
+Furthermore, we find that the dominant contribution to the total mass in GC
+candidates changes from those formed insitu to the accreted population around 
+$10$~kpc. Again we show the mass excess of the simulations compared to the Milky
+Way and Andromeda GCS. We find a decreasing mass excess with increasing radius 
+in the range $0.2$ to \textasciitilde{}$5$ kpc, followed by an increase attributed
+to the accreted subpopulation. We further investigate a breakdown of the total mass
+in Auriga GC candidates into bins of both metallicity and radius in the following
+section.
 
@@
 
-We investigate whether the Auriga simulations still produce sufficient mass in 
-old star particles to be consistent with the MW (M31) GCS when two-dimensionally 
-binned in both [Fe/H] and $R_\text{GC}$. We sum the total simulated mass in 
-each bin and then divide it by the total mass in the MW (M31) GCS. We show this
-mass excess in Figure~\ref{}, respectively Figure~\ref{}
+We investigate whether the Auriga simulations still produce sufficient mass when 
+the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{GC}$. First
+we sum the total simulated mass in each bin (for an individual Auriga simulation),
+then we calculate the median over all thirty Auriga L4 haloes (in each bin, see
+Figure~\ref{fig:Au-FeHRgc} which can be compared to 
+Figure~\ref{fig:observations_FeHRgc}). Finally, we divide these value by the total 
+mass in the MW (M31) GCS to obtain the median mass excess produced by the star 
+formation model implemented in the Auriga simulations. See the top (bottom) panel
+of Figure~\ref{fig:Au-FeHRgc} for mass excess with respect to the MW (M31) GCS.
+
 \begin{figure}

### 2019-05-14 AurigaGCS.tex
Updated figures for 4.3

@@
         151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
-        is 98.19 \% of the total MW GCS mass in the Harris catalog.
-        \emph{Bottom}: Same for M31, showing 366 GCs and 88.38 \% of the total
-        mass in CR16 \citep[data from][]{2016ApJ...824...42C}. Note that the
-        range of the colourmap differs in both figures.
+        is 98.6 (92.2) \% of the total mass (clusters) of the MW GCS in the Harris 
+        catalog. \emph{Bottom}: Same for M31, showing 366 GCs and 88.4 (83.9) \% 
+        of the total mass (clusters) in CR16 \citep[data from][]{2016ApJ...824...42C}. 
+        Note that the range of the colourmap differs in both figures.
         \label{fig:observations_FeHRgc}
@@
 increases with increasing mean value of the radial distribution as may be expected
-for a quantity that cannot have negative values.
+for a non-negative quantity.
 
@@
 formation model implemented in the Auriga simulations. See the top (bottom) panel
-of Figure~\ref{fig:Au-FeHRgc} for mass excess with respect to the MW (M31) GCS.
+of Figure~\ref{fig:Au-FeHRgc-ratio} for mass excess with respect to the MW (M31) GCS.
 
@@
     \includegraphics[width=0.49\textwidth]
-        {{Au-all_RgcFeH_HistogramMassWeighted_iold_36bins_mean}.png}
+        {{Au4-median_RgcFeH_HistogramMassWeighted_iold-trim}.png}
     \caption{
-        Mass-weighted [Fe/H]-$R_{\text{GC}}$ distribution of all Auriga haloes
-        (level 3, 4 and 5). Here we consider the old ($>$~10~Gyr) stars in all
-        simulations and color-code the \textbf{mean value} (of 40 Auriga haloes)
+        Mass-weighted [Fe/H]-$R_{\text{GC}}$ distribution of all thirty Auriga 
+        L4 haloes. Here we consider only the GC candidates (age $>$~10~Gyr) stars
+        in and color-code by the \textbf{median} (values also shown in each bin). 
+        The numbers in parenthesis show how many star particles fall within the
+        bin. Note that the range of the colourmap again differs (for improved
+        contrast within the plot).
         \label{fig:Au-FeHRgc}
@@
     \includegraphics[width=0.49\textwidth]
-        {{Au-all_RgcFeH_HistogramMassWeighted_MW_iold_36bins_mean}.png}
+        {{Au4-median_RgcFeH_HistogramMassWeighted_MW_iold-trim}.png}
     \includegraphics[width=0.49\textwidth]
-        {{Au-all_RgcFeH_HistogramMassWeighted_M31_iold_36bins_mean}.png}
+        {{Au4-median_RgcFeH_HistogramMassWeighted_M31_iold-trim}.png}
     \caption{
-        Caption
+        The top (bottom) panel shows the logarithm of the ratio of simulated mass
+        to mass in the MW (M31) GCS, i.e. the logarithm of the mass excess. The 
+        color-coded values are also shown in each bin. Note that the three bins 
+        in the upper right corner are left blank because the observations have
+        zero mass there, and that the numbers indicate how much (median) mass is 
+        produced by the simulations in those bins.
         \label{fig:Au-FeHRgc-ratio}
@@
     \includegraphics[width=0.31\textwidth]{{logMFeH_Au24}.png}
-    \caption{Same as Figure~\ref{fig:FeH}, but here the colours indicate resolution
-        level: L3 green, L4 orange, and L5 blue. \emph{Left:} Auriga halo 6.
-        \emph{Mid:} Auriga halo 16. \emph{Right:} Auriga halo 24. For all three
-        haloes we find marginal increases in the mass normalization with increasing
-        resolution level.
+    \caption{Similar to Figure~\ref{fig:FeH}, but showing one individual Auriga
+        halo, where colours indicate the resolution level: L3 green, L4 orange, 
+        and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo 16.
+        \emph{Right:} Auriga halo 24. For all three haloes we find marginal 
+        increases in the mass normalization with increasing resolution level.
         \label{fig:logMFeH_res}
@@
     \includegraphics[width=0.31\textwidth]{{logMRgc_Au24}.png}
-    \caption{Same as Figure~\ref{fig:Rgc}, but here the colours indicate resolution
-        level: L3 green, L4 orange, and L5 blue. \emph{Left:} Auriga halo 6.
-        \emph{Mid:} Auriga halo 16. \emph{Right:} Auriga halo 24. For all three
-        haloes we find marginal increases in the mass normalization with increasing
-        resolution level.
+    \caption{Similar to Figure~\ref{fig:Rgc}, but showing one individual Auriga 
+        halo, where colours indicate the resolution level: L3 green, L4 orange, 
+        and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo 16. 
+        \emph{Right:} Auriga halo 24. For all three haloes we find marginal 
+        increases in the mass normalization with increasing resolution level.
         \label{fig:logMRgc_res}

### 2019-05-23 AurigaGCS.tex
Wrote some discussion

@@
 \begin{abstract}
-\todo[inline]{Rob Grand: `for many Auriga papers Carlos Frenk and Adrian Jenkins
-are offered co-authorship. Perhaps you could ask Simon about this.'}
 We investigate whether the galaxy formation model used for the Auriga simulations
 can produce a realistic globular cluster population at redshift zero. We compare
-properties of the simulated star particles in the Auriga haloes with
-catalogues of observations of the Milky Way globular cluster population available
+properties of the simulated star particles in the Auriga haloes with catalogues 
+of observations of the Milky Way and Andromeda globular cluster populations available
 in the literature. We find that the Auriga simulations do produce sufficient mass
@@
 different values for the combined product of the bound cluster formation efficiency
-and the globular cluster disruption rate. We investigate whether these differences
-could result from formation insitu vs. accreted star particles. We find ... TODO.
-Furthermore we test whether any of the Auriga galaxies has a metallicity and radial
-distribution that is consistent with the MW (M31) GCS. For all of the Auriga haloes
-we reject the null hypothesis that the simulated and observed metallicities are
-drawn from the same distribution at $\geq98.32$~\% confidence level, for the GCS
-of the Milky Way as well as that of the Andromeda galaxy. The same holds true for
-the distribution of galactocentric radius.
+and the globular cluster disruption rate. Furthermore we test whether any of the
+Auriga galaxies has a metallicity and radial distribution that is consistent with
+the MW (M31) GCS. For all of the Auriga haloes we reject the null hypothesis that
+the simulated and observed metallicities are drawn from the same distribution at
+$\geq98.32$~\% confidence level, for the GCS of the Milky Way as well as that of
+the Andromeda galaxy. The same holds true for the distribution of galactocentric 
+radius. Overall, the Auriga simulations produce old star particles with higher
+metallicities than the MW and M31 GCS and at larger radii. The formation efficiency
+would have to linearly decrease with increasing metallicity for the Auriga GC
+candidates to be consistent with the MW GCS.
 \end{abstract}
@@
 chemical- and structural properties, and on the phase-space distribution 
-of the MW GC system.
-% https://arxiv.org/abs/1805.01408
-% https://arxiv.org/abs/1807.09775
-% https://www.aanda.org/articles/aa/abs/2018/08/aa32698-18/aa32698-18.html
-Moreover, the visbility and ubiquity of GCs makes it possible to obtain integrated 
-properties of GCs within the Local Group with reasonable certainty, and even of 
-those that are located further away within the Virgo Supercluster.
+of the MW GC system \citep[e.g.][]{2018A&A...616A..12G, 2018ApJ...859L..13B,
+2019A&A...621A..56P, 2019MNRAS.484.2832V}. Moreover, the visbility and ubiquity
+of GCs makes it possible to obtain integrated properties of GCs within the Local 
+Group with reasonable certainty, and even beyond the Local Group \citep[e.g.][]{1991ARA&A..29..543H}.
 
@@
 a record of these properties and offer unique insight into the detailed chemical 
-and dynamical evolution history of their host galaxies. In theory, this information 
-should be readily available and easily observable in the low redshift Universe, given 
-that GCs survive nearly a Hubble time of evolution within the violent galactic 
-environments they live in. However, these long and complex evolution histories
-themselves imposes their imprints onto the GCs observables. Thus, a prerequisite to 
-infer galactic histories from studies of GC systems is to understand the 
-subtleties of the GC formation and evolution itself.
+and dynamical evolution history of their host galaxies \citep[see][for a recent review]
+{2006ARA&A..44..193B}. In theory, this information should be readily available
+and easily observable in the low redshift Universe, given that GCs survive nearly
+a Hubble time of evolution within the violent galactic environments they live in. 
+However, these long and complex evolution histories themselves impose their
+imprints onto the GCs observables. Thus, a prerequisite to infer galactic histories
+from studies of GC systems is to understand the subtleties of the GC formation
+and evolution itself.
 
-The literature offers several formation scenerarios that are consistent with the 
-data. One important constraint comes from bimodality in the colour distribution, 
-which is indicative of a bimodality in the underlying metallicity distribution 
-of GC systems. For example, GCs in the MW are typically split up in a metal-rich 
-(red) and metal-poor (blue) subpopulation divided at [Fe/H]~$=-1$ 
-\citep[e.g.][]{Harris2001}. These two subpopulations could be associated to the 
-galactic disk, respectively to the stellar halo \citep[e.g.][]{1985ApJ...293..424Z}. 
+One important ingredient for plausible formation mechanisms comes from observed 
+bimodality in the colour distribution, believed to be indicative of bimodality
+in the underlying metallicity distribution of GC systems. GCs in the MW can 
+be split up into a metal-rich (red) disk, and a metal-poor (blue) halo
+(sub)population. The exact dividing value slightly differs between authors,
+e.g. [Fe/H]~$=-0.8$ \citep[according to][]{1985ApJ...293..424Z}, or
+[Fe/H]~$=-1.0$ \citep[according to][]{Harris2001}, and may also differ between
+\newpage
+galaxies \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L,
+2006ApJ...639...95P}. It has long been debated whether the Andromeda GCS metallicity 
+distribution is uni- bi- or multimodal, with \citet{2016ApJ...824...42C} recently
+arguing that the data favours three groups (split at [Fe/H] $= -0.4$ and $-1.5$)
+after more accurate age-measurements improved classification of star clusters
+as globular (or otherwise).
+
+The literature offers several formation scenarios.
+
 The latter is supported by observed similarities between the spatial distribution
@@
 metal-poor subpopulation may be $1.5$~Gyr younger than the metal-rich counterpart 
-\citep{2005AJ....130..116D}, providing futher support that the GC population indeed
+\citep{2005AJ....130..116D}, providing further support that the GC population indeed
 consists of two distinct classes.
@@
 
-\citet{2006ARA&A..44..193B} for a review of extragalactic GCs and galaxy
-formation.
+\citet{2010MNRAS.404.1203F} collected age-metallicity observations from the
+literature and found one track with constant age of 12.8~Gyr, and one track
+with branches towards younger ages. These branches are dominated by GCs associated 
+with the Sagittarius, Canis Major and other accreted dwarf galaxies, ultimately
+indicating that 27-47 GCs (about one 25\% of the MW GCS) have been accreted
+from six to eight dwarf galaxies. \citet{2019MNRAS.486.3134K, 2019MNRAS.486.3180K}
+show that GC simulated age-metallicity space of the E-MOSAICS suite indeed allows 
+for a reconstruction of the merger history of the Milky Way-like galaxies, and 
+conclude that 40\% of the MW GCS has been accreted from galaxies with a stellar
+mass range of $2 \cdot 10^{7} - 2 \cdot 10^{9}$ M\Sun, and $6\pm1$ are core remnants
+of accreted dwarfs.
 
@@
 $5 \times 10^4$, $6 \times 10^3$]~M\Sun \, with gravitational softening of
-collissionless particles $\epsilon$~=~[$738, 369, 184$]~pc.
+collissionless particles $\epsilon$~=~[$738, 369, 184$]~pc. The mass resolution
+of the Auriga simulations is thus close to the characteristic peak mass of the
+lognormal GC mass distribution of $10^{5}$~M\Sun \citep{1991ARA&A..29..543H}, 
+although the gravitational softening is two orders of magnitudes larger than
+typical GC radii. High-density gaseous regions are thus not expected to produce
+surviving stellar clumps (GCs) with masses and radii consistent with GCs because
+such objects would numerically disperse, even in the highest-resolution runs.
+On the other hand, we can investigate (statistical) properties of age-selected 
+GC candidates because each star particle represents a single stellar population
+with a total mass that could be consistent with one globular cluster.
 
@@
 
-We find that the age cut lowers the mean metallicity from \textasciitilde{}$0.0$
-to \textasciitilde{}$-0.6$.
+We find that the age cut lowers the mean metallicity from $0.0$ to $-0.6$.
 Furthermore, the old accreted stars generally have lower metallicities than the
@@
 and 98.32~\%). Here we find that the cumulative distributions are more or less 
-similar up to [Fe/H]~\textasciitilde{}$-0.5$, above which the simulations yield higher number 
+similar up to [Fe/H]~$-0.5$, above which the simulations yield higher number 
 counts which drives the KS test statistic over the critical values. This affirms
@@
 of GC candidates that is consistent with the MW. For the GC candidates in M31
-we find a constant mass excess up to \textasciitilde{}$-0.9$, above which the 
+we find a constant mass excess up to $-0.9$, above which the 
 simulations produce a higher mass excess with increasing metallicity. If dynamical
@@
 \label{sec:discussion_FeH}
-\citet[][p. 234]{1998gcs..book.....A} and \citet[][p. 38]{Harris2001} describe
-the bimodal [Fe/H] distribution of the MW GCS. The latter fits a double
-Gaussian that peaks at [Fe/H] = $-1.59$ (metal-poor) and $-0.51$ (metal-rich)
-with dispersions of $0.34$ and $0.23$. T
-KMM mixture-modeling
+We find that the metallicity distributions of GC candidates in the Auriga
+simulations are more metal-rich than the MW (M31) GCS. Although the (old) star 
+particles represent single stellar populations with a mass (resolution) comparable 
+to the peak of the GCMF, they are in fact statistical tracers of the stellar 
+population of the galaxy as a whole. Therefore only a (small) fraction of the 
+star particles may represent plausible formation sites of GCs, whereas the majority
+represent (halo) field stars - the disk component effectively falls outside
+our selection of star particles due to the age cut. Globular clusters are 
+$\sim$~$0.5$ dex more metal-poor than spheroid stars observed at the same radius
+for almost all galaxies \citep{1991ARA&A..29..543H}. Our finding that star particles older 
+than 10~Gyr have higher metallicities than the MW (M31) GCS may simply be a 
+reflection thereof.
 
-Furthermore, 
-We note that the scatter between different
-Auriga haloes is much smaller than the difference between the MW and M31 GCSs.
-We conclude that old star particles in the Auriga simulation suite as a whole
-cannot be consistent with both the Milky Way and the Andromeda globular cluster
-system.
+\citet[][p. 234]{1998gcs..book.....A} and \citet[][p. 38]{Harris2001} quantify
+the bimodality of the [Fe/H] distribution of the MW GCS, the latter fit a double
+Gaussian which peaks at [Fe/H] = $-1.59$ (metal-poor) and $-0.51$ (metal-rich)
+and dispersions of $0.34$ and $0.23$. However, the metallicity distribution of 
+GC candidates in the Auriga simulations is not bimodal, although an offset between
+the mean values does emerge when further splitting them up according to birth location 
+(accreted or in-situ). The majority of the simulations show an offset in the mean 
+values of roughly $0.3$~dex between both subpopulations, while a small number of 
+simulations has an offset of order $0.5$~dex. Our finding that the mean values of 
+the old insitu GC candidates are roughly consistent with the metal-rich MW GCs 
+could be interpreted as an indication that this subpopulation may have formed 
+in-situ. However, we also notice that a substantial number of simulations has
+similar mean values for all GC candidates, and the simulated insitu GC candidates 
+have larger dispersions than the metal-rich GCs. Moreover, the offset between the 
+mean of the metal-rich and metal-poor populations in the MW is $1$ dex, a factor 
+$2-3$ larger than the offset we find between the insitu and accreted populations. 
+The simulations are not consistent with the picture that all metal-rich GCs 
+formed insitu and that all metal-poor GCs were accreted.
 
-We observe an increasing trend with increasing metallicity
-for the Milky Way over the entire range of the data, while the M31 GCS shows
-this increase only in the range [Fe/H]$>$-0.5 (although not for the \emph{old
-accreted} component.
+\citet{2006ARA&A..44..193B} compare the number of metal-poor GCs to the stellar
+halo mass and find\footnote{the quantity $T$ is the number of GCs per $10^9$ M\Sun \,
+of galaxy stellar mass} $T^n_{\text{blue}} \sim 100$, while the
+number of metal-rich GCs compared to the bulge mass yields $T^n_{\text{red}} \sim 5$,
+and therefore conclude that the formation efficiency of metal-poor GCs is
+twenty times higher than the metal-rich GCs with respect to field stars.
 
-Furthermore we test the null hypothesis that the metallicity distribution of the
-MW (M31) GCS and the \emph{old}, \emph{old insitu}, and \emph{old accreted} star
-particles in the Auriga simulations are drawn from the same underlying
-distribution. We calculate the two-sample Kolmogorov-Smirnov test statistic for
-all thirty Auriga level 4 haloes and reject the null hypothesis for every halo,
-for every sub set of star particles at least at the 99.99\% confidence level.
-In addition, the null hypothesis that the metallicity distributions of the MW
-and M31 GCS are drawn from the same distribution is rejected at the 99.99997\%
-confidence level.
+% Interestingly, the cross-over point above (below) which the mass-weighted 
+% metallicity distribution of GC candidates is dominated by those that have
+% formed insitu (were accreted) coincides with the separation between the metal-rich
+% and metal-poor population for the MW GCS at [Fe/H]~=~$-1$.
 
@@
 \label{sec:discussion_Rgc}
+The M31 GCS has a factor 2-3 more GCs at large radii compared to the MW GCS,
+which may indicate that M31 has a richer merger history than the MW. In the 
+Auriga simulations we find that the GC candidates at radii larger than 
+$\sim20$~kpc are indeed dominated by accreted star particles. However, we select
+star particles that are bound to the main halo and main subhalo, which means that
+we include particles up to the virial radius $R_{200}$. The Auriga simulations 
+have no problem populating the stellar halo up to the virial radius, even with 
+our additional age cut. On the other hand, the MW and M31 have fewer GCs at large
+radii. We expect tidal disruption to be less efficient at larger radii, thus, 
+the formation efficiencies of the accreted GC candidates would have to be lower.
+Our classification as GC candidates could, for example, be improved by selecting
+a number of globular clusters based on the $M_{vir}-N_{\text{GC}}$ correlation
+found by \citet{2019arXiv190100900B}, and taking a virial mass below which none
+of the star particles is treated as GC candidate.
 
-\todo[inline]{
-    Harris: `Somewhat arbitrarily, I will take the region $r_p > 3$ kpc
-    (containing 75 clusters) as the fiducial Milky Way sample. If we were to
-    view the Milky Way at the same inclination angle to the disk as we see
-    M31, this cutoff in projected distance would correspond roughly to the
-    inner distance limits in the M31 halo sample.'
-}
+% \todo[inline]{
+%     Harris: `Somewhat arbitrarily, I will take the region $r_p > 3$ kpc
+%     (containing 75 clusters) as the fiducial Milky Way sample. If we were to
+%     view the Milky Way at the same inclination angle to the disk as we see
+%     M31, this cutoff in projected distance would correspond roughly to the
+%     inner distance limits in the M31 halo sample.'
+% }
 
-\subsection{Metallicity-radial space}
-\label{sec:discussion_FeHRgc}
-See Figure~\ref{fig:observations_FeHRgc} in Sec.~\ref{sec:observations_FeHRgc}.
-
-\todo[inline]{
-``The fraction of all star formation that occurs in bound stellar clusters (the cluster formation efficiency, hereafter CFE) follows by integration of these local clustering and survival properties over the full density spectrum of the ISM, and hence is set by galaxy-scale physics.
-We derive the CFE as a function of observable galaxy properties, and find that it increases with the gas surface density'' \citep{2012MNRAS.426.3008K}
-}
-
-\subsection{Age cut}
-Although the age distribution of M31 Perhaps an age cut of 6~Gyr would would be more
-appropriate for M31, see Figure~\ref{fig:MW-M31-age}.
-
-\todo[inline]{
-\citet{2016ApJ...824...42C} writes:
-``there are two broad, well-established differences:
-(1) the M31 GC system is more populous than the MW system, by a factor of
-$\sim$2-3, and (2) it does not exhibit the same obvious bimodality in
-metallicity \citep{2000AJ....119..727B, 2009A&A...508.1285G, 2011AJ....141...61C,
-2013A&A...549A..60C}. Both of these aspects may be reflections of dramatic
-differences discovered in these galaxies stellar halos, where the M31 halo
-appears much more metal-enriched, with massive substructures suggesting a more
-active satellite accretion history \citep[e.g.][]{2009Natur.461...66M}''
-}
-
-\subsection{From star particles to globular clusters}
+\subsection{Star particles are not globular clusters}
 \label{sec:discussion_mass_excess}
-Star particles are not globular clusters. Many stars do form in clusters, but
-not all clusters end up gravitationally bound. Star particles in the
-Auriga simulations represent single-age stellar populations that have formed
-at the same location within the galaxy. Therefore one could assume a model
-for the star cluster formation efficiency $\Gamma$, which could be used to
-`convert' star particles to bound star clusters e.g. Kruijssen (2012). This
-model relies on the local birth properties of the star particles. However,
-in our analysis we can retrieve the properties of the star particle in the
-first snapshot it was recorded, but not the gas properties at times of birth.
-Therefore we are unable to model the formation of star clusters in more detail.
+A major improvement to our classification of star particles as GC candidates
+could be made by explicitly taking into the formation efficiency of bound star 
+clusters \citep{2012MNRAS.426.3008K}, which depends on the local ISM properties
+(density, pressure, sound speed). However, the only information available in 
+post-processing are the properties of the star particles recorded in the first 
+snapshot after formation. We could attempt to obtain the properties of the nearest
+gas cell, but this would have to be limited to a very narrow time window between
+the time of formation and the time of the snapshot because the star particle could 
+otherwise be in a completely different location than where it was born initially. 
+Moreover, even if the birth time and snapshot time would coincide, it would not
+be obvious that the gas cell will yield the correct quantities as the formation
+of the star itself alters the properties of the gas. We therefore did not further
+attempt a more sophisticated modeling of the cluster formation efficiency in
+post-processing.
 
@@
 ignoring the effects of (dynamical) disruption of globular clusters over nearly
-a Hubble time. As shown by Pfeffer et al. (2018), a detailed model of the tidal
+a Hubble time. As shown by \citep{2018MNRAS.475.4309P}, a detailed model of the tidal
 history of star clusters requires a temporal resolution of order mega year. For
-the Auriga level 4 simulations we have 128 snapshots for the age of the Universe,
-thus, a far too coarse temporal resolution for meaningful calculations.
+the Auriga L4 simulations we have a total of 128 snapshots available over the
+age of the Universe, thus, far too coarse temporal resolution for meaningful 
+calculations of tidal disruption along the orbit of our GC candidates. Therefore 
+we can only combine these two shortcomings of our analysis into the `mass excess',
+which includes the cluster formation efficiency and consecutive globular cluster 
+disruption.
 
-Therefore we investigate the over-production of simulated mass in the metallicity
-and radial bins and use the term `efficiency' to refer to the combined product
-of bound cluster formation and globular cluster disruption. In Figure~\ref{fig:todo}
-we show the efficiencies that we find when we compare the simulations to the
-globular cluster systems of the Milky Way as well as that of Andromeda (M31).
+% \todo[inline]{
+% \citet{2019MNRAS.486.3134K} ``Due to the multitude of low-mass progenitors and 
+% rapid merging during this early phase of galaxy growth, we recommend to reserve
+% the term `ex situ GCs' for accretion events taking place at $z < 2$, when the
+% central spheroid has formed and accretion events unambiguously contribute to the
+% spatially extended (`halo') GC population.''
+% }
+% 
+% 
+% \citet{2016ApJ...824...42C}
+% ``We find that the clusters can be divided into three major metallicity groups 
+% based on their radial distributions: (1) an inner metal-rich group ([Fe/H] $> -0.4$);
+% (2) a group with intermediate metallicity (with median [Fe/H] $= -1$); and (3) 
+% a metal-poor group, with [Fe/H] $< -1.5$.''
+% 
+% \citet{2016ApJ...824...42C}
+% ``Although this disk mode of GCs is intriguing, the very dominant subpopulations 
+% in M31 are the lower-metallicity GCs. It seems likely that these objects were 
+% brought in by the accretion of satellite galaxies (minor mergers). The populous
+% GC system of M31, relative to the MW, would then reflect a more active accretion
+% history, and the radial gradient of GC metallicities could arise through 
+% correlations of both metallicity and dynamical friction with satellite galaxy
+% mass (e.g., Amorisco 2016).''
 
@@
 \label{sec:conclusions}
+
+We investigate GC candidates in the Auriga simulations and draw the following
+conclusions.
+
+\begin{itemize}
+    \item The star formation model implemented in the Auriga simulations produces
+    metallicity distributions that are more metal-rich the Milky Way and M31 
+    globular cluster systems.
+    \item We reject the null hypothesis $H_0$ that MW (M31) and the GC candidates
+    (all, insitu, and accreted) are drawn from the same underlying distribution
+    for all Auriga L4 galaxies with $\geq 98.68$~\% confidence.
+    \item GC candidates in the Auriga simulations may be found out to $R_{200}$,
+    given our selection function of star particles selects all stars bound to the
+    main subhalo in the main halo. The stellar mass is dominated by accreted star
+    particles at radii beyond $20$~kpc The GCs in the MW and M31, on the other hand,
+    have a much smaller radial extend. 
+    \item The cluster formation efficiency would have to increase with decreasing
+    metallicity for GC candidates in the Auriga simulations to be consistent
+    with the Milky Way GC system, given that we expect dynamical evolution to more strongly affect GC
+    candidates at smaller radii.
+    \item The Auriga simulations are not consistent with the picture that all 
+    metal-rich GCs formed insitu and that all metal-poor GCs were accreted.
+\end{itemize}
 

### 2019-06-03 AurigaGCS.tex
Some updates to introduction

@@
 Globular clusters (GC)s are omnipresent, bright, old, and amongst the simplest
-stellar configurations in the Universe. The globular cluster systems (GCS) of
-the Milky Way (MW) and the Andromeda galaxy (M31) have been studied extensively 
-over the last decades. More recent analyses of the Gaia data shed new light on the 
-chemical- and structural properties, and on the phase-space distribution 
-of the MW GC system \citep[e.g.][]{2018A&A...616A..12G, 2018ApJ...859L..13B,
-2019A&A...621A..56P, 2019MNRAS.484.2832V}. Moreover, the visbility and ubiquity
-of GCs makes it possible to obtain integrated properties of GCs within the Local 
-Group with reasonable certainty, and even beyond the Local Group \citep[e.g.][]{1991ARA&A..29..543H}.
-
+stellar configurations in the Universe. The GC system of the Milky Way (MW) consists
+of $\sim$160 GCs, most of which are older than $\sim$10~Gyr, and the Andromeda 
+galaxy (M31) hosts roughly twice as many GCs with ages $\geq 6$~Gyr. With masses of 
+$10^{4-6}$ M\Sun within typical half-mass radii of a few parsec, the combined stellar 
+light emitted by GCs makes it possible to obtain integrated properties within the Local
+Group with reasonable certainty, and even allows for observations beyond the Local Group 
+\citep[e.g.][]{1991ARA&A..29..543H}. The extensive literature on GCs is summarised in
+several books and review articles \citep[e.g.][]{Harris2001, 2004Natur.427...31W, 
+2006ARA&A..44..193B, 2012A&ARv..20...50G, 2014CQGra..31x4006K, 2018RSPSA.47470616F}, and
+recent analyses of the Gaia data shed new light on the chemical- and structural properties,
+and on the phase-space distribution of the MW GC system \citep[e.g.][]{2018A&A...616A..12G, 
+2018ApJ...859L..13B, 2019A&A...621A..56P, 2019MNRAS.484.2832V}.
+
+\todo[inline]{Correlations between GC systems and their host galaxies}
 The natal gas regions in which globular clusters form inherit key characteristics 
@@
 
-One important ingredient for plausible formation mechanisms comes from observed 
-bimodality in the colour distribution, believed to be indicative of bimodality
-in the underlying metallicity distribution of GC systems. GCs in the MW can 
-be split up into a metal-rich (red) disk, and a metal-poor (blue) halo
-(sub)population. The exact dividing value slightly differs between authors,
-e.g. [Fe/H]~$=-0.8$ \citep[according to][]{1985ApJ...293..424Z}, or
+The literature offers a wealth of formation channels, most of which can be broadly
+classified as ex situ, or as in situ scenarios. In the former picture, GCs form 
+in smaller, more metal-poor progenitors that are accreted in subsequent mergers,
+as can naturally be expected in the framework of hierarchical galaxy formation
+\citep[e.g.][]{1978ApJ...225..357S, 1984ApJ...277..470P}, and Rosenblatt et al. 1988; 
+Cen 2001; Bromm \& Clarke 2002; Diemand et al. 2005; Moore et al. 2006; Boley et al. 2009;
+Griffen et al. 2010; Trenti et al. 2015; Kimm et al. 2016; Ricotti et al. 2016;
+Boylan-Kolchin 2017; Creasey et al. 2019. As for in situ scenarios,
+\citet{1985ApJ...298...18F} propose that thermal instabilities in the collapsing
+proto-galaxy may lead to GC formation, \citet{1992ApJ...384...50A, 2010ApJ...718.1266M,
+2018MNRAS.480.2343C} suggest that GC formation is triggered by (major) gas-rich
+galaxy-galaxy mergers and/or interactions, and \citet{2005ApJ...623..650K} envision
+GCs to form in the cores of supergiant molecular clouds located within gaseous disks
+of (high-redshift) galaxies.
+
+Another broad distinction between formation mechanisms are models that rely on 
+special conditions in the early Universe, or those that test the hypothesis that
+GC formation at high redshift is governed by the same physical processes of young 
+massive clusters \citep[see][for a review]{2010ARA&A..48..431P} in the Local
+Universe, where differences arise as the result of nearly a Hubble time of
+(dynamical) evolution. This (latter) scenario is extensively tested in the recent
+E-MOSAICS project \citep{2018MNRAS.475.4309P, 2019MNRAS.486.3134K}, which 
+comprises a suite of cosmological zoom simulations of MW-like galaxies. As for
+the former category, \citet{2017Ap&SS.362..183R} investigate what fraction of 
+(multiple) stellar populations ends up in bound star clusters after their
+formation in gravitationally unstable expanding supershells, which arise from
+hypernova explosions of massive pop. III stars. \citet{2019arXiv190408941C} 
+speculate in a recent study that GCs may form in supersonically induced gasseous 
+objects at high redshifts, and \citet{2019arXiv190508951M} propose that high speed
+collisions leave cooling gas without their DM subhaloes which could form GC 
+populations that can reproduce the observed $N_{\text{GC}}-M_{\text{vir}}$
+correlation \citep[e.g.][]{2019arXiv190100900B} with bimodal metallicity
+distributions and ages consistent with observations.
+
+One important constraint on plausible formation mechanisms comes from observed 
+bimodality in the colour distribution of most galaxies, believed to be indicative 
+of bimodality in the underlying metallicity distribution of GC systems. GCs in
+the MW can indeed be split up into a metal-rich (red), and a metal-poor (blue) 
+(sub)population. The former group is associated to the galactic disk because it
+is a flattened, rotating population found at radii smaller than solar. The latter,
+on the other hand, is more radially extended, more populated (with three times
+more blue than red GCs), and may be $\leq 1.5$~Gyr older \citep{2005AJ....130..116D}. 
+The exact dividing metallicity slightly differs between authors, e.g.
+[Fe/H]~$=-0.8$ \citep[according to][]{1985ApJ...293..424Z}, or
 [Fe/H]~$=-1.0$ \citep[according to][]{Harris2001}, and may also differ between
-\newpage
 galaxies \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L,
-2006ApJ...639...95P}. It has long been debated whether the Andromeda GCS metallicity 
-distribution is uni- bi- or multimodal, with \citet{2016ApJ...824...42C} recently
-arguing that the data favours three groups (split at [Fe/H] $= -0.4$ and $-1.5$)
+2006ApJ...639...95P}. In contrast, it has long been debated whether the Andromeda 
+GCS metallicity distribution is uni- bi- or multimodal, and \citet{2016ApJ...824...42C}
+argue that the data favours three groups (split at [Fe/H] $= -0.4$ and $-1.5$)
 after more accurate age-measurements improved classification of star clusters
-as globular (or otherwise).
-
-The literature offers several formation scenarios.
+as globular (or otherwise). Moreover, the Andromeda GCS has $2-3$ times as many
+GCs at large radii, believed to be indicative of a more rich merger history.
 
@@
 are expected to be long-lived.
-
-In a recent study, Chiou et al. speculate that GCs may form in supersonically
-induced gasseous objects at high redshifts. These objects are free of dark matter 
-and populate a mass range consistent with the typical mass scale of GCs. 
-Interestingly, the authors find present-day absolute visual magnitude and 
-characteristic scales consistent with GCs in the Local group, based on a 
-rudimentary star formation model.
 
@@
 \todo[inline]{Paragraph: narrow down to this work}
-\begin{itemize}
-    \item The star formation model implemented in the Auriga simulations is capable of producing a suite/population of realistic Milky Way-like galaxies at redshift zero.
-    \item Therefore the question naturally arises whether or not the Auriga simulations are also capable of faithfully producing a globular cluster population as observed in the Milky Way (or Andromeda).
-    \item Globular cluster formation in cosmological zoom simulations is very interesting for two reasons.
-First of all, extragalactic observations typically show the integrated properties of globular clusters rather than that of the individual stars within the clusters.
-Moreover, the typical mass scale of globular clusters is comparable to the numerical (mass) resolution of cosmological zoom simulations.
-The detailed small scale physics that is at play for real world globular clusters appears in observations as the combined effect of the $10^{3-6}$ M\Sun, compared to a mass resolution of $10^{3-5}$ M\Sun for the Auriga simulations.
-Globular clusters can therefore serve as an ultimate test to the star formation model that is implemented in the numerical simulations.
-Secondly, cosmological zoom simulations provide an accurate recording of the full and detailed merger history of the simulated galaxy.
-This is important because theoretical paradigms for globular cluster formation in the literature know two distinct classes of GCs that are separated by their exact formation sites: an in-situ versus an accreted population.
-Cosmological zoom simulations uniquely allow for an investigation into globular cluster formation with particular focus on the in-situ and accreted populations.
-\end{itemize}
+The star formation model implemented in the Auriga simulations is capable of 
+producing realistic Milky Way-like (spiral disk) galaxies at redshift zero. Therefore 
+the question naturally arises whether or not the Auriga simulations also produce
+a subset of star particles (GC candidates) which is consistent with the GC system
+of the Milky Way and/or the Andromeda galaxy (M31). The typical mass scale of 
+globular clusters is comparable to the numerical (mass) resolution of cosmological 
+zoom simulations. The detailed physics of GC formation in the Universe appears in
+observations as the combined effect of the $10^{3-6}$ M\Sun, compared to a mass 
+resolution of $10^{3-5}$ M\Sun in the Auriga simulations. Globular clusters can 
+therefore serve as an ultimate test to the star formation model that is implemented 
+in the numerical simulations. Moreover, cosmological zoom simulations provide a
+detailed (formation and merger) history of the simulated galaxies. This is 
+important because theoretical paradigms for globular cluster formation in the 
+literature know two distinct classes of GCs that are separated by their exact 
+formation sites: an in situ versus an accreted population. Cosmological zoom 
+simulations uniquely allow for an investigation into globular cluster formation 
+with a particular focus on the properties of the in situ versus accreted subpopulations.
 

### 2019-06-05 AurigaGCS.tex
Introduction

@@
 Auriga galaxies has a metallicity and radial distribution that is consistent with
-the MW (M31) GCS. For all of the Auriga haloes we reject the null hypothesis that
+the MW (M31) GCS. For any one of the Auriga haloes we reject the null hypothesis that
 the simulated and observed metallicities are drawn from the same distribution at
@@
 \section{Introduction}
-Globular clusters (GC)s are omnipresent, bright, old, and amongst the simplest
-stellar configurations in the Universe. The GC system of the Milky Way (MW) consists
-of $\sim$160 GCs, most of which are older than $\sim$10~Gyr, and the Andromeda 
-galaxy (M31) hosts roughly twice as many GCs with ages $\geq 6$~Gyr. With masses of 
-$10^{4-6}$ M\Sun within typical half-mass radii of a few parsec, the combined stellar 
-light emitted by GCs makes it possible to obtain integrated properties within the Local
-Group with reasonable certainty, and even allows for observations beyond the Local Group 
-\citep[e.g.][]{1991ARA&A..29..543H}. The extensive literature on GCs is summarised in
-several books and review articles \citep[e.g.][]{Harris2001, 2004Natur.427...31W, 
-2006ARA&A..44..193B, 2012A&ARv..20...50G, 2014CQGra..31x4006K, 2018RSPSA.47470616F}, and
-recent analyses of the Gaia data shed new light on the chemical- and structural properties,
-and on the phase-space distribution of the MW GC system \citep[e.g.][]{2018A&A...616A..12G, 
-2018ApJ...859L..13B, 2019A&A...621A..56P, 2019MNRAS.484.2832V}.
-
-\todo[inline]{Correlations between GC systems and their host galaxies}
-The natal gas regions in which globular clusters form inherit key characteristics 
-from their parent (proto-)galaxies. GC populations, in turn, will therefore retain 
-a record of these properties and offer unique insight into the detailed chemical 
-and dynamical evolution history of their host galaxies \citep[see][for a recent review]
-{2006ARA&A..44..193B}. In theory, this information should be readily available
-and easily observable in the low redshift Universe, given that GCs survive nearly
-a Hubble time of evolution within the violent galactic environments they live in. 
-However, these long and complex evolution histories themselves impose their
-imprints onto the GCs observables. Thus, a prerequisite to infer galactic histories
-from studies of GC systems is to understand the subtleties of the GC formation
-and evolution itself.
+Globular clusters (GC)s are omnipresent, bright (with ${<}M^0_V{>} = -7.1 \pm 0.4$
+that is nearly independent of the host galaxy size and environment,
+\citealt{1991ARA&A..29..543H}), old ($\gtrsim$10~Gyr, \citealt{2005A&A...439..997P,
+2005AJ....130.1315S, 2009ApJ...694.1498M, 2013ApJ...775..134V}), and amongst the
+simplest stellar configurations in the Universe. The typical luminosity gives
+a characteristic mass of $1.4\cdot 10^5$~M\Sun \, (assuming a mass to light ratio
+$M/L_V \simeq 2$), and GCs have typical half-mass radii $r_h$ of a few parsec.
+GCs within the Milky Way can thus be studied in great detail (at the level of 
+individual stars), whereas integrated quantities can be explored with reasonable 
+certainty for GCs within - and even beyond \citep[e.g.][]{1991ARA&A..29..543H} -
+the Local Group.
+
+The extensive literature on GCs is summarised in several 
+books and review articles \citep[e.g.][]{1991ARA&A..29..543H, Harris2001, 2004Natur.427...31W, 
+2006ARA&A..44..193B, 2012A&ARv..20...50G, 2014CQGra..31x4006K, 2018RSPSA.47470616F},
+and recent analyses of the Gaia data shed new light on the chemical- and structural 
+properties, and on the phase-space distribution of the MW GC system \citep[e.g.][]{
+2018A&A...616A..12G, 2018ApJ...859L..13B, 2019A&A...621A..56P, 2019MNRAS.484.2832V}.
+A clear picture of the formation GC systems has yet to emerge, despite decades 
+of studies and the tremendous advances the last couple of years. It is clear, 
+however, that a fundamental understanding of GC formation and evolution promises 
+exciting insight into the detailed histories of their host galaxies due to their
+old ages and several correlations between GC systems and their parent galaxies.
+
+% There are several correlations between globular cluster systems and their
+% host galaxy. For example, the total mass of globular cluster systems
+% correlates with the halo mass \citep[e.g.][]{2010MNRAS.406.1967G}, the
+% the total number of GCs increases linearly with increasing virial mass
+% \citep[e.g.][]{2019arXiv190100900B}, and THIRD EXAMPLE.
 

### 2019-06-06 AurigaGCS.tex
Copy-pasted some paragraphs from references

@@
 distributions and ages consistent with observations.
+
+\citep{2019arXiv190505199C}
+``The  mean  and  dispersion  of  GC system MDFs have also been found to scale 
+with the mass of the host galaxy over a large range in galaxy mass (Peng et al.
+2006). Qualitatively, many galaxies have clearly multi-modal MDF (e.g., Gebhardt
+\& Kissler-Patig 1999; Peng et al. 2006; Brodie \&  Strader  2006;  Brodie  et  
+al.  2012),  but  the  most massive galaxies typically show broad, single-peaked 
+distributions (Harris et al. 2014, 2016, 2017a)''
 
@@
 
+\citep{2019MNRAS.486.5838R}
+``Out of the cluster formation models considered, the `no formation physics' model, 
+in which both the CFE and the ICMF are fixed throughout cosmic time, is 
+approximately equivalent to those studies  that  use  `particle-tagging' 
+techniques  to  identify  GCs  in cosmological simulations (e.g. Tonini 2013, 
+Renaud et al. 2017). We find that this cluster formation model continues to form GCs
+at a vigorous rate until the present time, which implies it overproduces 
+the total GC mass in the Milky Way by a factor
+5.5 relative to the mass formed in the fiducial model. Likewise, the continued
+formation  of  GCs  in  this  model  predicts  the  on-going  formation
+of massive (M $>10^5$ M\Sun) clusters with [Fe/H]< −0.5 should be observed in 
+Milky Way-mass galaxies at z=0. For these reasons, an environmentally independent
+cluster formation description is not compatible with observations.''
+
 \section{Summary and conclusions}

### 2019-06-11 AurigaGCS.tex
Start over w/ introduction. Sorta satisfied w/ first three paragraphs now

@@
 \section{Introduction}
-Globular clusters (GC)s are omnipresent, bright (with ${<}M^0_V{>} = -7.1 \pm 0.4$
-that is nearly independent of the host galaxy size and environment,
-\citealt{1991ARA&A..29..543H}), old ($\gtrsim$10~Gyr, \citealt{2005A&A...439..997P,
-2005AJ....130.1315S, 2009ApJ...694.1498M, 2013ApJ...775..134V}), and amongst the
-simplest stellar configurations in the Universe. The typical luminosity gives
-a characteristic mass of $1.4\cdot 10^5$~M\Sun \, (assuming a mass to light ratio
-$M/L_V \simeq 2$), and GCs have typical half-mass radii $r_h$ of a few parsec.
-GCs within the Milky Way can thus be studied in great detail (at the level of 
-individual stars), whereas integrated quantities can be explored with reasonable 
-certainty for GCs within - and even beyond \citep[e.g.][]{1991ARA&A..29..543H} -
-the Local Group.
+Globular clusters (GC)s are old, bright, ubiquitous, and various properties of
+GC systems show correlations with their host galaxies. GC systems are believed to
+retain information about the galactic (gas) conditions at times of formation,
+thus, could offer unique insight into the chemodynamical evolution of their 
+parent galaxies, if the formation and evolution of GCs- and GC systems themselves 
+is adequately understood. However, despite decades of research (the extensive 
+literature on GCs is summarised in several books and review articles, e.g.~\citealt{
+1991ARA&A..29..543H, Harris2001, 2004Natur.427...31W, 2006ARA&A..44..193B, 
+2012A&ARv..20...50G, 2014CQGra..31x4006K, 2018RSPSA.47470616F}), consensus on an 
+exhaustive picture of the formation of GCs is yet to be reached.
 
-The extensive literature on GCs is summarised in several 
-books and review articles \citep[e.g.][]{1991ARA&A..29..543H, Harris2001, 2004Natur.427...31W, 
-2006ARA&A..44..193B, 2012A&ARv..20...50G, 2014CQGra..31x4006K, 2018RSPSA.47470616F},
-and recent analyses of the Gaia data shed new light on the chemical- and structural 
-properties, and on the phase-space distribution of the MW GC system \citep[e.g.][]{
-2018A&A...616A..12G, 2018ApJ...859L..13B, 2019A&A...621A..56P, 2019MNRAS.484.2832V}.
-A clear picture of the formation GC systems has yet to emerge, despite decades 
-of studies and the tremendous advances the last couple of years. It is clear, 
-however, that a fundamental understanding of GC formation and evolution promises 
-exciting insight into the detailed histories of their host galaxies due to their
-old ages and several correlations between GC systems and their parent galaxies.
+The literature offers a wealth of formation scenarios. \citet{1968ApJ...154..891P}
+and \citet{1984ApJ...277..470P} argue that GCs form as the earliest bound
+structures in the Universe (i.e. prior to formation of the main galaxy), 
+noting that the Jeans length and mass shortly after recombination is consistent
+with typical GC masses and sizes. Alternative models suggest that GCs form during
+formation of proto-galaxies, for example as a result of thermal instabilities
+in hot gas-rich haloes \citep{1985ApJ...298...18F}, or triggered by other mechanisms
+such as shock compression or cloud-cloud colissions \citep[e.g.][]{
+1980glcl.conf..301G, 1992ApJ...400..265M, 1996ASPC...92..241L, 1994ApJ...429..177H,
+2001ApJ...560..592C}.
 
-% There are several correlations between globular cluster systems and their
-% host galaxy. For example, the total mass of globular cluster systems
-% correlates with the halo mass \citep[e.g.][]{2010MNRAS.406.1967G}, the
-% the total number of GCs increases linearly with increasing virial mass
-% \citep[e.g.][]{2019arXiv190100900B}, and THIRD EXAMPLE.
+Yet another hypothesis is that star cluster formation is triggered by (major) 
+gas-rich galaxy mergers \citep{1987nngp.proc...18S, 1992ApJ...384...50A},
+which is naturally expected within the framework of hierarchical assembly. One
+testable prediction of this scenario is the formation of young clusters in
+interacting and merging galaxies, which has been observed and show remarkable
+similarities with globulars in the Milky Way \citep[e.g.][]{1995AJ....109..960W, 
+1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}. Moreover, models
+that test this hypothesis yield GC populations consistent with various 
+observables \citep[e.g.][]{2010ApJ...718.1266M, 2018MNRAS.480.2343C}, and
+the recent numerical simulation of an isolated dwarf-dwarf merger executed at 
+very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$) 
+produce promising star clusters that could be globular progenitors \citep{2019arXiv190509840L}.
 
-The literature offers a wealth of formation channels, most of which can be broadly
-classified as ex situ, or as in situ scenarios. In the former picture, GCs form
-in smaller, more metal-poor progenitors that are accreted in subsequent mergers,
-as can naturally be expected in the framework of hierarchical galaxy formation
-\citep[e.g.][]{1978ApJ...225..357S, 1984ApJ...277..470P}, and Rosenblatt et al. 1988;
-Cen 2001; Bromm \& Clarke 2002; Diemand et al. 2005; Moore et al. 2006; Boley et al. 2009;
-Griffen et al. 2010; Trenti et al. 2015; Kimm et al. 2016; Ricotti et al. 2016;
-Boylan-Kolchin 2017; Creasey et al. 2019. As for in situ scenarios,
-\citet{1985ApJ...298...18F} propose that thermal instabilities in the collapsing
-proto-galaxy may lead to GC formation, \citet{1992ApJ...384...50A, 2010ApJ...718.1266M,
-2018MNRAS.480.2343C} suggest that GC formation is triggered by (major) gas-rich
-galaxy-galaxy mergers and/or interactions, and \citet{2005ApJ...623..650K} envision
-GCs to form in the cores of supergiant molecular clouds located within gaseous disks
-of (high-redshift) galaxies.
+More recent modelling efforts combine various aspects from the aforementioned
+formation channels \citep[e.g.][]{2000ApJ...533..869C, 2002ApJ...567..853C, 2002MNRAS.333..383B,
+2003egcs.conf..224G}
 
-Another broad distinction between formation mechanisms are models that rely on
-special conditions in the early Universe, or those that test the hypothesis that
-GC formation at high redshift is governed by the same physical processes of young
-massive clusters \citep[see][for a review]{2010ARA&A..48..431P} in the Local
-Universe, where differences arise as the result of nearly a Hubble time of
-(dynamical) evolution. This (latter) scenario is extensively tested in the recent
-E-MOSAICS project \citep{2018MNRAS.475.4309P, 2019MNRAS.486.3134K}, which
-comprises a suite of cosmological zoom simulations of MW-like galaxies. As for
-the former category, \citet{2017Ap&SS.362..183R} investigate what fraction of
-(multiple) stellar populations ends up in bound star clusters after their
-formation in gravitationally unstable expanding supershells, which arise from
-hypernova explosions of massive pop. III stars. \citet{2019arXiv190408941C}
-speculate in a recent study that GCs may form in supersonically induced gasseous
-objects at high redshifts, and \citet{2019arXiv190508951M} propose that high speed
-collisions leave cooling gas without their DM subhaloes which could form GC
-populations that can reproduce the observed $N_{\text{GC}}-M_{\text{vir}}$
-correlation \citep[e.g.][]{2019arXiv190100900B} with bimodal metallicity
-distributions and ages consistent with observations.
-
-\citep{2019arXiv190505199C}
-``The  mean  and  dispersion  of  GC system MDFs have also been found to scale 
-with the mass of the host galaxy over a large range in galaxy mass (Peng et al.
-2006). Qualitatively, many galaxies have clearly multi-modal MDF (e.g., Gebhardt
-\& Kissler-Patig 1999; Peng et al. 2006; Brodie \&  Strader  2006;  Brodie  et  
-al.  2012),  but  the  most massive galaxies typically show broad, single-peaked 
-distributions (Harris et al. 2014, 2016, 2017a)''
-
-One important constraint on plausible formation mechanisms comes from observed
-bimodality in the colour distribution of most galaxies, believed to be indicative
-of bimodality in the underlying metallicity distribution of GC systems. GCs in
-the MW can indeed be split up into a metal-rich (red), and a metal-poor (blue)
-(sub)population. The former group is associated to the galactic disk because it
-is a flattened, rotating population found at radii smaller than solar. The latter,
-on the other hand, is more radially extended, more populated (with three times
-more blue than red GCs), and may be $\leq 1.5$~Gyr older \citep{2005AJ....130..116D}.
-The exact dividing metallicity slightly differs between authors, e.g.
-[Fe/H]~$=-0.8$ \citep[according to][]{1985ApJ...293..424Z}, or
-[Fe/H]~$=-1.0$ \citep[according to][]{Harris2001}, and may also differ between
-galaxies \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L,
-2006ApJ...639...95P}. In contrast, it has long been debated whether the Andromeda
-GCS metallicity distribution is uni- bi- or multimodal, and \citet{2016ApJ...824...42C}
-argue that the data favours three groups (split at [Fe/H] $= -0.4$ and $-1.5$)
-after more accurate age-measurements improved classification of star clusters
-as globular (or otherwise). Moreover, the Andromeda GCS has $2-3$ times as many
-GCs at large radii, believed to be indicative of a more rich merger history.
-
-The latter is supported by observed similarities between the spatial distribution
-and chemical signature of the `blue' GCs and the Galactic stellar halo
-\citep{2008A&ARv..15..145H}. Moreover, relative age-estimates indicate that the
-metal-poor subpopulation may be $1.5$~Gyr younger than the metal-rich counterpart
-\citep{2005AJ....130..116D}, providing further support that the GC population indeed
-consists of two distinct classes.
-
-People postulate that the frequent mergers that occur during hierarchical build-up
-of galaxies naturally produce (sub)populations of GCs from enriched gas on tight
-orbits, if the mass ratios and gas fractions of the mergers are sufficiently high.
-
-Boylan-Kolchin: the blue population could form in high density regions along the
-cosmic filament before or during the collapse of the proto-galaxy itself.
-This formation scenario would explain the presence of the oldest GCs with
-primordial metallicities in the (outer) haloes of galaxies as the GCs are
-accreted over time. Moreover, the tidal fields experienced by GCs at (outer) halo
-orbits is significantly lower than by GCs in the inner galaxy, thus such GCs
-are expected to be long-lived.
-
-An alternative paradigm is that GC formation does not rely on special conditions
-at high redshifts. Rather, the same physics that governs the formation of young
-massive clusters (YMCs) in the Local Group can be applied to the high redshift
-Universe. The observed differences between YMCs and GCs, in this scenario, arise
-naturally as the result intrinsic GC evolution within galactic tidal fields over
-a Hubble time. This interesting hypothesis is tested numerically by the E-MOSAICS
-people.
-
-\citet{2010MNRAS.404.1203F} collected age-metallicity observations from the
-literature and found one track with constant age of 12.8~Gyr, and one track
-with branches towards younger ages. These branches are dominated by GCs associated
-with the Sagittarius, Canis Major and other accreted dwarf galaxies, ultimately
-indicating that 27-47 GCs (about one 25\% of the MW GCS) have been accreted
-from six to eight dwarf galaxies. \citet{2019MNRAS.486.3134K, 2019MNRAS.486.3180K}
-show that GC simulated age-metallicity space of the E-MOSAICS suite indeed allows
-for a reconstruction of the merger history of the Milky Way-like galaxies, and
-conclude that 40\% of the MW GCS has been accreted from galaxies with a stellar
-mass range of $2 \cdot 10^{7} - 2 \cdot 10^{9}$ M\Sun, and $6\pm1$ are core remnants
-of accreted dwarfs.
-
-% \begin{itemize}
-%     \item \citet{2005MNRAS.364..367D}: ``The radial profile of the stellar halo
-%     and metal-poor globular clusters of the Milky Way suggest that these components
-%     formed in rare early peaks above $2.5 \sigma$ at redshift above 10. ''
-%
-%     \item \citet{2017MNRAS.465.3622R}: ``GCs among oldest astrophysical objects.
-%     GCs form in the early Universe in highest density peaks
-%     \citep[e.g.][]{2005MNRAS.364..367D, 2009ApJ...706L.192B}''
-%
-%     \item ``Hence, they witness most of the formation and evolution processes
-%     of galaxies, and can be used to probe them'' \citep{2006ARA&A..44..193B}
-% \end{itemize}
-
-\begin{itemize}
-    \item Special conditions in early Universe?
-    \item Formation in collapsing proto-galaxies (in-situ-ish?)
-    \item Formation as a result of (wet) mergers?
-    \item Formation in satellites that are later accreted?
-    \item No special conditions at high z, but connection between low-z YMC-
-        and high-z GC-formation where differences could result from Hubble time
-        of evolution?
-    \item This means that in order to test formation models against observations,
-        one not only needs needs to model GC formation, but also include the full
-        evolution over their lifetime in a cosmological tidal field.
-\end{itemize}
-
-\todo[inline]{Paragraph: ingredients for numerical studies}
-\begin{itemize}
-    \item High resolution in the ISM
-    \item Full cosmological evolution
-\end{itemize}
-
-% \todo[inline]{Paragraph: scientific context / state of the field: briefly summarise
-%     previous work and references work of other groups}
-% \begin{itemize}
-% \item Origin of the Milky Way globular clusters \citep{2017MNRAS.465.3622R}
-% \item GCs in FIRE \citep{2018MNRAS.474.4232K}
-% \item EMOSAICS project \citep{2018MNRAS.475.4309P}
-% \item GC-DMhalo connection \citep{2017MNRAS.472.3120B}
-% \item Origin of GC bimodality? \citep{2018MNRAS.479..200F}
-% \item \textit{GAIA} DR2: GC kinematics \citep{2018A&A...616A..12G}
-% \item Dating GC Tidal Disruption \citep{2018ApJ...859L..13B}
-% \item GC in N-body simulation \citep{2018ApJ...861...69C}
-% \item (Role of GC mass evolution on stream properties \citep{2018MNRAS.474.2479B})
-% \item GC formation from dwarfs to giants \citep{2018MNRAS.480.2343C}
-% \item (GC contribution to EOR \citep{2018MNRAS.479..332B})
-% \item Early Universe supermassive star / GC formation \citep{2018MNRAS.478.2461G}
-% \item GC formation in cold filaments \citep{2018ApJ...861..148M}
-% \item GC formation in high-redshift dwarf galaxies \citep{2018MNRAS.477..480Z}
-% \item GCs in MW outer region \citep{2017arXiv170804542P}
-% \item Impact of the Cutoff of the Cluster Initial Mass Function \citep{2018arXiv181001888C}
-% \item Metallicity gradients in the globular cluster systems of early-type galaxies: in situ and accreted components \citep{2018MNRAS.479.4760F}
-% \item Globular clusters in M31, Local Group, and external galaxies \citep{2016IAUS..317..120L}
-% \item Globular Clusters Formed within Dark Halos I: present-day abundance, distribution and kinematics \citep{2019MNRAS.482..219C}
-% \item (The mass of the Milky Way from satellite dynamics \citep{2018arXiv180810456C})
-% \item Globular cluster formation and evolution in the context of cosmological galaxy assembly: open questions \citep{2018RSPSA.47470616F}
-% \item The kinematics of globular clusters systems in the outer halos of the Aquarius simulations \citep{2016A&A...592A..55V}
-% \item Star Cluster Formation in Cosmological Simulations \citep{2017ApJ...834...69L, 2018ApJ...861..107L, 2018arXiv181011036L}
-% \item (A systematic analysis of star cluster disruption by tidal shocks - I. Controlled N-body simulations and a new theoretical model \citep{2018arXiv181200014W})
-% \item Spatial mixing of binary stars in multiple-population globular clusters \citep{2018MNRAS.tmp.3147H}
-% \item Star Clusters Across Cosmic Time \citep{2018arXiv181201615K}
-% \item Kinematics of Subclusters in Star Cluster Complexes: Imprint of their Parental Molecular Clouds \citep{2018arXiv181201858F}
-% \item Investigating the population of Galactic star formation regions and star clusters within a Wide-Fast-Deep Coverage of the Galactic Plane  \citep{2018arXiv181203025P}
-% \item Globular cluster number density profiles using \textit{Gaia} DR2 \citep{2019arXiv190108072D}
-% \item Clustering Clusters: unsupervised learning on GC observations (of log $M$,
-%     log $\sigma_0$, log $R_e$ , [Fe/H], log $|Z|$) to determine number of groups
-%     $k=2$ (disk/halo) or $k=3$ (disk/inner-halo/outer-halo): the optimal number
-%     of groups given the data is $k=3$. \citep{2019arXiv190105354P}.
-% \item There is a well-known hypothesis that Open Stars Clusters (OSCs) could form as a result
-%     of GCs crossing the disk. New kinematical data does not support
-%     this claim for two particular OSC-GC pairs, and does seem consistent
-%     with this scenario for six OSC-GC pairs \citep{2019arXiv190106481B}. (Note
-%     that GC crossing the disk could also trigger formation of multiple OSCs!)
-% \item DM halo mass can be inferred from number of globular cluster in galaxy
-%     \citep{2019arXiv190100900B}
-% \item GCs in M31 outer halo \citep{2019arXiv190111229W}
-% % TODO: last checked arXiv Mar 2, 2019
-% \end{itemize}
-
-% \todo[inline]{Paragraph, narrowing open questions in GC research down to formation,
-%     possibly ``Bimodality suggests two formation mechanisms''. In-situ
-%     formation vs. accretion in hierarchical build-up of galaxies naturally produces
-%     two populations of globular cluster.}
-% \begin{itemize}
-%     \item ``colour bimodality, blue and red clusters \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L, 2006ApJ...639...95P}
-%     \item ``blue metal-poor (with distribution peaking at [Fe/H] $\approx -1.5$ for the Milky Way), no sign of rotation as a population (..) more metal-rich (peak at [Fe/H] $\approx -0.5$ in the Milky  Way) more spatially concentrated and rotating with the galaxy.'' \citep{1996AJ....112.1487H}
-%     \item ``Blue clusters from in early Universe in galaxies that merge later. In (wet) merger process starbursts generate red population \cite{1992ApJ...384...50A, 1987nngp.proc...18S}''
-%     \item ``\citet{1997AJ....113.1652F} propose instead that blue globulars form when the protogalaxy itself collapses, in a metal-poor and turbulence media.
-The red population would form later, once the galactic disc has settled.
-The formation of globular clusters would then be a multiphase process, with the first phase being interrupted possibly by cosmic reionization \citep{2002MNRAS.333..383B}.''
-%     \item ``\citet{2005ApJ...623..650K, 2014ApJ...796...10L} advocate
-% that major mergers are at the origin of both sub-populations: blue
-% clusters form during early mergers (z > 4) while the red ones appear
-% in mergers at lower redshifts (even after z = 1). Although, this
-% scenario, combined with star formation enhancement in mergers,
-% seems appropriate in dense galactic environment leading to the
-% assembly of massive elliptical galaxies, like in the Virgo Cluster
-% as tested by \citet{2014ApJ...796...10L}, it does not apply to Milky Way-
-% like systems where no recent major merger took place (Wyse 2001;
-% Deason et al. 2013; Ruchti et al. 2014, 2015).
-% \item ``\citet{1998ApJ...501..554C} argue that red clusters form in situ while the blue ones are accreted, either via merging satellite galaxies, or by tidal capture of the clusters themselves \citep[see also][]{2013ApJ...762...39T}.''
-% \end{itemize}
-
-\todo[inline]{Paragraph: narrow down to this work}
-The star formation model implemented in the Auriga simulations is capable of
-producing realistic Milky Way-like (spiral disk) galaxies at redshift zero. Therefore
-the question naturally arises whether or not the Auriga simulations also produce
-a subset of star particles (GC candidates) which is consistent with the GC system
-of the Milky Way and/or the Andromeda galaxy (M31). The typical mass scale of
-globular clusters is comparable to the numerical (mass) resolution of cosmological
-zoom simulations. The detailed physics of GC formation in the Universe appears in
-observations as the combined effect of the $10^{3-6}$ M\Sun, compared to a mass
-resolution of $10^{3-5}$ M\Sun in the Auriga simulations. Globular clusters can
-therefore serve as an ultimate test to the star formation model that is implemented
-in the numerical simulations. Moreover, cosmological zoom simulations provide a
-detailed (formation and merger) history of the simulated galaxies. This is
-important because theoretical paradigms for globular cluster formation in the
-literature know two distinct classes of GCs that are separated by their exact
-formation sites: an in situ versus an accreted population. Cosmological zoom
-simulations uniquely allow for an investigation into globular cluster formation
-with a particular focus on the properties of the in situ versus accreted subpopulations.
+Previous studies
+\citep{2005ApJ...623..650K}
+\citep{2016ApJ...831..204R}
+\citep{2017ApJ...834...69L}
+\citep{2017MNRAS.465.3622R}
+\citep{2018MNRAS.474.4232K}
+\citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}
 
@@
 section~\ref{sec:auriga}, followed by a summary of the observations of the
-Milky Way (MW) globular cluster system (GCS) in section~\ref{sec:observations}
-that we use to compare our simulations to in section~\ref{sec:results}. We
-discuss our findings in section~\ref{sec:discussion} to come to our conclusions
-in section~\ref{sec:conclusions}.
+Milky Way (MW) and Andromeda globular cluster system (GCS) in
+section~\ref{sec:observations} that we use to compare our simulations to in
+section~\ref{sec:results}. We discuss our findings in section~\ref{sec:discussion}
+to come to our conclusions in section~\ref{sec:conclusions}.
 

### 2019-06-12 AurigaGCS.tex
More paragraphs for the introduction. Now reached paragraph focusing on (globular) star cluster formation in zoom simulations

@@
 retain information about the galactic (gas) conditions at times of formation,
-thus, could offer unique insight into the chemodynamical evolution of their 
+thus, could offer unique insight into the (chemodynamical) evolution of their 
 parent galaxies, if the formation and evolution of GCs- and GC systems themselves 
@@
 noting that the Jeans length and mass shortly after recombination is consistent
-with typical GC masses and sizes. Alternative models suggest that GCs form during
-formation of proto-galaxies, for example as a result of thermal instabilities
-in hot gas-rich haloes \citep{1985ApJ...298...18F}, or triggered by other mechanisms
-such as shock compression or cloud-cloud colissions \citep[e.g.][]{
-1980glcl.conf..301G, 1992ApJ...400..265M, 1996ASPC...92..241L, 1994ApJ...429..177H,
-2001ApJ...560..592C}.
+with typical GC masses and sizes. \citet{2005MNRAS.364..367D} and \citet{
+2009ApJ...706L.192B} argue that (the blue subpopulations of) GCs form in biased 
+dark matter halos at high redshift. Other recent hypotheses of GC formation prior 
+to collapse of the proto-galaxy include formation in colliding supershells 
+\citep{2017Ap&SS.362..183R}, in supersonically induced gaseous objects
+\citep{2019arXiv190408941C}, or in high-speed collisions of dark matter subhaloes
+\citep{2019arXiv190508951M}. \citet{2017MNRAS.472.3120B} suggests
+that (the blue subpopulation of) GCs could form in high density regions along
+the cosmic filament before or during collapse.
+
+Other models also date GCs formation during formation of the proto-galaxy itself,
+for example as a result of thermal instabilities in hot gas-rich haloes 
+(\citealt{1985ApJ...298...18F}, also see the discussions in \citealt{
+1990ApJ...363..488K}). Alternative formation trigggers are also explored, such as 
+(other causes of) shock compression, or cloud-cloud colissions \citep[e.g.][]{
+1980glcl.conf..301G, 1992ApJ...400..265M, 1994ApJ...429..177H, 1995ApJ...442..618V,
+1996ASPC...92..241L, 2001ApJ...560..592C}.
 
 Yet another hypothesis is that star cluster formation is triggered by (major) 
-gas-rich galaxy mergers \citep{1987nngp.proc...18S, 1992ApJ...384...50A},
+gas-rich (spiral) galaxy mergers \citep{1987nngp.proc...18S, 1992ApJ...384...50A},
 which is naturally expected within the framework of hierarchical assembly. One
 testable prediction of this scenario is the formation of young clusters in
-interacting and merging galaxies, which has been observed and show remarkable
-similarities with globulars in the Milky Way \citep[e.g.][]{1995AJ....109..960W, 
-1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}. Moreover, models
-that test this hypothesis yield GC populations consistent with various 
-observables \citep[e.g.][]{2010ApJ...718.1266M, 2018MNRAS.480.2343C}, and
-the recent numerical simulation of an isolated dwarf-dwarf merger executed at 
+interacting and merging galaxies, which has been observed and are found to show 
+remarkable similarities with globulars in the Milky Way \citep[e.g.][]{
+1995AJ....109..960W, 1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}.
+Moreover, modelling efforts of this framework yield GC (sub)populations consistent 
+with various observables \citep[e.g.][]{2010ApJ...718.1266M, 2018MNRAS.480.2343C}, 
+and the recent numerical simulation of an isolated dwarf-dwarf merger executed at 
 very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$) 
-produce promising star clusters that could be globular progenitors \citep{2019arXiv190509840L}.
+produce star clusters that could be globular progenitors \citep{
+2019arXiv190509840L}.
 
-More recent modelling efforts combine various aspects from the aforementioned
-formation channels \citep[e.g.][]{2000ApJ...533..869C, 2002ApJ...567..853C, 2002MNRAS.333..383B,
-2003egcs.conf..224G}
+As for the formation timeline, the scenarios (and flavours thereof) of \citet{
+1985ApJ...298...18F} and \citet{1992ApJ...384...50A} are intertwined because
+accretion and mergers continuously occurs trough out hierarchical build-up of
+galaxies. Various (other) hierarchical formation channels thus combine different
+aspects of the aforementioned paradigms, such as GC formation in (small) galactic
+disks before they are accreted onto an assembling galaxy \citep[e.g.][]{
+2000ApJ...533..869C, 2002ApJ...567..853C, 2002MNRAS.333..383B, 2003egcs.conf..224G}. 
+We refer to \citet{2001astro.ph..8034G} for a scoreboard of the aforementioned 
+paradigms compared to observations of the Milky Way globular cluster system.
 
-Previous studies
+% Rosenblatt+ 1988, Cen 2001, Bromm \& Clarke 2002, Diemand+ 2002, Moore+ 2006,
+% Boley+ 2009, Griffen+ 2010, Trenti+ 2015, Kimm+ 2016, Ricotti+ 2016, Boylan-Kolchin 2017,
+% Creasey+ 2019.
+
+We now turn to recent studies that focus on the hypothesis that the physical 
+processes responsible for the formation of young massive clusters (YMC)s (observable)
+in the local Universe also governs GC formation at high redshifts and differences
+between both classes of objects are caused by nearly a Hubble time of (dynamical)
+evolution. This picture is based on observed similarities between YMCs and GCs
+\citep[e.g.][]{1992AJ....103..691H}, % Schweizer+ 1996, Whitmore+ 1999, Bastian+ 2006
+and strengthened by observations of gravitationally lensed objects at high redshifts
+($z = 2-6)$. These sources have properties reminiscent of (local) YMCs and may be
+GC progenitors at times of formation (Vanzella et al. 2017; Johnson et al. 2017).
+Early modelling work by \citet{2015MNRAS.454.1658K} is now incorporated into
+cosmological zoom simulations and shows promising results
+\citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}.
+
+Recent studies by other groups also incorporate formation of (globular) star 
+clusters into cosmological zoom simulations.
+\todo[inline]{
+Cosmological Galform simulations (e.g. Oser et al. 2010; Cook et al. 2016; 
+Rodriguez-Gomez et al. 2016), in situ vs. ex situ, particle tagging.}
+
 \citep{2005ApJ...623..650K}
@@
 \citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}
+
+\citep{2010ApJ...718.1266M,2014ApJ...796...10L,2018MNRAS.480.2343C,
+2019MNRAS.486..331C,2019arXiv190505199C}
+
+% bimodality in the broad-band colours of many (perhaps most) GC systems (e.g.
+% Zepf & Ashman 1993; Elson, Santiago & Gilmore 1996; Geisler,
+% Lee & Kim 1996; Forbes, Brodie & Huchra 1997a; Gebhardt &
+% Kissler-Patig 1999; Kundu & Whitmore 2001; Larsen et al. 2001).
 

### 2019-06-13 AurigaGCS.tex
First version of the introduction done

@@
 % Keep the title short and informative.
-\title[Auriga GCS]{The Globular Cluster System of the Auriga Simulations}
+\title[Auriga GCS]{The globular cluster system of the Auriga simulations}
 
@@
 
-We now turn to recent studies that focus on the hypothesis that the physical 
-processes responsible for the formation of young massive clusters (YMC)s (observable)
-in the local Universe also governs GC formation at high redshifts and differences
+An idea that has recently been studied in detail is the hypothesis that the physical 
+processes responsible for the formation of young massive clusters \citep[YMCs, 
+see][for a review]{2010ARA&A..48..431P}, observable in the local Universe in great
+detail, also governs GC formation at high redshifts. In this framework, differences
 between both classes of objects are caused by nearly a Hubble time of (dynamical)
-evolution. This picture is based on observed similarities between YMCs and GCs
-\citep[e.g.][]{1992AJ....103..691H}, % Schweizer+ 1996, Whitmore+ 1999, Bastian+ 2006
+evolution \citep[e.g.][]{1987degc.book.....S}. This picture is based on observed 
+similarities between YMCs and GCs \citep[e.g.][]{1992AJ....103..691H,1999AJ....118.1551W}
 and strengthened by observations of gravitationally lensed objects at high redshifts
 ($z = 2-6)$. These sources have properties reminiscent of (local) YMCs and may be
-GC progenitors at times of formation (Vanzella et al. 2017; Johnson et al. 2017).
-Early modelling work by \citet{2015MNRAS.454.1658K} is now incorporated into
-cosmological zoom simulations and shows promising results
+GC progenitors at times of formation \citep{2017MNRAS.467.4304V,2017ApJ...843L..21J}.
+The modelling work by \citet{2011MNRAS.414.1339K,2012MNRAS.421.1927K,2015MNRAS.454.1658K} 
+is now incorporated into cosmological zoom simulations and shows promising results
 \citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}.
 
-Recent studies by other groups also incorporate formation of (globular) star 
-clusters into cosmological zoom simulations.
-\todo[inline]{
-Cosmological Galform simulations (e.g. Oser et al. 2010; Cook et al. 2016; 
-Rodriguez-Gomez et al. 2016), in situ vs. ex situ, particle tagging.}
-
-\citep{2005ApJ...623..650K}
-\citep{2016ApJ...831..204R}
-\citep{2017ApJ...834...69L}
-\citep{2017MNRAS.465.3622R}
-\citep{2018MNRAS.474.4232K}
-\citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}
-
-\citep{2010ApJ...718.1266M,2014ApJ...796...10L,2018MNRAS.480.2343C,
-2019MNRAS.486..331C,2019arXiv190505199C}
+Simulation resolutions have reached the mass range populated by GCs, and the
+gravitational force softening can be as low several parsec. A number of groups 
+can thus incorporate formation of (globular) star clusters into their 
+high-resolution hydrodynamical cosmological zoom simulations. \citet{
+2016ApJ...831..204R} run parsec scale simulations of the high-redshift universe 
+prior to reionization (the simulations stop at $z=9$), \citet{2017ApJ...834...69L} 
+implement a new subgrid model for star (cluster) formation and run simulations 
+that reach $z=3.3$, and the run of \citet{2017MNRAS.465.3622R} reaches $z=0.5$. 
+\citet{2018MNRAS.474.4232K} find that mergers can push gas to high density that
+quickly forms clustered stars that end up tightly bound by the end of the 
+simulation. A somewhat different approach couples semi-analytical models to DM-only
+simulations \citep{2010ApJ...718.1266M,2014ApJ...796...10L,2018MNRAS.480.2343C,
+2019MNRAS.486..331C,2019arXiv190505199C}, as is done in the work by 
+\citet{2019MNRAS.482.4528E}.
 
@@
 
-\todo[inline]{Paragraph: Paper outline}
-We summarise the relevant characteristics of the Auriga simulations in
+In this work we use state of the art simulations that produce realistic 
+spiral galaxies at redshift zero that reproduce a number of observables. Therefore
+the question naturally arises whether the simulations (also) yield a population 
+of star particles that is consistent with the Milky Way and/or Andromeda globular 
+cluster systems. In particular, we investigate the Auriga suite of cosmological 
+zoom simulations (\citealt{2017MNRAS.467..179G}, and described in 
+Sec.~\ref{sec:auriga}) which can serve as an ultimate test of the star formation 
+model implemented in these simulations. The plan of the paper is as follows. We
+summarise the relevant characteristics of the Auriga simulations in
 section~\ref{sec:auriga}, followed by a summary of the observations of the
@@
 TLRH acknowledges support from the International Max-Planck Research School (IMPRS) on Astrophysics.
-
 \todo[inline]{Check Auriga boilerplate that we need to acknowledge}
@@
 
+The analysis in this work was performed using the Python \citep{python}
+programming language, the IPython \citep{2007CSE.....9c..21P} environment, 
+the Numpy \citep{2011CSE....13b..22V}, Scipy \citep{scipy}, and Astropy 
+\citep{2013A&A...558A..33A} packages. Plots were generated using 
+Matplotlib \citep{2007CSE.....9...90H}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \bibliographystyle{mnras}
-\bibliography{AurigaGCS} % if your bibtex file is called example.bib
+\bibliography{AurigaGCS}
 
@@
 %%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-\clearpage
-\appendix
-\section{Scatter between individual Auriga haloes, and numerical convergence}
-\label{sec:scatter-convergence}
-We check whether the properties of the Auriga globular cluster candidates
-are well converged between the three different resolution levels used for the
-Auriga simulations. Here we consider all three Auriga haloes for which simulation
-runs were performed at all three resolution levels: Au6, Au16, and Au24. Here
-we can investigate differences between individual haloes.
-
-Figure~\ref{fig:logMFeH_res} shows the mass-weighted metallicity distribution,
-Figure~\ref{fig:logMRgc_res} shows the mass-weighted radial distribution, and
-Figure~\ref{fig:logMRgcFeH_res}
-
-\begin{figure*}
-    \includegraphics[width=0.31\textwidth]{{logMFeH_Au6}.png}
-    \includegraphics[width=0.31\textwidth]{{logMFeH_Au16}.png}
-    \includegraphics[width=0.31\textwidth]{{logMFeH_Au24}.png}
-    \caption{Similar to Figure~\ref{fig:FeH}, but showing one individual Auriga
-        halo, where colours indicate the resolution level: L3 green, L4 orange,
-        and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo 16.
-        \emph{Right:} Auriga halo 24. For all three haloes we find marginal
-        increases in the mass normalization with increasing resolution level.
-        \label{fig:logMFeH_res}
-    }
-
-\end{figure*}
-\begin{figure*}
-    \includegraphics[width=0.31\textwidth]{{logMRgc_Au6}.png}
-    \includegraphics[width=0.31\textwidth]{{logMRgc_Au16}.png}
-    \includegraphics[width=0.31\textwidth]{{logMRgc_Au24}.png}
-    \caption{Similar to Figure~\ref{fig:Rgc}, but showing one individual Auriga
-        halo, where colours indicate the resolution level: L3 green, L4 orange,
-        and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo 16.
-        \emph{Right:} Auriga halo 24. For all three haloes we find marginal
-        increases in the mass normalization with increasing resolution level.
-        \label{fig:logMRgc_res}
-    }
-
-\end{figure*}
+% \clearpage
+% \appendix
+% \section{Scatter between individual Auriga haloes, and numerical convergence}
+% \label{sec:scatter-convergence}
+% We check whether the properties of the Auriga globular cluster candidates
+% are well converged between the three different resolution levels used for the
+% Auriga simulations. Here we consider all three Auriga haloes for which simulation
+% runs were performed at all three resolution levels: Au6, Au16, and Au24. Here
+% we can investigate differences between individual haloes.
+% 
+% Figure~\ref{fig:logMFeH_res} shows the mass-weighted metallicity distribution,
+% Figure~\ref{fig:logMRgc_res} shows the mass-weighted radial distribution, and
+% Figure~\ref{fig:logMRgcFeH_res}
+% 
+% 
+% 
+% \begin{figure*}
+%     \includegraphics[width=0.31\textwidth]{{logMFeH_Au6}.png}
+%     \includegraphics[width=0.31\textwidth]{{logMFeH_Au16}.png}
+%     \includegraphics[width=0.31\textwidth]{{logMFeH_Au24}.png}
+%     \caption{Similar to Figure~\ref{fig:FeH}, but showing one individual Auriga
+%         halo, where colours indicate the resolution level: L3 green, L4 orange,
+%         and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo 16.
+%         \emph{Right:} Auriga halo 24. For all three haloes we find marginal
+%         increases in the mass normalization with increasing resolution level.
+%         \label{fig:logMFeH_res}
+%     }
+% 
+% \end{figure*}
+% \begin{figure*}
+%     \includegraphics[width=0.31\textwidth]{{logMRgc_Au6}.png}
+%     \includegraphics[width=0.31\textwidth]{{logMRgc_Au16}.png}
+%     \includegraphics[width=0.31\textwidth]{{logMRgc_Au24}.png}
+%     \caption{Similar to Figure~\ref{fig:Rgc}, but showing one individual Auriga
+%         halo, where colours indicate the resolution level: L3 green, L4 orange,
+%         and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo 16.
+%         \emph{Right:} Auriga halo 24. For all three haloes we find marginal
+%         increases in the mass normalization with increasing resolution level.
+%         \label{fig:logMRgc_res}
+%     }
+% 
+% \end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-06-14 AurigaGCS.tex
Some minor rephrasings. Now only need to write discussion ...

@@
 the MW (M31) GCS. For any one of the Auriga haloes we reject the null hypothesis that
-the simulated and observed metallicities are drawn from the same distribution at
-$\geq98.32$~\% confidence level, for the GCS of the Milky Way as well as that of
-the Andromeda galaxy. The same holds true for the distribution of galactocentric
-radius. Overall, the Auriga simulations produce old star particles with higher
-metallicities than the MW and M31 GCS and at larger radii. The formation efficiency
-would have to linearly decrease with increasing metallicity for the Auriga GC
-candidates to be consistent with the MW GCS.
+the observed and simulated metallicities of GCs (GC candidates) are drawn from 
+the same distribution at $\geq98.32$~\% confidence level, for the GCS of the 
+Milky Way as well as that of the Andromeda galaxy. The same holds true for the 
+distribution of galactocentric radius. Overall, the Auriga simulations produce 
+old star particles with higher metallicities than the MW and M31 GCS and at 
+larger radii. The formation efficiency would have to linearly decrease with 
+increasing metallicity for the Auriga GC candidates to be consistent with the MW GCS.
 \end{abstract}
@@
 processes responsible for the formation of young massive clusters \citep[YMCs, 
-see][for a review]{2010ARA&A..48..431P}, observable in the local Universe in great
-detail, also governs GC formation at high redshifts. In this framework, differences
+see][for a review]{2010ARA&A..48..431P}, as observable in detail in the local 
+Universe in great
+, also governs GC formation at high redshifts. In this framework, differences
 between both classes of objects are caused by nearly a Hubble time of (dynamical)
@@
 can thus incorporate formation of (globular) star clusters into their 
-high-resolution hydrodynamical cosmological zoom simulations. \citet{
-2016ApJ...831..204R} run parsec scale simulations of the high-redshift universe 
+high-resolution hydrodynamical simulations. \citet{2016ApJ...831..204R} 
+run parsec scale simulations of the high-redshift universe 
 prior to reionization (the simulations stop at $z=9$), \citet{2017ApJ...834...69L} 
@@
 
-In this work we use state of the art simulations that produce realistic 
-spiral galaxies at redshift zero that reproduce a number of observables. Therefore
-the question naturally arises whether the simulations (also) yield a population 
-of star particles that is consistent with the Milky Way and/or Andromeda globular 
-cluster systems. In particular, we investigate the Auriga suite of cosmological 
-zoom simulations (\citealt{2017MNRAS.467..179G}, and described in 
-Sec.~\ref{sec:auriga}) which can serve as an ultimate test of the star formation 
-model implemented in these simulations. The plan of the paper is as follows. We
-summarise the relevant characteristics of the Auriga simulations in
-section~\ref{sec:auriga}, followed by a summary of the observations of the
-Milky Way (MW) and Andromeda globular cluster system (GCS) in
-section~\ref{sec:observations} that we use to compare our simulations to in
+In this work we use state of the art simulations that produce realistic spiral 
+galaxies at redshift zero for which several global properties are consistent with 
+the observations. The simulations yield realistic Milky Way analogues, and such
+galaxies are known to host globular cluster systems. The question thus naturally 
+arises whether the simulations (also) yield a population of star particles that 
+is consistent with the Milky Way and/or Andromeda globular cluster systems. In 
+particular, we investigate the Auriga suite of cosmological zoom simulations 
+(\citealt{2017MNRAS.467..179G}, and described in Sec.~\ref{sec:auriga}) because
+a study of its GC system could serve as an ultimate test of the star formation 
+model. The plan of the paper is as follows. We summarise the relevant characteristics 
+of the Auriga simulations in section~\ref{sec:auriga}, followed by a summary of 
+the observations of the Milky Way (MW) and Andromeda globular cluster system (GCS)
+in section~\ref{sec:observations} that we use to compare our simulations to in
 section~\ref{sec:results}. We discuss our findings in section~\ref{sec:discussion}
@@
 suite of high-resolution cosmological zoom simulations of Milky Way-mass
-selected initial conditions. The simulations are performed with the
-state-of-the art code \textsc{arepo} \citep{2010MNRAS.401..791S,
-2016MNRAS.455.1134P}, that solves the magnetohydrodynamical equations on a
-moving mesh, and an elaborate galaxy formation model that produces realistic
-spiral galaxies at redshift $z=0$.
+selected initial conditions. The simulations are performed with the \textsc{arepo} 
+\citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} code that solves the 
+magnetohydrodynamical equations on a moving mesh. The galaxy formation model 
+produces realistic spiral galaxies at redshift $z=0$.
 
@@
 typical GC radii. High-density gaseous regions are thus not expected to produce
-surviving stellar clumps (GCs) with masses and radii consistent with GCs because
+surviving stellar clumps with masses and radii consistent with GCs because
 such objects would numerically disperse, even in the highest-resolution runs.
@@
 GC candidates because each star particle represents a single stellar population
-with a total mass that could be consistent with one globular cluster.
+with a total mass that could be consistent with one globular cluster. This means
+that their formation sites and that of a real-world GC may be consistent.
 
@@
 thus, their catalogue to be $\sim$85\% complete. However, an additional 59 GCs
-have since been discovered by various authors. The total confirmed number of GCs
-in the MW adds up to 216 with new estimates now anticipating an additional thirty
-GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
+are claimed to have been discovered by various authors. The total number of GCs
+in the MW might add up to 216 with recent estimates now anticipating an additional 
+thirty GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
 We still use data from the Harris catalogue, but caution that it may (only) be
@@
     globular cluster systems.
-    \item We reject the null hypothesis $H_0$ that MW (M31) and the GC candidates
-    (all, insitu, and accreted) are drawn from the same underlying distribution
-    for all Auriga L4 galaxies with $\geq 98.68$~\% confidence.
+
+    \item We reject the null hypothesis $H_0$ for any one of the Auriga simulations 
+    that the GC candidates and the MW GCs are drawn from the same underlying 
+    distribution with $\geq 98.68$~\% confidence. This statement holds true when
+    we select all old star particles (GC candidates), but also when we select the 
+    old accreted or the old in situ star particles. In addition, this is also
+    the case when we test against the M31 GCS instead of the MW GCS.
+
     \item GC candidates in the Auriga simulations may be found out to $R_{200}$,
-    given our selection function of star particles selects all stars bound to the
-    main subhalo in the main halo. The stellar mass is dominated by accreted star
-    particles at radii beyond $20$~kpc The GCs in the MW and M31, on the other hand,
-    have a much smaller radial extend.
+    given that our selection function of star particles selects all stars bound
+    to the main subhalo in the main halo. The stellar mass is dominated by accreted 
+    star particles at radii beyond $20$~kpc. The GCs in the MW and M31, on the 
+    other hand, have a much smaller radial extend.
+
     \item The cluster formation efficiency would have to increase with decreasing
     metallicity for GC candidates in the Auriga simulations to be consistent
-    with the Milky Way GC system, given that we expect dynamical evolution to more strongly affect GC
-    candidates at smaller radii.
+    with the Milky Way GC system, given that we expect dynamical evolution to 
+    more strongly affect GC candidates at smaller radii. This trent of over-production
+    of old star particles that are metal-rich and at large radii compared to 
+    observed GCs is less clear for the M31 GCS.
+
     \item The Auriga simulations are not consistent with the picture that all
     metal-rich GCs formed insitu and that all metal-poor GCs were accreted.
+
 \end{itemize}
@@
 programming language, the IPython \citep{2007CSE.....9c..21P} environment, 
-the Numpy \citep{2011CSE....13b..22V}, Scipy \citep{scipy}, and Astropy 
-\citep{2013A&A...558A..33A} packages. Plots were generated using 
+the NumPy \citep{2011CSE....13b..22V}, SciPy \citep{scipy}, and Astropy 
+\citep{2013A&A...558A..33A} packages. Plots were created with
 Matplotlib \citep{2007CSE.....9...90H}.

### 2019-06-14 AurigaGCS.tex
Intermediate version

@@
 
-% Rosenblatt+ 1988, Cen 2001, Bromm \& Clarke 2002, Diemand+ 2002, Moore+ 2006,
-% Boley+ 2009, Griffen+ 2010, Trenti+ 2015, Kimm+ 2016, Ricotti+ 2016, Boylan-Kolchin 2017,
-% Creasey+ 2019.
-
 An idea that has recently been studied in detail is the hypothesis that the physical 
@@
 \citet{2019MNRAS.482.4528E}.
-
-% bimodality in the broad-band colours of many (perhaps most) GC systems (e.g.
-% Zepf & Ashman 1993; Elson, Santiago & Gilmore 1996; Geisler,
-% Lee & Kim 1996; Forbes, Brodie & Huchra 1997a; Gebhardt &
-% Kissler-Patig 1999; Kundu & Whitmore 2001; Larsen et al. 2001).
 
@@
 
-% \todo[inline]{
-% TODO: paraphrase ``The diversity in morphological properties of these simulated
-% galaxies reflects the stochasticity inherent to the process of galaxy formation
-% and evolution
-% \citep[e.g.][]{2005ApJ...635..931B, 2010MNRAS.406..744C, 2010ApJ...708.1398T}.''
-% }
-%
-% \todo[inline]{Paragraph about Auriga's stellar haloes.
-% ``The Auriga Stellar Haloes: Connecting stellar population properties with
-% accretion and merging history'' \citet{2018arXiv180407798M}
-% }
-
 \section{Observational data}
@@
 157 GCs. The authors initially estimated the size of the MW GCS to be 180~$\pm$~10,
-thus, their catalogue to be $\sim$85\% complete. However, an additional 59 GCs
+thus, their catalogue to be ${\sim}$85\% complete. However, an additional 59 GCs
 are claimed to have been discovered by various authors. The total number of GCs
@@
 C11 and CR16 present a uniform set of spectroscopic observations calibrated
-on the Milky Way GCS of the inner $1.6^\circ~(\sim21)$~kpc that
+on the Milky Way GCS of the inner $1.6^\circ~({\sim}21)$~kpc that
 is believed to be 94\% complete. GCs in the outer stellar halo, up to
@@
 \end{figure}
-% \begin{figure}
-%     \includegraphics[width=\columnwidth]{{MW_M31_Age_HistogramMassWeighted_Msun}.png}
-%     \caption{
-%         Mass-weighted age distribution of 55 GCs in the MW
-%         \citep[data from][]{2013ApJ...775..134V} and 85 GCs
-%         in M31 \citep[data from][]{2016ApJ...824...42C}.
-%         \label{fig:MW-M31-age}
-%     }
-% \end{figure}
 
@@
 (0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
-and distance $D_{\text{M31}} = 778$~kpc (McConnachie et al. 2005; Conn  et  al. 2012).
+and distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}
 We calculate $R_{\text{GC}}$ as `average deprojected distance`
@@
 Figure~\ref{fig:Au4-10and21_FeH} shows the normalized metallicity distribution
-of \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the resolution
-level (4) and halo number (10 - indicating which set of initial conditions was
-used the run).} and \mbox{Au4-21}, showing the GC candidates in green. The accreted GC
-candidates are shown in red, and the insitu subpopulation in blue. The top panels
-show the MW (M31) GC system in purple (magenta). We overplot a double Gaussian
-for the MW GCS (the purple dashed lines), adopting literature values of the
-mean $\mu$ and standard deviation $\sigma$ of the metal-rich and metal-poor
-populations \citep[][p. 38]{Harris2001}.
+of \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
+resolution level (4) and halo number (10, indicating which set of initial
+conditions was used the run).}, \mbox{Au4-21}, and \mbox{Au4-4}, showing the GC
+candidates in green. The accreted GC candidates are shown in red, and the insitu 
+subpopulation in blue. The top panel of the left panel shows the MW (M31) GC 
+system in purple (magenta). We overplot a double Gaussian for the MW GCS (the 
+purple dashed lines), adopting literature values of the mean $\mu$ and standard
+deviation $\sigma$ of the metal-rich and metal-poor populations \citep[][p. 38]{Harris2001}.
 
-We find that the age cut lowers the mean metallicity from $0.0$ to $-0.6$.
+We find that the age cut, on average, lowers the mean metallicity from $0.0$ to $-0.5$.
 Furthermore, the old accreted stars generally have lower metallicities than the
 old insitu stars. The difference between the mean metallicity of the old insitu
-and old accreted stars for the majority of the simulations is \textasciitilde{}$0.3$ (e.g.
-\mbox{Au4-21}), and \textasciitilde{}$0.5$ dex for \mbox{Au4-10}, \mbox{Au4-16}, \mbox{Au4-17},
+and old accreted stars for the majority of the simulations is ${\sim}0.3$ (e.g.
+\mbox{Au4-21}), and ${\sim}0.5$ dex for \mbox{Au4-10}, \mbox{Au4-16}, \mbox{Au4-17},
 \mbox{Au4-18} and \mbox{Au4-22}. This trend is only reversed for \mbox{Au4-1}
 and \mbox{Au4-4}, for which the old insitu population has a lower mean metallicity
-instead. For \mbox{Au4-1} we find $\mu = -1.51$ (-0.74) for the old insitu (accreted),
+instead. For \mbox{Au4-1} we find $\mu = -1.51 \, ({-0.74})$ for the old insitu (accreted),
 but the former consists of only $1019$ particles ($1.3$\% of all GC candidates, and
@@
 flawed for this halo due to misclassification of the primary halo in the merger
-tree by subfind. For \mbox{Au4-4}, $10.8$ \% of the GC candidates is classified
-as insitu (compared to insitu fractions of $40-80$\% for other haloes). Overall
+tree by subfind. For \mbox{Au4-4}, ${10.8}$\% of the GC candidates is classified
+as insitu (compared to insitu fractions of ${40-80}$\% for other haloes). Overall
 we find that the simulations produce (sub)populations of GC candidates that are
@@
 our finding that the simulations produce GC candidates that are more metal-rich
-than the MW (M31) GCS. The main reason reasons that $H_0$ is rejected with such
+than the MW (M31) GCS. The main reasons that $H_0$ is rejected with such
 high confidence are under-production of old stars with [Fe/H]~$\leq$~-1.5,
@@
 CR16 argues that the data, after removal of younger objects due to improved age
-classification, leans towards unimodality. Therefore we do not show two data
+classification, hints at three populations. However, we do not show these (unknown)
 points for the M31 GCS.
@@
 GC candidates are split up according to birth location, rather than selecting
-typical examples of individual galaxies. Figure~\ref{fig:FeH} shows the mass-weighted
-metallicity distribution of all Auriga L4 galaxies. Once again we notice that the
-peak metallicity shifts down from $0$ to $-0.5$ for old stars (green solid)
-compared to all stars (green dotted), and we learn that the mass at the peak
-lowers by roughly one dex. The mass budget of the old stars is dominated by the
-old insitu population (blue solid) below [Fe/H]~=~$-1$, and by the old accreted
+typical examples of individual (simulated) galaxies. Figure~\ref{fig:FeH} shows 
+the mass-weighted metallicity distribution of all Auriga L4 galaxies. Once again 
+we notice that the peak metallicity shifts down from $0$ to $-0.5$ for old stars
+(green solid) compared to all stars (green dotted), and we learn that the mass at 
+the peak lowers by roughly one dex. The mass budget of the old stars is dominated
+by the old insitu population (blue solid) below [Fe/H]~=~$-1$, and by the old accreted
 stars (red solid) above this value. We show the MW (M31) GCS in purple (magenta)
@@
 Way and Andromeda GCS. We find a decreasing mass excess with increasing radius
-in the range $0.2$ to \textasciitilde{}$5$ kpc, followed by an increase attributed
+in the range $0.2$ to ${\sim}5$ kpc, followed by an increase attributed
 to the accreted subpopulation. We further investigate a breakdown of the total mass
@@
 \section{Discussion}
+% ``The Auriga Stellar Haloes: Connecting stellar population properties with
+% accretion and merging history'' \citet{2018arXiv180407798M}
+
 \label{sec:discussion}
@@
 \label{sec:discussion_FeH}
-We find that the metallicity distributions of GC candidates in the Auriga
+Globular clusters are ${\sim}0.5$ dex more metal-poor than spheroid stars observed 
+at the same radius for almost all galaxies \citep{1991ARA&A..29..543H}. Our 
+selection function (age cut) does lower the mean metallicity by $0.5$ dex, but
+we still find that the metallicity distributions of GC candidates in the Auriga
 simulations are more metal-rich than the MW (M31) GCS. Although the (old) star
-particles represent single stellar populations with a mass (resolution) comparable
-to the peak of the GCMF, they are in fact statistical tracers of the stellar
-population of the galaxy as a whole. Therefore only a (small) fraction of the
-star particles may represent plausible formation sites of GCs, whereas the majority
-represent (halo) field stars - the disk component effectively falls outside
-our selection of star particles due to the age cut. Globular clusters are
-$\sim$~$0.5$ dex more metal-poor than spheroid stars observed at the same radius
-for almost all galaxies \citep{1991ARA&A..29..543H}. Our finding that star particles older
-than 10~Gyr have higher metallicities than the MW (M31) GCS may simply be a
-reflection thereof.
+particles represent single stellar populations with a mass (resolution) consistent 
+with that of GCs, they are in fact statistical tracers of the stellar population 
+of the galaxy as a whole. Therefore only a (small) fraction of the star particles 
+may represent plausible formation sites of GCs, whereas the majority represents 
+(halo) field stars - the disk component effectively falls outside our selection 
+of star particles due to the age cut.
 
-\citet[][p. 234]{1998gcs..book.....A} and \citet[][p. 38]{Harris2001} quantify
-the bimodality of the [Fe/H] distribution of the MW GCS, the latter fit a double
-Gaussian which peaks at [Fe/H] = $-1.59$ (metal-poor) and $-0.51$ (metal-rich)
-and dispersions of $0.34$ and $0.23$. However, the metallicity distribution of
-GC candidates in the Auriga simulations is not bimodal, although an offset between
-the mean values does emerge when further splitting them up according to birth location
-(accreted or in-situ). The majority of the simulations show an offset in the mean
-values of roughly $0.3$~dex between both subpopulations, while a small number of
-simulations has an offset of order $0.5$~dex. Our finding that the mean values of
-the old insitu GC candidates are roughly consistent with the metal-rich MW GCs
-could be interpreted as an indication that this subpopulation may have formed
-in-situ. However, we also notice that a substantial number of simulations has
-similar mean values for all GC candidates, and the simulated insitu GC candidates
-have larger dispersions than the metal-rich GCs. Moreover, the offset between the
-mean of the metal-rich and metal-poor populations in the MW is $1$ dex, a factor
-$2-3$ larger than the offset we find between the insitu and accreted populations.
-The simulations are not consistent with the picture that all metal-rich GCs
-formed insitu and that all metal-poor GCs were accreted.
+In general, the colour (metallicity) distribution of most GC systems is bimodal 
+with typical separating value [Fe/H]$\sim -1$ \citep{1985ApJ...293..424Z,
+1999AJ....118.1526G,2001AJ....121.2974L,2006ApJ...639...95P}. Indeed, 
+\citet[][p. 234]{1998gcs..book.....A} and \citet[][p. 38]{Harris2001} find that
+the MW GCS has a bimodality [Fe/H] distribution: the latter fit a double Gaussian 
+which peaks at [Fe/H] = $-1.59$ (metal-poor) and $-0.51$ (metal-rich) and 
+dispersions of $0.34$ and $0.23$. Observations of GCs in M31, however, may be
+best split into three distinct metallicity groups, one found at small radii with 
+[Fe/H] $>-0.4$, one intermediate [Fe/H] group, and a dominant (metal-poor) group 
+with [Fe/H] $< -1.5$ \citep{2016ApJ...824...42C}. The numerical simulation of
+\citet{2017MNRAS.465.3622R} does yield a bimodal metallicity distribution where
+the metal-poor population is dominated by accreted star particles and the metal-rich
+population by insitu stars.
 
-\citet{2006ARA&A..44..193B} compare the number of metal-poor GCs to the stellar
-halo mass and find\footnote{the quantity $T$ is the number of GCs per $10^9$ M\Sun \,
-of galaxy stellar mass} $T^n_{\text{blue}} \sim 100$, while the
-number of metal-rich GCs compared to the bulge mass yields $T^n_{\text{red}} \sim 5$,
-and therefore conclude that the formation efficiency of metal-poor GCs is
-twenty times higher than the metal-rich GCs with respect to field stars.
+We find that none of the Auriga simulations produces a bimodal 
+metallicity distribution for age-selected GC candidates. Interestingly, the 
+cross-over point above (below) which the mass-weighted metallicity distribution
+of GC candidates is dominated by those that have formed insitu (were accreted) 
+does coincide with the separation between the metal-rich and metal-poor populations 
+of GC systems at [Fe/H]~=~$-1$. Moreover, we do find that the mean metallicity
+shifts when we split the GC candidates up according to birth location (accreted
+or in-situ). In particular, the mean values of the old insitu GC candidates are 
+roughly consistent with the metal-rich MW GCs. However, we also notice that a 
+substantial number of simulations has similar mean values for all GC candidates, 
+and the simulated insitu GC candidates have larger dispersions than the metal-rich 
+GCs. Moreover, the offset between the mean of the metal-rich and metal-poor 
+populations in the MW is $1$ dex, a factor $2-3$ larger than the offset that we 
+find between the insitu and accreted populations. The Auriga simulations therefore
+do not support the view that the metal-poor GCs could have formed in satellites
+that have later been accreted whereas the metal-rich GC subpopulation has formed
+insitu. With this statement, however, we do caution that \citet{2019MNRAS.486.3134K} 
+suggests to reserve the `ex situ' classification for accretion after $z=2$, when
+the central galaxy has formed and accretion unambigously contributes to the
+radially extended halo GC population. In fact, our classification appears flawed
+in Au4-1.
 
-% Interestingly, the cross-over point above (below) which the mass-weighted
-% metallicity distribution of GC candidates is dominated by those that have
-% formed insitu (were accreted) coincides with the separation between the metal-rich
-% and metal-poor population for the MW GCS at [Fe/H]~=~$-1$.
+Finally, we note that \citet{2006ARA&A..44..193B} compares the number of metal-poor 
+GCs to the stellar halo mass and find\footnote{the quantity $T$ is the number of 
+GCs per $10^9$ M\Sun \, of galaxy stellar mass} $T^n_{\text{blue}} \sim 100$, 
+while the number of metal-rich GCs compared to the bulge mass yields 
+$T^n_{\text{red}} \sim 5$, and therefore conclude that the formation efficiency
+of metal-poor GCs is twenty times higher than the metal-rich GCs with respect to 
+field stars. We find that gradual linear increase in formation efficiency of GCs
+with respect to field stars would be required with decreasing metallicity for
+the GC candidates in the Auriga simulations to yield sufficient total mass to
+be consistent with the Milky Way GCS.
 
@@
 The M31 GCS has a factor 2-3 more GCs at large radii compared to the MW GCS,
-which may indicate that M31 has a richer merger history than the MW. In the
-Auriga simulations we find that the GC candidates at radii larger than
-$\sim20$~kpc are indeed dominated by accreted star particles. However, we select
-star particles that are bound to the main halo and main subhalo, which means that
-we include particles up to the virial radius $R_{200}$. The Auriga simulations
-have no problem populating the stellar halo up to the virial radius, even with
-our additional age cut. On the other hand, the MW and M31 have fewer GCs at large
-radii. We expect tidal disruption to be less efficient at larger radii, thus,
-the formation efficiencies of the accreted GC candidates would have to be lower.
-Our classification as GC candidates could, for example, be improved by selecting
-a number of globular clusters based on the $M_{vir}-N_{\text{GC}}$ correlation
-found by \citet{2019arXiv190100900B}, and taking a virial mass below which none
-of the star particles is treated as GC candidate.
+which may indicate that M31 has a richer merger history than the MW 
+\citep{2016ApJ...824...42C}. In the Auriga simulations we find that the GC 
+candidates at radii larger than ${\sim}20$~kpc are indeed dominated by accreted
+star particles. However, we select star particles that are bound to the main 
+halo and main subhalo, which means that we include particles up to the virial 
+radius $R_{200}$. The Auriga simulations have no problem populating the stellar 
+halo up to the virial radius, even with our additional age cut. On the other hand, 
+the MW and M31 have fewer GCs at large radii. We expect tidal disruption to be
+less efficient at larger radii, thus, the formation efficiencies of the accreted 
+GC candidates would have to be lower. Our classification as GC candidates could, 
+for example, be improved by selecting a number of globular clusters based on the 
+$M_{vir}-N_{\text{GC}}$ correlation found by \citet{2019arXiv190100900B}, and 
+taking a virial mass below which none of the star particles is treated as GC candidate.
 
@@
 \label{sec:discussion_mass_excess}
-A major improvement to our classification of star particles as GC candidates
-could be made by explicitly taking into the formation efficiency of bound star
-clusters \citep{2012MNRAS.426.3008K}, which depends on the local ISM properties
-(density, pressure, sound speed). However, the only information available in
-post-processing are the properties of the star particles recorded in the first
-snapshot after formation. We could attempt to obtain the properties of the nearest
-gas cell, but this would have to be limited to a very narrow time window between
-the time of formation and the time of the snapshot because the star particle could
-otherwise be in a completely different location than where it was born initially.
-Moreover, even if the birth time and snapshot time would coincide, it would not
-be obvious that the gas cell will yield the correct quantities as the formation
-of the star itself alters the properties of the gas. We therefore did not further
-attempt a more sophisticated modeling of the cluster formation efficiency in
-post-processing.
+% A major improvement to our classification of star particles as GC candidates
+% could be made by explicitly taking into the formation efficiency of bound star
+% clusters \citep{2012MNRAS.426.3008K}, which depends on the local ISM properties
+% (density, pressure, sound speed). However, the only information available in
+% post-processing are the properties of the star particles recorded in the first
+% snapshot after formation. We could attempt to obtain the properties of the nearest
+% gas cell, but this would have to be limited to a very narrow time window between
+% the time of formation and the time of the snapshot because the star particle could
+% otherwise be in a completely different location than where it was born initially.
+% Moreover, even if the birth time and snapshot time would coincide, it would not
+% be obvious that the gas cell will yield the correct quantities as the formation
+% of the star itself alters the properties of the gas. We therefore did not further
+% attempt a more sophisticated modeling of the cluster formation efficiency in
+% post-processing.
+% 
+% Furthermore, we compare star particles to present-day globular clusters, thereby
+% ignoring the effects of (dynamical) disruption of globular clusters over nearly
+% a Hubble time. As shown by \citep{2018MNRAS.475.4309P}, a detailed model of the tidal
+% history of star clusters requires a temporal resolution of order mega year. For
+% the Auriga L4 simulations we have a total of 128 snapshots available over the
+% age of the Universe, thus, far too coarse temporal resolution for meaningful
+% calculations of tidal disruption along the orbit of our GC candidates. Therefore
+% we can only combine these two shortcomings of our analysis into the `mass excess',
+% which includes the cluster formation efficiency and consecutive globular cluster
+% disruption.
 
-Furthermore, we compare star particles to present-day globular clusters, thereby
-ignoring the effects of (dynamical) disruption of globular clusters over nearly
-a Hubble time. As shown by \citep{2018MNRAS.475.4309P}, a detailed model of the tidal
-history of star clusters requires a temporal resolution of order mega year. For
-the Auriga L4 simulations we have a total of 128 snapshots available over the
-age of the Universe, thus, far too coarse temporal resolution for meaningful
-calculations of tidal disruption along the orbit of our GC candidates. Therefore
-we can only combine these two shortcomings of our analysis into the `mass excess',
-which includes the cluster formation efficiency and consecutive globular cluster
-disruption.
-
-% \todo[inline]{
-% \citet{2019MNRAS.486.3134K} ``Due to the multitude of low-mass progenitors and
-% rapid merging during this early phase of galaxy growth, we recommend to reserve
-% the term `ex situ GCs' for accretion events taking place at $z < 2$, when the
-% central spheroid has formed and accretion events unambiguously contribute to the
-% spatially extended (`halo') GC population.''
-% }
-%
-%
-% \citet{2016ApJ...824...42C}
-% ``We find that the clusters can be divided into three major metallicity groups
-% based on their radial distributions: (1) an inner metal-rich group ([Fe/H] $> -0.4$);
-% (2) a group with intermediate metallicity (with median [Fe/H] $= -1$); and (3)
-% a metal-poor group, with [Fe/H] $< -1.5$.''
-%
-% \citet{2016ApJ...824...42C}
-% ``Although this disk mode of GCs is intriguing, the very dominant subpopulations
-% in M31 are the lower-metallicity GCs. It seems likely that these objects were
-% brought in by the accretion of satellite galaxies (minor mergers). The populous
-% GC system of M31, relative to the MW, would then reflect a more active accretion
-% history, and the radial gradient of GC metallicities could arise through
-% correlations of both metallicity and dynamical friction with satellite galaxy
-% mass (e.g., Amorisco 2016).''
-
-\citep{2019MNRAS.486.5838R}
+\todo[inline]{Paraphrase the following}
+\citet{2019MNRAS.486.5838R}
 ``Out of the cluster formation models considered, the `no formation physics' model,
@@
 formation  of  GCs  in  this  model  predicts  the  on-going  formation
-of massive (M $>10^5$ M\Sun) clusters with [Fe/H]< −0.5 should be observed in
-Milky Way-mass galaxies at z=0. For these reasons, an environmentally independent
+of massive (M $>10^5$ M\Sun) clusters with [Fe/H]$ <-0.5$ should be observed in
+Milky Way-mass galaxies at $z=0$. For these reasons, an environmentally independent
 cluster formation description is not compatible with observations.''
@@
     we select all old star particles (GC candidates), but also when we select the 
-    old accreted or the old in situ star particles. In addition, this is also
+    old accreted or the old insitu star particles. In addition, this is also
     the case when we test against the M31 GCS instead of the MW GCS.

### 2019-06-27 latexdiff.sh
Started processing SW feedback, but unfinished

@@ -1,0 +1,11 @@
+#!/bin/bash
+set -e
+
+diff="diff_with_respect_to_20190614.tex"
+if [ -f "${diff}" ]; then
+    rm -f "${diff}"
+fi
+
+# Ignore (sub)sections: https://tex.stackexchange.com/questions/87536
+latexdiff --exclude-textcmd="section,subsection" AurigaGCS_20190614.tex AurigaGCS.tex > "${diff}"
+timotex "${diff}"

### 2019-07-09 AurigaGCS.tex
Attempt to motivate each figure, and  explain their take away message for Sec. 4.1

@@
 galaxies at redshift zero for which several global properties are consistent with 
-the observations. The simulations yield realistic Milky Way analogues, and such
-galaxies are known to host globular cluster systems. The question thus naturally 
-arises whether the simulations (also) yield a population of star particles that 
-is consistent with the Milky Way and/or Andromeda globular cluster systems. In 
-particular, we investigate the Auriga suite of cosmological zoom simulations 
-(\citealt{2017MNRAS.467..179G}, and described in Sec.~\ref{sec:auriga}) because
-a study of its GC system could serve as an ultimate test of the star formation 
-model. The plan of the paper is as follows. We summarise the relevant characteristics 
+the observations. The simulations yield realistic Milky Way analogues, and real
+galaxies host globular cluster systems. The question thus naturally arises whether 
+the star formation histories of the simulations (also) give rise to a GC system 
+similar to the Milky Way and/or Andromeda globular cluster systems. In particular, 
+we use the Auriga suite of cosmological zoom simulations 
+(\citealt{2017MNRAS.467..179G}, and described in Sec.~\ref{sec:auriga}) to
+investigate whether the star formation model implemented produces metallicity, 
+radial, and metallicity-radial distributions that are consistent with the MW 
+and/or M31 GC systems, and whether the model produces enough stellar mass with
+the right properties to allow for formation efficiencies lower than unity and
+the expected (dynamical) mass loss over the cluster lifetime (not modelled 
+explicitly in this study).
+
+The plan of the paper is as follows. We summarise the relevant characteristics 
 of the Auriga simulations in section~\ref{sec:auriga}, followed by a summary of 
@@
 assuming $M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$,
-the mean for MW clusters \citep{2005ApJS..161..304M}.
+the mean for MW clusters \citep{2005ApJS..161..304M}. We supplement the catalogue
+with age-estimates from isochrone fits to stars near the main-sequence turnoff 
+in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.
 
@@
 % other quantities, but
-
-We supplement the catalogue with age-estimates from isochrone fits to stars
-near the main-sequence turnoff in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.
-The mean value of the age-estimates in this data set is $11.9 \pm 0.1$~Gyr and
-the dispersion is $0.8$~Gyr. Furthermore, only one of the 55 GC age-estimates is
-below $10$~Gyr.
 
@@
 
-The M31 GCS has a mean age of $11.0 \pm 0.2$~Gyr with a dispersion of $2.2$~Gyr,
-and $24$ GCs have age-estimates below $10$~Gyr with a minimum age of $4.8$~Gyr.
-We show a histogram of the age-estimates of the $55$ MW GCs in V13 and $88$ GCs
-in M31 for which age-estimates are available in CR16, see Figure~\ref{fig:MW-M31-age}.
+\subsection{Age-estimates}
+Figure~\ref{fig:MW-M31-age} shows a histogram of the age-estimates of the $55$
+MW GCs in V13 and $88$ GCs in M31 for which age-estimates are available in CR16.
+The mean age of the MW GCs in this data set is $11.9 \pm 0.1$~Gyr and the 
+dispersion is $0.8$~Gyr. Furthermore, only one of the 55 GC age-estimates is
+below $10$~Gyr. The M31 GCS has a mean age of $11.0 \pm 0.2$~Gyr with a dispersion 
+of $2.2$~Gyr, and $24$ GCs have age-estimates below $10$~Gyr with a minimum age 
+of $4.8$~Gyr. The Milky Way appears to host a globular cluster system that is
+somewhat older than the Andromeda galaxy, although we caution that both data 
+sets are incomplete and the age measurements have large uncertainties (of $1-2$~Gyr)
 
@@
 We investigate whether the star formation model implemented in Auriga produces
-metallicity distributions consistent with the MW (M31) GC system, and whether
+metallicity distributions consistent with the MW and M31 GC systems, and whether
 the subgrid generates sufficient total mass at metallicities typical for the
-MW (M31) GCS.
+MW and M31 GCS's. To visually inspect the former we show the normalized metallicity 
+distribution of three specific Auriga galaxies in Figure~\ref{fig:Au4-10and21_FeH}
+in comparison to the MW and M31 [Fe/H] distributions.
 
@@
 \end{figure*}
-Figure~\ref{fig:Au4-10and21_FeH} shows the normalized metallicity distribution
-of \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
+We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
 resolution level (4) and halo number (10, indicating which set of initial
-conditions was used the run).}, \mbox{Au4-21}, and \mbox{Au4-4}, showing the GC
-candidates in green. The accreted GC candidates are shown in red, and the insitu 
-subpopulation in blue. The top panel of the left panel shows the MW (M31) GC 
-system in purple (magenta). We overplot a double Gaussian for the MW GCS (the 
-purple dashed lines), adopting literature values of the mean $\mu$ and standard
-deviation $\sigma$ of the metal-rich and metal-poor populations \citep[][p. 38]{Harris2001}.
+conditions was used the run).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
+distributions of three individual simulation runs that we consider representative
+for specific behaviour, and to highlight that different runs could give rise to 
+different distributions. We plot the age-selected GC candidates in green, those
+that are accreted in red, and the insitu subpopulation in blue. The top 
+half of the left figure shows the MW (M31) GC system in purple (magenta), where 
+we overplot a double Gaussian for the MW GCS (the purple dashed lines) by 
+adopting literature values of the mean $\mu$ and standard deviation $\sigma$ of 
+the metal-rich and metal-poor subpopulations \citep[][p. 38]{Harris2001}.
 
-We find that the age cut, on average, lowers the mean metallicity from $0.0$ to $-0.5$.
-Furthermore, the old accreted stars generally have lower metallicities than the
-old insitu stars. The difference between the mean metallicity of the old insitu
-and old accreted stars for the majority of the simulations is ${\sim}0.3$ (e.g.
-\mbox{Au4-21}), and ${\sim}0.5$ dex for \mbox{Au4-10}, \mbox{Au4-16}, \mbox{Au4-17},
-\mbox{Au4-18} and \mbox{Au4-22}. This trend is only reversed for \mbox{Au4-1}
-and \mbox{Au4-4}, for which the old insitu population has a lower mean metallicity
-instead. For \mbox{Au4-1} we find $\mu = -1.51 \, ({-0.74})$ for the old insitu (accreted),
-but the former consists of only $1019$ particles ($1.3$\% of all GC candidates, and
-with a total mass of 5e7 M\Sun) thus we believe our classification of insitu is
-flawed for this halo due to misclassification of the primary halo in the merger
-tree by subfind. For \mbox{Au4-4}, ${10.8}$\% of the GC candidates is classified
-as insitu (compared to insitu fractions of ${40-80}$\% for other haloes). Overall
-we find that the simulations produce (sub)populations of GC candidates that are
+We find that the age cut, on average, lowers the mean metallicity from $0.0$ to
+$-0.6$. Furthermore, the old accreted stars generally have lower mean metallicities
+than the old insitu stars with differences of roughly ${\sim}0.3$ for the majority 
+of the simulation runs. This behaviour can be seen in \mbox{Au4-21}, while a 
+slightly larger difference of ${\sim}0.5$ dex is seen for \mbox{Au4-10} (as plotted), 
+\mbox{Au4-16}, \mbox{Au4-17}, \mbox{Au4-18} and \mbox{Au4-22}. However, this trend 
+is reversed for \mbox{Au4-1} and \mbox{Au4-4} for which the old insitu population 
+has a lower mean metallicity instead. We caution that \mbox{Au4-1} is undergoing
+a major merger at redshift zero and note that we find $\mu = -1.51 \, ({-0.74})$ 
+for the old insitu (accreted) although the former consists of only $1019$ 
+particles ($1.3$\% of all GC candidates, and with a total mass of 5e7 M\Sun). 
+For \mbox{Au4-4}, ${10.8}$\% of the GC candidates is classified as insitu (compared 
+to insitu fractions of ${40-80}$\% for other haloes). Overall we find that the 
+simulations produce (sub)populations of GC candidates that are
 more metal-rich than the MW and M31 GC systems. Moreover, none of the simulations
@@
 We show the mean metallicity and standard deviation of all thirty Auriga L4 haloes
-in Figure~\ref{fig:FeH_mu_sigma}. The green crosses are to be compared to the
-purple (magenta) cross, which shows the mean value of all MW (M31) GCs.
-We test the null hypothesis that MW (M31) and the GC candidates (all, insitu, and
+in Figure~\ref{fig:FeH_mu_sigma} to show the behaviour for the full set of Auriga
+galaxies. The green crosses are to be compared to the purple (magenta) cross, 
+which shows the mean value of all MW (M31) GCs. In addition, we show the metal-rich 
+(metal-poor) population of the MW GCS using a solid (open) dot. We caution that
+these literature values result from individual Gaussian fits to sub sets of the 
+observational data cut at [Fe/H]~$= -1$. We do not include corresponding data 
+points calculated using such an artificial cut for the simulated star particles.
+Having said that, we do find it interesting that the mean metallicities of the 
+old insitu populations appear roughly consistent with that of the metal-rich 
+population of the MW although the simulations show larger dispersions. The latter 
+could simply be caused by the hard separation of the data into two groups, which 
+means the range is smaller and the resulting dispersion could be lower. With 
+regard to the M31 GCS, we are uncertain whether definitive consensus is reached
+concerning uni- bi- or trimodality in the [Fe/H] distribution, but CR16 argues 
+that the data, after removal of younger objects due to improved age classification, 
+hints at three populations separated at [Fe/H]~$>-0.4$ and [Fe/H]~$ < 1.5$. None 
+of the Auriga sub sets has a mean value that offers much hope that the simulated 
+distribution is consistent with the lowest metallicity group in the M31 GCS. This 
+is also true for the metal-poor population of the MW with a mean value of $-1.6$.
+The main take-away from this plot, again, is that all Auriga L4 galaxies have
+metallicity distributions with (much) larger mean values than what is observed
+for the MW and M31 GCS, and that we systematiclly find lower mean metallicities
+for the accreted GC candidates than for those that have formed in situ.
+
+Finally, we test the null hypothesis that MW (M31) and the GC candidates (all, insitu, and
 accreted) are drawn from the same underlying distribution by calculating the KS
@@
 
-In addition, we show the metal-rich (metal-poor) population of the MW GCS using
-a solid (open) dot. The mean metallicities of the old insitu populations appear
-roughly consistent with that of the metal-rich population of the MW, but the
-simulations show larger dispersions. We are uncertain whether definitive consensus
-is reached concerning uni- or bimodality in the [Fe/H] distribution of M31, but
-CR16 argues that the data, after removal of younger objects due to improved age
-classification, hints at three populations. However, we do not show these (unknown)
-points for the M31 GCS.
-
 \begin{figure}
@@
 \end{figure}
-We now turn to the total mass in GC candidates produced by the Auriga simulations.
-We show the median (coloured lines) for all thirty Auriga L4 haloes with the
-$1\sigma$ interval around it (shaded regions, which shows the scatter between
-runs that have different initial conditions, thus, have unique merger histories).
-We chose to aggregate the data to indicate a general trend that we find when the
-GC candidates are split up according to birth location, rather than selecting
-typical examples of individual (simulated) galaxies. Figure~\ref{fig:FeH} shows 
-the mass-weighted metallicity distribution of all Auriga L4 galaxies. Once again 
-we notice that the peak metallicity shifts down from $0$ to $-0.5$ for old stars
-(green solid) compared to all stars (green dotted), and we learn that the mass at 
-the peak lowers by roughly one dex. The mass budget of the old stars is dominated
-by the old insitu population (blue solid) below [Fe/H]~=~$-1$, and by the old accreted
-stars (red solid) above this value. We show the MW (M31) GCS in purple (magenta)
-and we show the ratio of the simulated to the observed profiles in the middle
-(bottom) panel. This mass excess can be thought of the `mass budget' that the
-Auriga GC candidates can `afford to lose' due to a combination of smaller than
-unity bound cluster formation efficiencies combined with a Hubble time of dynamical
-evolution, while still producing a GC system with sufficient mass to be consistent
-with the MW (M31) GCS. The cluster formation efficiency would have to linearly
-decrease with decreasing metallicity for Auriga GC candidates to produce a population
-of GC candidates that is consistent with the MW. For the GC candidates in M31
-we find a constant mass excess up to $-0.9$, above which the
-simulations produce a higher mass excess with increasing metallicity. If dynamical
-evolution is not expected to more efficiently disrupt GCs of higher metallicity,
-then we would find that the efficiency to form bound star clusters would have to
-decrease with increasing metallicity.
+We now turn to the second goal, which is to see whether sufficient total mass in 
+GC candidates produced by the Auriga simulations. To answer this question we plot
+a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
+median (coloured lines) for all thirty Auriga L4 haloes with the $1\sigma$ 
+interval around it (shaded regions, which shows the scatter between runs that 
+have different initial conditions, thus, have unique merger histories). We chose 
+to aggregate the data to indicate general trends that we find when the GC candidates 
+are split up according to birth location, rather than selecting typical examples 
+of individual (simulated) galaxies. Once again we notice that the peak metallicity 
+shifts down from $0$ to $-0.6$ for old stars (green solid) compared to all stars 
+(green dotted), and we learn that the mass at the peak lowers by roughly one dex. 
+The mass budget of the old stars is dominated by the old insitu population (blue 
+solid) below [Fe/H]~=~$-1$, and by the old accreted stars (red solid) above this 
+value. We show the MW (M31) GCS in purple (magenta) and we show the ratio of the 
+simulated to the observed profiles in the middle (bottom) panel. This mass excess 
+can be thought of the `mass budget' that the Auriga GC candidates can `afford to 
+lose' due to a combination of smaller than unity bound cluster formation 
+efficiencies combined with a Hubble time of dynamical evolution, while still 
+producing a GC system with sufficient mass to be consistent with the MW (M31) GCS. 
+The cluster formation efficiency would have to linearly decrease with decreasing 
+metallicity for Auriga GC candidates to produce a population of GC candidates 
+that is consistent with the MW. For the GC candidates in M31 we find a constant 
+mass excess up to $-0.9$, above which the simulations produce a higher mass excess 
+with increasing metallicity. If dynamical evolution is not expected to more 
+efficiently disrupt GCs of higher metallicity, then we would find that the 
+efficiency to form bound star clusters would have to decrease with increasing 
+metallicity.
 

### 2019-07-10 AurigaGCS.tex
Comment on Fig. 1 and 2: MW and M31 age, FeH, Rgc not statistically consistent (= take-away from these figures?)

@@
 of $2.2$~Gyr, and $24$ GCs have age-estimates below $10$~Gyr with a minimum age 
-of $4.8$~Gyr. The Milky Way appears to host a globular cluster system that is
-somewhat older than the Andromeda galaxy, although we caution that both data 
-sets are incomplete and the age measurements have large uncertainties (of $1-2$~Gyr)
+of $4.8$~Gyr. Based on these data, we find that the age distributions of the MW 
+and M31 GCS's are not statistically consistent. Moreover, the Milky Way appears 
+to host a globular cluster system that is somewhat older than the Andromeda galaxy,
+which is somewhat surprising given that M31 is generally considered to be earlier
+type than the MW meaning that an older stellar population would naively be expected
+. However, we do caution that both data sets are incomplete and the age 
+measurements have large uncertainties (of $1-2$~Gyr). On the other hand, the 
+magnitude of the uncertainty is insufficient to explain the low-age tail in M31.
 
@@
 radii in general ($R_{\text{GC}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
-the MW and $17$ or 4.6\% in M31). We compare these observations to the Auriga
-simulations later on in Sec.~\ref{sec:results_FeHRgc}.
+the MW and $17$ or 4.6\% in M31). Moreover, the M31 hosts more metal-rich 
+([Fe/H]$ > -1$) GCs in each radial bin in comparison to the MW GCSs than what
+would be expected when accounting for the fact that Andromeda hosts a larger GC 
+system than the MW. Finally, given that both marginalized (i.e. the metallicity 
+and radial) distributions are not statistically consistent, we find that the 
+two-dimensional distributions are also not consistent. More generally, the GC
+systems of the Milky Way and that of Andromeda both differ significantly. We 
+compare these observations to the Auriga simulations later on in 
+Sec.~\ref{sec:results_FeHRgc}.
 

### 2019-07-10 AurigaGCS.tex
Attempt to motivate each figure, and  explain their take away message for Sec. 4.2

@@
 % candidates. The CatClu catalog contains reference papers, positions, distances,
-% and total absolute V magnitude. Therefore we rely on the H96e10 dataset for all
-% other quantities, but
+% and total absolute V magnitude. Therefore we rely on the H96e10 dataset.
 
@@
 solid) below [Fe/H]~=~$-1$, and by the old accreted stars (red solid) above this 
-value. We show the MW (M31) GCS in purple (magenta) and we show the ratio of the 
-simulated to the observed profiles in the middle (bottom) panel. This mass excess 
-can be thought of the `mass budget' that the Auriga GC candidates can `afford to 
-lose' due to a combination of smaller than unity bound cluster formation 
-efficiencies combined with a Hubble time of dynamical evolution, while still 
-producing a GC system with sufficient mass to be consistent with the MW (M31) GCS. 
-The cluster formation efficiency would have to linearly decrease with decreasing 
+value. We show the MW (M31) GCS in purple (magenta) and notice that the difference 
+between the MW and M31 distributions is substantially larger than the scatter
+between different Auriga galaxies, particularly around [Fe/H]~$=-1$. In addition, 
+Andromeda does host (a hand full) GCs with [Fe/H]~$< -2.5$ as well as GCs with 
+[Fe/H]~$ > 0$ while the Milky Way does not.
+
+We show the ratio of the  simulated to the observed profiles in the middle (bottom) 
+panel. This mass excess can be thought of the `mass budget' that the Auriga GC 
+candidates can `afford to lose' due to a combination of smaller than unity bound
+cluster formation efficiencies combined with a Hubble time of dynamical evolution,
+while still producing sufficient mass at the right metallicities. In particular,
+the cluster formation efficiency would have to linearly decrease with decreasing 
 metallicity for Auriga GC candidates to produce a population of GC candidates 
@@
 \end{figure}
-Figure~\ref{fig:Rgc_mu_sigma} shows the mean and standard deviation of the
-radial distribution of star particles in all Auriga L4 simulations. We notice
-that the old insitu populations are much more centrally distributed, whereas
-the old accreted component has a larger radial extent. Moreover, the dispersion
-increases with increasing mean value of the radial distribution as may be expected
-for a non-negative quantity.
+We repeat the analysis of the previous subsection for the distribution of
+galactocentric radius instead of metallicity. We look for general trends present
+in all Auriga L4 galaxies. Figure~\ref{fig:Rgc_mu_sigma} shows the mean and 
+standard deviation of the radial distribution of star particles in all Auriga L4 
+simulations. We notice that the old insitu populations are more centrally 
+distributed, whereas the old accreted subsets have a larger radial extent. This 
+is not surprising because the classification of in situ requires star particles 
+to have formed within the virial radius, thus they could naturally be expected 
+to end up at small galactocentric radii. Accreted star particles, on the other 
+hand, have formed in another (sub)halo beyond the virial radius, thus, would 
+first have to migrate inwards in order to populate the innermost radii. Moreover, 
+we notice that the dispersion increases with increasing mean value of the radial 
+distribution as may be expected for a non-negative quantity. The purple (magenta)
+cross indicates the values for the MW (M31) GCS, which are to be compared to the
+green crosses. The MW GCS lies roughly within the range of values seen for the 
+radial distributions produced by the Auriga simulations, whereas the mean of M31
+is larger and closer to typical mean values of the accreted GC candidates in
+the Auriga simulations. The larger radial extend of the M31 GCS is generally
+believed to hint at a more accretion-dominated origin of the GCS, and may reflect
+a richer accretion history of the galaxy in comparison to the Milky Way.
 
@@
 in the range $0.2$ to ${\sim}5$ kpc, followed by an increase attributed
-to the accreted subpopulation. We further investigate a breakdown of the total mass
-in Auriga GC candidates into bins of both metallicity and radius in the following
-section.
+to the accreted subpopulation. For the Milky Way we notice that significantly
+fewer GCs are found beyond $40$~kpc than for M31, and that accreted GC candidates
+contribute mostly to the Auriga GCS at these radii. We further investigate a 
+breakdown of the total mass in Auriga GC candidates into bins of both metallicity 
+and radius in the following section.
 

### 2019-07-11 AurigaGCS.tex
Attempt to motivate each figure, and  explain their take away message for Sec. 4.3

@@
 
+We notice in Figure~\ref{fig:Au-FeHRgc} that the Auriga simulations, on average,
+produce fewer GCs in the lowest metallicity bins ($-2.5$ to $-1.5$) than at higher 
+metallicities in the three innermost radial bins. In addition, Auriga produces 
+fewer high-metallicity GCs at large radii, similar to the MW and M31 GC systems. 
+However, the three bins in the upper right corner are populated in the Auriga
+simulations, in contrast to the observations. The top panel of 
+Figure~\ref{fig:Au-FeHRgc-ratio} shows that the mass excess for Auriga GCs within
+the Solar radius decreases with decreasing metallicity. This means that either
+the formation efficiency should increase with decreasing metallicity, or that 
+the lowest-metallicity GCs in the Auriga simulations are less strongly affected
+by disruptive processes, if the star formation histories in the Auriga simulations
+are to give rise to a GC system that can be similar to the GCS that is observed
+in the Milky Way. Moreover, either a lower formation efficiency is required at
+large radii, or stronger disruption. Disruption of star clusters is expected to
+be more efficient at smaller radii due to higher tidal forces in the innermost
+region for GCs on orbits that pass through the disk, or with pericenters close 
+to the bar or bulge. Compared to Andromeda, the mass excess (bottom panel of 
+Figure~\ref{fig:Au-FeHRgc-ratio}) shows a less clear trent than for the Milky Way. 
+Most bins show mass surplus factors of few tens, meaning that high formation 
+efficiencies would be required in addition to little disruption for the Auriga 
+simulations to yield a GC system consistent with that of the Andromeda galaxy.
+
 \begin{figure}

### 2019-08-01 AurigaGCS_20190712.tex
Started processing SW's feedback, but not finished

--- 2019-07-11 AurigaGCS.tex
@@
 \usepackage{todonotes}
-\graphicspath{{img/}}   % Set image path
+\graphicspath{{figures/}}   % Set figure path
 
@@
 We investigate whether the galaxy formation model used for the Auriga simulations
-can produce a realistic globular cluster population at redshift zero. We compare
-properties of the simulated star particles in the Auriga haloes with catalogues
-of observations of the Milky Way and Andromeda globular cluster populations available
-in the literature. We find that the Auriga simulations do produce sufficient mass
-at radii and metallicities that are typical for the MW GCS, although we observe
-a varying mass-excess for the different $R_{\text{GC}}$-[Fe/H] bins. This implies
-different values for the combined product of the bound cluster formation efficiency
-and the globular cluster disruption rate. Furthermore we test whether any of the
+can produce a realistic globular cluster (GC) population at redshift zero. We
+compare properties of the simulated star particles in the Auriga haloes with
+catalogues of observations of the Milky Way (MW) and Andromeda (M31) globular
+cluster populations available in the literature. We find that the Auriga 
+simulations do produce sufficient mass at radii and metallicities that are 
+typical for the MW globular cluster system (GCS), although we observe a varying 
+mass-excess for different $R_{\text{GC}}$-[Fe/H] bins. This implies different 
+values for the combined product of the bound cluster formation efficiency and 
+the globular cluster disruption rate. Furthermore we test whether any of the 
 Auriga galaxies has a metallicity and radial distribution that is consistent with 
-the MW (M31) GCS. For any one of the Auriga haloes we reject the null hypothesis that
-the observed and simulated metallicities of GCs (GC candidates) are drawn from 
-the same distribution at $\geq98.32$~\% confidence level, for the GCS of the 
-Milky Way as well as that of the Andromeda galaxy. The same holds true for the 
-distribution of galactocentric radius. Overall, the Auriga simulations produce 
+the MW or M31 GCS. For any one of the Auriga haloes we reject the null hypothesis
+that the observed and simulated metallicities of GCs (GC candidates) are drawn
+from the same distribution at $\geq98.32$~\% confidence level, for the GCS of 
+the Milky Way as well as that of the Andromeda galaxy. The same holds true for 
+the distribution of galactocentric radius. Overall, the Auriga simulations produce 
 old star particles with higher metallicities than the MW and M31 GCS and at 
 larger radii. The formation efficiency would have to linearly decrease with 
-increasing metallicity for the Auriga GC candidates to be consistent with the MW GCS.
+increasing metallicity for the Auriga GC candidates to be consistent with the 
+MW GCS, if cluster disruption is equally efficient regardless of metallicity.
+In addition, the number of GCs relative to field stars would have to be smaller
+for higher metallicity star particles at large radii than for those with lower 
+metallicity at smaller radii, assuming GC disruption is more efficient in the
+inner regions of the Galaxy.
+
 \end{abstract}
@@
 
-% \todo[inline]{
-%     Harris: `Somewhat arbitrarily, I will take the region $r_p > 3$ kpc
-%     (containing 75 clusters) as the fiducial Milky Way sample. If we were to
-%     view the Milky Way at the same inclination angle to the disk as we see
-%     M31, this cutoff in projected distance would correspond roughly to the
-%     inner distance limits in the M31 halo sample.'
-% }
-
-\subsection{Star particles are not globular clusters}
-\label{sec:discussion_mass_excess}
-% A major improvement to our classification of star particles as GC candidates
-% could be made by explicitly taking into the formation efficiency of bound star
-% clusters \citep{2012MNRAS.426.3008K}, which depends on the local ISM properties
-% (density, pressure, sound speed). However, the only information available in
-% post-processing are the properties of the star particles recorded in the first
-% snapshot after formation. We could attempt to obtain the properties of the nearest
-% gas cell, but this would have to be limited to a very narrow time window between
-% the time of formation and the time of the snapshot because the star particle could
-% otherwise be in a completely different location than where it was born initially.
-% Moreover, even if the birth time and snapshot time would coincide, it would not
-% be obvious that the gas cell will yield the correct quantities as the formation
-% of the star itself alters the properties of the gas. We therefore did not further
-% attempt a more sophisticated modeling of the cluster formation efficiency in
-% post-processing.
-% 
-% Furthermore, we compare star particles to present-day globular clusters, thereby
-% ignoring the effects of (dynamical) disruption of globular clusters over nearly
-% a Hubble time. As shown by \citep{2018MNRAS.475.4309P}, a detailed model of the tidal
-% history of star clusters requires a temporal resolution of order mega year. For
-% the Auriga L4 simulations we have a total of 128 snapshots available over the
-% age of the Universe, thus, far too coarse temporal resolution for meaningful
-% calculations of tidal disruption along the orbit of our GC candidates. Therefore
-% we can only combine these two shortcomings of our analysis into the `mass excess',
-% which includes the cluster formation efficiency and consecutive globular cluster
-% disruption.
-
-\todo[inline]{Paraphrase the following}
-\citet{2019MNRAS.486.5838R}
-``Out of the cluster formation models considered, the `no formation physics' model,
-in which both the CFE and the ICMF are fixed throughout cosmic time, is
-approximately equivalent to those studies  that  use  `particle-tagging'
-techniques  to  identify  GCs  in cosmological simulations (e.g. Tonini 2013,
-Renaud et al. 2017). We find that this cluster formation model continues to form GCs
-at a vigorous rate until the present time, which implies it overproduces
-the total GC mass in the Milky Way by a factor
-5.5 relative to the mass formed in the fiducial model. Likewise, the continued
-formation  of  GCs  in  this  model  predicts  the  on-going  formation
-of massive (M $>10^5$ M\Sun) clusters with [Fe/H]$ <-0.5$ should be observed in
-Milky Way-mass galaxies at $z=0$. For these reasons, an environmentally independent
-cluster formation description is not compatible with observations.''
+% Copy-pasted from \citet{2019MNRAS.486.5838R}
+% ``Out of the cluster formation models considered, the `no formation physics' model,
+% in which both the CFE and the ICMF are fixed throughout cosmic time, is
+% approximately equivalent to those studies  that  use  `particle-tagging'
+% techniques  to  identify  GCs  in cosmological simulations (e.g. Tonini 2013,
+% Renaud et al. 2017). We find that this cluster formation model continues to form GCs
+% at a vigorous rate until the present time, which implies it overproduces
+% the total GC mass in the Milky Way by a factor
+% 5.5 relative to the mass formed in the fiducial model. Likewise, the continued
+% formation  of  GCs  in  this  model  predicts  the  on-going  formation
+% of massive (M $>10^5$ M\Sun) clusters with [Fe/H]$ <-0.5$ should be observed in
+% Milky Way-mass galaxies at $z=0$. For these reasons, an environmentally independent
+% cluster formation description is not compatible with observations.''
 

### 2019-08-01 latexdiff.sh

@@ -1,11 +1,11 @@
 #!/bin/bash
 set -e
 
-diff="diff_with_respect_to_20190614.tex"
+diff="diff_with_respect_to_20190712.tex"
 if [ -f "${diff}" ]; then
     rm -f "${diff}"
 fi
 
 # Ignore (sub)sections: https://tex.stackexchange.com/questions/87536
-latexdiff --exclude-textcmd="section,subsection" AurigaGCS_20190614.tex AurigaGCS.tex > "${diff}"
+latexdiff --exclude-textcmd="section,subsection" AurigaGCS_20190712.tex AurigaGCS.tex > "${diff}"
 timotex "${diff}"

### 2019-08-02 AurigaGCS.tex
Move relevant/used figures to separate folder
Done processing SW's feedback

@@
 mass-estimate\footnote{The authors assumed $M/L_V = 2$ independent of [Fe/H]}.
+Radii are calculated from RA and DEC, further discussed in Sec.~\ref{sec:Rgc}.
 
 \subsection{Age-estimates}
-Figure~\ref{fig:MW-M31-age} shows a histogram of the age-estimates of the $55$
-MW GCs in V13 and $88$ GCs in M31 for which age-estimates are available in CR16.
-The mean age of the MW GCs in this data set is $11.9 \pm 0.1$~Gyr and the 
+The top panel of Figure~\ref{fig:MW-M31-age-Rgc} shows a histogram of the age-estimates
+of the $55$ MW GCs in V13 and $88$ GCs in M31 for which age-estimates are available
+in CR16. The mean age of the MW GCs in this data set is $11.9 \pm 0.1$~Gyr and the 
 dispersion is $0.8$~Gyr. Furthermore, only one of the 55 GC age-estimates is
@@
 which is somewhat surprising given that M31 is generally considered to be earlier
-type than the MW meaning that an older stellar population would naively be expected
-. However, we do caution that both data sets are incomplete and the age 
+type than the MW meaning that an older stellar population would naively be expected.
+However, we do caution that both data sets are incomplete and the age 
 measurements have large uncertainties (of $1-2$~Gyr). On the other hand, the 
@@
 
+\subsection{Radial distribution}
+\label{sec:Rgc}
+The bottom panel of Figure~\ref{fig:MW-M31-age-Rgc} shows the radial distribution
+of the MW and M31 GCS. Both quantities are readily available in H96e10 (assuming
+$R_{\odot}=8.0$~kpc), but the galactocentric radius of GCs in M31 is not available
+in CR16. Therefore we follow \citet[][Sec.~4.1]{2019arXiv190111229W} to calculate
+the projected radius $R_{\text{proj}}$ from the observed positions, adopting M31's
+central position from the NASA Extragalactic 
+Database\footnote{\url{https://ned.ipac.caltech.edu/}} $(\alpha_0, \, \delta_0) =
+(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
+and distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}.
+We calculate $R_{\text{GC}}$ as `average deprojected distance`
+$R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$.
+
+The solid lines show the distributions using all available data (because the
+sky coordinates are known for each GC), while the subset for which age-estimates
+are available is indicated using dotted lines. The latter shows a narrower range
+of radii than the full data set: it appears that age-estimates are neither
+available for the innermost ($<1$~kpc) GCs, nor for those beyond roughly twenty
+kpc (the halo GCs). We compare both distributions of the full data set (solid 
+lines) and find that the Milky Way has more GCs in the range $1-4$~kpc than M31
+(when accounting for the larger number of total GCs in M31). Interestingly, both
+distributions show a similar trend for $R_{\text{GC}} > 4$~kpc and host a 
+subpopulation of halo GCs. However, both radial distributions are not 
+statistically consistent due to substantial differences at intermediate radii.
+
 \begin{figure}
     \includegraphics[width=\columnwidth]{{MW_M31_Age_Histogram-trim}.png}
+    \includegraphics[width=\columnwidth]{{MW_M31_Rgc_Histogram-trim}.png}
     \caption{
-        Age distribution of 55 GCs in the MW
+        \emph{Top}: Age distribution of 55 GCs in the MW
         \citep[data from][]{2013ApJ...775..134V} and 88 GCs
         in M31 \citep[data from][]{2016ApJ...824...42C}.
-        \label{fig:MW-M31-age}
+        \emph{Bottom:} Distribution of galactocentric radius in the MW and M31.
+        The dotted lines show the subset of data that also have age measurements
+        (i.e. the same sample as used in the top panel).
+        \label{fig:MW-M31-age-Rgc}
     }
@@
 
-\subsection{Total GC mass in metallicity-radial space}
-\label{sec:observations_FeHRgc}
+\subsection{Total GC mass in metallicity-radial space} \label{sec:observations_FeHRgc}
 We show the two-dimensional mass-weighted metallicity-radial distribution of the
-MW (M31) GCS in the top (bottom) panel of Figure~\ref{fig:observations_FeHRgc}. Both
-quantities are readily available in H96e10 (assuming $R_{\odot}=8.0$~kpc), but
-the galactocentric radius of GCs in M31 is not available in CR16. Therefore we
-follow \citet[][Sec.~4.1]{2019arXiv190111229W} to calculate the projected radius
-$R_{\text{proj}}$ from the observed positions, adopting M31's central position
-from the NASA Extragalactic Database\footnote{\url{https://ned.ipac.caltech.edu/}}
-$(\alpha_0, \, \delta_0) =
-(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
-and distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}
-We calculate $R_{\text{GC}}$ as `average deprojected distance`
-$R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$. The observations indicate that
+MW (M31) GCS in the top (bottom) panel of Figure~\ref{fig:observations_FeHRgc}. 
+The observations indicate that
 no GCs with high metallicities are to be expected at large radii (the three bins
@@
 We define GC candidates in the Auriga simulations as all star particles older
-than $10$~Gyr based on the age distribution of the MW GCS (Figure~\ref{fig:MW-M31-age}),
-and following the analysis of \citet{2017MNRAS.465.3622R}.
+than $10$~Gyr based on the age distribution of the MW GCS (top panel of 
+Figure~\ref{fig:MW-M31-age-Rgc}), and following \citet{2017MNRAS.465.3622R}.
 
-Trough out our analysis we compare the distributions of three subsets of star
-particles: \emph{old stars} (age $>10$~Gyr, or GC candidates), \emph{old insitu}
+Troughout our analysis we compare the distributions of three subsets of star
+particles: \emph{old stars} (age $>10$~Gyr, or GC candidates), \emph{old in~situ}
 stars (defined as those bound to the most-massive halo/subhalo in the first
 snapshot that the particle was recorded), and \emph{old accreted} star particles
-(those that have formed ex-situ and are bound to the most-massive halo/subhalo
+(those that have formed {\it ex~situ} and are bound to the most-massive halo/subhalo
 at $z=0$). For comparison we also include the results for \emph{all stars} (when
@@
 metallicity distributions consistent with the MW and M31 GC systems, and whether
-the subgrid generates sufficient total mass at metallicities typical for the
+the simulations generate sufficient total mass at metallicities typical for the
 MW and M31 GCS's. To visually inspect the former we show the normalized metallicity 
@@
         the GG candicates in green. We split the GC candidates into two
-        subpopulations, those that have formed insitu (blue), and those that have
+        subpopulations, those that have formed {\it in~situ} (blue), and those that have
         been accreted (red). The dotted green line shows all star particles.
@@
 different distributions. We plot the age-selected GC candidates in green, those
-that are accreted in red, and the insitu subpopulation in blue. The top 
+that are accreted in red, and the {\it in~situ} subpopulation in blue. The top 
 half of the left figure shows the MW (M31) GC system in purple (magenta), where 
@@
 $-0.6$. Furthermore, the old accreted stars generally have lower mean metallicities
-than the old insitu stars with differences of roughly ${\sim}0.3$ for the majority 
+than the old {\it in~situ} stars with differences of roughly ${\sim}0.3$ for the majority 
 of the simulation runs. This behaviour can be seen in \mbox{Au4-21}, while a 
@@
 \mbox{Au4-16}, \mbox{Au4-17}, \mbox{Au4-18} and \mbox{Au4-22}. However, this trend 
-is reversed for \mbox{Au4-1} and \mbox{Au4-4} for which the old insitu population 
+is reversed for \mbox{Au4-1} and \mbox{Au4-4} for which the old {\it in~situ} population 
 has a lower mean metallicity instead. We caution that \mbox{Au4-1} is undergoing
 a major merger at redshift zero and note that we find $\mu = -1.51 \, ({-0.74})$ 
-for the old insitu (accreted) although the former consists of only $1019$ 
+for the old {\it in~situ} (accreted) although the former consists of only $1019$ 
 particles ($1.3$\% of all GC candidates, and with a total mass of 5e7 M\Sun). 
-For \mbox{Au4-4}, ${10.8}$\% of the GC candidates is classified as insitu (compared 
-to insitu fractions of ${40-80}$\% for other haloes). Overall we find that the 
-simulations produce (sub)populations of GC candidates that are
-more metal-rich than the MW and M31 GC systems. Moreover, none of the simulations
-has a population of GC candidates with a bimodal metallicity distribution
-(the green curves).
+For \mbox{Au4-4}, ${10.8}$\% of the GC candidates is classified as {\it in~situ} (compared 
+to {\it in~situ} fractions of ${40-80}$\% for other haloes). After inspection of
+the same figure for every one of the thirty Auriga L4 haloes we find that the 
+simulations produce (sub)populations of GC candidates that are more metal-rich
+than the MW and M31 GC systems. Moreover, none of the simulations has a 
+population of GC candidates with a bimodal metallicity distribution (the green
+curves).
 
@@
         Each cross (for a given colour) represents one simulation. The green (blue)
-        [red] crosses show the values calculated using the old (old insitu)
+        [red] crosses show the values calculated using the old (old {\it in~situ})
         [old accreted] star particles. Green triangles indicate that all stars
@@
 Having said that, we do find it interesting that the mean metallicities of the 
-old insitu populations appear roughly consistent with that of the metal-rich 
+old {\it in~situ} populations appear roughly consistent with that of the metal-rich 
 population of the MW although the simulations show larger dispersions. The latter 
-could simply be caused by the hard separation of the data into two groups, which 
-means the range is smaller and the resulting dispersion could be lower. With 
+could simply be caused by the hard separation of the MW data into two groups, 
+which means the range is smaller and the resulting dispersion lower. With 
 regard to the M31 GCS, we are uncertain whether definitive consensus is reached
-concerning uni- bi- or trimodality in the [Fe/H] distribution, but CR16 argues 
-that the data, after removal of younger objects due to improved age classification, 
-hints at three populations separated at [Fe/H]~$>-0.4$ and [Fe/H]~$ < 1.5$. None 
-of the Auriga sub sets has a mean value that offers much hope that the simulated 
-distribution is consistent with the lowest metallicity group in the M31 GCS. This 
-is also true for the metal-poor population of the MW with a mean value of $-1.6$.
-The main take-away from this plot, again, is that all Auriga L4 galaxies have
-metallicity distributions with (much) larger mean values than what is observed
-for the MW and M31 GCS, and that we systematiclly find lower mean metallicities
-for the accreted GC candidates than for those that have formed in situ.
+in the literature concerning uni- bi- or trimodality in the [Fe/H] distribution, 
+but CR16 argues that the data, after removal of younger objects due to improved 
+age classification, hints at three populations separated at [Fe/H]~$>-0.4$ and 
+[Fe/H]~$ < 1.5$. None of the Auriga sub sets has a mean value that offers much 
+hope that the simulated distribution is consistent with the lowest metallicity 
+group in the M31 GCS. This is also true for the metal-poor population of the 
+MW with a mean value of $-1.6$. The main take-away from this plot, again, is 
+that all Auriga L4 galaxies have metallicity distributions with (much) larger
+mean values than what is observed for the MW and M31 GCS, and that we 
+systematically find lower mean metallicities for the accreted GC candidates
+than for those that have formed {\it in~situ}.
 
-Finally, we test the null hypothesis that MW (M31) and the GC candidates (all, insitu, and
-accreted) are drawn from the same underlying distribution by calculating the KS
-test statistic (i.e. six KS tests per simulation). We reject $H_0$ at the 100.00~\%
-confidence level for virtually all subsets of all simulations, both for MW and M31,
-except when comparing the old accreted stars of \mbox{Au4-10} to the MW GCS. In this
-case we still reject $H_0$ with, but with $\leq 98.68$~\% confidence. When comparing
-to the M31 GCS, the `best' matches are the old accreted subpopulations of \mbox{Au4-13},
-\mbox{Au4-15}, and \mbox{Au4-17} ($H_0$ rejected with $\leq$ 99.82~\% confidence, 99.95~\%,
-and 98.32~\%). Here we find that the cumulative distributions are more or less
-similar up to [Fe/H]~$-0.5$, above which the simulations yield higher number
-counts which drives the KS test statistic over the critical values. This affirms
-our finding that the simulations produce GC candidates that are more metal-rich
-than the MW (M31) GCS. The main reasons that $H_0$ is rejected with such
-high confidence are under-production of old stars with [Fe/H]~$\leq$~-1.5,
-and over-production of stars with [Fe/H]$\geq$~-0.5.
+% Finally, we test the null hypothesis that MW (M31) and the GC candidates (all,
+% {\it in~situ}, and accreted) are drawn from the same underlying distribution 
+% by calculating the KS test statistic (i.e. six KS tests per simulation). We 
+% reject $H_0$ at the 100.00~\% confidence level for virtually all subsets of all 
+% simulations, both for MW and M31, except when comparing the old accreted stars 
+% of \mbox{Au4-10} to the MW GCS. In this case we still reject $H_0$ with, but 
+% with $\leq 98.68$~\% confidence. When comparing to the M31 GCS, the `best' 
+% matches are the old accreted subpopulations of \mbox{Au4-13}, \mbox{Au4-15}, and 
+% \mbox{Au4-17} ($H_0$ rejected with $\leq$ 99.82~\% confidence, 99.95~\%,
+% and 98.32~\%). Here we find that the cumulative distributions are more or less
+% similar up to [Fe/H]~$-0.5$, above which the simulations yield higher number
+% counts which drives the KS test statistic over the critical values. This affirms
+% our finding that the simulations produce GC candidates that are more metal-rich
+% than the MW (M31) GCS. The main reasons that $H_0$ is rejected with such
+% high confidence are under-production of old stars with [Fe/H]~$\leq$~-1.5,
+% and over-production of stars with [Fe/H]$\geq$~-0.5.
 
@@
         age $>$~10~Gyr; green solid). The latter sub set is further split up
-        between stars that formed in-situ (blue solid), and those that were accreted
+        between stars that formed {\it in~situ} (blue solid), and those that were accreted
         (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
@@
 We now turn to the second goal, which is to see whether sufficient total mass in 
-GC candidates produced by the Auriga simulations. To answer this question we plot
+GC candidates is produced by the Auriga simulations. To answer this question we plot
 a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
@@
 (green dotted), and we learn that the mass at the peak lowers by roughly one dex. 
-The mass budget of the old stars is dominated by the old insitu population (blue 
+The mass budget of the old stars is dominated by the old {\it in~situ} population (blue 
 solid) below [Fe/H]~=~$-1$, and by the old accreted stars (red solid) above this 
@@
 while still producing sufficient mass at the right metallicities. In particular,
-the cluster formation efficiency would have to linearly decrease with decreasing 
+the cluster formation efficiency would have to decrease with decreasing 
 metallicity for Auriga GC candidates to produce a population of GC candidates 
@@
 \begin{figure}
-    \includegraphics[width=\columnwidth]{{Rgc_mu_sigma-trim}.png}
+    \includegraphics[width=\columnwidth]{{LogRgc_mu_sigma-trim}.png}
     \caption{
-        Mean and standard deviation of the radial distribution of star particles
-        in each of the thirty Auriga L4 haloes compared to the MW (M31) GCS
-        shown in purple (magenta).
+        Mean and standard deviation of the logarithm of radial distribution 
+        of star particles in each of the thirty Auriga L4 haloes compared to
+        the MW (M31) GCS shown in purple (magenta).
         \label{fig:Rgc_mu_sigma}
@@
 in all Auriga L4 galaxies. Figure~\ref{fig:Rgc_mu_sigma} shows the mean and 
-standard deviation of the radial distribution of star particles in all Auriga L4 
-simulations. We notice that the old insitu populations are more centrally 
+standard deviation of $\log_{10}(R_{\text{GC}})$ of star particles in all Auriga
+L4 simulations. The purple (magenta) cross again shows the mean of the MW (M31)
+GCs (which are to be compared to the green crosses), but solid (open) dot now
+shows our calculation of the mean value of the metal-rich (metal-poor) population 
+as no literature values were available. We split the radii up into the 
+metal-rich/metal-poor groups by taking a metallicity cut at [Fe/H]~=~-1 as is 
+done in the literature.
+
+We notice that the old {\it in~situ} populations are more centrally 
 distributed, whereas the old accreted subsets have a larger radial extent. This 
-is not surprising because the classification of in situ requires star particles 
+is not surprising because the classification of {\it in~situ} requires star particles 
 to have formed within the virial radius, thus they could naturally be expected 
@@
 first have to migrate inwards in order to populate the innermost radii. Moreover,
-we notice that the dispersion increases with increasing mean value of the radial 
-distribution as may be expected for a non-negative quantity. The purple (magenta)
-cross indicates the values for the MW (M31) GCS, which are to be compared to the
-green crosses. The MW GCS lies roughly within the range of values seen for the 
-radial distributions produced by the Auriga simulations, whereas the mean of M31
-is larger and closer to typical mean values of the accreted GC candidates in
-the Auriga simulations. The larger radial extend of the M31 GCS is generally
-believed to hint at a more accretion-dominated origin of the GCS, and may reflect
-a richer accretion history of the galaxy in comparison to the Milky Way.
+we find that the simulations have a wider dispersion in $\log(R_{\text{GC}}$ than
+the MW GCS, while the dispersion of M31 seems to lie witin the range of dispersions
+found in the Auriga galaxies. Furthermore, the mean of the MW GCS lies roughly 
+within the range of values produced by the Auriga simulations, whereas the mean 
+of M31 is somewhat larger and slightly closer to typical mean values of the 
+accreted GC candidates in the Auriga simulations. The larger radial extent 
+of the M31 GCS is generally believed to hint at a more accretion-dominated origin 
+of the GCS, and may reflect a richer accretion history of the galaxy in comparison 
+to the Milky Way.
 
@@
         age $>$~10~Gyr; green solid). The latter sub set is further split up
-        between stars that formed in-situ (blue solid), and those that were accreted
-        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
-        GCS is shown in purple (magenta). The middle (bottom) panel shows the
-        ratio of the simulated mass to the mass in the MW (M31) GCS.
+        between stars that formed {\it in~situ} (blue solid), and those that 
+        were accreted (red solid). Shaded regions indicate the $1\sigma$ 
+        interval. The MW (M31) GCS is shown in purple (magenta). The middle 
+        (bottom) panel shows the ratio of the simulated mass to the mass in the 
+        MW (M31) GCS.
         \label{fig:Rgc}
@@
 Furthermore, we find that the dominant contribution to the total mass in GC
-candidates changes from those formed insitu to the accreted population around
+candidates changes from those formed {\it in~situ} to the accreted population around
 $10$~kpc. Again we show the mass excess of the simulations compared to the Milky
@@
 to the bar or bulge. Compared to Andromeda, the mass excess (bottom panel of 
-Figure~\ref{fig:Au-FeHRgc-ratio}) shows a less clear trent than for the Milky Way. 
+Figure~\ref{fig:Au-FeHRgc-ratio}) shows a less clear trend than for the Milky Way,
+which suggests that both galaxies have diverse GC formation histories.
 Most bins show mass surplus factors of few tens, meaning that high formation 
@@
 (halo) field stars - the disk component effectively falls outside our selection 
-of star particles due to the age cut.
+of star particles due to the age cut. It is implausible that all halo stars 
+come from disrupted GCs because GC systems that survive down to redshift zero 
+are generally few orders of magnitude less massive than galactic stellar haloes.
 
@@
 the metal-poor population is dominated by accreted star particles and the metal-rich
-population by insitu stars.
+population by {\it in~situ} stars.
 
@@
 cross-over point above (below) which the mass-weighted metallicity distribution
-of GC candidates is dominated by those that have formed insitu (were accreted) 
-does coincide with the separation between the metal-rich and metal-poor populations 
-of GC systems at [Fe/H]~=~$-1$. Moreover, we do find that the mean metallicity
-shifts when we split the GC candidates up according to birth location (accreted
-or in-situ). In particular, the mean values of the old insitu GC candidates are 
-roughly consistent with the metal-rich MW GCs. However, we also notice that a 
-substantial number of simulations has similar mean values for all GC candidates, 
-and the simulated insitu GC candidates have larger dispersions than the metal-rich 
-GCs. Moreover, the offset between the mean of the metal-rich and metal-poor 
-populations in the MW is $1$ dex, a factor $2-3$ larger than the offset that we 
-find between the insitu and accreted populations. The Auriga simulations therefore
-do not support the view that the metal-poor GCs could have formed in satellites
-that have later been accreted whereas the metal-rich GC subpopulation has formed
-insitu. With this statement, however, we do caution that \citet{2019MNRAS.486.3134K} 
-suggests to reserve the `ex situ' classification for accretion after $z=2$, when
+of GC candidates is dominated by those that have formed {\it in~situ} (were
+accreted) does coincide with the separation between the metal-rich and metal-poor
+populations of GC systems at [Fe/H]~=~$-1$. Moreover, we do find that the mean
+metallicity shifts when we split the GC candidates up according to birth location
+(accreted or {\it in~situ}). In particular, the mean values of the old 
+{\it in~situ} GC candidates are roughly consistent with the metal-rich MW GCs.
+However, we also notice that a substantial number of simulations has similar 
+mean values for all GC candidates, and the simulated {\it in~situ} GC candidates 
+have larger dispersions than the metal-rich GCs. Moreover, the offset between 
+the mean of the metal-rich and metal-poor populations in the MW is $1$ dex, a
+factor $2-3$ larger than the offset that we find between the {\it in~situ} and 
+accreted populations. The Auriga simulations therefore do not support the view 
+that the metal-poor GCs could have formed in satellites that have later been 
+accreted whereas the metal-rich GC subpopulation has formed {\it in~situ}. With 
+this statement, however, we do caution that \citet{2019MNRAS.486.3134K} suggests 
+to reserve the `{\it ex~situ}' classification for accretion after $z=2$, when
 the central galaxy has formed and accretion unambigously contributes to the
@@
     \item The star formation model implemented in the Auriga simulations produces
-    metallicity distributions that are more metal-rich the Milky Way and M31
+    metallicity distributions that are more metal-rich than the Milky Way and M31
     globular cluster systems.
@@
     that the GC candidates and the MW GCs are drawn from the same underlying 
-    distribution with $\geq 98.68$~\% confidence. This statement holds true when
-    we select all old star particles (GC candidates), but also when we select the 
-    old accreted or the old insitu star particles. In addition, this is also
-    the case when we test against the M31 GCS instead of the MW GCS.
+    distribution. This statement holds true when we select all old star particles 
+    (GC candidates), but also when we select the old accreted or the old {\it in~situ} 
+    star particles. In addition, this is also the case when we test against the 
+    M31 GCS instead of the MW GCS. Moreover, the difference between the MW and
+    M31 is big compared to the scatter in GC candidate properties in the Auriga
+    simulations.
 
@@
     star particles at radii beyond $20$~kpc. The GCs in the MW and M31, on the 
-    other hand, have a much smaller radial extend.
+    other hand, have a much smaller radial extent.
 
@@
     with the Milky Way GC system, given that we expect dynamical evolution to 
-    more strongly affect GC candidates at smaller radii. This trent of over-production
+    more strongly affect GC candidates at smaller radii. This trend of over-production
     of old star particles that are metal-rich and at large radii compared to 
     observed GCs is less clear for the M31 GCS.
-
-    \item The Auriga simulations are not consistent with the picture that all
-    metal-rich GCs formed insitu and that all metal-poor GCs were accreted.
 

### 2019-08-05 latexdiff.sh
Remove Volker Springel as author b/c he has not contributed directly (his words)

@@ -1,11 +1,13 @@
 #!/bin/bash
 set -e
 
-diff="diff_with_respect_to_20190712.tex"
+diff="diff_with_respect_to_20190802.tex"
 if [ -f "${diff}" ]; then
     rm -f "${diff}"
 fi
 
 # Ignore (sub)sections: https://tex.stackexchange.com/questions/87536
-latexdiff --exclude-textcmd="section,subsection" AurigaGCS_20190712.tex AurigaGCS.tex > "${diff}"
+# NB, removed by hand Volker Springel from AurigaGCS_20180802.tex b/c
+# latexdiff breaks on changes in the \author block
+latexdiff --exclude-textcmd="section,subsection" AurigaGCS_20190802.tex AurigaGCS.tex > "${diff}"
 timotex "${diff}"

### 2019-08-14 AurigaGCS_20190802.tex
Remove Volker Springel as author b/c he has not contributed directly (his words)
LaTeXdiff dislikes changes in author/affilation list. Updated based on co-author feedback (affiliation FM, and H. for Wilma. #1

--- 2019-08-02 AurigaGCS.tex
@@
     Robert J. J. Grand$^{1}$,
-    Volker Springel$^{1}$,
     Facundo A. G\'{o}mez$^{2,3}$,
-    Federico Marinacci$^{4,5}$,
+    Federico Marinacci$^{4}$,
     R\"{u}diger Pakmor$^{1}$,
-    Wilma Trick$^{1}$,
+    Wilma H. Trick$^{1}$,
     Philipp Busch$^{1}$,
@@
     Juan Cisternas 1200 N, La Serena, Chile \\
-$^{4}$ Department of Physics, Kavli Institute for Astrophysics and Space Research,
-    MIT, Cambridge, MA 02139, USA \\
-$^{5}$ Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge,
-    MA 02138, USA \\
+$^{4}$ Department of Physics \& Astronomy, University of Bologna, via Gobetti 93/2, 40129 Bologna, Italy \\
 }

### 2019-08-14 AurigaGCS.tex
Processed two random remarks. Now go onto a structured approach :-) ... #1

@@
 typical for the MW globular cluster system (GCS), although we observe a varying 
-mass-excess for different $R_{\text{GC}}$-[Fe/H] bins. This implies different 
+mass-excess for different $R_{\text{GC}}$-[Fe/H] bins of simulated GC candidates
+relative to the observed mass in the MW and M31 GC systems. This implies different 
 values for the combined product of the bound cluster formation efficiency and 
@@
         to mass in the MW (M31) GCS, i.e. the logarithm of the mass excess. The
-        color-coded values are also shown in each bin. Note that the three bins
-        in the upper right corner are left blank because the observations have
-        zero mass there, and that the numbers indicate how much (median) mass is
-        produced by the simulations in those bins.
+        number in each bin shows the color-coded value that is plotted, and the
+        (median) star particle count is given in parenthesis. Note that the three 
+        bins in the upper right corner are left blank because the observations
+        have zero mass there.
         \label{fig:Au-FeHRgc-ratio}
@@
 \citet[][p. 234]{1998gcs..book.....A} and \citet[][p. 38]{Harris2001} find that
-the MW GCS has a bimodality [Fe/H] distribution: the latter fit a double Gaussian 
+the MW GCS has a bimodal [Fe/H] distribution: the latter fit a double Gaussian 
 which peaks at [Fe/H] = $-1.59$ (metal-poor) and $-0.51$ (metal-rich) and 

### 2019-08-16 AurigaGCS.tex
Acknowledgements: remarks FM + RG. Thanks MPCDF for Freya

@@
 \section*{Acknowledgements}
-TLRH acknowledges support from the International Max-Planck Research School (IMPRS) on Astrophysics.
-\todo[inline]{Check Auriga boilerplate that we need to acknowledge}
-RG and VS acknowledge support by the DFG Research Centre SFB-881 `The
-Milky Way System' through project A1. This work has also been
-supported by the European Research Council under ERC-StG grant
-EXAGAL- 308037. Part of the simulations of this paper used the
-SuperMUC system at the Leibniz Computing Centre, Garching,
-under the project PR85JE of the Gauss Centre for Supercomputing.
-This work used the DiRAC Data Centric system at Durham
-University, operated by the Institute for Computational Cosmology
-on behalf of the STFC DiRAC HPC Facility `www.dirac.ac.uk'.
-This equipment was funded by BIS National E-infrastructure capital
-grant ST/K00042X/1, STFC capital grant ST/H008519/1 and
-STFC DiRAC Operations grant ST/K003267/1 and Durham University.
+TLRH acknowledges support from the International Max-Planck Research School (IMPRS)
+on Astrophysics. TLRH thanks the Max Planck Computing and Data Facility for
+maintaining the Freya compute cluster, where the simulations were post-processed.
+FM is supported by the program "Rita Levi Montalcini" of the Italian MIUR.
+This work has been supported by the European Research Council under ERC-StG grant
+EXAGAL- 308037. Part of the simulations of this paper used the SuperMUC system 
+at the Leibniz Computing Centre, Garching, under the project PR85JE of the Gauss 
+Centre for Supercomputing. This work used the DiRAC Data Centric system at Durham
+University, operated by the Institute for Computational Cosmology on behalf of
+the STFC DiRAC HPC Facility `www.dirac.ac.uk'. This equipment was funded by BIS 
+National E-infrastructure capital grant ST/K00042X/1, STFC capital grant 
+ST/H008519/1 and STFC DiRAC Operations grant ST/K003267/1 and Durham University.
 DiRAC is part of the UK National E-Infrastructure.

### 2019-08-16 AurigaGCS.tex
Updated Figure 1 for #1

@@
 typical for the MW globular cluster system (GCS), although we observe a varying 
-mass-excess for different $R_{\text{GC}}$-[Fe/H] bins of simulated GC candidates
+mass-excess for different galactocentric radius-metallicity 
+($R_{\text{gal}}$-[Fe/H]) bins of simulated GC candidates
 relative to the observed mass in the MW and M31 GC systems. This implies different 
@@
 the Milky Way as well as that of the Andromeda galaxy. The same holds true for 
-the distribution of galactocentric radius. Overall, the Auriga simulations produce 
+the distribution of $R_{\text{gal}}$ . Overall, the Auriga simulations produce 
 old star particles with higher metallicities than the MW and M31 GCS and at 
@@
 center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic
-Pole. We calculate the galactocentric radius $R_{\text{GC}}=\sqrt{(X-R_\odot)^2
+Pole. We calculate the galactocentric radius $R_{\text{gal}}=\sqrt{(X-R_\odot)^2
 + Y^2 + Z^2}$, assuming the solar radius $R_\odot=8$~kpc.}, and absolute
@@
 and distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}.
-We calculate $R_{\text{GC}}$ as `average deprojected distance`
-$R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$.
+We calculate $R_{\text{gal}}$ as `average deprojected distance`
+$R_{\text{gal}} = R_{\text{proj}} \times (4/\pi)$.
 
@@
 (when accounting for the larger number of total GCs in M31). Interestingly, both
-distributions show a similar trend for $R_{\text{GC}} > 4$~kpc and host a 
+distributions show a similar trend for $R_{\text{gal}} > 4$~kpc and host a 
 subpopulation of halo GCs. However, both radial distributions are not 
@@
         The dotted lines show the subset of data that also have age measurements
-        (i.e. the same sample as used in the top panel).
+        (i.e. the same sample as in the top panel).
         \label{fig:MW-M31-age-Rgc}
@@
 in the upper right corner, both for MW and M31), and relatively few GCs at large
-radii in general ($R_{\text{GC}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
+radii in general ($R_{\text{gal}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
 the MW and $17$ or 4.6\% in M31). Moreover, the M31 hosts more metal-rich 
@@
     \caption{
-        \emph{Top}: Mass-weighted $R_{\text{GC}}$-[Fe/H] distribution of
-        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
-        is 98.6 (92.2) \% of the total mass (clusters) of the MW GCS in the Harris
-        catalog. \emph{Bottom}: Same for M31, showing 366 GCs and 88.4 (83.9) \%
-        of the total mass (clusters) in CR16 \citep[data from][]{2016ApJ...824...42C}.
-        Note that the range of the colourmap differs in both figures.
+        \emph{Top}: Mass-weighted $R_{\text{gal}}$-[Fe/H] distribution of
+        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H},
+        color-coded by the \textbf{median} (values also shown in each bin). The 
+        numbers in parenthesis show how many star particles fall within the bin.
+        \emph{Bottom}: Same for M31, showing the 366 GCs in CR16 
+        \citep[data from][]{2016ApJ...824...42C}. Note that the range of the 
+        colourmap differs in both figures.
         \label{fig:observations_FeHRgc}
@@
 in all Auriga L4 galaxies. Figure~\ref{fig:Rgc_mu_sigma} shows the mean and 
-standard deviation of $\log_{10}(R_{\text{GC}})$ of star particles in all Auriga
+standard deviation of $\log_{10}(R_{\text{gal}})$ of star particles in all Auriga
 L4 simulations. The purple (magenta) cross again shows the mean of the MW (M31)
@@
 first have to migrate inwards in order to populate the innermost radii. Moreover,
-we find that the simulations have a wider dispersion in $\log(R_{\text{GC}}$ than
+we find that the simulations have a wider dispersion in $\log(R_{\text{gal}})$ than
 the MW GCS, while the dispersion of M31 seems to lie witin the range of dispersions
@@
 We investigate whether the Auriga simulations still produce sufficient mass when
-the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{GC}$. First
+the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{gal}$. First
 we sum the total simulated mass in each bin (for an individual Auriga simulation),
@@
     \caption{
-        Mass-weighted [Fe/H]-$R_{\text{GC}}$ distribution of all thirty Auriga
+        Mass-weighted [Fe/H]-$R_{\text{gal}}$ distribution of all thirty Auriga
         L4 haloes. Here we consider only the GC candidates (age $>$~10~Gyr) stars
@@
 for example, be improved by selecting a number of globular clusters based on the 
-$M_{vir}-N_{\text{GC}}$ correlation found by \citet{2019arXiv190100900B}, and 
+$M_{vir}-N_{\text{gal}}$ correlation found by \citet{2019arXiv190100900B}, and 
 taking a virial mass below which none of the star particles is treated as GC candidate.

### 2019-08-16 AurigaGCS.tex
Updated Figure 2 for #1
Updated Figure 3 for #1

@@
         {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
+    \centering \textcolor{lightgray}{\rule[2mm]{\columnwidth}{0.05mm}}
     \includegraphics[width=\columnwidth]
@@
 
-\begin{figure*}
-    \includegraphics[width=\columnwidth]{{Au4-10_FeH_cleaner-trim}.png}
-    \includegraphics[width=\columnwidth]{{Au4-4_and_Au4_21_FeH-trim}.png}
+\begin{figure}
+    \includegraphics[width=\columnwidth]{{FeH_obs_Au4-4_Au4-10_Au4-21}.png}
     \caption{
-        \emph{Left:} Metallicity distribution of Au4-10 (bottom panel). We show
-        the GG candicates in green. We split the GC candidates into two
-        subpopulations, those that have formed {\it in~situ} (blue), and those that have
-        been accreted (red). The dotted green line shows all star particles.
-        The solid purple (magenta) line in the top panel shows the GC system
-        of the MW (M31). \emph{Right:} Au4-4 (bottom), and Au4-21 (top).
+        \emph{Top}: Metallicity distribution of the MW and M31 GCS. The solid 
+        purple (magenta) line shows the GC system of the MW (M31), and we 
+        indicate the mean value with an arrow at the bottom of the x-axis. We
+        overplot a double Gaussian for the MW GCS using purple dotted lines, taking
+        the mean and dispersion from \citep{Harris2001}.
+        \emph{Other panels}: three selected Auriga haloes as indicated in the 
+        upper right corner. In each of these three panels we show the GG 
+        candicates in green, and use a green dotted line for all star particles. 
+        We split the GC candidates up into two subpopulations, those that have 
+        formed {\it in~situ} (blue), and those that have been accreted (red).
         \label{fig:Au4-10and21_FeH}
     }
-\end{figure*}
+\end{figure}
 We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the

### 2019-08-18 AurigaGCS.tex
Updated Figure 4 and 6 for #1
Updated Figure 5 and 7 for #1

@@
 typical for the MW globular cluster system (GCS), although we observe a varying 
-mass-excess for different galactocentric radius-metallicity 
+mass-ratio for different galactocentric radius-metallicity 
 ($R_{\text{gal}}$-[Fe/H]) bins of simulated GC candidates
@@
     \caption{
-        First vs second central moment of the Auriga L4 metallicity distributions.
+        First vs. second central moment of the Auriga L4 metallicity distributions.
         Each cross (for a given colour) represents one simulation. The green (blue)
@@
 that is consistent with the MW. For the GC candidates in M31 we find a constant 
-mass excess up to $-0.9$, above which the simulations produce a higher mass excess 
+mass ratio up to $-0.9$, above which the simulations produce a higher mass ratio 
 with increasing metallicity. If dynamical evolution is not expected to more 
@@
 candidates changes from those formed {\it in~situ} to the accreted population around
-$10$~kpc. Again we show the mass excess of the simulations compared to the Milky
-Way and Andromeda GCS. We find a decreasing mass excess with increasing radius
+$10$~kpc. Again we show the mass ratio of the simulations compared to the Milky
+Way and Andromeda GCS. We find a decreasing mass ratio with increasing radius
 in the range $0.2$ to ${\sim}5$ kpc, followed by an increase attributed
@@
 Figure~\ref{fig:observations_FeHRgc}). Finally, we divide these value by the total
-mass in the MW (M31) GCS to obtain the median mass excess produced by the star
+mass in the MW (M31) GCS to obtain the median mass ratio produced by the star
 formation model implemented in the Auriga simulations. See the top (bottom) panel
-of Figure~\ref{fig:Au-FeHRgc-ratio} for mass excess with respect to the MW (M31) GCS.
+of Figure~\ref{fig:Au-FeHRgc-ratio} for mass ratio with respect to the MW (M31) GCS.
 
@@
 simulations, in contrast to the observations. The top panel of 
-Figure~\ref{fig:Au-FeHRgc-ratio} shows that the mass excess for Auriga GCs within
+Figure~\ref{fig:Au-FeHRgc-ratio} shows that the mass ratio for Auriga GCs within
 the Solar radius decreases with decreasing metallicity. This means that either
@@
 region for GCs on orbits that pass through the disk, or with pericenters close 
-to the bar or bulge. Compared to Andromeda, the mass excess (bottom panel of 
+to the bar or bulge. Compared to Andromeda, the mass ratio (bottom panel of 
 Figure~\ref{fig:Au-FeHRgc-ratio}) shows a less clear trend than for the Milky Way,
@@
         {{Au4-median_RgcFeH_HistogramMassWeighted_MW_iold-trim}.png}
+    \centering \textcolor{lightgray}{\rule[2mm]{\columnwidth}{0.05mm}}
     \includegraphics[width=0.49\textwidth]
@@
         The top (bottom) panel shows the logarithm of the ratio of simulated mass
-        to mass in the MW (M31) GCS, i.e. the logarithm of the mass excess. The
+        to mass in the MW (M31) GCS, i.e. the logarithm of the mass ratio. The
         number in each bin shows the color-coded value that is plotted, and the

### 2019-08-18 AurigaGCS.tex
Updated Figure 9 for #1

@@
     \includegraphics[width=0.49\textwidth]
-        {{Au4-median_RgcFeH_HistogramMassWeighted_MW_iold-trim}.png}
+        {{Au4-median_RgcFeH_HistogramMassWeighted_MW_iold_diverging-trim}.png}
     \centering \textcolor{lightgray}{\rule[2mm]{\columnwidth}{0.05mm}}
     \includegraphics[width=0.49\textwidth]
-        {{Au4-median_RgcFeH_HistogramMassWeighted_M31_iold-trim}.png}
+        {{Au4-median_RgcFeH_HistogramMassWeighted_M31_iold_diverging-trim}.png}
     \caption{
         The top (bottom) panel shows the logarithm of the ratio of simulated mass
-        to mass in the MW (M31) GCS, i.e. the logarithm of the mass ratio. The
-        number in each bin shows the color-coded value that is plotted, and the
-        (median) star particle count is given in parenthesis. Note that the three 
-        bins in the upper right corner are left blank because the observations
-        have zero mass there.
+        to mass in the MW (M31) GCS, i.e. the logarithm of the mass ratio, minus
+        the median value. This way red indicates regions of with a higher mass
+        excess than the median, conversely blue highlights bins with a lower than
+        median mass ratio. The number in each bin shows the color-coded value 
+        that is plotted, and the (median) star particle count is given in 
+        parenthesis. Note that the three bins in the upper right corner are white
+        because the observations have zero mass there.
         \label{fig:Au-FeHRgc-ratio}

### 2019-08-18 AurigaGCS_20190802.tex
Updated Figure 9 for #1

@@
     \includegraphics[width=0.49\textwidth]
-        {{Au4-median_RgcFeH_HistogramMassWeighted_MW_iold-trim}.png}
+        {{Au4-median_RgcFeH_HistogramMassWeighted_MW_iold_diverging-trim}.png}
     \includegraphics[width=0.49\textwidth]
-        {{Au4-median_RgcFeH_HistogramMassWeighted_M31_iold-trim}.png}
+        {{Au4-median_RgcFeH_HistogramMassWeighted_M31_iold_diverging-trim}.png}
     \caption{

### 2019-08-19 AurigaGCS.tex
Edited abstract/introduction based on feedback WHT, RG, FM for #1. Textual remarks only, not yet feedback onto the content itself.

@@
 We investigate whether the galaxy formation model used for the Auriga simulations
-can produce a realistic globular cluster (GC) population at redshift zero. We
-compare properties of the simulated star particles in the Auriga haloes with
-catalogues of observations of the Milky Way (MW) and Andromeda (M31) globular
-cluster populations available in the literature. We find that the Auriga 
-simulations do produce sufficient mass at radii and metallicities that are 
-typical for the MW globular cluster system (GCS), although we observe a varying 
-mass-ratio for different galactocentric radius-metallicity 
-($R_{\text{gal}}$-[Fe/H]) bins of simulated GC candidates
-relative to the observed mass in the MW and M31 GC systems. This implies different 
-values for the combined product of the bound cluster formation efficiency and 
-the globular cluster disruption rate. Furthermore we test whether any of the 
+can produce a realistic globular cluster (GC) population. We compare statistics 
+of GC candidate star particles in the Auriga haloes with catalogues of the Milky 
+Way (MW) and Andromeda (M31) globular cluster populations. We find that the Auriga 
+simulations do produce sufficient stellar mass for GC candidates at radii and 
+metallicities that are typical for the MW GC system (GCS), although we observe a 
+varying mass-ratio for different galactocentric radius-metallicity 
+($R_{\text{gal}}$-[Fe/H]) bins of simulated GC candidates relative to the 
+observed mass in the MW and M31 GC systems.
+This implies different values for the combined product of the bound cluster 
+formation efficiency and the GC disruption rate. Furthermore we test whether any of the 
 Auriga galaxies has a metallicity and radial distribution that is consistent with 
@@
 from the same distribution at $\geq98.32$~\% confidence level, for the GCS of 
-the Milky Way as well as that of the Andromeda galaxy. The same holds true for 
-the distribution of $R_{\text{gal}}$ . Overall, the Auriga simulations produce 
-old star particles with higher metallicities than the MW and M31 GCS and at 
-larger radii. The formation efficiency would have to linearly decrease with 
-increasing metallicity for the Auriga GC candidates to be consistent with the 
-MW GCS, if cluster disruption is equally efficient regardless of metallicity.
-In addition, the number of GCs relative to field stars would have to be smaller
-for higher metallicity star particles at large radii than for those with lower 
-metallicity at smaller radii, assuming GC disruption is more efficient in the
-inner regions of the Galaxy.
-
+the MW and M31. The same holds true for the distribution of $R_{\text{gal}}$.
+Overall, the Auriga simulations produce old star particles with higher metallicities 
+than the MW and M31 GCS and at larger radii. This implies that the bound cluster
+formation efficiency would have to decrease with increasing metallicity for the 
+Auriga GC candidates to be consistent with the MW GCS, if GC disruption is equally 
+efficient regardless of metallicity. In addition, the number of GCs relative to
+field stars would have to be smaller for higher metallicity star particles at
+large radii than for those with lower metallicity at smaller radii, assuming GC 
+disruption is more efficient in the inner regions of the Galaxy.
 \end{abstract}
@@
 \section{Introduction}
-Globular clusters (GC)s are old, bright, ubiquitous, and various properties of
+Globular clusters (GC)s are old, bright, and ubiquitous. Various properties of
 GC systems show correlations with their host galaxies. GC systems are believed to
-retain information about the galactic (gas) conditions at times of formation,
-thus, could offer unique insight into the (chemodynamical) evolution of their 
+retain information about the galactic (gas) conditions at their times of formation.
+Thus they could offer a unique insight into the (chemodynamical) evolution of their 
 parent galaxies, if the formation and evolution of GCs- and GC systems themselves 
@@
 with typical GC masses and sizes. \citet{2005MNRAS.364..367D} and \citet{
-2009ApJ...706L.192B} argue that (the blue subpopulations of) GCs form in biased 
-dark matter halos at high redshift. Other recent hypotheses of GC formation prior 
-to collapse of the proto-galaxy include formation in colliding supershells 
+2009ApJ...706L.192B} argue that (the blue subpopulations of) GCs form in radially
+biased dark matter halos at high redshift. Other recent hypotheses of GC formation 
+prior to collapse of the proto-galaxy include formation in colliding supershells 
 \citep{2017Ap&SS.362..183R}, in supersonically induced gaseous objects
@@
 (\citealt{1985ApJ...298...18F}, also see the discussions in \citealt{
-1990ApJ...363..488K}). Alternative formation trigggers are also explored, such as 
+1990ApJ...363..488K}). Alternative formation triggers are also explored, such as 
 (other causes of) shock compression, or cloud-cloud colissions \citep[e.g.][]{
@@
 
-Yet another hypothesis is that star cluster formation is triggered by (major) 
+Yet another hypothesis is that star cluster formation is triggered by major 
 gas-rich (spiral) galaxy mergers \citep{1987nngp.proc...18S, 1992ApJ...384...50A},
@@
 interacting and merging galaxies, which has been observed and are found to show 
-remarkable similarities with globulars in the Milky Way \citep[e.g.][]{
+remarkable similarities with GCs in the Milky Way \citep[e.g.][]{
 1995AJ....109..960W, 1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}.
@@
 and the recent numerical simulation of an isolated dwarf-dwarf merger executed at 
-very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$) 
-produce star clusters that could be globular progenitors \citep{
+very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$~pc) 
+produces star clusters that could be globular progenitors \citep{
 2019arXiv190509840L}.
@@
 1985ApJ...298...18F} and \citet{1992ApJ...384...50A} are intertwined because
-accretion and mergers continuously occurs trough out hierarchical build-up of
+accretion and mergers continuously occurs during the hierarchical build-up of
 galaxies. Various (other) hierarchical formation channels thus combine different
@@
 2000ApJ...533..869C, 2002ApJ...567..853C, 2002MNRAS.333..383B, 2003egcs.conf..224G}. 
-We refer to \citet{2001astro.ph..8034G} for a scoreboard of the aforementioned 
-paradigms compared to observations of the Milky Way globular cluster system.
+We refer to \citet{2001astro.ph..8034G} for a scoreboard of GC formation models 
+compared to observations of the Milky Way globular cluster system.
 
-An idea that has recently been studied in detail is the hypothesis that the physical 
-processes responsible for the formation of young massive clusters \citep[YMCs, 
-see][for a review]{2010ARA&A..48..431P}, as observable in detail in the local 
-Universe in great
-, also governs GC formation at high redshifts. In this framework, differences
-between both classes of objects are caused by nearly a Hubble time of (dynamical)
-evolution \citep[e.g.][]{1987degc.book.....S}. This picture is based on observed 
-similarities between YMCs and GCs \citep[e.g.][]{1992AJ....103..691H,1999AJ....118.1551W}
-and strengthened by observations of gravitationally lensed objects at high redshifts
-($z = 2-6)$. These sources have properties reminiscent of (local) YMCs and may be
-GC progenitors at times of formation \citep{2017MNRAS.467.4304V,2017ApJ...843L..21J}.
-The modelling work by \citet{2011MNRAS.414.1339K,2012MNRAS.421.1927K,2015MNRAS.454.1658K} 
-is now incorporated into cosmological zoom simulations and shows promising results
+An idea that has recently been studied extensively is the hypothesis that the formation
+mechanisms of young massive clusters \citep[YMCs, see][for a review]{2010ARA&A..48..431P} 
+and GCs are the same. The proximity of YMCs in the local Universe allows to study these 
+processes with a level of detail that cannot be achieved for GCs at high redshifts. In 
+this framework, differences between both classes of objects are caused by nearly a 
+Hubble time of (dynamical) evolution \citep[e.g.][]{1987degc.book.....S}. This picture 
+is based on observed similarities between YMCs and GCs
+\citep[e.g.][]{1992AJ....103..691H,1999AJ....118.1551W} and strengthened by observations
+of gravitationally lensed objects at high redshifts ($z = 2-6)$. These sources have 
+properties reminiscent of (local) YMCs and may be GC progenitors at times of formation 
+\citep{2017MNRAS.467.4304V,2017ApJ...843L..21J}. The modelling work by 
+\citet{2011MNRAS.414.1339K,2012MNRAS.421.1927K,2015MNRAS.454.1658K} is now 
+incorporated into cosmological zoom simulations and shows promising results
 \citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}.
 
-Simulation resolutions have reached the mass range populated by GCs, and the
-gravitational force softening can be as low several parsec. A number of groups 
-can thus incorporate formation of (globular) star clusters into their 
-high-resolution hydrodynamical simulations. \citet{2016ApJ...831..204R} 
-run parsec scale simulations of the high-redshift universe 
+The (mass) resolution of cosmological zoom simulations has reached the mass range 
+populated by GCs, and the gravitational force softening can be as low several 
+parsec. A number of groups can thus incorporate formation of (globular) star 
+clusters into their high-resolution hydrodynamical simulations. \citet{2016ApJ...831..204R} 
+ran parsec scale simulations of the high-redshift universe 
 prior to reionization (the simulations stop at $z=9$), \citet{2017ApJ...834...69L} 
@@
 In this work we use state of the art simulations that produce realistic spiral 
-galaxies at redshift zero for which several global properties are consistent with 
-the observations. The simulations yield realistic Milky Way analogues, and real
-galaxies host globular cluster systems. The question thus naturally arises whether 
-the star formation histories of the simulations (also) give rise to a GC system 
+galaxies (Milky Way analogues) at redshift zero for which several global properties 
+are consistent with the observations. The question thus naturally arises whether 
+the star formation histories of the simulations give rise to a GC system 
 similar to the Milky Way and/or Andromeda globular cluster systems. In particular, 
@@
 corrections. Reionization is completed at redshift six by a time-varying
-spatially uniform UV background \citep{2009ApJ...703.1416F, 2013MNRAS.436.3031V}
+spatially uniform UV background \citep{2009ApJ...703.1416F, 2013MNRAS.436.3031V}.
 The interstellar medium is described by an equation of state for a two-phase medium

### 2019-08-19 AurigaGCS.tex
Edited Sec. 3 (observations) based on feedback WHT, RG, FM for #1.

@@
 catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}}
-of the Milky Way globular cluster system that contains properties of
-157 GCs. The authors initially estimated the size of the MW GCS to be 180~$\pm$~10,
+of the Milky Way globular cluster system that contains properties of 157 GCs. 
+The authors initially estimated the number of GCs in the MW GCS to be 180~$\pm$~10,
 thus, their catalogue to be ${\sim}$85\% complete. However, an additional 59 GCs
@@
 + Y^2 + Z^2}$, assuming the solar radius $R_\odot=8$~kpc.}, and absolute
-magnitude in the V-band $M_V$. We use the latter to calculate mass-estimates by
+magnitude in the V~band $M_V$. We use the latter to calculate mass-estimates by
 assuming $M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$,
@@
 \label{sec:andromeda}
-The fifth revision of the revised bologna catalogue (RBC~5, last updated
+The fifth revision of the revised Bologna catalogue (RBC~5, last updated
 August, 2012) is the latest edition of three decades of systematically
@@
 \url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}}
-of the C11 dataset, further revised by CR16. It seems that CR16 is the most
+of the C11 dataset, further revised by CR16. We use CR16 because it is the most
 recent aggregated dataset of M31's GCS that contains properties of interest
-for our study as it contains GCs in the inner region and in the outer halo. The
+for our study and it includes GCs in the inner region and in the outer halo. The
 relevant fields in the CR16 dataset that we use are the age, metallicity, and the
@@
 which is somewhat surprising given that M31 is generally considered to be earlier
-type than the MW meaning that an older stellar population would naively be expected.
+type than the MW meaning that an older stellar population would be naively expected.
 However, we do caution that both data sets are incomplete and the age 
@@
 $R_{\odot}=8.0$~kpc), but the galactocentric radius of GCs in M31 is not available
-in CR16. Therefore we follow \citet[][Sec.~4.1]{2019arXiv190111229W} to calculate
+in CR16. Therefore, we follow \citet[][Sec.~4.1]{2019arXiv190111229W} to calculate
 the projected radius $R_{\text{proj}}$ from the observed positions, adopting M31's
@@
 are available is indicated using dotted lines. The latter shows a narrower range
-of radii than the full data set: it appears that age-estimates are neither
-available for the innermost ($<1$~kpc) GCs, nor for those beyond roughly twenty
+of radii than the full data set: it appears that few age-estimates are available 
+for the innermost ($<1$~kpc) GCs, and none for those beyond roughly twenty
 kpc (the halo GCs). We compare both distributions of the full data set (solid 
@@
 distributions show a similar trend for $R_{\text{gal}} > 4$~kpc and host a 
-subpopulation of halo GCs. However, both radial distributions are not 
-statistically consistent due to substantial differences at intermediate radii.
+subpopulation of halo GCs. However, the two radial distributions are not statistically
+consistent with being drawn from the same underlying distribution due to substantial 
+differences at intermediate radii.
 
@@
 two-dimensional distributions are also not consistent. More generally, the GC
-systems of the Milky Way and that of Andromeda both differ significantly. We 
-compare these observations to the Auriga simulations later on in 
-Sec.~\ref{sec:results_FeHRgc}.
+system of the MW differs significantly from that of M31. We compare these 
+observations to the Auriga simulations later on in Sec.~\ref{sec:results_FeHRgc}.
 
@@
 resolution level (4) and halo number (10, indicating which set of initial
-conditions was used the run).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
+conditions was used).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
 distributions of three individual simulation runs that we consider representative

### 2019-08-19 AurigaGCS.tex
Edited Sec. 2 (Auriga) based on feedback WHT, RG, FM for #1.

@@
 \renewcommand{\deg}{\ensuremath{^{\circ}}}
+\defcitealias{2017MNRAS.467..179G}{G17}
 
@@
 similar to the Milky Way and/or Andromeda globular cluster systems. In particular, 
-we use the Auriga suite of cosmological zoom simulations 
-(\citealt{2017MNRAS.467..179G}, and described in Sec.~\ref{sec:auriga}) to
-investigate whether the star formation model implemented produces metallicity, 
+we use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, 
+further described in Sec.~\ref{sec:auriga}. We investigate whether the star 
+formation model implemented produces metallicity, 
 radial, and metallicity-radial distributions that are consistent with the MW 
@@
 \label{sec:auriga}
-We use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, a
-suite of high-resolution cosmological zoom simulations of Milky Way-mass
-selected initial conditions. The simulations are performed with the \textsc{arepo} 
-\citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} code that solves the 
-magnetohydrodynamical equations on a moving mesh. The galaxy formation model 
-produces realistic spiral galaxies at redshift $z=0$.
+We use the Auriga simulations \citepalias{2017MNRAS.467..179G}, a suite of 
+high-resolution cosmological zoom simulations. The Milky Way-mass
+selected initial conditions were selected from the \mbox{\textsc{eagle}} DM only 
+box, see \citetalias{2017MNRAS.467..179G} for details. The simulations are performed with the \textsc{arepo} 
+code \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} that solves the 
+magnetohydrodynamical equations on a moving mesh.
 
-The interstellar medium is modelled using a sub-grid approach which implements
-the physical processes most relevant to galaxy formation and evolution.
+The galaxy formation model includes primordial and metal-line cooling with 
+self-shielding corrections. Reionization is completed at redshift six by a
+time-varying spatially uniform UV background \citep{2009ApJ...703.1416F, 
+2013MNRAS.436.3031V}. The interstellar medium (ISM) is described by an equation of 
+state for a two-phase medium in pressure equilibrium \citep{2003MNRAS.339..289S}: 
+cold clouds embedded in a hot ambient medium, whose mass and energy densities
+are described by processes important for star formation, such as the condensation 
+of cold clouds and the photoevaporation of clouds. Stars form stocastically in 
+thermally unstable gas with a density threshold of $n = 0.13 \, \text{cm}^{-3}$,
+and consecutive stellar evolution is accounted for. The channel for energetic
+stellar feedback is from non-local SNII, which is modelled with wind particles
+(\citealt{2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}). Galactic 
+winds enrich the ISM
+with metals from SNIa, SNII, and AGB stars \citep{2013MNRAS.436.3031V}. Supermassive
+black holes grow via Bondi–Hoyle–Lyttleton accretion \citep{1944MNRAS.104..273B,
+1952MNRAS.112..195B}, and feedback from the active galactic nuclei has a low-accretion
+and high-accretion mode (radio and quasar) (\citealt{2005MNRAS.361..776S, 
+2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}). Finally, the simulations 
+follow the evolution of a magnetic field of $10^{-14}$ (comoving)~G seeded at 
+$z = 127$ \citep{2013MNRAS.432..176P, 2014ApJ...783L..20P}.
+
 This model was tailored to the \textsc{arepo} code and calibrated to reproduce
@@
 density, the stellar mass to halo mass relation, and galaxy luminosity functions.
+The galaxy formation model produces realistic spiral galaxies at redshift $z=0$.
+Moreover, Auriga reproduces the HI disc properties \citep{2017MNRAS.466.3859M},
+the chemical thin/thick disc \citep{2018MNRAS.474.3629G}, the diversity in 
+accreted stellar halo properties found in observations \citep{2019MNRAS.485.2589M},
+and the \textit{Gaia} Sausage \citep{2019MNRAS.484.4471F}. These last two 
+bolster the point that the simulations are similar (and detailed) enough to the 
+MW to reproduce major, distinct features of the Galaxy, and so looking for the 
+GC population properties and comparing them to the MW/M31 is all the more relevant.
 
-The sub-grid includes primordial and metal-line cooling with self-shielding
-corrections. Reionization is completed at redshift six by a time-varying
-spatially uniform UV background \citep{2009ApJ...703.1416F, 2013MNRAS.436.3031V}.
-The interstellar medium is described by an equation of state for a two-phase medium
-in pressure equilibrium \citep{2003MNRAS.339..289S} with stochastic star formation
-in thermally unstable gas with a density threshold of $n = 0.13 \text{cm}^{-3}$,
-and consecutive stellar evolution is accounted for. Stars provide feedback by
-stellar winds \citep{2014MNRAS.437.1750M, 2017MNRAS.467..179G}, and further
-enrich the ISM with metals from SNIa, SNII, and AGB stars \citep{2013MNRAS.436.3031V}.
-The formation of black holes is modelled which results in feedback from active
-galactic nuclei \citep{2005MNRAS.361..776S, 2014MNRAS.437.1750M, 2017MNRAS.467..179G}.
-Finally, the simulations follow the evolution of a magnetic field of $10^{-14}$
-(comoving)~G seeded at $z = 127$ \citep{2013MNRAS.432..176P, 2014ApJ...783L..20P}.
-See G17 for further details of the numerical setup as well as the galaxy formation
-model.
-
-The Auriga suite has a fiducial resolution level L4, accompanied by the lower
-(higher) level L5 (L3) that is available for selected initial condition runs.
-The baryonic mass resolution in order of increasing level is $m_b$~=~[$4 \times 10^5$,
-$5 \times 10^4$, $6 \times 10^3$]~M\Sun \, with gravitational softening of
-collissionless particles $\epsilon$~=~[$738, 369, 184$]~pc. The mass resolution
-of the Auriga simulations is thus close to the characteristic peak mass of the
-lognormal GC mass distribution of $10^{5}$~M\Sun \citep{1991ARA&A..29..543H},
-although the gravitational softening is two orders of magnitudes larger than
-typical GC radii. High-density gaseous regions are thus not expected to produce
-surviving stellar clumps with masses and radii consistent with GCs because
-such objects would numerically disperse, even in the highest-resolution runs.
-On the other hand, we can investigate (statistical) properties of age-selected
-GC candidates because each star particle represents a single stellar population
-with a total mass that could be consistent with one globular cluster. This means
-that their formation sites and that of a real-world GC may be consistent.
+The Auriga suite has a fiducial baryonic mass resolution $m_b$~=~$5 \times 10^4$~M\Sun,
+with gravitational softening of collissionless particles $\epsilon$~=~369~pc.
+Simulations at this resolution are referred to as level 4 (L4). Selected
+initial condition runs are acompanied by the lower (higher) resolution level L5 (L3).
+The resolution for these levels is $m_b$~=~$4 \times 10^5$~M\Sun \, with 
+$\epsilon$~=~738~pc, and $m_b$~=~$6 \times 10^3$~M\Sun \, with $\epsilon$~=~184~pc,
+respectively. The mass resolution of the Auriga simulations is thus close to the 
+characteristic peak mass of the lognormal GC mass distribution of $10^{5}$~M\Sun 
+\citep{1991ARA&A..29..543H}, although the gravitational softening is two orders 
+of magnitudes larger than typical GC radii of several parsec. High-density gaseous 
+regions are thus not expected to produce surviving stellar clumps with masses and 
+radii consistent with GCs because such objects would numerically disperse, even 
+in the highest-resolution runs. On the other hand, we can investigate (statistical) 
+properties of age-selected GC candidates because each star particle represents a
+single stellar population with a total mass that could be consistent with one 
+globular cluster. This means that their formation sites and that of a real-world 
+GC may be consistent.
 
@@
 \section{Discussion}
-% ``The Auriga Stellar Haloes: Connecting stellar population properties with
-% accretion and merging history'' \citet{2018arXiv180407798M}
-
 \label{sec:discussion}

### 2019-08-19 AurigaGCS.tex
Edited Sec. 4 (results) based on feedback WHT, RG, FM for #1. Textual remarks only, not yet feedback onto the content itself.

@@
 the MW and M31. The same holds true for the distribution of $R_{\text{gal}}$.
-Overall, the Auriga simulations produce old star particles with higher metallicities 
+Overall, the Auriga simulations produce GC candidates with higher metallicities 
 than the MW and M31 GCS and at larger radii. This implies that the bound cluster
@@
 We still use data from the Harris catalogue, but caution that it may (only) be
-53-72\% complete. Specifically, the relevant data fields that we use from H96e10
+50-70\% complete. Specifically, the relevant data fields that we use from H96e10
 are the metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in
@@
 + Y^2 + Z^2}$, assuming the solar radius $R_\odot=8$~kpc.}, and absolute
-magnitude in the V~band $M_V$. We use the latter to calculate mass-estimates by
-assuming $M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$,
-the mean for MW clusters \citep{2005ApJS..161..304M}. We supplement the catalogue
-with age-estimates from isochrone fits to stars near the main-sequence turnoff 
-in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.
+magnitude in the V~band, $M_V$. We use the V~band magnitude to calculate 
+mass-estimates by assuming $M_{V,\odot}=4.83$ and a mass to light ratio 
+$M/L_V = 1.7$~M/L$_{\odot}$, the mean for MW clusters \citep{2005ApJS..161..304M}. 
+We supplement the catalogue with age-estimates from isochrone fits to stars near 
+the main-sequence turnoff in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.
 
@@
 
-Troughout our analysis we compare the distributions of three subsets of star
-particles: \emph{old stars} (age $>10$~Gyr, or GC candidates), \emph{old in~situ}
-stars (defined as those bound to the most-massive halo/subhalo in the first
-snapshot that the particle was recorded), and \emph{old accreted} star particles
-(those that have formed {\it ex~situ} and are bound to the most-massive halo/subhalo
-at $z=0$). For comparison we also include the results for \emph{all stars} (when
-no additional selection criterion is applied to the star particles). We consider
-the metallicity distribution in Sec.~\ref{sec:results_FeH}, the distribution of
-galactocentric radii in Sec.~\ref{sec:results_Rgc}, and the combination of both
+Throughout our analysis we compare distributions of age-selected GC 
+candidates (age $>10$~Gyr) with those of all star particles (i.e.
+when no additional selection criterion is applied). We further split the GC
+candidates into an {\it in~situ} subset (defined as GC candidates that are 
+bound to the most-massive halo/subhalo in the first snapshot that the particle 
+was recorded), and an accreted subpopulation (those that have formed {\it ex~situ} and 
+are bound to the most-massive halo/subhalo at $z=0$). A GC candidate either formed
+{\it in~situ} or it was accreted. We consider the metallicity distribution in 
+Sec.~\ref{sec:results_FeH}, the distribution of galactocentric radii in 
+Sec.~\ref{sec:results_Rgc}, and the combination of both 
 in Sec.~\ref{sec:results_FeHRgc}.
@@
 \label{sec:results_FeH}
-We investigate whether the star formation model implemented in Auriga produces
-metallicity distributions consistent with the MW and M31 GC systems, and whether
+We investigate whether the model implemented in Auriga produces metallicity 
+distributions consistent with the MW and M31 GC systems, and whether
 the simulations generate sufficient total mass at metallicities typical for the
@@
 for specific behaviour, and to highlight that different runs could give rise to 
-different distributions. We plot the age-selected GC candidates in green, those
-that are accreted in red, and the {\it in~situ} subpopulation in blue. The top 
-half of the left figure shows the MW (M31) GC system in purple (magenta), where 
-we overplot a double Gaussian for the MW GCS (the purple dashed lines) by 
+different distributions. We show the age-selected GC candidates as well as the 
+accreted and {\it in~situ} subsets. The top half of the left figure shows the MW 
+and M31 GC systems, where we overplot a double Gaussian for the MW GCS by 
 adopting literature values of the mean $\mu$ and standard deviation $\sigma$ of 
-the metal-rich and metal-poor subpopulations \citep[][p. 38]{Harris2001}.
+the metal-rich and metal-poor subpopulations \citep{Harris2001}.
 
-We find that the age cut, on average, lowers the mean metallicity from $0.0$ to
-$-0.6$. Furthermore, the old accreted stars generally have lower mean metallicities
-than the old {\it in~situ} stars with differences of roughly ${\sim}0.3$ for the majority 
-of the simulation runs. This behaviour can be seen in \mbox{Au4-21}, while a 
-slightly larger difference of ${\sim}0.5$ dex is seen for \mbox{Au4-10} (as plotted), 
-\mbox{Au4-16}, \mbox{Au4-17}, \mbox{Au4-18} and \mbox{Au4-22}. However, this trend 
-is reversed for \mbox{Au4-1} and \mbox{Au4-4} for which the old {\it in~situ} population 
-has a lower mean metallicity instead. We caution that \mbox{Au4-1} is undergoing
-a major merger at redshift zero and note that we find $\mu = -1.51 \, ({-0.74})$ 
-for the old {\it in~situ} (accreted) although the former consists of only $1019$ 
-particles ($1.3$\% of all GC candidates, and with a total mass of 5e7 M\Sun). 
-For \mbox{Au4-4}, ${10.8}$\% of the GC candidates is classified as {\it in~situ} (compared 
-to {\it in~situ} fractions of ${40-80}$\% for other haloes). After inspection of
-the same figure for every one of the thirty Auriga L4 haloes we find that the 
-simulations produce (sub)populations of GC candidates that are more metal-rich
-than the MW and M31 GC systems. Moreover, none of the simulations has a 
-population of GC candidates with a bimodal metallicity distribution (the green
-curves).
+We find that the age cut, on average, lowers the mean metallicity [Fe/H] from 
+$0.0$ to $-0.6$. Furthermore, accreted GC candidates generally have lower mean 
+metallicities than the {\it in~situ} subset with differences of roughly
+${\sim}0.3$~dex for the majority of the simulation runs. This behaviour can be 
+seen in \mbox{Au4-21}, while a slightly larger difference of ${\sim}0.5$~dex is 
+seen for \mbox{Au4-10} (as plotted), \mbox{Au4-16}, \mbox{Au4-17}, \mbox{Au4-18} 
+and \mbox{Au4-22}. However, this trend is reversed for \mbox{Au4-1} and \mbox{Au4-4} 
+for which the {\it in~situ} subset has a lower mean metallicity instead. 
+\mbox{Au4-1} is undergoing a major merger at redshift zero and we find 
+$\mu = -1.51 \, ({-0.74})$ for the {\it in~situ} (accreted) GC candidates, 
+although the former consists of only $1019$ particles ($1.3$\% of all GC 
+candidates, and with a total mass of $5 \times 10^{7}$~M\Sun). For \mbox{Au4-4}, 
+only ${10.8}$\% of the GC candidates is classified as {\it in~situ} (compared to 
+{\it in~situ} fractions of ${40-80}$\% for other haloes). We note that \mbox{Au4-4}
+has undergone a major merger around 2~Gyr lookback time, which is probably why
+the accreted population is more metal rich. After inspection of the same figure 
+for every one of the thirty Auriga L4 haloes we find that the simulations produce
+(sub)populations of GC candidates that are more metal-rich than the MW and M31 GC 
+systems. Moreover, none of the simulations has a (total) population of GC 
+candidates with a bimodal metallicity distribution.
 
@@
         Each cross (for a given colour) represents one simulation. The green (blue)
-        [red] crosses show the values calculated using the old (old {\it in~situ})
-        [old accreted] star particles. Green triangles indicate that all stars
+        [red] crosses show the values calculated using all (only {\it in~situ})
+        [only accreted] GC candidates. Green triangles indicate that all stars
         were used. The purple (magenta) cross denotes our calculation using all
@@
 We show the mean metallicity and standard deviation of all thirty Auriga L4 haloes
-in Figure~\ref{fig:FeH_mu_sigma} to show the behaviour for the full set of Auriga
+in Figure~\ref{fig:FeH_mu_sigma} to illustrate the behaviour for the full set of Auriga
 galaxies. The green crosses are to be compared to the purple (magenta) cross, 
@@
 Having said that, we do find it interesting that the mean metallicities of the 
-old {\it in~situ} populations appear roughly consistent with that of the metal-rich 
+{\it in~situ} GC candidates appear roughly consistent with that of the metal-rich 
 population of the MW although the simulations show larger dispersions. The latter 
@@
 which means the range is smaller and the resulting dispersion lower. With 
-regard to the M31 GCS, we are uncertain whether definitive consensus is reached
+regard to the M31 GCS, so far no definitive consensus has been reached
 in the literature concerning uni- bi- or trimodality in the [Fe/H] distribution, 
 but CR16 argues that the data, after removal of younger objects due to improved 
-age classification, hints at three populations separated at [Fe/H]~$>-0.4$ and 
-[Fe/H]~$ < 1.5$. None of the Auriga sub sets has a mean value that offers much 
+age classification, hints at three populations separated at [Fe/H]~$=-0.4$ and 
+[Fe/H]~$ = 1.5$. None of the Auriga sub sets has a mean value that offers much 
 hope that the simulated distribution is consistent with the lowest metallicity 
@@
         Mass-weighted metallicity distribution of star particles in the Auriga
-        simulations. We show the median value of all Auriga haloes for all
+        L4 simulations. We show the median value of all Auriga haloes for all
         stars (green dotted) and globular cluster candidates (i.e. stars with
@@
 a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
-median (coloured lines) for all thirty Auriga L4 haloes with the $1\sigma$ 
-interval around it (shaded regions, which shows the scatter between runs that 
-have different initial conditions, thus, have unique merger histories). We chose 
-to aggregate the data to indicate general trends that we find when the GC candidates 
-are split up according to birth location, rather than selecting typical examples 
+median for all thirty Auriga L4 haloes with the $1\sigma$ interval around it 
+(shaded regions, which shows the scatter between runs that have different initial 
+conditions, thus, have unique merger histories). We chose to aggregate the data 
+to indicate general trends that we find when the GC candidates are split up into
+the accreted and {\it in situ} subsets, rather than selecting typical examples 
 of individual (simulated) galaxies. Once again we notice that the peak metallicity 
-shifts down from $0$ to $-0.6$ for old stars (green solid) compared to all stars 
-(green dotted), and we learn that the mass at the peak lowers by roughly one dex. 
-The mass budget of the old stars is dominated by the old {\it in~situ} population (blue 
-solid) below [Fe/H]~=~$-1$, and by the old accreted stars (red solid) above this 
-value. We show the MW (M31) GCS in purple (magenta) and notice that the difference 
-between the MW and M31 distributions is substantially larger than the scatter
-between different Auriga galaxies, particularly around [Fe/H]~$=-1$. In addition, 
-Andromeda does host (a hand full) GCs with [Fe/H]~$< -2.5$ as well as GCs with 
-[Fe/H]~$ > 0$ while the Milky Way does not.
+shifts down from [Fe/H]~=~$0$ to [Fe/H]~=~$-0.6$ for GC candidates compared to all stars, 
+and we find that the mass at the peak lowers by roughly one dex. The mass budget 
+of the GC candidates is dominated by the {\it in~situ} subpopulation above
+[Fe/H]~=~$-1$, and by the accreted subset below this value. We show the MW (M31) 
+GCS in purple (magenta) and notice that the difference between the MW and M31 
+distributions is substantially larger than the scatter between different Auriga 
+galaxies, particularly around [Fe/H]~$=-1$. In addition, Andromeda does host 
+(a handful of) GCs with [Fe/H]~$< -2.5$ as well as GCs with [Fe/H]~$ > 0$ while 
+the Milky Way does not.
 
@@
 that is consistent with the MW. For the GC candidates in M31 we find a constant 
-mass ratio up to $-0.9$, above which the simulations produce a higher mass ratio 
+mass ratio up to [Fe/H]=$-0.9$, above which the simulations produce a higher mass ratio 
 with increasing metallicity. If dynamical evolution is not expected to more 
@@
 GCs (which are to be compared to the green crosses), but solid (open) dot now
-shows our calculation of the mean value of the metal-rich (metal-poor) population 
-as no literature values were available. We split the radii up into the 
-metal-rich/metal-poor groups by taking a metallicity cut at [Fe/H]~=~-1 as is 
-done in the literature.
+shows our calculation of the mean value of the `red' metal-rich (`blue` metal-poor) 
+population. We split the radii up into the metal-rich/metal-poor groups by taking
+a metallicity cut at [Fe/H]~=~-1 as is done in the literature.
 
-We notice that the old {\it in~situ} populations are more centrally 
-distributed, whereas the old accreted subsets have a larger radial extent. This 
+We notice that the {\it in~situ} GC candidates are more centrally distributed, 
+whereas the accreted subsets have a larger radial extent. This 
 is not surprising because the classification of {\it in~situ} requires star particles 
@@
 to end up at small galactocentric radii. Accreted star particles, on the other 
-hand, have formed in another (sub)halo beyond the virial radius, thus, would 
+hand, have formed in another (sub)halo beyond the virial radius, thus, they would 
 first have to migrate inwards in order to populate the innermost radii. Moreover,
 we find that the simulations have a wider dispersion in $\log(R_{\text{gal}})$ than
-the MW GCS, while the dispersion of M31 seems to lie witin the range of dispersions
+the MW GCS, while the dispersion of M31 seems to lie within the range of dispersions
 found in the Auriga galaxies. Furthermore, the mean of the MW GCS lies roughly 
@@
 of the M31 GCS is generally believed to hint at a more accretion-dominated origin 
-of the GCS, and may reflect a richer accretion history of the galaxy in comparison 
+of the GCS, and may reflect a richer accretion history of M31 in comparison 
 to the Milky Way.
@@
         Mass-weighted radial distribution of star particles in the Auriga
-        simulations. We show the median value of all Auriga haloes for all
+        L4 simulations. We show the median value of all Auriga haloes for all
         stars (green dotted) and globular cluster candidates (i.e. stars with
@@
         Mass-weighted [Fe/H]-$R_{\text{gal}}$ distribution of all thirty Auriga
-        L4 haloes. Here we consider only the GC candidates (age $>$~10~Gyr) stars
-        in and color-code by the \textbf{median} (values also shown in each bin).
-        The numbers in parenthesis show how many star particles fall within the
-        bin. Note that the range of the colourmap again differs (for improved
-        contrast within the plot).
+        L4 haloes. Here we consider only the GC candidates and color-code by the 
+        median mass (values also shown in each bin). The numbers in parenthesis 
+        show how many star particles fall within the bin. Note that the range of 
+        the colourmap differs from both panels in Figure~\ref{fig:observations_FeHRgc} 
+        (for improved contrast within the plot).
         \label{fig:Au-FeHRgc}
@@
 fewer high-metallicity GCs at large radii, similar to the MW and M31 GC systems. 
-However, the three bins in the upper right corner are populated in the Auriga
-simulations, in contrast to the observations. The top panel of 
-Figure~\ref{fig:Au-FeHRgc-ratio} shows that the mass ratio for Auriga GCs within
-the Solar radius decreases with decreasing metallicity. This means that either
-the formation efficiency should increase with decreasing metallicity, or that 
-the lowest-metallicity GCs in the Auriga simulations are less strongly affected
+The top panel of Figure~\ref{fig:Au-FeHRgc-ratio} shows that the mass ratio for 
+Auriga GCs within the Solar radius decreases with decreasing metallicity. This
+means that either the formation efficiency should increase with decreasing metallicity,
+or that the lowest-metallicity GCs in the Auriga simulations are less strongly affected
 by disruptive processes, if the star formation histories in the Auriga simulations
@@
         to mass in the MW (M31) GCS, i.e. the logarithm of the mass ratio, minus
-        the median value. This way red indicates regions of with a higher mass
-        excess than the median, conversely blue highlights bins with a lower than
-        median mass ratio. The number in each bin shows the color-coded value 
-        that is plotted, and the (median) star particle count is given in 
-        parenthesis. Note that the three bins in the upper right corner are white
-        because the observations have zero mass there.
+        the median value of these 25 bins. The values are 2.68 and 1.69 dex for 
+        the MW and M31, respectively. Red (blue) indicates a higher (lower) overall 
+        mass excess. The number in each bin shows the color-coded value that is 
+        plotted, and the (median) star particle count is given in parenthesis. 
+        Note that the three bins in the upper right corner are white because the 
+        observations have zero mass there.
         \label{fig:Au-FeHRgc-ratio}

### 2019-08-19 AurigaGCS.tex
Semi-full rewrite of Sec. 4.3 to reflect updates to Figure 9 (which now shows a diverging colour map) for #1

@@
 
-We investigate whether the Auriga simulations still produce sufficient mass when
-the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{gal}$. First
-we sum the total simulated mass in each bin (for an individual Auriga simulation),
-then we calculate the median over all thirty Auriga L4 haloes (in each bin, see
-Figure~\ref{fig:Au-FeHRgc} which can be compared to
-Figure~\ref{fig:observations_FeHRgc}). Finally, we divide these value by the total
-mass in the MW (M31) GCS to obtain the median mass ratio produced by the star
-formation model implemented in the Auriga simulations. See the top (bottom) panel
-of Figure~\ref{fig:Au-FeHRgc-ratio} for mass ratio with respect to the MW (M31) GCS.
-
 \begin{figure}
@@
 
-We notice in Figure~\ref{fig:Au-FeHRgc} that the Auriga simulations, on average,
-produce fewer GCs in the lowest metallicity bins ($-2.5$ to $-1.5$) than at higher 
-metallicities in the three innermost radial bins. In addition, Auriga produces 
-fewer high-metallicity GCs at large radii, similar to the MW and M31 GC systems. 
-The top panel of Figure~\ref{fig:Au-FeHRgc-ratio} shows that the mass ratio for 
+We investigate whether the Auriga simulations still produce sufficient mass when
+the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{gal}$. First
+we sum the total mass of GC candidates in each bin (for an individual Auriga 
+simulation), then we calculate the median total mass in each bin over all 
+thirty Auriga L4 haloes. The result is shown in Figure~\ref{fig:Au-FeHRgc} (which 
+can be compared to the observed total GC mass shown in 
+Figure~\ref{fig:observations_FeHRgc}). We notice that the Auriga simulations, 
+on average, produce fewer GCs in the lowest metallicity bins ($-2.5$ to $-1.5$) 
+than at higher metallicities in the three innermost radial bins. In addition, 
+Auriga produces fewer high-metallicity GCs at large radii, similar to the MW 
+and M31 GC systems.
+
+To ease the comparison between the simulations and observations we take the ratio
+of the total mass of GC candidates in Auriga to the total GC mass in the MW 
+(and M31). We use a diverging colour map centered around the overall median of the 
+mass ratio (i.e. we subtract the median of these twenty-five bins from the value 
+in each bin). We show this in the top (bottom) panel of Figure~\ref{fig:Au-FeHRgc-ratio}.
+Note that the data in three top right bins is masked because the mass ratio cannot 
+be calculated due to zero mass in the observations (therefore the bins are white).
+If the product of the bound cluster formation efficiency and consecutive GC 
+disruption over a Hubble time would be constant, then the value in each bin would
+have been zero. The red and blue bins indicate deviations from such as scenario and
+indicate a higher and lower than average mass excess. In particular, the median 
+value used to shift the mass ratio is $2.68$ and $1.69$ dex for the MW and M31, 
+respectively. This means that the overall `mass budget' that the simulations `can 
+afford to lose' is roughly a factor $480$ and $50$ for the MW and M31, respectively. 
+The lowest mass surplus for both galaxies is the the bin where $-2.5 <$ [Fe/H] 
+$< -1.5$ and $3 < R_{\text{gal}}/\text{kpc} < 8$, for which the simulations produce 
+a factor $10^{2.68}/10^{1.33} \approx 22$ and $10^{1.69}/10^{0.75} \approx 9$ 
+more mass in GC candidates than what is observed in the MW and M31 respectively.
+The highest factor for the MW is $2.1 \times 10^{5}$, and $1.1 \times 10^{3}$
+for M31.
+
+The top panel of Figure~\ref{fig:Au-FeHRgc-ratio} shows that mass excess for
 Auriga GCs within the Solar radius decreases with decreasing metallicity. This
@@
 at the same radius for almost all galaxies \citep{1991ARA&A..29..543H}. Our 
-selection function (age cut) does lower the mean metallicity by $0.5$ dex, but
-we still find that the metallicity distributions of GC candidates in the Auriga
-simulations are more metal-rich than the MW (M31) GCS. Although the (old) star
-particles represent single stellar populations with a mass (resolution) consistent 
-with that of GCs, they are in fact statistical tracers of the stellar population 
-of the galaxy as a whole. Therefore only a (small) fraction of the star particles 
-may represent plausible formation sites of GCs, whereas the majority represents 
-(halo) field stars - the disk component effectively falls outside our selection 
-of star particles due to the age cut. It is implausible that all halo stars 
-come from disrupted GCs because GC systems that survive down to redshift zero 
-are generally few orders of magnitude less massive than galactic stellar haloes.
+selection function (age cut) does lower the mean metallicity of GC candidates by 
+$0.5$ dex with respect to all star particles, but we still find that the GC 
+candidates in the Auriga simulations are more metal-rich than the MW and M31 GCSs. 
+Although the (old) star particles represent single stellar populations with a mass 
+(resolution) consistent with that of GCs, they are in fact statistical tracers 
+of the stellar population of the galaxy as a whole. Therefore only a (small) 
+fraction of the star particles may represent plausible formation sites of GCs, 
+whereas the majority represents (halo) field stars - the disk component effectively 
+falls outside our selection of star particles due to the age cut. It is implausible 
+that all halo stars come from disrupted GCs because the total mass in GC systems 
+at redshift zero is generally a few orders of magnitude lower than the total 
+mass of stellar haloes of galaxies. If stellar haloes solely consist of disrupted
+GCs, then the GC disruption rate would have to be considerably higher than expected
+from theoretical models. Overall, our set of GC candidates most likely contains
+an overabundance of regular stars. It could be that the resulting metallicity
+distribution is then biased towards higher values than what is observed for real 
+GCs. An alternative explanation could overmixing of metals at early times.
 
@@
 1999AJ....118.1526G,2001AJ....121.2974L,2006ApJ...639...95P}. Indeed, 
-\citet[][p. 234]{1998gcs..book.....A} and \citet[][p. 38]{Harris2001} find that
-the MW GCS has a bimodal [Fe/H] distribution: the latter fit a double Gaussian 
-which peaks at [Fe/H] = $-1.59$ (metal-poor) and $-0.51$ (metal-rich) and 
-dispersions of $0.34$ and $0.23$. Observations of GCs in M31, however, may be
-best split into three distinct metallicity groups, one found at small radii with 
-[Fe/H] $>-0.4$, one intermediate [Fe/H] group, and a dominant (metal-poor) group 
-with [Fe/H] $< -1.5$ \citep{2016ApJ...824...42C}. The numerical simulation of
-\citet{2017MNRAS.465.3622R} does yield a bimodal metallicity distribution where
-the metal-poor population is dominated by accreted star particles and the metal-rich
-population by {\it in~situ} stars.
+\citet{1998gcs..book.....A} and \citet{Harris2001} find that the MW GCS has a 
+bimodal [Fe/H] distribution. Observations of GCs in M31, however, may be best 
+split into three distinct metallicity groups \citep{2016ApJ...824...42C}. The 
+numerical simulation of \citet{2017MNRAS.465.3622R} does yield a bimodal 
+metallicity distribution where the metal-poor population is dominated by accreted 
+star particles and the metal-rich population by {\it in~situ} stars.
 
@@
 accreted) does coincide with the separation between the metal-rich and metal-poor
-populations of GC systems at [Fe/H]~=~$-1$. Moreover, we do find that the mean
-metallicity shifts when we split the GC candidates up according to birth location
-(accreted or {\it in~situ}). In particular, the mean values of the old 
-{\it in~situ} GC candidates are roughly consistent with the metal-rich MW GCs.
+populations of GC systems at [Fe/H]~=~$-1$, as for the MW. Moreover, we do find 
+that the mean metallicity shifts when we split the GC candidates up according 
+to birth location (accreted or {\it in~situ}). In particular, the mean values of 
+the {\it in~situ} GC candidates are roughly consistent with the metal-rich MW GCs.
 However, we also notice that a substantial number of simulations has similar 
@@
 accreted populations. The Auriga simulations therefore do not support the view 
-that the metal-poor GCs could have formed in satellites that have later been 
-accreted whereas the metal-rich GC subpopulation has formed {\it in~situ}. With 
-this statement, however, we do caution that \citet{2019MNRAS.486.3134K} suggests 
+that the metal-poor GCs could have only formed in satellites that have later been 
+accreted whereas the metal-rich GC subpopulation has only formed {\it in~situ}. 
+With this statement, however, we do caution that \citet{2019MNRAS.486.3134K} suggests 
 to reserve the `{\it ex~situ}' classification for accretion after $z=2$, when
 the central galaxy has formed and accretion unambigously contributes to the
-radially extended halo GC population. In fact, our classification appears flawed
-in Au4-1.
+radially extended halo GC population. In fact, our classification might not hold
+for Au4-1.
 
 Finally, we note that \citet{2006ARA&A..44..193B} compares the number of metal-poor 
-GCs to the stellar halo mass and find\footnote{the quantity $T$ is the number of 
-GCs per $10^9$ M\Sun \, of galaxy stellar mass} $T^n_{\text{blue}} \sim 100$, 
+GCs to the stellar halo mass and find\footnote{The quantity $T$ is the number of 
+GCs per $10^9$ M\Sun \, of galaxy stellar mass.} $T^n_{\text{blue}} \sim 100$, 
 while the number of metal-rich GCs compared to the bulge mass yields 
@@
 of metal-poor GCs is twenty times higher than the metal-rich GCs with respect to 
-field stars. We find that gradual linear increase in formation efficiency of GCs
+field stars. We find that a gradual increase in formation efficiency of GCs
 with respect to field stars would be required with decreasing metallicity for
 the GC candidates in the Auriga simulations to yield sufficient total mass to
-be consistent with the Milky Way GCS.
+be consistent with the MW or M31 GCS.
 

### 2019-08-20 AurigaGCS.tex
Consistently use abbreviations GCS, MW and M31 for #1.

@@
 \begin{abstract}
-We investigate whether the galaxy formation model used for the Auriga simulations
+We investigate whether the galaxy and star formation model used for the Auriga simulations
 can produce a realistic globular cluster (GC) population. We compare statistics 
@@
 \section{Introduction}
-Globular clusters (GC)s are old, bright, and ubiquitous. Various properties of
-GC systems show correlations with their host galaxies. GC systems are believed to
+Globular star clusters (GC)s are old, bright, and ubiquitous. Various properties of
+GC systems (GCS) show correlations with their host galaxies. GCSs are believed to
 retain information about the galactic (gas) conditions at their times of formation.
@@
 interacting and merging galaxies, which has been observed and are found to show 
-remarkable similarities with GCs in the Milky Way \citep[e.g.][]{
+remarkable similarities with GCs in the MW \citep[e.g.][]{
 1995AJ....109..960W, 1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}.
@@
 We refer to \citet{2001astro.ph..8034G} for a scoreboard of GC formation models 
-compared to observations of the Milky Way globular cluster system.
+compared to observations of the MW GCSs.
 
@@
 In this work we use state of the art simulations that produce realistic spiral 
-galaxies (Milky Way analogues) at redshift zero for which several global properties 
+galaxies (MW analogues) at redshift zero for which several global properties 
 are consistent with the observations. The question thus naturally arises whether 
-the star formation histories of the simulations give rise to a GC system 
-similar to the Milky Way and/or Andromeda globular cluster systems. In particular, 
+the star formation histories of the simulations give rise to a GCS similar to 
+the MW and/or M31 GCSs. In particular, 
 we use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, 
@@
 radial, and metallicity-radial distributions that are consistent with the MW 
-and/or M31 GC systems, and whether the model produces enough stellar mass with
+and/or M31 GCSs, and whether the model produces enough stellar mass with
 the right properties to allow for formation efficiencies lower than unity and
@@
 of the Auriga simulations in section~\ref{sec:auriga}, followed by a summary of 
-the observations of the Milky Way (MW) and Andromeda globular cluster system (GCS)
+the observations of the MW and M31 GCSs
 in section~\ref{sec:observations} that we use to compare our simulations to in
@@
 We use the Auriga simulations \citepalias{2017MNRAS.467..179G}, a suite of 
-high-resolution cosmological zoom simulations. The Milky Way-mass
+high-resolution cosmological zoom simulations of MW analogues. The MW-mass
 selected initial conditions were selected from the \mbox{\textsc{eagle}} DM only 
-box, see \citetalias{2017MNRAS.467..179G} for details. The simulations are performed with the \textsc{arepo} 
-code \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} that solves the 
-magnetohydrodynamical equations on a moving mesh.
+box, see \citetalias{2017MNRAS.467..179G} for details. The simulations are 
+performed with the \textsc{arepo} code \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} 
+that solves the magnetohydrodynamical equations on a moving mesh.
 
@@
 We describe the observations of the MW GCS in Sec.~\ref{sec:milkyway},
-and of the Andromeda (M31) GCS in Sec.~\ref{sec:andromeda}
+and of the M31 GCS in Sec.~\ref{sec:andromeda}
 
@@
 catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}}
-of the Milky Way globular cluster system that contains properties of 157 GCs. 
+of the MW GCS that contains properties of 157 GCs. 
 The authors initially estimated the number of GCs in the MW GCS to be 180~$\pm$~10,
@@
 % available data, presented in their CatClu catalog. Amongst 10978 star clusters
-% and alike objects in the Milky Way, the catalog contains 200 GCs and 94 GC
+% and alike objects in the MW, the catalog contains 200 GCs and 94 GC
 % candidates. The CatClu catalog contains reference papers, positions, distances,
@@
 August, 2012) is the latest edition of three decades of systematically
-collecting integrated properties of the globular cluster system of the
-Andromeda galaxy \citep[][and references therein]{2004A&A...416..917G}. One
+collecting integrated properties of the GCS of M31 \citep[][and references therein]{2004A&A...416..917G}. One
 contribution to RBC~5 is the work by \citet[][hereafter C11]{2011AJ....141...61C},
@@
 C11 and CR16 present a uniform set of spectroscopic observations calibrated
-on the Milky Way GCS of the inner $1.6^\circ~({\sim}21)$~kpc that
+on the MW GCS of the inner $1.6^\circ~({\sim}21)$~kpc that
 is believed to be 94\% complete. GCs in the outer stellar halo, up to
@@
 of $4.8$~Gyr. Based on these data, we find that the age distributions of the MW 
-and M31 GCS's are not statistically consistent. Moreover, the Milky Way appears 
-to host a globular cluster system that is somewhat older than the Andromeda galaxy,
-which is somewhat surprising given that M31 is generally considered to be earlier
+and M31 GCSs are not statistically consistent. Moreover, the MW appears 
+to host a GCS that is somewhat older than that of M31.
+This is somewhat surprising given that M31 is generally considered to be earlier
 type than the MW meaning that an older stellar population would be naively expected.
@@
 kpc (the halo GCs). We compare both distributions of the full data set (solid 
-lines) and find that the Milky Way has more GCs in the range $1-4$~kpc than M31
+lines) and find that the MW has more GCs in the range $1-4$~kpc than M31
 (when accounting for the larger number of total GCs in M31). Interestingly, both
@@
 ([Fe/H]$ > -1$) GCs in each radial bin in comparison to the MW GCSs than what
-would be expected when accounting for the fact that Andromeda hosts a larger GC 
-system than the MW. Finally, given that both marginalized (i.e. the metallicity 
+would be expected when accounting for the fact that M31 hosts a larger GCS
+than the MW. Finally, given that both marginalized (i.e. the metallicity 
 and radial) distributions are not statistically consistent, we find that the 
-two-dimensional distributions are also not consistent. More generally, the GC
-system of the MW differs significantly from that of M31. We compare these 
+two-dimensional distributions are also not consistent. More generally, the GCS
+of the MW differs significantly from that of M31. We compare these 
 observations to the Auriga simulations later on in Sec.~\ref{sec:results_FeHRgc}.
@@
 We investigate whether the model implemented in Auriga produces metallicity 
-distributions consistent with the MW and M31 GC systems, and whether
+distributions consistent with the MW and M31 GCSs, and whether
 the simulations generate sufficient total mass at metallicities typical for the
-MW and M31 GCS's. To visually inspect the former we show the normalized metallicity 
+MW and M31 GCSs. To visually inspect the former we show the normalized metallicity 
 distribution of three specific Auriga galaxies in Figure~\ref{fig:Au4-10and21_FeH}
@@
         \emph{Top}: Metallicity distribution of the MW and M31 GCS. The solid 
-        purple (magenta) line shows the GC system of the MW (M31), and we 
+        purple (magenta) line shows the GCSs of the MW (M31), and we 
         indicate the mean value with an arrow at the bottom of the x-axis. We
@@
 accreted and {\it in~situ} subsets. The top half of the left figure shows the MW 
-and M31 GC systems, where we overplot a double Gaussian for the MW GCS by 
+and M31 GCSs, where we overplot a double Gaussian for the MW GCS by 
 adopting literature values of the mean $\mu$ and standard deviation $\sigma$ of 
@@
 for every one of the thirty Auriga L4 haloes we find that the simulations produce
-(sub)populations of GC candidates that are more metal-rich than the MW and M31 GC 
-systems. Moreover, none of the simulations has a (total) population of GC 
+(sub)populations of GC candidates that are more metal-rich than the MW and M31 GCSs.
+Moreover, none of the simulations has a (total) population of GC 
 candidates with a bimodal metallicity distribution.
@@
 distributions is substantially larger than the scatter between different Auriga 
-galaxies, particularly around [Fe/H]~$=-1$. In addition, Andromeda does host 
+galaxies, particularly around [Fe/H]~$=-1$. In addition, M31 does host 
 (a handful of) GCs with [Fe/H]~$< -2.5$ as well as GCs with [Fe/H]~$ > 0$ while 
-the Milky Way does not.
+the MW does not.
 
@@
 of the GCS, and may reflect a richer accretion history of M31 in comparison 
-to the Milky Way.
+to the MW.
 
@@
 candidates changes from those formed {\it in~situ} to the accreted population around
-$10$~kpc. Again we show the mass ratio of the simulations compared to the Milky
-Way and Andromeda GCS. We find a decreasing mass ratio with increasing radius
+$10$~kpc. Again we show the mass ratio of the simulations compared to the MW 
+and M31 GCS. We find a decreasing mass ratio with increasing radius
 in the range $0.2$ to ${\sim}5$ kpc, followed by an increase attributed
-to the accreted subpopulation. For the Milky Way we notice that significantly
+to the accreted subpopulation. For the MW we notice that significantly
 fewer GCs are found beyond $40$~kpc than for M31, and that accreted GC candidates
@@
 Auriga produces fewer high-metallicity GCs at large radii, similar to the MW 
-and M31 GC systems.
+and M31 GCSs.
 
@@
 by disruptive processes, if the star formation histories in the Auriga simulations
-are to give rise to a GC system that can be similar to the GCS that is observed
-in the Milky Way. Moreover, either a lower formation efficiency is required at
+are to give rise to a GCS that can be similar to the GCS that is observed
+in the MW. Moreover, either a lower formation efficiency is required at
 large radii, or stronger disruption. Disruption of star clusters is expected to
@@
 region for GCs on orbits that pass through the disk, or with pericenters close 
-to the bar or bulge. Compared to Andromeda, the mass ratio (bottom panel of 
-Figure~\ref{fig:Au-FeHRgc-ratio}) shows a less clear trend than for the Milky Way,
+to the bar or bulge. Compared to M31, the mass ratio (bottom panel of 
+Figure~\ref{fig:Au-FeHRgc-ratio}) shows a less clear trend than for the MW,
 which suggests that both galaxies have diverse GC formation histories.
@@
 efficiencies would be required in addition to little disruption for the Auriga 
-simulations to yield a GC system consistent with that of the Andromeda galaxy.
+simulations to yield a GCS consistent with that of M31.
 
@@
 Although the (old) star particles represent single stellar populations with a mass 
-(resolution) consistent with that of GCs, they are in fact statistical tracers 
+consistent with that of GCs, they are in fact statistical tracers 
 of the stellar population of the galaxy as a whole. Therefore only a (small) 
@@
 falls outside our selection of star particles due to the age cut. It is implausible 
-that all halo stars come from disrupted GCs because the total mass in GC systems 
+that all halo stars come from disrupted GCs because the total mass in GCSs 
 at redshift zero is generally a few orders of magnitude lower than the total 
@@
 
-In general, the colour (metallicity) distribution of most GC systems is bimodal 
+In general, the colour (metallicity) distribution of most GCSs is bimodal 
 with typical separating value [Fe/H]$\sim -1$ \citep{1985ApJ...293..424Z,
@@
 accreted) does coincide with the separation between the metal-rich and metal-poor
-populations of GC systems at [Fe/H]~=~$-1$, as for the MW. Moreover, we do find 
+populations of GCSs at [Fe/H]~=~$-1$, as for the MW. Moreover, we do find 
 that the mean metallicity shifts when we split the GC candidates up according 
@@
 % at a vigorous rate until the present time, which implies it overproduces
-% the total GC mass in the Milky Way by a factor
+% the total GC mass in the MW by a factor
 % 5.5 relative to the mass formed in the fiducial model. Likewise, the continued
@@
 % of massive (M $>10^5$ M\Sun) clusters with [Fe/H]$ <-0.5$ should be observed in
-% Milky Way-mass galaxies at $z=0$. For these reasons, an environmentally independent
+% MW-mass galaxies at $z=0$. For these reasons, an environmentally independent
 % cluster formation description is not compatible with observations.''
@@
     \item The star formation model implemented in the Auriga simulations produces
-    metallicity distributions that are more metal-rich than the Milky Way and M31
-    globular cluster systems.
+    metallicity distributions that are more metal-rich than the MW and M31
+    GCSs.
 
@@
     metallicity for GC candidates in the Auriga simulations to be consistent
-    with the Milky Way GC system, given that we expect dynamical evolution to 
+    with the MW GCS, given that we expect dynamical evolution to 
     more strongly affect GC candidates at smaller radii. This trend of over-production
@@
 the NumPy \citep{2011CSE....13b..22V}, SciPy \citep{scipy}, and Astropy 
-\citep{2013A&A...558A..33A} packages. Plots were created with
-Matplotlib \citep{2007CSE.....9...90H}.
+\citep{2013A&A...558A..33A} packages. Plots were created with Matplotlib 
+\citep{2007CSE.....9...90H}, using the perceptually uniform colour maps
+from \citet{2015arXiv150903700K} for two-dimensional plots.
 

### 2019-08-20 AurigaGCS_20190820.tex
Updated version

--- 2019-08-20 AurigaGCS.tex
@@
 \begin{abstract}
-We investigate whether the galaxy and star formation model used for the Auriga simulations
-can produce a realistic globular cluster (GC) population. We compare statistics 
-of GC candidate star particles in the Auriga haloes with catalogues of the Milky 
-Way (MW) and Andromeda (M31) globular cluster populations. We find that the Auriga 
-simulations do produce sufficient stellar mass for GC candidates at radii and 
-metallicities that are typical for the MW GC system (GCS), although we observe a 
-varying mass-ratio for different galactocentric radius-metallicity 
-($R_{\text{gal}}$-[Fe/H]) bins of simulated GC candidates relative to the 
-observed mass in the MW and M31 GC systems.
-This implies different values for the combined product of the bound cluster 
-formation efficiency and the GC disruption rate. Furthermore we test whether any of the 
-Auriga galaxies has a metallicity and radial distribution that is consistent with 
-the MW or M31 GCS. For any one of the Auriga haloes we reject the null hypothesis
-that the observed and simulated metallicities of GCs (GC candidates) are drawn
-from the same distribution at $\geq98.32$~\% confidence level, for the GCS of 
-the MW and M31. The same holds true for the distribution of $R_{\text{gal}}$.
-Overall, the Auriga simulations produce GC candidates with higher metallicities 
-than the MW and M31 GCS and at larger radii. This implies that the bound cluster
-formation efficiency would have to decrease with increasing metallicity for the 
-Auriga GC candidates to be consistent with the MW GCS, if GC disruption is equally 
-efficient regardless of metallicity. In addition, the number of GCs relative to
-field stars would have to be smaller for higher metallicity star particles at
-large radii than for those with lower metallicity at smaller radii, assuming GC 
-disruption is more efficient in the inner regions of the Galaxy.
+We investigate whether the galaxy and star formation model used for the Auriga
+simulations can produce a realistic GC population. We compare statistics of GC 
+candidate star particles in the Auriga haloes with catalogues of the Milky Way 
+(MW) and Andromeda (M31) GC populations. We find that the Auriga simulations do 
+produce sufficient stellar mass for GC candidates at radii and metallicities that 
+are typical for the MW GC system (GCS). We do observe varying mass-ratios of the
+simulated GC candidates relative to the observed mass in the MW and M31 GC systems
+for different bins of galactocentric radius-metallicity ($R_{\text{gal}}$-[Fe/H]).
+This implies that different values for the combined product of the bound cluster 
+formation efficiency and the GC disruption rate are needed. Overall, the Auriga 
+simulations produce GC candidates with higher metallicities than the MW and M31 
+GCS and they are found at larger radii than observed. Bound cluster formation
+efficiencies higher than ten percent are needed for the metal-poor GC candidates,
+and those within the Solar radius should experience negligible destruction rates.
+GC candidates in the outer halo, on the other hand, should either have low formation
+efficiencies, or experience high mass loss for the Auriga simulations to produce a
+GCS that is consistent with that of the MW or M31. Finally, the scatter in the 
+metallicity as well as in the radial distribution between different Auriga runs 
+is considerably smaller than the differences between that of the MW and M31 GCSs. 
+The Auriga model is unlikely to give rise to a GCS that can be consistent with
+both galaxies.
 \end{abstract}
@@
 very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$~pc) 
-produces star clusters that could be globular progenitors \citep{
+produces star clusters that could be GC progenitors \citep{
 2019arXiv190509840L}.
@@
 properties of age-selected GC candidates because each star particle represents a
-single stellar population with a total mass that could be consistent with one 
-globular cluster. This means that their formation sites and that of a real-world 
-GC may be consistent.
+single stellar population with a total mass that could be consistent with one GC. 
+This means that their formation sites and that of a real-world GC may be consistent.
 
@@
 
-We find that the age cut, on average, lowers the mean metallicity [Fe/H] from 
+We find that the age cut, on average, lowers the mean metallicity $<$[Fe/H]$>$ from 
 $0.0$ to $-0.6$. Furthermore, accreted GC candidates generally have lower mean 
@@
 (sub)populations of GC candidates that are more metal-rich than the MW and M31 GCSs.
-Moreover, none of the simulations has a (total) population of GC 
-candidates with a bimodal metallicity distribution.
+Moreover, none of the simulations produces GC candidates with a bimodal metallicity 
+distribution.
 
@@
         L4 simulations. We show the median value of all Auriga haloes for all
-        stars (green dotted) and globular cluster candidates (i.e. stars with
+        stars (green dotted) and GC candidates (i.e. stars with
         age $>$~10~Gyr; green solid). The latter sub set is further split up
@@
 simulation), then we calculate the median total mass in each bin over all 
-thirty Auriga L4 haloes. The result is shown in Figure~\ref{fig:Au-FeHRgc} (which 
+thirty Auriga L4 haloes. The result is shown in Figure~\ref{fig:Au-FeHRgc}, which 
 can be compared to the observed total GC mass shown in 
-Figure~\ref{fig:observations_FeHRgc}). We notice that the Auriga simulations, 
-on average, produce fewer GCs in the lowest metallicity bins ($-2.5$ to $-1.5$) 
-than at higher metallicities in the three innermost radial bins. In addition, 
-Auriga produces fewer high-metallicity GCs at large radii, similar to the MW 
-and M31 GCSs.
-
-To ease the comparison between the simulations and observations we take the ratio
+Figure~\ref{fig:observations_FeHRgc}.
+
+To ease this comparison between the simulations and observations we take the ratio
 of the total mass of GC candidates in Auriga to the total GC mass in the MW 
@@
 in each bin). We show this in the top (bottom) panel of Figure~\ref{fig:Au-FeHRgc-ratio}.
-Note that the data in three top right bins is masked because the mass ratio cannot 
+Note that the data in the three top right bins is masked because the mass ratio cannot 
 be calculated due to zero mass in the observations (therefore the bins are white).
@@
 have been zero. The red and blue bins indicate deviations from such as scenario and
-indicate a higher and lower than average mass excess. In particular, the median 
+indicate a higher and lower than average mass excess in the simulations. The median 
 value used to shift the mass ratio is $2.68$ and $1.69$ dex for the MW and M31, 
-respectively. This means that the overall `mass budget' that the simulations `can 
+respectively. This means that the median `mass budget' that the simulations `can 
 afford to lose' is roughly a factor $480$ and $50$ for the MW and M31, respectively. 
@@
 
-The top panel of Figure~\ref{fig:Au-FeHRgc-ratio} shows that mass excess for
-Auriga GCs within the Solar radius decreases with decreasing metallicity. This
-means that either the formation efficiency should increase with decreasing metallicity,
-or that the lowest-metallicity GCs in the Auriga simulations are less strongly affected
-by disruptive processes, if the star formation histories in the Auriga simulations
-are to give rise to a GCS that can be similar to the GCS that is observed
-in the MW. Moreover, either a lower formation efficiency is required at
-large radii, or stronger disruption. Disruption of star clusters is expected to
-be more efficient at smaller radii due to higher tidal forces in the innermost
-region for GCs on orbits that pass through the disk, or with pericenters close 
-to the bar or bulge. Compared to M31, the mass ratio (bottom panel of 
-Figure~\ref{fig:Au-FeHRgc-ratio}) shows a less clear trend than for the MW,
-which suggests that both galaxies have diverse GC formation histories.
-Most bins show mass surplus factors of few tens, meaning that high formation 
-efficiencies would be required in addition to little disruption for the Auriga 
-simulations to yield a GCS consistent with that of M31.
+We now focus on four quadrants of this diagram, split at [Fe/H]~=~-1 (metal-poor 
+or metal-rich) and $R_\text{gal}$~=~8~kpc (inside or outside the Solar radius).
+The majority of the mass in Auriga GC candidates is produced in metal-rich star
+particles inside the Solar radius. The total mass is dominated by the {\it in situ} 
+component, for [Fe/H] as well as for $R_\text{gal}$. The total mass excess in 
+this region increases with decreasing metallicity for the MW and M31, and there
+is a weak trend of decreasing over-production with increasing radius for the
+{\it in situ} subsets but no trend with radius for the accreted GC candidates.
+As for the metal-rich GC candidates outside the Solar radius, we find that the
+mass excess with respect to the median is largest in this corner for the MW and
+M31. The main reason for this trend are the lower GC counts in the observations,
+whereas the Auriga simulations efficiently form metal-rich GC candidates and
+have no problem to produce them at large radii. The opposite is true for the
+metal-poor GC candidates inside the Solar radius, where the mass surplus with
+respect to the median is smallest for both galaxies. However, the disruption rates
+are expected to be particularly high for GCs in the inner regions of galaxies
+that are on orbits with pericentres close to the galactic bulge or bar. In addition, 
+disk crossings in this region will cause spikes in the tidal tensor due to steep
+density gradients that could be highly disruptive to the GCs. The bins with the 
+lowest `mass budget' are in this region (a factor 9 for the MW and 22 for M31).
+The bound cluster formation efficiency has to exceed 10\%, and none of the GC 
+candidates in this region can experience significant mass loss in order for Auriga
+to produce sufficient mass in this quadrant. Finally, the metal-poor GC candidates
+outside the Solar radius have lower than average mass ratios, which is not 
+surprising given that the Auriga simulations overall underproduce low-metallicity
+stars particles.
 
@@
 \label{sec:discussion_FeH}
-Globular clusters are ${\sim}0.5$ dex more metal-poor than spheroid stars observed 
+GCs are ${\sim}0.5$ dex more metal-poor than spheroid stars observed 
 at the same radius for almost all galaxies \citep{1991ARA&A..29..543H}. Our 
@@
 
-We find that none of the Auriga simulations produces a bimodal 
+However, we find that none of the Auriga simulations produces a bimodal 
 metallicity distribution for age-selected GC candidates. Interestingly, the 
@@
 the {\it in~situ} GC candidates are roughly consistent with the metal-rich MW GCs.
-However, we also notice that a substantial number of simulations has similar 
+On the other hand, we also notice that a substantial number of simulations has similar 
 mean values for all GC candidates, and the simulated {\it in~situ} GC candidates 
@@
 the GC candidates in the Auriga simulations to yield sufficient total mass to
-be consistent with the MW or M31 GCS.
+be consistent with the MW or M31 GCS. In addition, the metal-poor GC candidates
+would have to experience low mass los rates, especially those within the Solar
+radius.
 
@@
 less efficient at larger radii, thus, the formation efficiencies of the accreted 
-GC candidates would have to be lower. Our classification as GC candidates could, 
-for example, be improved by selecting a number of globular clusters based on the 
-$M_{vir}-N_{\text{gal}}$ correlation found by \citet{2019arXiv190100900B}, and 
-taking a virial mass below which none of the star particles is treated as GC candidate.
+GC candidates would have to be lower. Our classification as GC candidates could
+especially be improved for the accreted subset. For example, we could tag only a
+subset of the accreted star particles as GC candidates, where the number
+number of GCs is determined by the satellite halo mass, given the 
+$M_{vir}-N_{\text{gal}}$ correlation found by \citet{2019arXiv190100900B}.
 
@@
 
-We investigate GC candidates in the Auriga simulations and draw the following
-conclusions.
+We investigate statistics of age-selected ($>$~10~Gyr) GC candidates in the 
+Auriga simulations and compare the simulations to the MW and M31 GCSs. Based on
+our analysis we draw the following conclusions.
 
@@
     metallicity distributions that are more metal-rich than the MW and M31
-    GCSs.
-
-    \item We reject the null hypothesis $H_0$ for any one of the Auriga simulations 
-    that the GC candidates and the MW GCs are drawn from the same underlying 
-    distribution. This statement holds true when we select all old star particles 
-    (GC candidates), but also when we select the old accreted or the old {\it in~situ} 
-    star particles. In addition, this is also the case when we test against the 
-    M31 GCS instead of the MW GCS. Moreover, the difference between the MW and
-    M31 is big compared to the scatter in GC candidate properties in the Auriga
-    simulations.
+    GCSs. For most of the Auriga simulations we find that the subset of accreted 
+    GC candidates has a lower mean metallicity than the {\it in situ} subpopulation.
+    However, the accreted subsets are still more metal-rich than the MW and M31 GCSs.
+    Moreover, none of the simulated subsets has a mean metallicity as low as the mean
+    of the `blue' metal-poor component of the MW GCS.
+
+    \item We find that the difference between the metallicity distributions of 
+    the MW and M31 GCSs is big compared to the scatter in the Auriga GC candidates 
+    of different Auriga runs. The radial distributions of the MW and M31 GCSs are
+    somewhat more similar, but they are not consistent with being drawn from the
+    same distribution. The scatter between the radial distributions of different
+    Auriga simulations is smaller than the difference between the MW and M31 GCSs.
 
@@
     given that our selection function of star particles selects all stars bound
-    to the main subhalo in the main halo. The stellar mass is dominated by accreted 
-    star particles at radii beyond $20$~kpc. The GCs in the MW and M31, on the 
-    other hand, have a much smaller radial extent.
+    to the main subhalo in the main halo. The total mass of GC candidates is 
+    dominated by accreted star particles at radii beyond $20$~kpc. The GCs in 
+    the MW and M31, on the other hand, have a much smaller radial extent.
 

### 2019-08-23 latexdiff.sh
Updated latexdiff.sh to process RG's final remarks + FG feedback #1

@@ -1,7 +1,7 @@
 #!/bin/bash
 set -e
 
-diff="diff_with_respect_to_20190802.tex"
+diff="diff_with_respect_to_20190820.tex"
 if [ -f "${diff}" ]; then
     rm -f "${diff}"
 fi
@@ -9,5 +9,5 @@ fi
 # Ignore (sub)sections: https://tex.stackexchange.com/questions/87536
 # NB, removed by hand Volker Springel from AurigaGCS_20180802.tex b/c
 # latexdiff breaks on changes in the \author block
-latexdiff --exclude-textcmd="section,subsection" AurigaGCS_20190802.tex AurigaGCS.tex > "${diff}"
+latexdiff --exclude-textcmd="section,subsection" AurigaGCS_20190820.tex AurigaGCS.tex > "${diff}"
 timotex "${diff}"

### 2019-09-05 AurigaGCS.tex
Rgal --> rgal b/c 3D radii

@@
 \begin{abstract}
-We investigate whether the galaxy and star formation model used for the Auriga simulations
-can produce a realistic globular cluster (GC) population. We compare statistics 
-of GC candidate star particles in the Auriga haloes with catalogues of the Milky 
-Way (MW) and Andromeda (M31) globular cluster populations. We find that the Auriga 
-simulations do produce sufficient stellar mass for GC candidates at radii and 
-metallicities that are typical for the MW GC system (GCS), although we observe a 
-varying mass-ratio for different galactocentric radius-metallicity 
-($R_{\text{gal}}$-[Fe/H]) bins of simulated GC candidates relative to the 
-observed mass in the MW and M31 GC systems.
-This implies different values for the combined product of the bound cluster 
-formation efficiency and the GC disruption rate. Furthermore we test whether any of the 
-Auriga galaxies has a metallicity and radial distribution that is consistent with 
-the MW or M31 GCS. For any one of the Auriga haloes we reject the null hypothesis
-that the observed and simulated metallicities of GCs (GC candidates) are drawn
-from the same distribution at $\geq98.32$~\% confidence level, for the GCS of 
-the MW and M31. The same holds true for the distribution of $R_{\text{gal}}$.
-Overall, the Auriga simulations produce GC candidates with higher metallicities 
-than the MW and M31 GCS and at larger radii. This implies that the bound cluster
-formation efficiency would have to decrease with increasing metallicity for the 
-Auriga GC candidates to be consistent with the MW GCS, if GC disruption is equally 
-efficient regardless of metallicity. In addition, the number of GCs relative to
-field stars would have to be smaller for higher metallicity star particles at
-large radii than for those with lower metallicity at smaller radii, assuming GC 
-disruption is more efficient in the inner regions of the Galaxy.
+We investigate whether the galaxy and star formation model used for the Auriga
+simulations can produce a realistic GC population. We compare statistics of GC 
+candidate star particles in the Auriga haloes with catalogues of the Milky Way 
+(MW) and Andromeda (M31) GC populations. We find that the Auriga simulations do 
+produce sufficient stellar mass for GC candidates at radii and metallicities that 
+are typical for the MW GC system (GCS). We do observe varying mass-ratios of the
+simulated GC candidates relative to the observed mass in the MW and M31 GC systems
+for different bins of galactocentric radius-metallicity ($r_{\text{gal}}$-[Fe/H]).
+This implies that different values for the combined product of the bound cluster 
+formation efficiency and the GC disruption rate are needed. Overall, the Auriga 
+simulations produce GC candidates with higher metallicities than the MW and M31 
+GCS and they are found at larger radii than observed. Bound cluster formation
+efficiencies higher than ten percent are needed for the metal-poor GC candidates,
+and those within the Solar radius should experience negligible destruction rates.
+GC candidates in the outer halo, on the other hand, should either have low formation
+efficiencies, or experience high mass loss for the Auriga simulations to produce a
+GCS that is consistent with that of the MW or M31. Finally, the scatter in the 
+metallicity as well as in the radial distribution between different Auriga runs 
+is considerably smaller than the differences between that of the MW and M31 GCSs. 
+The Auriga model is unlikely to give rise to a GCS that can be consistent with
+both galaxies.
 \end{abstract}
@@
 center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic
-Pole. We calculate the galactocentric radius $R_{\text{gal}}=\sqrt{(X-R_\odot)^2
-+ Y^2 + Z^2}$, assuming the solar radius $R_\odot=8$~kpc.}, and absolute
+Pole. We calculate the galactocentric radius $r_{\text{gal}}=\sqrt{(X-r_\odot)^2
++ Y^2 + Z^2}$, assuming the solar radius $r_\odot=8$~kpc.}, and absolute
 magnitude in the V~band, $M_V$. We use the V~band magnitude to calculate 
@@
 is believed to be 94\% complete. GCs in the outer stellar halo, up to
-$R_{\text{proj}}\sim150$~kpc, are observed in the Pan-Andromeda Archaeological
+$r_{\text{proj}}\sim150$~kpc, are observed in the Pan-Andromeda Archaeological
 Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H}, but see also
@@
 The bottom panel of Figure~\ref{fig:MW-M31-age-Rgc} shows the radial distribution
-of the MW and M31 GCS. Both quantities are readily available in H96e10 (assuming
-$R_{\odot}=8.0$~kpc), but the galactocentric radius of GCs in M31 is not available
-in CR16. Therefore, we follow \citet[][Sec.~4.1]{2019arXiv190111229W} to calculate
-the projected radius $R_{\text{proj}}$ from the observed positions, adopting M31's
-central position from the NASA Extragalactic 
+of the MW and M31 GCS. We divide the radii of M31 by its virial radius\footnote{
+$r_{\text{vir}}$ is the radius in a spherical `top-hat' perturbation model at which
+the average density reaches an overdensity of $\Delta_{\text{vir}}=357$ times the 
+background density, adopting the values and cosmology from \citet{2017MNRAS.464.3825P}}
+$r_{\text{vir,M31}} = 299$~kpc and multiply by $r_{\text{vir,MW}} = 261$~kpc to 
+account for the different intrinsic sizes of both galaxies. Values for 
+R$_{\text{gal}}$ are readily available in H96e10 (assuming $r_{\odot}=8.0$~kpc), but the galactocentric radius of GCs
+in M31 is not available in CR16. Therefore, we follow \citet[][Sec.~4.1]{2019arXiv190111229W} 
+to calculate the projected radius $r_{\text{proj}}$ from the observed positions,
+adopting M31's central position from the NASA Extragalactic 
 Database\footnote{\url{https://ned.ipac.caltech.edu/}} $(\alpha_0, \, \delta_0) =
@@
 and distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}.
-We calculate $R_{\text{gal}}$ as `average deprojected distance`
-$R_{\text{gal}} = R_{\text{proj}} \times (4/\pi)$.
+We calculate $r_{\text{gal}}$ as `average deprojected distance`
+$r_{\text{gal}} = r_{\text{proj}} \times (4/\pi)$.
 
@@
 (when accounting for the larger number of total GCs in M31). Interestingly, both
-distributions show a similar trend for $R_{\text{gal}} > 4$~kpc and host a 
+distributions show a similar trend for $r_{\text{gal}} > 4$~kpc and host a 
 subpopulation of halo GCs. However, the two radial distributions are not statistically
@@
         The dotted lines show the subset of data that also have age measurements
-        (i.e. the same sample as in the top panel).
+        (i.e. the same sample as in the top panel). We divide the radii of M31 by
+        $r_{\text{vir,M31}} = 299$~kpc and multiply by $r_{\text{vir,MW}} = 261$~kpc 
+        \citep{2017MNRAS.464.3825P} to compensate for the different intrinsic 
+        sizes of both galaxies. 
         \label{fig:MW-M31-age-Rgc}
@@
 in the upper right corner, both for MW and M31), and relatively few GCs at large
-radii in general ($R_{\text{gal}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
+radii in general ($r_{\text{gal}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
 the MW and $17$ or 4.6\% in M31). Moreover, the M31 hosts more metal-rich 
@@
     \caption{
-        \emph{Top}: Mass-weighted $R_{\text{gal}}$-[Fe/H] distribution of
+        \emph{Top}: Mass-weighted $r_{\text{gal}}$-[Fe/H] distribution of
         151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H},
@@
         \emph{Bottom}: Same for M31, showing the 366 GCs in CR16 
-        \citep[data from][]{2016ApJ...824...42C}. Note that the range of the 
-        colourmap differs in both figures.
+        \citep[data from][]{2016ApJ...824...42C}. Radii of M31 are again divided by 
+        $r_{\text{vir,M31}}$ and multiplied by $r_{\text{vir,MW}}$. Note that the 
+        range of the colourmap differs in both figures. 
         \label{fig:observations_FeHRgc}
@@
         of star particles in each of the thirty Auriga L4 haloes compared to
-        the MW (M31) GCS shown in purple (magenta).
+        the MW (M31) GCS shown in purple (magenta). The Auriga (M31) radii are 
+        divided by $r_{\text{vir,Au}}$ ($r_{\text{vir,M31}}$) and multiplied 
+        by $r_{\text{vir,MW}}$ to compensate for different intrinsic sizes of
+        the galaxies.
         \label{fig:Rgc_mu_sigma}
@@
 We repeat the analysis of the previous subsection for the distribution of
-galactocentric radius instead of metallicity. We look for general trends present
+galactocentric radius instead of metallicity. We divide the Auriga radii by
+$r_{\text{vir,Au}}$ and multiply by $r_{\text{vir,MW}}$ to compensate for the different
+intrinsic sizes of the Auriga galaxies. We look for general trends present
 in all Auriga L4 galaxies. Figure~\ref{fig:Rgc_mu_sigma} shows the mean and 
-standard deviation of $\log_{10}(R_{\text{gal}})$ of star particles in all Auriga
+standard deviation of $\log_{10}(r_{\text{gal}})$ of star particles in all Auriga
 L4 simulations. The purple (magenta) cross again shows the mean of the MW (M31)
@@
 first have to migrate inwards in order to populate the innermost radii. Moreover,
-we find that the simulations have a wider dispersion in $\log(R_{\text{gal}})$ than
+we find that the simulations have a wider dispersion in $\log(r_{\text{gal}})$ than
 the MW GCS, while the dispersion of M31 seems to lie within the range of dispersions
@@
         Mass-weighted radial distribution of star particles in the Auriga
-        L4 simulations. We show the median value of all Auriga haloes for all
-        stars (green dotted) and globular cluster candidates (i.e. stars with
+        L4 simulations, where the Auriga (M31) radii are again divided by 
+        $r_{\text{vir,Au}}$ ($r_{\text{vir,M31}}$) and multiplied by 
+        $r_{\text{vir,MW}}$. We show the median value of all Auriga haloes for all
+        stars (green dotted) and GC candidates (i.e. stars with
         age $>$~10~Gyr; green solid). The latter sub set is further split up
@@
     \caption{
-        Mass-weighted [Fe/H]-$R_{\text{gal}}$ distribution of all thirty Auriga
+        Mass-weighted [Fe/H]-$r_{\text{gal}}$ distribution of all thirty Auriga
         L4 haloes. Here we consider only the GC candidates and color-code by the 
@@
 We investigate whether the Auriga simulations still produce sufficient mass when
-the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{gal}$. First
+the GC candidates are two-dimensionally binned in [Fe/H] and $r_\text{gal}$. First
 we sum the total mass of GC candidates in each bin (for an individual Auriga 
 simulation), then we calculate the median total mass in each bin over all 
-thirty Auriga L4 haloes. The result is shown in Figure~\ref{fig:Au-FeHRgc} (which 
+thirty Auriga L4 haloes. The result is shown in Figure~\ref{fig:Au-FeHRgc}, which 
 can be compared to the observed total GC mass shown in 
-Figure~\ref{fig:observations_FeHRgc}). We notice that the Auriga simulations, 
-on average, produce fewer GCs in the lowest metallicity bins ($-2.5$ to $-1.5$) 
-than at higher metallicities in the three innermost radial bins. In addition, 
-Auriga produces fewer high-metallicity GCs at large radii, similar to the MW 
-and M31 GCSs.
-
-To ease the comparison between the simulations and observations we take the ratio
+Figure~\ref{fig:observations_FeHRgc}.
+
+To ease this comparison between the simulations and observations we take the ratio
 of the total mass of GC candidates in Auriga to the total GC mass in the MW 
@@
 have been zero. The red and blue bins indicate deviations from such as scenario and
-indicate a higher and lower than average mass excess. In particular, the median 
+indicate a higher and lower than average mass excess in the simulations. The median 
 value used to shift the mass ratio is $2.68$ and $1.69$ dex for the MW and M31, 
-respectively. This means that the overall `mass budget' that the simulations `can 
+respectively. This means that the median `mass budget' that the simulations `can 
 afford to lose' is roughly a factor $480$ and $50$ for the MW and M31, respectively. 
 The lowest mass surplus for both galaxies is the the bin where $-2.5 <$ [Fe/H] 
-$< -1.5$ and $3 < R_{\text{gal}}/\text{kpc} < 8$, for which the simulations produce 
+$< -1.5$ and $3 < r_{\text{gal}}/\text{kpc} < 8$, for which the simulations produce 
 a factor $10^{2.68}/10^{1.33} \approx 22$ and $10^{1.69}/10^{0.75} \approx 9$ 
@@
 
-The top panel of Figure~\ref{fig:Au-FeHRgc-ratio} shows that mass excess for
-Auriga GCs within the Solar radius decreases with decreasing metallicity. This
-means that either the formation efficiency should increase with decreasing metallicity,
-or that the lowest-metallicity GCs in the Auriga simulations are less strongly affected
-by disruptive processes, if the star formation histories in the Auriga simulations
-are to give rise to a GCS that can be similar to the GCS that is observed
-in the MW. Moreover, either a lower formation efficiency is required at
-large radii, or stronger disruption. Disruption of star clusters is expected to
-be more efficient at smaller radii due to higher tidal forces in the innermost
-region for GCs on orbits that pass through the disk, or with pericenters close 
-to the bar or bulge. Compared to M31, the mass ratio (bottom panel of 
-Figure~\ref{fig:Au-FeHRgc-ratio}) shows a less clear trend than for the MW,
-which suggests that both galaxies have diverse GC formation histories.
-Most bins show mass surplus factors of few tens, meaning that high formation 
-efficiencies would be required in addition to little disruption for the Auriga 
-simulations to yield a GCS consistent with that of M31.
+We now focus on four quadrants of this diagram, split at [Fe/H]~=~-1 (metal-poor 
+or metal-rich) and $r_\text{gal}$~=~8~kpc (inside or outside the Solar radius).
+The majority of the mass in Auriga GC candidates is produced in metal-rich star
+particles inside the Solar radius. The total mass is dominated by the {\it in situ} 
+component, for [Fe/H] as well as for $r_\text{gal}$. The total mass excess in 
+this region increases with decreasing metallicity for the MW and M31, and there
+is a weak trend of decreasing over-production with increasing radius for the
+{\it in situ} subsets but no trend with radius for the accreted GC candidates.
+As for the metal-rich GC candidates outside the Solar radius, we find that the
+mass excess with respect to the median is largest in this corner for the MW and
+M31. The main reason for this trend are the lower GC counts in the observations,
+whereas the Auriga simulations efficiently form metal-rich GC candidates and
+have no problem to produce them at large radii. The opposite is true for the
+metal-poor GC candidates inside the Solar radius, where the mass surplus with
+respect to the median is smallest for both galaxies. However, the disruption rates
+are expected to be particularly high for GCs in the inner regions of galaxies
+that are on orbits with pericentres close to the galactic bulge or bar. In addition, 
+disk crossings in this region will cause spikes in the tidal tensor due to steep
+density gradients that could be highly disruptive to the GCs. The bins with the 
+lowest `mass budget' are in this region (a factor 9 for the MW and 22 for M31).
+The bound cluster formation efficiency has to exceed 10\%, and none of the GC 
+candidates in this region can experience significant mass loss in order for Auriga
+to produce sufficient mass in this quadrant. Finally, the metal-poor GC candidates
+outside the Solar radius have lower than average mass ratios, which is not 
+surprising given that the Auriga simulations overall underproduce low-metallicity
+stars particles.
 
@@
 halo and main subhalo, which means that we include particles up to the virial 
-radius $R_{200}$. The Auriga simulations have no problem populating the stellar 
+radius $r_{200}$. The Auriga simulations have no problem populating the stellar 
 halo up to the virial radius, even with our additional age cut. On the other hand, 
@@
     metallicity distributions that are more metal-rich than the MW and M31
-    GCSs.
-
-    \item We reject the null hypothesis $H_0$ for any one of the Auriga simulations 
-    that the GC candidates and the MW GCs are drawn from the same underlying 
-    distribution. This statement holds true when we select all old star particles 
-    (GC candidates), but also when we select the old accreted or the old {\it in~situ} 
-    star particles. In addition, this is also the case when we test against the 
-    M31 GCS instead of the MW GCS. Moreover, the difference between the MW and
-    M31 is big compared to the scatter in GC candidate properties in the Auriga
-    simulations.
-
-    \item GC candidates in the Auriga simulations may be found out to $R_{200}$,
+    GCSs. For most of the Auriga simulations we find that the subset of accreted 
+    GC candidates has a lower mean metallicity than the {\it in situ} subpopulation.
+    However, the accreted subsets are still more metal-rich than the MW and M31 GCSs.
+    Moreover, none of the simulated subsets has a mean metallicity as low as the mean
+    of the `blue' metal-poor component of the MW GCS.
+
+    \item We find that the difference between the metallicity distributions of 
+    the MW and M31 GCSs is big compared to the scatter in the Auriga GC candidates 
+    of different Auriga runs. The radial distributions of the MW and M31 GCSs are
+    somewhat more similar, but they are not consistent with being drawn from the
+    same distribution. The scatter between the radial distributions of different
+    Auriga simulations is smaller than the difference between the MW and M31 GCSs.
+
+    \item GC candidates in the Auriga simulations may be found out to $r_{200}$,
     given that our selection function of star particles selects all stars bound
-    to the main subhalo in the main halo. The stellar mass is dominated by accreted 
-    star particles at radii beyond $20$~kpc. The GCs in the MW and M31, on the 
-    other hand, have a much smaller radial extent.
+    to the main subhalo in the main halo. The total mass of GC candidates is 
+    dominated by accreted star particles at radii beyond $20$~kpc. The GCs in 
+    the MW and M31, on the other hand, have a much smaller radial extent.
 

### 2019-09-05 AurigaGCS.tex
Time to submit to MNRAS

@@
 for different bins of galactocentric radius-metallicity ($r_{\text{gal}}$-[Fe/H]).
-This implies that different values for the combined product of the bound cluster 
+This may imply that different values for the combined product of the bound cluster 
 formation efficiency and the GC disruption rate are needed. Overall, the Auriga 
@@
 density, the stellar mass to halo mass relation, and galaxy luminosity functions.
-The galaxy formation model produces realistic spiral galaxies at redshift $z=0$.
-Moreover, Auriga reproduces the HI disc properties \citep{2017MNRAS.466.3859M},
-the chemical thin/thick disc \citep{2018MNRAS.474.3629G}, the diversity in 
-accreted stellar halo properties found in observations \citep{2019MNRAS.485.2589M},
-and the \textit{Gaia} Sausage \citep{2019MNRAS.484.4471F}. These last two 
-bolster the point that the simulations are similar (and detailed) enough to the 
-MW to reproduce major, distinct features of the Galaxy, and so looking for the 
-GC population properties and comparing them to the MW/M31 is all the more relevant.
+The galaxy formation model produces realistic spiral galaxies at redshift zero
+that match observations such as sizes, morphologies (\citetalias{2017MNRAS.467..179G}),
+HI disc properties \citep{2017MNRAS.466.3859M}, and the diversity of accreted stellar
+halo properties \citep{2019MNRAS.485.2589M}. Furthermore, the simulations are able to
+reproduce major Galactic components, such as the chemical thin/thick disc dichotomy
+\citep{2018MNRAS.474.3629G} and the recently discovered \textit{Gaia} Sausage 
+\citep{2019MNRAS.484.4471F}. They are thus a large set of detailed simulations
+similar enough to the Galaxy to make predictions for the GC population properties
+of the MW and M31.
 
@@
 disruption over a Hubble time would be constant, then the value in each bin would
-have been zero. The red and blue bins indicate deviations from such as scenario and
+have been zero. The red and blue bins indicate deviations from such a scenario and
 indicate a higher and lower than average mass excess in the simulations. The median 

### 2019-09-09 latexdiff.sh
FAG acknowledgment

@@ -1,7 +1,7 @@
 #!/bin/bash
 set -e
 
-diff="diff_with_respect_to_20190820.tex"
+diff="diff_with_respect_to_20190905.tex"
 if [ -f "${diff}" ]; then
     rm -f "${diff}"
 fi
@@ -9,5 +9,5 @@ fi
 # Ignore (sub)sections: https://tex.stackexchange.com/questions/87536
 # NB, removed by hand Volker Springel from AurigaGCS_20180802.tex b/c
 # latexdiff breaks on changes in the \author block
-latexdiff --exclude-textcmd="section,subsection" AurigaGCS_20190820.tex AurigaGCS.tex > "${diff}"
+latexdiff --exclude-textcmd="section,subsection" AurigaGCS_20190905.tex AurigaGCS.tex > "${diff}"
 timotex "${diff}"

### 2019-10-28 response_to_referee.tex
Process feedback referee / General comments about style / MNRAS style to refer to...

\documentclass{article}

\begin{document}

\section*{General comments about style}
\begin{itemize}
\item
\item
\item
\item
\item I replaced `Sec.' by `Section' to refer to sections in the present work.
Moreover, I changed `Sec.' to `section' to refer to a section in one of the references.
\end{itemize}

\section*{Major comments and concerns}
\begin{itemize}
\item Item
\end{itemize}

\section*{Additional major comments}
\begin{itemize}
\item Item
\end{itemize}

\section*{Comments for each section}
\begin{itemize}
\item Item
\end{itemize}

\section*{Minor comments}
\begin{itemize}
\item Item
\end{itemize}

\end{document}

### 2019-10-28 AurigaGCS.tex
Submitted.
Process feedback referee / General comments about style / MNRAS style to refer to...

@@
 \begin{keywords}
-methods: numerical -- galaxies: formation -- galaxies: star clusters: general.
+galaxies: formation -- galaxies: star clusters: general.
 \end{keywords}
@@
 we use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, 
-further described in Sec.~\ref{sec:auriga}. We investigate whether the star 
+further described in Section~\ref{sec:auriga}. We investigate whether the star 
 formation model implemented produces metallicity, 
@@
 \label{sec:observations}
-We describe the observations of the MW GCS in Sec.~\ref{sec:milkyway},
-and of the M31 GCS in Sec.~\ref{sec:andromeda}
+We describe the observations of the MW GCS in Section~\ref{sec:milkyway},
+and of the M31 GCS in Section~\ref{sec:andromeda}
 
@@
 R$_{\text{gal}}$ are readily available in H96e10 (assuming $r_{\odot}=8.0$~kpc), but the galactocentric radius of GCs
-in M31 is not available in CR16. Therefore, we follow \citet[][Sec.~4.1]{2019arXiv190111229W} 
+in M31 is not available in CR16. Therefore, we follow \citet[][section~4.1]{2019arXiv190111229W} 
 to calculate the projected radius $r_{\text{proj}}$ from the observed positions,
@@
         distribution). The black solid (open) dots indicate the literature values
-        of a bimodal Gaussian fit to the data \citep[values from][p. 38]{1998gcs..book.....A},
+        of a bimodal Gaussian fit to the data \citep[values from][page~38]{1998gcs..book.....A},
         showing the metal-rich (metal-poor) component of the MW.
@@
 maintaining the Freya compute cluster, where the simulations were post-processed.
-FM is supported by the program "Rita Levi Montalcini" of the Italian MIUR.
+FM is supported by the program "Rita Levi Montalcini" of the Italian MIUR. FAG 
+acknowledges financial support from CONICYT through the project FONDECYT Regular 
+Nr. 1181264, and funding from the Max Planck Society through a Partner Group grant.
 This work has been supported by the European Research Council under ERC-StG grant

### 2019-10-28 AurigaGCS.tex
Process feedback referee / General comments about style / acronyms need to be introduced

@@
 We investigate whether the galaxy and star formation model used for the Auriga
-simulations can produce a realistic GC population. We compare statistics of GC 
+simulations can produce a realistic globular cluster (GC) population. 
+We compare statistics of GC 
 candidate star particles in the Auriga haloes with catalogues of the Milky Way 
@@
 2009ApJ...706L.192B} argue that (the blue subpopulations of) GCs form in radially
-biased dark matter halos at high redshift. Other recent hypotheses of GC formation 
+biased dark matter (DM) halos at high redshift. Other recent hypotheses of GC formation 
 prior to collapse of the proto-galaxy include formation in colliding supershells 
@@
 interacting and merging galaxies, which has been observed and are found to show 
-remarkable similarities with GCs in the MW \citep[e.g.][]{
+remarkable similarities with GCs in the Milky Way (MW) \citep[e.g.][]{
 1995AJ....109..960W, 1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}.
@@
 the star formation histories of the simulations give rise to a GCS similar to 
-the MW and/or M31 GCSs. In particular, 
+the MW and/or Andromeda (M31) GCSs. In particular, 
 we use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, 
@@
 and consecutive stellar evolution is accounted for. The channel for energetic
-stellar feedback is from non-local SNII, which is modelled with wind particles
-(\citealt{2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}). Galactic 
-winds enrich the ISM
-with metals from SNIa, SNII, and AGB stars \citep{2013MNRAS.436.3031V}. Supermassive
+stellar feedback is from non-local type II supernovae (SN), which is modelled 
+with wind particles (\citealt{2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}).
+Galactic winds enrich the ISM with metals from SNIa, SNII, and asymptotic giant 
+branch (AGB) stars \citep{2013MNRAS.436.3031V}. Supermassive
 black holes grow via Bondi–Hoyle–Lyttleton accretion \citep{1944MNRAS.104..273B,

### 2019-10-28 AurigaGCS.tex
Process feedback referee / General comments about style / avoid colloquial expressions

@@
 points calculated using such an artificial cut for the simulated star particles.
-Having said that, we do find it interesting that the mean metallicities of the 
-{\it in~situ} GC candidates appear roughly consistent with that of the metal-rich 
-population of the MW although the simulations show larger dispersions. The latter 
-could simply be caused by the hard separation of the MW data into two groups, 
-which means the range is smaller and the resulting dispersion lower. With 
+It is interesting that the mean metallicities of the {\it in~situ} GC candidates 
+appear roughly consistent with that of the metal-rich population of the MW despite 
+the lack of such a metallicity cut, although the simulations show larger dispersions. 
+The latter could simply be caused by the hard separation of the MW data into two 
+groups, which means the range is smaller and the resulting dispersion lower. With 
 regard to the M31 GCS, so far no definitive consensus has been reached
@@
 group in the M31 GCS. This is also true for the metal-poor population of the 
-MW with a mean value of $-1.6$. The main take-away from this plot, again, is 
+MW with a mean value of $-1.6$. The main result of this figure is 
 that all Auriga L4 galaxies have metallicity distributions with (much) larger

### 2019-11-22 response_to_referee.tex
Process feedback referee / General comments about style / acronyms need to be introduced
Process feedback referee / Minor comments / first steps

@@
 Moreover, I changed `Sec.' to `section' to refer to a section in one of the references.
+\item All acronyms are introduced the first time they appear in the text
+(MW, M31, GC, GCS, YMC, ISM, SN, AGB, DM, and Au). The subset thereof that appears 
+in the abstract is also introduced the first time it appears.
 \end{itemize}
@@
 \begin{itemize}
-\item Item
+\item The indicated typos have been corrected.
+\item `missing error bars and references for the virial radii' $\rightarrow$
+    I moved the reference from the footnote to the main text.
+\item 4.1: `which model do the authors refer to?' $\rightarrow$ 
+    added `star formation'.
+\item 4.1: `The top half of the left figure' $\rightarrow$ 
+    `The top panel of Figure 3'.
 \end{itemize}

### 2019-11-22 AurigaGCS.tex
Process feedback referee / Minor comments / first steps

@@
 the average density reaches an overdensity of $\Delta_{\text{vir}}=357$ times the 
-background density, adopting the values and cosmology from \citet{2017MNRAS.464.3825P}}
-$r_{\text{vir,M31}} = 299$~kpc and multiply by $r_{\text{vir,MW}} = 261$~kpc to 
-account for the different intrinsic sizes of both galaxies. Values for 
-R$_{\text{gal}}$ are readily available in H96e10 (assuming $r_{\odot}=8.0$~kpc), but the galactocentric radius of GCs
-in M31 is not available in CR16. Therefore, we follow \citet[][section~4.1]{2019arXiv190111229W} 
+background density} $r_{\text{vir,M31}} = 299$~kpc and multiply by 
+$r_{\text{vir,MW}} = 261$~kpc to account for the different intrinsic sizes of both 
+galaxies, adopting the values and cosmology from \citet{2017MNRAS.464.3825P}.
+Values for $r_{\text{gal}}$ are readily available in H96e10 (assuming $r_{\odot}=8.0$~kpc), 
+but the galactocentric radius of GCs in M31 is not available in CR16. Therefore, we 
+follow \citet[][section~4.1]{2019arXiv190111229W} 
 to calculate the projected radius $r_{\text{proj}}$ from the observed positions,
@@
 \label{sec:results_FeH}
-We investigate whether the model implemented in Auriga produces metallicity 
-distributions consistent with the MW and M31 GCSs, and whether
+We investigate whether the star formation model implemented in Auriga produces 
+metallicity distributions consistent with the MW and M31 GCSs, and whether
 the simulations generate sufficient total mass at metallicities typical for the
@@
         upper right corner. In each of these three panels we show the GG 
-        candicates in green, and use a green dotted line for all star particles. 
+        candidates in green, and use a green dotted line for all star particles. 
         We split the GC candidates up into two subpopulations, those that have 
@@
 different distributions. We show the age-selected GC candidates as well as the 
-accreted and {\it in~situ} subsets. The top half of the left figure shows the MW 
+accreted and {\it in~situ} subsets. The top panel of Figure~\ref{fig:Au4-10and21_FeH} shows the MW 
 and M31 GCSs, where we overplot a double Gaussian for the MW GCS by 
@@
 afford to lose' is roughly a factor $480$ and $50$ for the MW and M31, respectively. 
-The lowest mass surplus for both galaxies is the the bin where $-2.5 <$ [Fe/H] 
+The lowest mass surplus for both galaxies is the bin where $-2.5 <$ [Fe/H] 
 $< -1.5$ and $3 < r_{\text{gal}}/\text{kpc} < 8$, for which the simulations produce 
@@
 be consistent with the MW or M31 GCS. In addition, the metal-poor GC candidates
-would have to experience low mass los rates, especially those within the Solar
+would have to experience low mass loss rates, especially those within the Solar
 radius.

### 2019-12-08 response_to_referee.tex
Response to Referee's conclusion that technique doesnt work for zoom-sims, but limit scope to Auriga

@@
 \begin{document}
+
+\section*{Introduction (of referee report)}
+``The results of the paper clearly demonstrate that the technique of simulating
+stellar clusters in cosmological hydrodynamical simulations by tagging stellar
+particles based on their ages does not reproduce key properties of observed GC 
+systems in the Milky Way and M31. However, the authors do not state this conclusion
+anywhere''.
+
+We feel that our conclusion would be too strongly phrased if we would generalise 
+our results obtained using the Auriga simulations to cosmological simulations 
+in general. Indeed, we do find that age-selected stellar particles do not 
+reproduce key properties of observed GC systems in the Milky Way and M31. However,
+our results might reflect characteristics that are specific to Auriga, 
+e.g. that the galaxy formation model overmixes metals at early times. 
+Therefore we did add a final bulletpoint to our conclusion to clarify the above, 
+but we limit the scope to the Auriga simulations.
 

### 2019-12-08 AurigaGCS.tex
Response to Referee's conclusion that technique doesnt work for zoom-sims, but limit scope to Auriga

@@
 
-    \item The cluster formation efficiency would have to increase with decreasing
+    \item Tidal forces are larger in the inner regions of galaxies than in the
+    outer halo. Therefore, we expect dynamical evolution to more strongly affect 
+    GC candidates at small radii than at large radii. However,
+    we find that the Auriga simulations produce more mass in GC candidates with
+    high metallicities at large radii than with low metallicities at small radii.
+    The cluster formation efficiency would have to increase with decreasing
     metallicity for GC candidates in the Auriga simulations to be consistent
-    with the MW GCS, given that we expect dynamical evolution to 
-    more strongly affect GC candidates at smaller radii. This trend of over-production
-    of old star particles that are metal-rich and at large radii compared to 
-    observed GCs is less clear for the M31 GCS.
+    with the MW GCS. This trend of over-production of old star particles that 
+    are metal-rich and at large radii compared to observed GCs is less clear for 
+    the M31 GCS.
+
+    \item
+    Overall, we conclude that the metallicity and radial distribution of age-selected
+    star particles in the Auriga simulations are not consistent with globular 
+    cluster system of the Milky Way or with that of the Andromeda galaxy.
 

### 2019-12-09 response_to_referee.tex
Update text to reflect changes in figures (colour palette and 25-75 percentitile range)

@@
 in the abstract is also introduced the first time it appears.
+\item The colour palette has been updated to improve colourblind-friendliness.
+\item We no longer use blue and red to prevent confusion because they are 
+typically used for metal-poor and metal-rich populations.
 \end{itemize}
@@
 \begin{itemize}
+\item We normalise the Auriga simulations by the virial radius of the
+dark matter halo to compensate for scatter between different simulation runs. We
+deliberately chose for $r_{vir}$ because there are several stellar length scales
+that could be used (e.g. the effective radius of the bulge, the radial scalelength
+or vertical scaleheight of the disk, the optical radius, the extent of the stellar 
+halo, etc). The simulations show a wide variety between properties of the Auriga
+galaxies with little correlation between these different stellar length scales.
+The mean virial radius of Auriga L4 is 299.67 $\pm$ 19.41 kpc.
 \item Item
@@
 \section*{Comments for each section}
+\subsection*{Introduction}
+\begin{itemize}
+\item Item
+\end{itemize}
+
+\subsection*{Sect. 2 -}
+\begin{itemize}
+\item Item
+\end{itemize}
+
+\subsection*{Sect. 3 -}
+\begin{itemize}
+\item Item 
+\end{itemize}
+
+\subsection*{Sect. 4 -}
+\begin{itemize}
+\item
+\item Figure 4 - now has a vertical line to indicate the metallicity cut 
+between metal-poor and metal-rich GC subpopulations in the Milky Way.
+\item
+\item
+\item Figure 6: no changes were made for rescaling the galaxies (i.e. we still
+use the virial radius)
+\item Figure 5 and 7: shaded regions now show the 25-75th percentiles.
+\item Figure 9: The values are removed from the masked upper right corner bins.
+\item Figure 2,8,9: The values of the upper and right axes have been removed from
+Figure 2 and 9 (observations) for clarity (rather than the suggestion to add 
+axis labels and units). However, we did not mask these bins for Figure 8 (Auriga)
+because it illustrates our finding that the simulations produce a considerable
+amount of mass in GC candidates with low metallicities at large radii.
+\end{itemize}
+
+\subsection*{Sect. 5 -}
 \begin{itemize}

### 2019-12-09 AurigaGCS.tex
Update text to reflect changes in figures (colour palette and 25-75 percentitile range)

@@
         upper right corner. In each of these three panels we show the GG 
-        candidates in green, and use a green dotted line for all star particles. 
+        candidates in beige, and use a beige dotted line for all star particles. 
         We split the GC candidates up into two subpopulations, those that have 
-        formed {\it in~situ} (blue), and those that have been accreted (red).
+        formed {\it in~situ} (brown), and those that have been accreted (teal).
         \label{fig:Au4-10and21_FeH}
@@
         First vs. second central moment of the Auriga L4 metallicity distributions.
-        Each cross (for a given colour) represents one simulation. The green (blue)
-        [red] crosses show the values calculated using all (only {\it in~situ})
-        [only accreted] GC candidates. Green triangles indicate that all stars
+        Each cross (for a given colour) represents one simulation. The beige (brown)
+        [teal] crosses show the values calculated using all (only {\it in~situ})
+        [only accreted] GC candidates. Beige triangles indicate that all stars
         were used. The purple (magenta) cross denotes our calculation using all
         MW (M31) observations (which would be appropriate for a unimodal
-        distribution). The black solid (open) dots indicate the literature values
+        distribution). The purple solid (open) dots indicate the literature values
         of a bimodal Gaussian fit to the data \citep[values from][page~38]{1998gcs..book.....A},
-        showing the metal-rich (metal-poor) component of the MW.
+        showing the metal-rich (metal-poor) component of the MW (separated at
+        [Fe/H] = -1 as indicated by the vertical dotted magenta line).
         \label{fig:FeH_mu_sigma}
@@
 in Figure~\ref{fig:FeH_mu_sigma} to illustrate the behaviour for the full set of Auriga
-galaxies. The green crosses are to be compared to the purple (magenta) cross, 
+galaxies. The beige crosses are to be compared to the purple (magenta) cross, 
 which shows the mean value of all MW (M31) GCs. In addition, we show the metal-rich 
@@
         L4 simulations. We show the median value of all Auriga haloes for all
-        stars (green dotted) and GC candidates (i.e. stars with
-        age $>$~10~Gyr; green solid). The latter sub set is further split up
-        between stars that formed {\it in~situ} (blue solid), and those that were accreted
-        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
+        stars (beige dotted) and GC candidates (i.e. stars with
+        age $>$~10~Gyr; beige solid). The latter sub set is further split up
+        between stars that formed {\it in~situ} (brown solid), and those that were accreted
+        (teal solid). Shaded regions indicate the 25-75 percentile range. The MW (M31)
         GCS is shown in purple (magenta). The middle (bottom) panel shows the
@@
 a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
-median for all thirty Auriga L4 haloes with the $1\sigma$ interval around it 
+median for all thirty Auriga L4 haloes with the 25-75 percentile range 
 (shaded regions, which shows the scatter between runs that have different initial 
@@
 L4 simulations. The purple (magenta) cross again shows the mean of the MW (M31)
-GCs (which are to be compared to the green crosses), but solid (open) dot now
+GCs (which are to be compared to the beige crosses), but solid (open) dot now
 shows our calculation of the mean value of the `red' metal-rich (`blue` metal-poor) 
@@
         $r_{\text{vir,MW}}$. We show the median value of all Auriga haloes for all
-        stars (green dotted) and GC candidates (i.e. stars with
-        age $>$~10~Gyr; green solid). The latter sub set is further split up
-        between stars that formed {\it in~situ} (blue solid), and those that 
-        were accreted (red solid). Shaded regions indicate the $1\sigma$ 
-        interval. The MW (M31) GCS is shown in purple (magenta). The middle 
+        stars (beige dotted) and GC candidates (i.e. stars with
+        age $>$~10~Gyr; beige solid). The latter sub set is further split up
+        between stars that formed {\it in~situ} (brown solid), and those that 
+        were accreted (teal solid). Shaded regions indicate the 25-75 percentile
+        range. The MW (M31) GCS is shown in purple (magenta). The middle 
         (bottom) panel shows the ratio of the simulated mass to the mass in the 

### 2019-12-11 response_to_referee.tex
More fairly straightforward changes

@@
 \begin{itemize}
+\item Numerical quantities are now described in arabic numbers, not words.
+\item TODO: parenthesis
 \item
-\item
-\item
-\item
-\item I replaced `Sec.' by `Section' to refer to sections in the present work.
-Moreover, I changed `Sec.' to `section' to refer to a section in one of the references.
+\item We replaced `Sec.' by `Section' to refer to sections in the present work.
+Moreover, we changed `Sec.' to `section' to refer to a section in one of the references.
 \item All acronyms are introduced the first time they appear in the text
@@
 \begin{itemize}
+\item We clarified that `blue' GC subpopulation means metal-poor with [Fe/H]~$<~1$
+\item The units of mass-to-light ratio have been corrected.
 \item The indicated typos have been corrected.
 \item `missing error bars and references for the virial radii' $\rightarrow$
-    I moved the reference from the footnote to the main text.
+    The reference was given in a footnote, but is now moved to the main text.
 \item 4.1: `which model do the authors refer to?' $\rightarrow$ 

### 2019-12-11 AurigaGCS.tex
More fairly straightforward changes

@@
 with typical GC masses and sizes. \citet{2005MNRAS.364..367D} and \citet{
-2009ApJ...706L.192B} argue that (the blue subpopulations of) GCs form in radially
-biased dark matter (DM) halos at high redshift. Other recent hypotheses of GC formation 
-prior to collapse of the proto-galaxy include formation in colliding supershells 
-\citep{2017Ap&SS.362..183R}, in supersonically induced gaseous objects
+2009ApJ...706L.192B} argue that the blue, metal-poor GCs ([Fe/H]$ < -1$) form in 
+radially biased dark matter (DM) halos at high redshift. Other recent hypotheses 
+of GC formation prior to collapse of the proto-galaxy include formation in colliding 
+supershells \citep{2017Ap&SS.362..183R}, in supersonically induced gaseous objects
 \citep{2019arXiv190408941C}, or in high-speed collisions of dark matter subhaloes
@@
 The galaxy formation model includes primordial and metal-line cooling with 
-self-shielding corrections. Reionization is completed at redshift six by a
+self-shielding corrections. Reionization is completed at redshift $6$ by a
 time-varying spatially uniform UV background \citep{2009ApJ...703.1416F, 
@@
 in the MW might add up to 216 with recent estimates now anticipating an additional 
-thirty GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
+$30$~GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
 We still use data from the Harris catalogue, but caution that it may (only) be
@@
 mass-estimates by assuming $M_{V,\odot}=4.83$ and a mass to light ratio 
-$M/L_V = 1.7$~M/L$_{\odot}$, the mean for MW clusters \citep{2005ApJS..161..304M}. 
+$M/L_V = 1.7$~M$_{\odot}$/L$_{\odot}$, the mean for MW clusters \citep{2005ApJS..161..304M}. 
 We supplement the catalogue with age-estimates from isochrone fits to stars near 
@@
 of radii than the full data set: it appears that few age-estimates are available 
-for the innermost ($<1$~kpc) GCs, and none for those beyond roughly twenty
-kpc (the halo GCs). We compare both distributions of the full data set (solid 
+for the innermost ($<1$~kpc) GCs, and none for those beyond roughly $20$~kpc
+(the halo GCs). We compare both distributions of the full data set (solid 
 lines) and find that the MW has more GCs in the range $1-4$~kpc than M31
@@
 the accreted population is more metal rich. After inspection of the same figure 
-for every one of the thirty Auriga L4 haloes we find that the simulations produce
+for every one of the $30$~Auriga L4 haloes we find that the simulations produce
 (sub)populations of GC candidates that are more metal-rich than the MW and M31 GCSs.
@@
         showing the metal-rich (metal-poor) component of the MW (separated at
-        [Fe/H] = -1 as indicated by the vertical dotted magenta line).
+        [Fe/H] = -1 as indicated by the purple dotted vertical line).
         \label{fig:FeH_mu_sigma}
@@
 
-We show the mean metallicity and standard deviation of all thirty Auriga L4 haloes
+We show the mean metallicity and standard deviation of all $30$~Auriga L4 haloes
 in Figure~\ref{fig:FeH_mu_sigma} to illustrate the behaviour for the full set of Auriga
@@
 % {\it in~situ}, and accreted) are drawn from the same underlying distribution 
-% by calculating the KS test statistic (i.e. six KS tests per simulation). We 
+% by calculating the KS test statistic (i.e. $6$ KS tests per simulation). We 
 % reject $H_0$ at the 100.00~\% confidence level for virtually all subsets of all 
@@
 a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
-median for all thirty Auriga L4 haloes with the 25-75 percentile range 
+median for all $30$~Auriga L4 haloes and the 25-75 percentile range 
 (shaded regions, which shows the scatter between runs that have different initial 
@@
         Mean and standard deviation of the logarithm of radial distribution 
-        of star particles in each of the thirty Auriga L4 haloes compared to
+        of star particles in each of the $30$~Auriga L4 haloes compared to
         the MW (M31) GCS shown in purple (magenta). The Auriga (M31) radii are 
@@
     \caption{
-        Mass-weighted [Fe/H]-$r_{\text{gal}}$ distribution of all thirty Auriga
+        Mass-weighted [Fe/H]-$r_{\text{gal}}$ distribution of all $30$~Auriga
         L4 haloes. Here we consider only the GC candidates and color-code by the 
@@
 simulation), then we calculate the median total mass in each bin over all 
-thirty Auriga L4 haloes. The result is shown in Figure~\ref{fig:Au-FeHRgc}, which 
+$30$~Auriga L4 haloes. The result is shown in Figure~\ref{fig:Au-FeHRgc}, which 
 can be compared to the observed total GC mass shown in 
@@
 (and M31). We use a diverging colour map centered around the overall median of the 
-mass ratio (i.e. we subtract the median of these twenty-five bins from the value 
+mass ratio (i.e. we subtract the median of these $25$ bins from the value 
 in each bin). We show this in the top (bottom) panel of Figure~\ref{fig:Au-FeHRgc-ratio}.
@@
 afford to lose' is roughly a factor $480$ and $50$ for the MW and M31, respectively. 
-The lowest mass surplus for both galaxies is the bin where $-2.5 <$ [Fe/H] 
-$< -1.5$ and $3 < r_{\text{gal}}/\text{kpc} < 8$, for which the simulations produce 
+The lowest mass surplus for both galaxies is the bin with metallicities in the range
+[Fe/H]~$\in [-2.5, -1.5]$ and gallactocentric radius $r_{\text{gal}}\in [3,8]$~kpc,
+for which the simulations produce 
 a factor $10^{2.68}/10^{1.33} \approx 22$ and $10^{1.69}/10^{0.75} \approx 9$ 
@@
 $T^n_{\text{red}} \sim 5$, and therefore conclude that the formation efficiency
-of metal-poor GCs is twenty times higher than the metal-rich GCs with respect to 
+of metal-poor GCs is 20 times higher than the metal-rich GCs with respect to 
 field stars. We find that a gradual increase in formation efficiency of GCs

### 2020-04-06 response_to_referee.tex
Response to first point in introduction of referee report

@@
 \section*{Introduction (of referee report)}
+The following listing shows our reponse to the 3 paragraphs in the introduction
+of the referee report.
+\begin{enumerate}
+\item We updated the abstract to clarify that we meant to describe what would
+be needed for the environmental dependence of the formation and disruption of
+bound clusters for the Auriga simulations to be consistent with the observations,
+rather than to argue that the Auriga simulations reflect these trends.
+\item
 ``The results of the paper clearly demonstrate that the technique of simulating
@@
 but we limit the scope to the Auriga simulations. 
+\end{enumerate}
 
@@
 \begin{itemize}
-\item Numerical quantities are now described in arabic numbers, not words.
+\item Numerical quantities are now described in arabic numbers instead of words.
+\item We now first use the name of the physical quantities in the given example,
+    followed by the symbolic representation.
 \item TODO: parenthesis
-\item
+\item Colloquial expressions have been rephrased.
 \item We replaced `Sec.' by `Section' to refer to sections in the present work.
@@
 \begin{itemize}
-\item Item
+\item TODO: add a paragraph in introduction to justify why we consider metallicity
+and galactocentric radius.
+\item TODO: justify age cut instead of using a more elaborate selection function.
 \end{itemize}
@@
 \begin{itemize}
+\item TODO justify the modelling philosophy.
+\item TODO: clarify why observational data has different numbers
 \item We normalise the Auriga simulations by the virial radius of the
@@
 The mean virial radius of Auriga L4 is 299.67 $\pm$ 19.41 kpc.
-\item Item
+
 \end{itemize}

### 2020-04-06 AurigaGCS.tex
Response to first point in introduction of referee report

@@
 produce sufficient stellar mass for GC candidates at radii and metallicities that 
-are typical for the MW GC system (GCS). We do observe varying mass-ratios of the
+are typical for the MW GC system (GCS). We also find varying mass-ratios of the
 simulated GC candidates relative to the observed mass in the MW and M31 GC systems
 for different bins of galactocentric radius-metallicity ($r_{\text{gal}}$-[Fe/H]).
-This may imply that different values for the combined product of the bound cluster 
-formation efficiency and the GC disruption rate are needed. Overall, the Auriga 
+Overall, the Auriga 
 simulations produce GC candidates with higher metallicities than the MW and M31 
-GCS and they are found at larger radii than observed. Bound cluster formation
-efficiencies higher than ten percent are needed for the metal-poor GC candidates,
-and those within the Solar radius should experience negligible destruction rates.
+GCS and they are found at larger radii than observed. The Auriga simulations would
+require bound cluster formation efficiencies higher than ten percent for the 
+metal-poor GC candidates, and those within the Solar radius should experience 
+negligible destruction rates to be consistent with observations.
 GC candidates in the outer halo, on the other hand, should either have low formation

### 2020-04-06 AurigaGCS.tex
Refer to Sections 3.3, 3.4, 3.5 in first paragraph of Section 3. Thank referee for thoughtful and elaborate report.

@@
 We describe the observations of the MW GCS in Section~\ref{sec:milkyway},
-and of the M31 GCS in Section~\ref{sec:andromeda}
+and of the M31 GCS in Section~\ref{sec:andromeda}. We discuss the age-estimates
+in Section~\ref{sec:age}, the distribution of galactocentric radius in 
+Section~\ref{sec:Rgc}, and the total mass in 2D bins of metallicity-galactocentric
+radius in Section~\ref{sec:observations_FeHRgc}. We focus on metallicity and
+galactocentric radius because these data are available in the observations and
+in the Auriga simulations.
 
@@
 \subsection{Age-estimates}
+\label{sec:age}
 The top panel of Figure~\ref{fig:MW-M31-age-Rgc} shows a histogram of the age-estimates
@@
 
-\subsection{Total GC mass in metallicity-radial space} \label{sec:observations_FeHRgc}
+\subsection{Total GC mass in metallicity-radial space} 
+\label{sec:observations_FeHRgc}
 We show the two-dimensional mass-weighted metallicity-radial distribution of the
@@
 \section*{Acknowledgements}
+We thank the anonymous referee for a thoughtful and elaborate report that we feel
+greatly improved the manuscript.
 TLRH acknowledges support from the International Max-Planck Research School (IMPRS)

### 2020-04-06 response_to_referee.tex
Refer to Sections 3.3, 3.4, 3.5 in first paragraph of Section 3. Thank referee for thoughtful and elaborate report --> diff and response

@@
 \section*{Introduction (of referee report)}
-The following listing shows our reponse to the 3 paragraphs in the introduction
-of the referee report.
+We thank the referee for a thoughtful and elaborate report that we feel greatly
+improved the manuscript. We address the comments in sections with names that match
+the headings of the referee report, starting with the following listing of our 
+response to the 3 paragraphs in the introduction.
 \begin{enumerate}
-\item We updated the abstract to clarify that we meant to describe what would
-be needed for the environmental dependence of the formation and disruption of
-bound clusters for the Auriga simulations to be consistent with the observations,
+\item We updated the abstract and conclusion to clarify that we meant to describe
+what would be needed for the environmental dependence of the formation and disruption
+of bound clusters for the Auriga simulations to be consistent with the observations,
 rather than to argue that the Auriga simulations reflect these trends.
 \item
-``The results of the paper clearly demonstrate that the technique of simulating
-stellar clusters in cosmological hydrodynamical simulations by tagging stellar
-particles based on their ages does not reproduce key properties of observed GC 
-systems in the Milky Way and M31. However, the authors do not state this conclusion
-anywhere''.
-
 We feel that our conclusion would be too strongly phrased if we would generalise 
 our results obtained using the Auriga simulations to cosmological simulations 
-in general. Indeed, we do find that age-selected stellar particles do not 
-reproduce key properties of observed GC systems in the Milky Way and M31. However,
-our results might reflect characteristics that are specific to Auriga, 
+in general. We find that age-selected stellar particles in the Auriga simulations 
+do not reproduce key properties of observed GC systems in the Milky Way and M31.
+However, our results might reflect characteristics that are specific to Auriga, 
 e.g. that the galaxy formation model overmixes metals at early times. 
 Therefore we did add a final bulletpoint to our conclusion to clarify the above, 
-but we limit the scope to the Auriga simulations. 
+but we limit the scope to the Auriga simulations. Thanks for pointing this out!
+
+Furthermore, we clarified in the manuscript that we investigate the metallicity
+and galactocentric radius because these properties are available for the observed
+GC systems and in the simulations.
 \end{enumerate}

### 2020-04-06 AurigaGCS.tex
First removal of parenthesis to improve readability

@@
 in Figure~\ref{fig:FeH_mu_sigma} to illustrate the behaviour for the full set of Auriga
-galaxies. The beige crosses are to be compared to the purple (magenta) cross, 
-which shows the mean value of all MW (M31) GCs. In addition, we show the metal-rich 
-(metal-poor) population of the MW GCS using a solid (open) dot. We caution that
+galaxies. The beige crosses are to be compared to the purple and magenta cross, 
+which shows the mean value of all MW and M31 GCs, respectively. In addition, we 
+show the metal-rich population of the MW GCS using a solid dot, and the metal-poor
+population with an open dot. We caution that
 these literature values result from individual Gaussian fits to sub sets of the 
@@
 of the GC candidates is dominated by the {\it in~situ} subpopulation above
-[Fe/H]~=~$-1$, and by the accreted subset below this value. We show the MW (M31) 
-GCS in purple (magenta) and notice that the difference between the MW and M31 
-distributions is substantially larger than the scatter between different Auriga 
-galaxies, particularly around [Fe/H]~$=-1$. In addition, M31 does host 
+[Fe/H]~=~$-1$, and by the accreted subset below this value. We show the MW GCS 
+in purple and that of M31 in magenta, and notice that the difference between the 
+MW and M31 distributions is substantially larger than the scatter between different 
+Auriga galaxies, particularly around [Fe/H]~$=-1$. In addition, M31 does host 
 (a handful of) GCs with [Fe/H]~$< -2.5$ as well as GCs with [Fe/H]~$ > 0$ while 

### 2020-04-06 response_to_referee.tex
First removal of parenthesis to improve readability
Reduce usage of parenthesis

@@
 
-\section*{Introduction (of referee report)}
+\section*{Introduction}
 We thank the referee for a thoughtful and elaborate report that we feel greatly
@@
 GC systems and in the simulations.
+\item TODO: disussion of implications for wider context.
 \end{enumerate}
@@
     followed by the symbolic representation.
-\item TODO: parenthesis
+\item The text has been updated to reduce the usage of parenthesis.
 \item Colloquial expressions have been rephrased.

### 2020-04-06 AurigaGCS.tex
Reduce usage of parenthesis

@@
 \documentclass[a4paper,fleqn,usenatbib]{mnras}
+% \hypersetup{draft}
 
@@
 
+\newpage  % to prevent reference split over two pages which breaks LaTeX
 Yet another hypothesis is that star cluster formation is triggered by major 
@@
 lines) and find that the MW has more GCs in the range $1-4$~kpc than M31
-(when accounting for the larger number of total GCs in M31). Interestingly, both
+when accounting for the larger number of total GCs in M31. Interestingly, both
 distributions show a similar trend for $r_{\text{gal}} > 4$~kpc and host a 
@@
 We show the two-dimensional mass-weighted metallicity-radial distribution of the
-MW (M31) GCS in the top (bottom) panel of Figure~\ref{fig:observations_FeHRgc}. 
-The observations indicate that
+MW and the M31 GCS in the top and bottom panel of Figure~\ref{fig:observations_FeHRgc},
+respectively. The observations indicate that
 no GCs with high metallicities are to be expected at large radii (the three bins
@@
 a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
-median for all $30$~Auriga L4 haloes and the 25-75 percentile range 
-(shaded regions, which shows the scatter between runs that have different initial 
-conditions, thus, have unique merger histories). We chose to aggregate the data 
+median for all $30$~Auriga L4 haloes and the 25-75 percentile range as shaded regions, 
+which shows the scatter between runs that have different initial 
+conditions, thus, have unique merger histories. We chose to aggregate the data 
 to indicate general trends that we find when the GC candidates are split up into
@@
 
-We show the ratio of the  simulated to the observed profiles in the middle (bottom) 
-panel. This mass excess can be thought of the `mass budget' that the Auriga GC 
+We show the ratio of the  simulated to the observed profiles in the middle and bottom
+panels. This mass excess can be thought of the `mass budget' that the Auriga GC 
 candidates can `afford to lose' due to a combination of smaller than unity bound
@@
 standard deviation of $\log_{10}(r_{\text{gal}})$ of star particles in all Auriga
-L4 simulations. The purple (magenta) cross again shows the mean of the MW (M31)
-GCs (which are to be compared to the beige crosses), but solid (open) dot now
-shows our calculation of the mean value of the `red' metal-rich (`blue` metal-poor) 
-population. We split the radii up into the metal-rich/metal-poor groups by taking
-a metallicity cut at [Fe/H]~=~-1 as is done in the literature.
+L4 simulations, respectively. The purple and magenta cross again shows the mean 
+of the MW and M31 GCs, which are to be compared to the beige crosses. The solid
+dot now shows our calculation of the mean value of the `red' metal-rich population,
+and the open dot that of the `blue` metal-poor population. We split the radii 
+up into the metal-rich/metal-poor groups by taking a metallicity cut at 
+[Fe/H]~=~-1 as is done in the literature.
 
@@
 To ease this comparison between the simulations and observations we take the ratio
-of the total mass of GC candidates in Auriga to the total GC mass in the MW 
-(and M31). We use a diverging colour map centered around the overall median of the 
+of the total mass of GC candidates in Auriga to the total GC mass in the observations.
+We use a diverging colour map centered around the overall median of the 
 mass ratio (i.e. we subtract the median of these $25$ bins from the value 
-in each bin). We show this in the top (bottom) panel of Figure~\ref{fig:Au-FeHRgc-ratio}.
-Note that the data in the three top right bins is masked because the mass ratio cannot 
-be calculated due to zero mass in the observations (therefore the bins are white).
+in each bin). We show this in the top and bottom panel of Figure~\ref{fig:Au-FeHRgc-ratio}
+for the MW and M31, respectively. Note that the 3 bins in the top right are empty (white)
+because the mass ratio cannot be calculated due to zero mass in the observations.
 If the product of the bound cluster formation efficiency and consecutive GC 
 disruption over a Hubble time would be constant, then the value in each bin would
-have been zero. The red and blue bins indicate deviations from such a scenario and
+be zero. The red and blue bins indicate deviations from such a scenario and
 indicate a higher and lower than average mass excess in the simulations. The median 

### 2020-04-07 AurigaGCS.tex
quantity T --> specific frequency. Add 1 reference to justify modeling philosophy

@@
 in CR16. The mean age of the MW GCs in this data set is $11.9 \pm 0.1$~Gyr and the 
-dispersion is $0.8$~Gyr. Furthermore, only one of the 55 GC age-estimates is
+dispersion is $0.8$~Gyr. Furthermore, only 1 of the 55 GC age-estimates is
 below $10$~Gyr. The M31 GCS has a mean age of $11.0 \pm 0.2$~Gyr with a dispersion 
@@
 than $10$~Gyr based on the age distribution of the MW GCS (top panel of 
-Figure~\ref{fig:MW-M31-age-Rgc}), and following \citet{2017MNRAS.465.3622R}.
+Figure~\ref{fig:MW-M31-age-Rgc}), adopting the definition of 
+\citet{2010ARA&A..48..431P} and following the method of 
+\citet{2017MNRAS.465.3622R}. However, we caution that his definition does exclude 
+1 GC in the MW and 24 in M31 as stated in Section~\ref{sec:age}.
 
@@
 Finally, we note that \citet{2006ARA&A..44..193B} compares the number of metal-poor 
-GCs to the stellar halo mass and find\footnote{The quantity $T$ is the number of 
-GCs per $10^9$ M\Sun \, of galaxy stellar mass.} $T^n_{\text{blue}} \sim 100$, 
+GCs to the stellar halo mass and find\footnote{The specific frequency $T$ is 
+the number of GCs per $10^9$ M\Sun \, of galaxy stellar mass.} $T^n_{\text{blue}} \sim 100$, 
 while the number of metal-rich GCs compared to the bulge mass yields 
@@
 \section*{Acknowledgements}
-We thank the anonymous referee for a thoughtful and elaborate report that we feel
-greatly improved the manuscript.
+We thank the anonymous referee for a thoughtful and elaborate report.
 TLRH acknowledges support from the International Max-Planck Research School (IMPRS)

### 2020-04-07 AurigaGCS.tex
Add -trim to all figures

@@
     \includegraphics[width=\columnwidth]
-        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
+        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data-trim}.png}
     \centering \textcolor{lightgray}{\rule[2mm]{\columnwidth}{0.05mm}}
     \includegraphics[width=\columnwidth]
-        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data}.png}
+        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data-trim}.png}
     \caption{
@@
 \begin{figure}
-    \includegraphics[width=\columnwidth]{{FeH_obs_Au4-4_Au4-10_Au4-21}.png}
+    \includegraphics[width=\columnwidth]{{FeH_obs_Au4-4_Au4-10_Au4-21-trim}.png}
     \caption{

### 2020-04-07 AurigaGCS_20190905.tex
Change filenames in AurigaGCS_20190905.tex to prevent latexdiff to break changed filenames ...

--- 2019-08-20 AurigaGCS_20190820.tex
@@
 simulated GC candidates relative to the observed mass in the MW and M31 GC systems
-for different bins of galactocentric radius-metallicity ($R_{\text{gal}}$-[Fe/H]).
-This implies that different values for the combined product of the bound cluster 
+for different bins of galactocentric radius-metallicity ($r_{\text{gal}}$-[Fe/H]).
+This may imply that different values for the combined product of the bound cluster 
 formation efficiency and the GC disruption rate are needed. Overall, the Auriga 
@@
     \includegraphics[width=\columnwidth]
-        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
+        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data-trim}.png}
     \centering \textcolor{lightgray}{\rule[2mm]{\columnwidth}{0.05mm}}
     \includegraphics[width=\columnwidth]
-        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data}.png}
+        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data-trim}.png}
     \caption{
-        \emph{Top}: Mass-weighted $R_{\text{gal}}$-[Fe/H] distribution of
+        \emph{Top}: Mass-weighted $r_{\text{gal}}$-[Fe/H] distribution of
         151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H},
@@
         Mass-weighted radial distribution of star particles in the Auriga
-        L4 simulations. We show the median value of all Auriga haloes for all
+        L4 simulations, where the Auriga (M31) radii are again divided by 
+        $r_{\text{vir,Au}}$ ($r_{\text{vir,M31}}$) and multiplied by 
+        $r_{\text{vir,MW}}$. We show the median value of all Auriga haloes for all
         stars (green dotted) and GC candidates (i.e. stars with
@@
 We investigate whether the Auriga simulations still produce sufficient mass when
-the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{gal}$. First
+the GC candidates are two-dimensionally binned in [Fe/H] and $r_\text{gal}$. First
 we sum the total mass of GC candidates in each bin (for an individual Auriga 
@@
 The lowest mass surplus for both galaxies is the the bin where $-2.5 <$ [Fe/H] 
-$< -1.5$ and $3 < R_{\text{gal}}/\text{kpc} < 8$, for which the simulations produce 
+$< -1.5$ and $3 < r_{\text{gal}}/\text{kpc} < 8$, for which the simulations produce 
 a factor $10^{2.68}/10^{1.33} \approx 22$ and $10^{1.69}/10^{0.75} \approx 9$ 
@@
 We now focus on four quadrants of this diagram, split at [Fe/H]~=~-1 (metal-poor 
-or metal-rich) and $R_\text{gal}$~=~8~kpc (inside or outside the Solar radius).
+or metal-rich) and $r_\text{gal}$~=~8~kpc (inside or outside the Solar radius).
 The majority of the mass in Auriga GC candidates is produced in metal-rich star
 particles inside the Solar radius. The total mass is dominated by the {\it in situ} 
-component, for [Fe/H] as well as for $R_\text{gal}$. The total mass excess in 
+component, for [Fe/H] as well as for $r_\text{gal}$. The total mass excess in 
 this region increases with decreasing metallicity for the MW and M31, and there
@@
 
-    \item GC candidates in the Auriga simulations may be found out to $R_{200}$,
+    \item GC candidates in the Auriga simulations may be found out to $r_{200}$,
     given that our selection function of star particles selects all stars bound

### 2020-04-08 response_to_referee.tex
quantity T --> specific frequency. Add 1 reference to justify modeling philosophy
Added two TODOs

@@
 \section*{Introduction}
-We thank the referee for a thoughtful and elaborate report that we feel greatly
-improved the manuscript. We address the comments in sections with names that match
+We thank the referee for a thoughtful and elaborate report. We address the 
+comments in sections with names that match
 the headings of the referee report, starting with the following listing of our 
@@
 galaxies with little correlation between these different stellar length scales.
-The mean virial radius of Auriga L4 is 299.67 $\pm$ 19.41 kpc.
+The mean virial radius of Auriga L4 is 299.67 $\pm$ 19.41 kpc. TODO
+\item TODO: Discussion on the implications for the formation and evolution of clusters
+    often feels a bit out of place and forced
 

### 2020-04-08 response_to_referee.tex
Other major comments

@@
 and galactocentric radius.
-\item TODO: justify age cut instead of using a more elaborate selection function.
+\item We added section 5.3 to discuss how our results change of we adopt an age cut
+of 8 or 6 Gyr.
 \end{itemize}
@@
 \item TODO justify the modelling philosophy.
-\item TODO: clarify why observational data has different numbers
+\item We added a section 5.3 to discuss how our results change if we adopt an
+age cut of 8 or 6 Gyr instead of 10 Gyr.
+\item We clarified that the number of observed GCs differs between Figure 1 and 
+Figure 2 because the latter shows metallicities between -2.5 and 0, galactocentric 
+radii between 1 and 250 kpc. Figure 1, on the other hand, shows the full range
+of radii, and the top panel of Figure 3 shows the full range of metallicities.
 \item We normalise the Auriga simulations by the virial radius of the
@@
 or vertical scaleheight of the disk, the optical radius, the extent of the stellar 
-halo, etc). The simulations show a wide variety between properties of the Auriga
-galaxies with little correlation between these different stellar length scales.
-The mean virial radius of Auriga L4 is 299.67 $\pm$ 19.41 kpc. TODO
-\item TODO: Discussion on the implications for the formation and evolution of clusters
-    often feels a bit out of place and forced
+halo, the half-mass stellar radius, etc). The simulations show a wide variety 
+between properties of the Auriga galaxies with little correlation between these 
+different stellar length scales. Therefore we could introduce unknown biases by 
+normalising to any one of these options which is why we use the virial radius instead.
+\item TODO: ``Discussion on the implications for the formation and evolution of clusters
+    often feels a bit out of place and forced.''
 

### 2020-04-08 AurigaGCS.tex
Other major comments

@@
 MW and the M31 GCS in the top and bottom panel of Figure~\ref{fig:observations_FeHRgc},
-respectively. The observations indicate that
+respectively. Note that the number of GCs is different than in 
+Figure~\ref{fig:MW-M31-age-Rgc} because here we plot [Fe/H] between -2.5 and 0 
+and $r_{\text{gal}}$ between 1 and 250 kpc whereas Figure~\ref{fig:MW-M31-age-Rgc}
+shows the full range of metallicities and radii.
+
+The observations indicate that
 no GCs with high metallicities are to be expected at large radii (the three bins
@@
         $r_{\text{vir,M31}}$ and multiplied by $r_{\text{vir,MW}}$. Note that the 
-        range of the colourmap differs in both figures. 
+        range of the colourmap differs in both figures,
         \label{fig:observations_FeHRgc}
@@
 than $10$~Gyr based on the age distribution of the MW GCS (top panel of 
-Figure~\ref{fig:MW-M31-age-Rgc}), adopting the definition of 
+Figure~\ref{fig:MW-M31-age-Rgc}), adopting the definition of a GC from
 \citet{2010ARA&A..48..431P} and following the method of 
 \citet{2017MNRAS.465.3622R}. However, we caution that his definition does exclude 
-1 GC in the MW and 24 in M31 as stated in Section~\ref{sec:age}.
+1 GC in the MW and 24 in M31 as stated in Section~\ref{sec:age}, and further
+discuss this in Section~\ref{sec:age_min}.
 
@@
 % cluster formation description is not compatible with observations.''
+
+\subsection{Lower age cut in the GC selection function}
+\label{sec:age_min}
+Our method is sensitive to the definition that we adopt to classify GC candidates
+\citep{2010MNRAS.404.1203F}. Therefore we explore how our results change if we 
+include all star particles older than 8 Gyr, and if we further lower the age cut 
+to 6 Gyr.
+
+We find that including more recently formed star particles in our subset 
+of GC candidates shifts the mean metallicity to higher values. Moreover, the
+total mass in metal-rich ([Fe/H] > -1) GC candidates increases for a lower age 
+threshold and moves closer to the dotted line that shows the distribution of
+all star particles. However, we notice that the Auriga simulations, on average, 
+do not form new stars with a metallicity below [Fe/H] = -1 more recent than 6 Gyr 
+ago: the behaviour of Figure~\ref{fig:FeH} does not change for metallicities
+below [Fe/H] = -1 when we change the age cut to 8 or 6 Gyr. The qualitative behaviour
+of the median distribution of galactocentric radii (Figure~\ref{fig:Rgc}), on 
+the other hand, is unaffected by lowering the age cut other than including
+more star particles (more mass) which leads to a higher normalisation and
+a higher mass ratio with respect to the observed GC systems of the MW and M31.
+The qualitative behavour presented in Figure~\ref{fig:Au-FeHRgc-ratio} does not 
+change when the age cut is lowered to 8 or 6 Gyr.
 

### 2020-04-08 response_to_referee.tex
Comments on Section 2
Comments on Section 3

@@
 \begin{itemize}
-\item Item
+\item We added the halo mass range of the Auriga simulations.
+\item The last paragraph should now make more sense after updating the introduction.
 \end{itemize}
@@
 \begin{itemize}
-\item Item 
+\item We added references to section 3.3, 3.4, and 3.5 in the first paragraph of section 3.
+\item Section 3.2 has been restructured.
+\item We removed the standard error on the mean and replaced `dispersion' 
+by `standard deviation' in section 3.3.
+\item We added a sentence to clarify the last statement in section 3.4.
 \end{itemize}

### 2020-04-08 AurigaGCS.tex
Comments on Section 2
Comments on Section 3

@@
 high-resolution cosmological zoom simulations of MW analogues. The MW-mass
-selected initial conditions were selected from the \mbox{\textsc{eagle}} DM only 
-box, see \citetalias{2017MNRAS.467..179G} for details. The simulations are 
+selected initial conditions in the range $1-2 \times 10^{12}$~M$_{\odot}$
+were selected from the \mbox{\textsc{eagle}} DM only box, see 
+\citetalias{2017MNRAS.467..179G} for details. The simulations are 
 performed with the \textsc{arepo} code \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} 
@@
 \label{sec:andromeda}
-The fifth revision of the revised Bologna catalogue (RBC~5, last updated
-August, 2012) is the latest edition of three decades of systematically
-collecting integrated properties of the GCS of M31 \citep[][and references therein]{2004A&A...416..917G}. One
-contribution to RBC~5 is the work by \citet[][hereafter C11]{2011AJ....141...61C},
-subsequently updated by \citet[][hereafter CR16]{2016ApJ...824...42C}.
-
-C11 and CR16 present a uniform set of spectroscopic observations calibrated
-on the MW GCS of the inner $1.6^\circ~({\sim}21)$~kpc that
-is believed to be 94\% complete. GCs in the outer stellar halo, up to
-$r_{\text{proj}}\sim150$~kpc, are observed in the Pan-Andromeda Archaeological
-Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H}, but see also
-\citet{2014MNRAS.442.2929V} and \citet{2019MNRAS.484.1756M}. H14 presents the
-discovery of 59 new GCs and publishes updates to RBC~5. The work of H14 is
-incorporated in the latest public release\footnote{Last revised 23 Sep 2015, see
-\url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}}
-of the C11 dataset, further revised by CR16. We use CR16 because it is the most
-recent aggregated dataset of M31's GCS that contains properties of interest
-for our study and it includes GCs in the inner region and in the outer halo. The
-relevant fields in the CR16 dataset that we use are the age, metallicity, and the
-mass-estimate\footnote{The authors assumed $M/L_V = 2$ independent of [Fe/H]}.
-Radii are calculated from RA and DEC, further discussed in Sec.~\ref{sec:Rgc}.
+\citet[][hereafter C11]{2011AJ....141...61C} and \citet[][hereafter CR16]{2016ApJ...824...42C}
+present a uniform set of spectroscopic observations of the inner 
+$1.6^\circ~({\sim}21)$~kpc of M31 that is believed to be 94\% complete. In addition,
+the outer stellar halo of M31 up to $r_{\text{proj}}\sim150$~kpc is observed in 
+the Pan-Andromeda Archaeological Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H,
+2014MNRAS.442.2929V, 2019MNRAS.484.1756M}. In fact, 
+the work of H14 is incorporated in the latest public release\footnote{Last 
+revised 23 Sep 2015, see \url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}}
+of the C11 and CR16 data sets. Therefore we use the latest data set of CR16 
+because it is the most recent aggregated dataset of M31's GCS that contains GCs 
+in the inner region and in the outer halo. The relevant fields in the CR16 dataset 
+that we use are the age, metallicity, and the mass-estimate\footnote{The authors 
+assumed $M/L_V = 2$ independent of [Fe/H]}. We calculate the galactocentric radii 
+from the observed positions RA and DEC, further discussed in Sec.~\ref{sec:Rgc}.
 
@@
 of the $55$ MW GCs in V13 and $88$ GCs in M31 for which age-estimates are available
-in CR16. The mean age of the MW GCs in this data set is $11.9 \pm 0.1$~Gyr and the 
-dispersion is $0.8$~Gyr. Furthermore, only 1 of the 55 GC age-estimates is
-below $10$~Gyr. The M31 GCS has a mean age of $11.0 \pm 0.2$~Gyr with a dispersion 
+in CR16. The mean age of the MW GCs in this data set is $11.9$~Gyr and the 
+standard deviation is $0.8$~Gyr. Furthermore, only 1 of the 55 GC age-estimates is
+below $10$~Gyr. The M31 GCS has a mean age of $11.0$~Gyr with a standard deviation 
 of $2.2$~Gyr, and $24$ GCs have age-estimates below $10$~Gyr with a minimum age 
@@
 distributions show a similar trend for $r_{\text{gal}} > 4$~kpc and host a 
-subpopulation of halo GCs. However, the two radial distributions are not statistically
-consistent with being drawn from the same underlying distribution due to substantial 
-differences at intermediate radii.
+subpopulation of halo GCs. Our naive expectation would be that the spiral galaxies
+in the Local Group host similar GC systems. However, the radial distributions of
+the GCS of the MW and M31 are not statistically consistent with being drawn from 
+the same underlying distribution due to substantial differences at intermediate radii.
 

### 2020-04-09 AurigaGCS.tex
Specify the number of star particles in each of the subsets

@@
 candidates (age $>10$~Gyr) with those of all star particles (i.e.
-when no additional selection criterion is applied). We further split the GC
+when no additional selection criterion is applied). The mean number of star 
+particles in the Auriga L4 simulations that we select as GC candidates is 
+$3.1 \cdot 10^5$ (with a mean mass of $1.15 \cdot 10^{10}$ M$_{\odot}$), 
+and the mean number of all star particles is $1.93 \cdot 10^6$ 
+($7.3\cdot10^{10}$ M$_{\odot}$). The subset of GC candidates is thus around 
+15\% of all the stars in the galaxy. We further split the GC
 candidates into an {\it in~situ} subset (defined as GC candidates that are 
@@
         formed {\it in~situ} (brown), and those that have been accreted (teal).
+        The numbers in parenthesis show how many star particles are included 
+        in the subset.
         \label{fig:Au4-10and21_FeH}
@@
 different distributions. We show the age-selected GC candidates as well as the 
-accreted and {\it in~situ} subsets. The top panel of Figure~\ref{fig:Au4-10and21_FeH} shows the MW 
+accreted and {\it in~situ} subsets. 
+:/The top panel of Figure~\ref{fig:Au4-10and21_FeH} shows the MW 
 and M31 GCSs, where we overplot a double Gaussian for the MW GCS by 

### 2020-04-09 response_to_referee.tex
Specify the number of star particles in each of the subsets
Show the median of the galactocentric radius in section 4.2 and Figure 6

@@
 \begin{itemize}
-\item
+\item We added the mean number of GC candidates compared to the mean number of
+star particles in the Auriga L4 galaxies. In addition, Figure 3 now shows the 
+number of star particles included in the subset.
+\item We clarified at various places whether we mean the mean or median among
+the simulations, or if we refer to the absolute value of one of the galaxies.
 \item Figure 4 - now has a vertical line to indicate the metallicity cut 
@@
 \item
-\item
+\item We now show the median instead of the mean for the galactocentric radius in
+section 4.2 and Figure 6.
 \item Figure 6: no changes were made for rescaling the galaxies (i.e. we still

### 2020-04-09 AurigaGCS.tex
Show the median of the galactocentric radius in section 4.2 and Figure 6

--- 2020-04-08 AurigaGCS.tex
@@
 candidates (age $>10$~Gyr) with those of all star particles (i.e.
-when no additional selection criterion is applied). We further split the GC
+when no additional selection criterion is applied). The mean number of star 
+particles in the Auriga L4 simulations that we select as GC candidates is 
+$3.1 \cdot 10^5$ (with a mean total mass of $1.15 \cdot 10^{10}$ M$_{\odot}$), 
+and the mean number of all star particles is $1.93 \cdot 10^6$ 
+($7.3\cdot10^{10}$ M$_{\odot}$). The subset of GC candidates is thus around 
+15\% of all the stars in the galaxy when averaged over all Auriga L4 haloes. 
+We further split the GC
 candidates into an {\it in~situ} subset (defined as GC candidates that are 
@@
 different distributions. We show the age-selected GC candidates as well as the 
-accreted and {\it in~situ} subsets. The top panel of Figure~\ref{fig:Au4-10and21_FeH} shows the MW 
+accreted and {\it in~situ} subsets. 
+The top panel of Figure~\ref{fig:Au4-10and21_FeH} shows the MW 
 and M31 GCSs, where we overplot a double Gaussian for the MW GCS by 
@@
 for which the {\it in~situ} subset has a lower mean metallicity instead. 
-\mbox{Au4-1} is undergoing a major merger at redshift zero and we find 
-$\mu = -1.51 \, ({-0.74})$ for the {\it in~situ} (accreted) GC candidates, 
-although the former consists of only $1019$ particles ($1.3$\% of all GC 
+\mbox{Au4-1} is undergoing a major merger at redshift zero and we find a mean
+metallicity in this simulations $\mu = -1.51 \, ({-0.74})$ for the {\it in~situ} 
+(accreted) GC candidates, although the former consists of only $1019$ particles 
+($1.3$\% of all GC 
 candidates, and with a total mass of $5 \times 10^{7}$~M\Sun). For \mbox{Au4-4}, 
@@
 We show the mean metallicity and standard deviation of all $30$~Auriga L4 haloes
-in Figure~\ref{fig:FeH_mu_sigma} to illustrate the behaviour for the full set of Auriga
-galaxies. The beige crosses are to be compared to the purple and magenta cross, 
-which shows the mean value of all MW and M31 GCs, respectively. In addition, we 
-show the metal-rich population of the MW GCS using a solid dot, and the metal-poor
-population with an open dot. We caution that
+in Figure~\ref{fig:FeH_mu_sigma} to illustrate the individual behaviour for the 
+full set of Auriga galaxies. The beige crosses are to be compared to the purple 
+and magenta cross, which shows the mean value of all MW and M31 GCs, respectively. 
+In addition, we show the metal-rich population of the MW GCS using a solid dot, 
+and the metal-poor population with an open dot. We caution that
 these literature values result from individual Gaussian fits to sub sets of the 
@@
 a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
-median for all $30$~Auriga L4 haloes and the 25-75 percentile range as shaded regions, 
+median over all the $30$~Auriga L4 haloes and the 25-75 percentile range as shaded regions, 
 which shows the scatter between runs that have different initial 
@@
 \begin{figure}
-    \includegraphics[width=\columnwidth]{{LogRgc_mu_sigma-trim}.png}
+    \includegraphics[width=\columnwidth]{{LogRgc_median_sigma-trim}.png}
     \caption{
-        Mean and standard deviation of the logarithm of radial distribution 
+        Median and standard deviation of the logarithm of radial distribution 
         of star particles in each of the $30$~Auriga L4 haloes compared to
@@
         the galaxies.
-        \label{fig:Rgc_mu_sigma}
+        \label{fig:Rgc_median_sigma}
     }
@@
 intrinsic sizes of the Auriga galaxies. We look for general trends present
-in all Auriga L4 galaxies. Figure~\ref{fig:Rgc_mu_sigma} shows the mean and 
+in all Auriga L4 galaxies. Figure~\ref{fig:Rgc_median_sigma} shows the median and 
 standard deviation of $\log_{10}(r_{\text{gal}})$ of star particles in all Auriga
-L4 simulations, respectively. The purple and magenta cross again shows the mean 
+L4 simulations, respectively. The purple and magenta cross show the median
 of the MW and M31 GCs, which are to be compared to the beige crosses. The solid
-dot now shows our calculation of the mean value of the `red' metal-rich population,
+dot now shows our calculation of the median value of the `red' metal-rich population,
 and the open dot that of the `blue` metal-poor population. We split the radii 
@@
 the MW GCS, while the dispersion of M31 seems to lie within the range of dispersions
-found in the Auriga galaxies. Furthermore, the mean of the MW GCS lies roughly 
-within the range of values produced by the Auriga simulations, whereas the mean 
-of M31 is somewhat larger and slightly closer to typical mean values of the 
+found in the Auriga galaxies. Furthermore, the median of the MW GCS lies roughly 
+within the range of values produced by the Auriga simulations, whereas the median
+of M31 is somewhat larger and slightly closer to typical median values of the 
 accreted GC candidates in the Auriga simulations. The larger radial extent 

### 2020-04-09 response_to_referee.tex
Done with Section 4

@@
 the simulations, or if we refer to the absolute value of one of the galaxies.
+\item We added the suggestion in the 3rd paragraph of section 4.1.
+\item Bimodality in GC systems is now discussed in the introduction.
 \item Figure 4 - now has a vertical line to indicate the metallicity cut 
 between metal-poor and metal-rich GC subpopulations in the Milky Way.
-\item
+\item We added a sentence about the cluster formation efficiency model of 
+Kruijssen (2012) in the last paragraph of section 4.1.
 \item We now show the median instead of the mean for the galactocentric radius in
@@
 \item Figure 5 and 7: shaded regions now show the 25-75th percentiles.
+\item We added a brief discussion of Figure 8.
+\item We clarified that we are referring to Figure 5 and Figure 7 for the claims about
+the {\it in situ} and accreted component in the third paragraph of section 4.3.
 \item Figure 9: The values are removed from the masked upper right corner bins.

### 2020-04-09 AurigaGCS.tex
Done with Section 4

@@
 to come to our conclusions in section~\ref{sec:conclusions}.
+
+TODO: ``\citet{2012MNRAS.426.1475U} shows the great variety in GC metallicity distributions
+present in the sample of early-type galaxies of the SLUGGS survey contradicts
+the classical idea that all the metallicity distributions of GCs should be bimodal.''
 
@@
 We find that the age cut, on average, lowers the mean metallicity $<$[Fe/H]$>$ from 
-$0.0$ to $-0.6$. Furthermore, accreted GC candidates generally have lower mean 
-metallicities than the {\it in~situ} subset with differences of roughly
+$0.0$ to $-0.6$. This reflects the enrichment history of the galaxy because the
+age cut neglects the more metal-rich stellar population which shifts the mean
+metallicity towards lower values. Furthermore, accreted GC candidates generally have
+lower mean metallicities than the {\it in~situ} subset with differences of roughly
 ${\sim}0.3$~dex for the majority of the simulation runs. This behaviour can be 
@@
 efficiency to form bound star clusters would have to decrease with increasing 
-metallicity.
+metallicity. This trend could be consistent with the cluster formation efficiency 
+model of \citet{2012MNRAS.426.3008K} as lower metallicity star particles formed 
+at earlier times when the bound cluster formation efficiencies are higher due
+to higher pressure birth environments.
 
@@
 can be compared to the observed total GC mass shown in 
-Figure~\ref{fig:observations_FeHRgc}.
+Figure~\ref{fig:observations_FeHRgc}. We notice that the simulations produce
+relatively little mass in metal-poor GC candidates at small radii and in metal-rich
+GC candidates at large radii. However, there is still few times $10^7$ M$_{\odot}$
+produced by the simulations in the uppermost 3 bins where no observed GCs are found.
 
@@
 particles inside the Solar radius. The total mass is dominated by the {\it in situ} 
-component, for [Fe/H] as well as for $r_\text{gal}$. The total mass excess in 
+component, for [Fe/H] as well as for $r_\text{gal}$ as can be seen in Figure~\ref{fig:FeH}
+and Figure~\ref{fig:Rgc}. The total mass excess in 
 this region increases with decreasing metallicity for the MW and M31, and there

### 2020-04-10 AurigaGCS.tex
Added Deason+ 2015, Conroy+ 2019 to comment about stellar halo

@@
 GCs, then the GC disruption rate would have to be considerably higher than expected
-from theoretical models. Overall, our set of GC candidates most likely contains
+from theoretical models. Moreover, disrupted dwarf galaxies are more likely to 
+contribute to the build up of the stellar halo than GCs \citep[e.g.][]{2015MNRAS.448L..77D, 
+2019ApJ...887..237C}. Overall, our set of GC candidates most likely contains
 an overabundance of regular stars. It could be that the resulting metallicity
@@
 Our method is sensitive to the definition that we adopt to classify GC candidates
-\citep{2010MNRAS.404.1203F}. Therefore we explore how our results change if we 
+\citep[e.g.][]{2018RSPSA.47470616F}. Therefore we explore how our results change if we 
 include all star particles older than 8 Gyr, and if we further lower the age cut 
-to 6 Gyr.
+to 6 Gyr. The average fraction of GC candidates that we select from the all the
+star particles increases to 35\% and 55\% for an age cut of 8 and 6 Gyr, respectively.
 

### 2020-04-10 response_to_referee.tex
Added Deason+ 2015, Conroy+ 2019 to comment about stellar halo
Half-ass the remarks for Section 5 and 6

@@
 \begin{itemize}
-\item Item
+\item TODO: overall comment
+\item We added references to Deason et al. (2015) and Conroy et al. (2019) in
+the first paragraph of section 5.1.
+\item TODO: bimodality in SLUGGS
+\item We still find that the accreted star particles are more metal-poor than 
+those that have formed {\textit in situ} if we lower the age cut to 8 or 6 Gyr.
+This has been added in section 5.3.
+\item We removed the quoted sentence.
+\item We clarified that our selection function is inconsistent with the definition
+of Kruijssen (2019) for {\textit ex. situ} GC formation.
+\end{itemize}
+
+\subsection*{Sect. 6 -}
+\begin{itemize}
+\item We repeat the goal of the study in section 6.
+\item We clarified the 4th point.
 \end{itemize}

### 2020-04-10 AurigaGCS.tex
Half-ass the remarks for Section 5 and 6

@@
 factor $2-3$ larger than the offset that we find between the {\it in~situ} and 
-accreted populations. The Auriga simulations therefore do not support the view 
-that the metal-poor GCs could have only formed in satellites that have later been 
-accreted whereas the metal-rich GC subpopulation has only formed {\it in~situ}. 
-With this statement, however, we do caution that \citet{2019MNRAS.486.3134K} suggests 
+accreted populations. However, we caution that \citet{2019MNRAS.486.3134K} suggests 
 to reserve the `{\it ex~situ}' classification for accretion after $z=2$, when
 the central galaxy has formed and accretion unambigously contributes to the
-radially extended halo GC population. In fact, our classification might not hold
-for Au4-1.
+radially extended halo GC population. Our classification of accreted GC candidates
+is thus not consistent with the aforementioned definition because our selection
+function mostly includes star particles that have formed before roughly $z=2$.
 
@@
 less efficient at larger radii, thus, the formation efficiencies of the accreted 
-GC candidates would have to be lower. Our classification as GC candidates could
-especially be improved for the accreted subset. For example, we could tag only a
-subset of the accreted star particles as GC candidates, where the number
-number of GCs is determined by the satellite halo mass, given the 
-$M_{vir}-N_{\text{gal}}$ correlation found by \citet{2019arXiv190100900B}.
+GC candidates would have to be lower Alternatively, the fraction of old star 
+particles in our subset of GC candidates may contain considerably more star 
+particles that represent stars in the old stellar halo that have been accreted
+during hierarchical buildup of the galaxy. Our classification of GC candidates 
+could be improved for the accreted subset in particular. For example, we could 
+select only a subset of the accreted star particles as GC candidates where the 
+number number of GCs would be determined by the satellite halo mass, given the 
+$M_{vir}-N_{\text{gal}}$ correlation found by \citet{2019arXiv190100900B}. However,
+we did not include such an analysis in this study.
 
@@
 threshold and moves closer to the dotted line that shows the distribution of
-all star particles. However, we notice that the Auriga simulations, on average, 
-do not form new stars with a metallicity below [Fe/H] = -1 more recent than 6 Gyr 
-ago: the behaviour of Figure~\ref{fig:FeH} does not change for metallicities
-below [Fe/H] = -1 when we change the age cut to 8 or 6 Gyr. The qualitative behaviour
-of the median distribution of galactocentric radii (Figure~\ref{fig:Rgc}), on 
-the other hand, is unaffected by lowering the age cut other than including
+all star particles in Figure~\ref{fig:FeH}. However, 
+we notice that the Auriga simulations, on average, do not form new stars with 
+a metallicity below [Fe/H]~=~-1 more recent than 6 Gyr ago: the behaviour of 
+Figure~\ref{fig:FeH} does not change for metallicities below [Fe/H]~=~-1 when 
+we change the age cut to 8 or 6 Gyr, and the slope of the masss ratio for 
+metallicities above [Fe/H]~=~-1 is slightly steeper. In addition, we still find
+that the accreted GC candidates are more metal-poor than those that have formed 
+{\textit in situ}.
+
+The qualitative behaviour of the median distribution of galactocentric radii 
+(Figure~\ref{fig:Rgc}) is unaffected by lowering the age cut other than including
 more star particles (more mass) which leads to a higher normalisation and
@@
 We investigate statistics of age-selected ($>$~10~Gyr) GC candidates in the 
-Auriga simulations and compare the simulations to the MW and M31 GCSs. Based on
-our analysis we draw the following conclusions.
+Auriga simulations and compare the simulations to the MW and M31 GCSs to test
+whether the star formation model implemented for the Auriga simulations can give
+rise to metallicity and radial distributions that are consistent with these two
+observed GC systems. Based on our analysis we draw the following conclusions.
 

### 2020-04-11 response_to_referee.tex
Minor updates

@@
 We thank the referee for a thoughtful and elaborate report. We address the 
-comments in sections with names that match
-the headings of the referee report, starting with the following listing of our 
-response to the 3 paragraphs in the introduction.
+comments in sections with headings that match those of the referee report, 
+starting with the following listing of our response to the 3 paragraphs in 
+the introduction.
 \begin{enumerate}
@@
 star particles in the Auriga L4 galaxies. In addition, Figure 3 now shows the 
-number of star particles included in the subset.
+number of star particles included in each subset.
 \item We clarified at various places whether we mean the mean or median among
@@
 \begin{itemize}
-\item TODO: overall comment
 \item We added references to Deason et al. (2015) and Conroy et al. (2019) in
@@
 \item We clarified that our selection function is inconsistent with the definition
+\item We clarified which which galaxy Brodie \& Strader provide the quoted number.
+\item We clarified footnote 8.
 of Kruijssen (2019) for {\textit ex. situ} GC formation.

### 2020-04-11 AurigaGCS.tex
Minor updates

@@
 
-TODO: ``\citet{2012MNRAS.426.1475U} shows the great variety in GC metallicity distributions
-present in the sample of early-type galaxies of the SLUGGS survey contradicts
-the classical idea that all the metallicity distributions of GCs should be bimodal.''
+% Referee: ``\citet{2012MNRAS.426.1475U} shows the great variety in GC metallicity distributions
+% present in the sample of early-type galaxies of the SLUGGS survey contradicts
+% the classical idea that all the metallicity distributions of GCs should be bimodal.''
 
@@
 \citep{2007CSE.....9...90H}, using the perceptually uniform colour maps
-from \citet{2015arXiv150903700K} for two-dimensional plots.
+from \citet{2015arXiv150903700K} for two-dimensional plots. This research 
+has made use of NASA's Astrophysics Data System Bibliographic Services.
 

### 2020-04-11 response_to_referee.tex
Version to send to Simon

@@
 comments in sections with headings that match those of the referee report, 
-starting with the following listing of our response to the 3 paragraphs in 
+starting with the following listing of our response to the first 2 paragraphs in 
 the introduction.
@@
 GC systems and in the simulations.
-\item TODO: disussion of implications for wider context.
+% \item TODO: disussion of implications for wider context.
 \end{enumerate}
@@
 \begin{itemize}
-\item TODO: add a paragraph in introduction to justify why we consider metallicity
-and galactocentric radius.
+\item We updated the introduction to make it more clear why we consider the metallicity
+and galactocentric radius in light of {\it in~situ} formation or accretion of GC
+candidates.
 \item We added section 5.3 to discuss how our results change of we adopt an age cut
@@
 \begin{itemize}
-\item TODO justify the modelling philosophy.
+% \item TODO justify the modelling philosophy.
 \item We added a section 5.3 to discuss how our results change if we adopt an
@@
 normalising to any one of these options which is why we use the virial radius instead.
-\item TODO: ``Discussion on the implications for the formation and evolution of clusters
-    often feels a bit out of place and forced.''
+% \item TODO: ``Discussion on the implications for the formation and evolution of clusters
+%    often feels a bit out of place and forced.''
 
@@
 \begin{itemize}
-\item Item
+\item We clarified that the blue and red GCs are observed to have different colour
+distributions that may reflect a different metallicity distribution which is argued
+to arise from two distinct formation channels. We briefly summarise that differences
+between their properties include the metallicity and radial distributions, which
+is why we investigate these properties in the Auriga simulations.
+\item We removed the quoted sentence.
 \end{itemize}
@@
 \item We clarified that we are referring to Figure 5 and Figure 7 for the claims about
-the {\it in situ} and accreted component in the third paragraph of section 4.3.
+the {\it in~situ} and accreted component in the third paragraph of section 4.3.
 \item Figure 9: The values are removed from the masked upper right corner bins.
@@
 the first paragraph of section 5.1.
-\item TODO: bimodality in SLUGGS
+\item We included a discussion of bimodality in metallicities in the introduction.
+In addition to that, the results of Usher et al. (2012) ``imply that most early-type 
+galaxies in the SLUGGS survey have bimodal metallicity as well as colour distributions'',
+and ``Combined with previous studies, nine of 12 galaxies show evidence for bimodality
+while in the remaining three galaxies bimodality cannot be ruled out.''. Our 
+interpretation of this study seems to differ from that of the referee.
 \item We still find that the accreted star particles are more metal-poor than 
-those that have formed {\textit in situ} if we lower the age cut to 8 or 6 Gyr.
+those that have formed {\it in~situ} if we lower the age cut to 8 or 6 Gyr.
 This has been added in section 5.3.
@@
 \item We clarified footnote 8.
-of Kruijssen (2019) for {\textit ex. situ} GC formation.
+of Kruijssen (2019) for {\it ex~situ} GC formation.
 \end{itemize}

### 2020-04-11 AurigaGCS.tex
Version to send to Simon

@@
 parent galaxies, if the formation and evolution of GCs- and GC systems themselves 
-is adequately understood. However, despite decades of research (the extensive 
-literature on GCs is summarised in several books and review articles, e.g.~\citealt{
+is adequately understood. However, despite decades of research (e.g.~\citealt{
 1991ARA&A..29..543H, Harris2001, 2004Natur.427...31W, 2006ARA&A..44..193B, 
 2012A&ARv..20...50G, 2014CQGra..31x4006K, 2018RSPSA.47470616F}), consensus on an 
-exhaustive picture of the formation of GCs is yet to be reached.
-
-The literature offers a wealth of formation scenarios. \citet{1968ApJ...154..891P}
+exhaustive picture of the formation of GCs is yet to be reached. Most galaxies host
+a GCS with a bimodal colour distribution that may reflect a bimodal metallicity 
+distribution which is argued to arise from two distinct formation channels 
+\citep{2006ARA&A..44..193B}. GCs are typically referred to as `blue' or `red' \citep[e.g.][]{
+1985ApJ...293..424Z,1999AJ....118.1526G,2001AJ....121.2974L} where the former class
+is more metal-poor, more radially extended, and showing little to no rotation wheras
+the later is more metal-rich, radially concentrated, and rotating with the galaxy.
+
+The literature offers a wealth of formation scenarios, many of which focus on the
+distinct characteristics of the blue or red subpopulation. \citet{1968ApJ...154..891P}
 and \citet{1984ApJ...277..470P} argue that GCs form as the earliest bound
@@
 
-\newpage  % to prevent reference split over two pages which breaks LaTeX
 Yet another hypothesis is that star cluster formation is triggered by major 
@@
 further described in Section~\ref{sec:auriga}. We investigate whether the star 
-formation model implemented produces metallicity, 
-radial, and metallicity-radial distributions that are consistent with the MW 
-and/or M31 GCSs, and whether the model produces enough stellar mass with
-the right properties to allow for formation efficiencies lower than unity and
-the expected (dynamical) mass loss over the cluster lifetime (not modelled 
-explicitly in this study).
+formation model implemented produces metallicity, radial, and metallicity-radial 
+distributions that are consistent with the MW and/or M31 GCSs, and whether the 
+model produces enough stellar mass with the right properties. Moreover, the simulations
+provide us with the history of the star particles, which allows us to investigate
+the differences between these properties for sub populations that have formed 
+{\it in~situ} versus those that have been accreted. We focus on the metallicity
+and radial distributions because observations of the red and blue GCs show
+distinct differences between these properties.
 
@@
         151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H},
-        color-coded by the \textbf{median} (values also shown in each bin). The 
+        colour-coded by the \textbf{median} (values also shown in each bin). The 
         numbers in parenthesis show how many star particles fall within the bin.
@@
         Mass-weighted [Fe/H]-$r_{\text{gal}}$ distribution of all $30$~Auriga
-        L4 haloes. Here we consider only the GC candidates and color-code by the 
+        L4 haloes. Here we consider only the GC candidates and colour-code by the 
         median mass (values also shown in each bin). The numbers in parenthesis 
@@
         the MW and M31, respectively. Red (blue) indicates a higher (lower) overall 
-        mass excess. The number in each bin shows the color-coded value that is 
+        mass excess. The number in each bin shows the colour-coded value that is 
         plotted, and the (median) star particle count is given in parenthesis. 
@@
 that the accreted GC candidates are more metal-poor than those that have formed 
-{\textit in situ}.
+{\it in~situ}.
 

### 2020-04-14 response_to_referee.tex
Updated after feedback SW 20200414

@@
 \item All acronyms are introduced the first time they appear in the text
-(MW, M31, GC, GCS, YMC, ISM, SN, AGB, DM, and Au). The subset thereof that appears 
+(MW, M31, GC, GCS, YMC, ISM, SN, DM, and Au). The subset thereof that appears 
 in the abstract is also introduced the first time it appears.
@@
 \item We removed the quoted sentence.
-\item We clarified that our selection function is inconsistent with the definition
+\item Our definition of `accreted GC candidate' considers when the GC candidate 
+was accreted onto the main object, not when it was formed. The age cut does not
+affect the time of accretion, but the time of accretion could have been before redshift
+$z=2$ (which would be inconsistent with the definition of Kruijssen et al. 2019).
 \item We clarified which which galaxy Brodie \& Strader provide the quoted number.

### 2020-05-13 AurigaGCS_20200414.tex
Ready for R2 (pending approval FG)

--- 2020-04-11 AurigaGCS.tex
@@
 1985ApJ...298...18F} and \citet{1992ApJ...384...50A} are intertwined because
-accretion and mergers continuously occurs during the hierarchical build-up of
+accretion and mergers continually occur during the hierarchical build-up of
 galaxies. Various (other) hierarchical formation channels thus combine different
@@
 processes with a level of detail that cannot be achieved for GCs at high redshifts. In 
-this framework, differences between both classes of objects are caused by nearly a 
+this framework, differences between the two classes of objects are caused by nearly a 
 Hubble time of (dynamical) evolution \citep[e.g.][]{1987degc.book.....S}. This picture 
@@
 simulations \citep{2010ApJ...718.1266M,2014ApJ...796...10L,2018MNRAS.480.2343C,
-2019MNRAS.486..331C,2019arXiv190505199C}, as is done in the work by 
+2019MNRAS.486..331C,2019arXiv190505199C}, also done in the work by 
 \citet{2019MNRAS.482.4528E}.
@@
 are consistent with the observations. The question thus naturally arises whether 
-the star formation histories of the simulations give rise to a GCS similar to 
+the star formation histories of the simulations could give rise to a GCS similar to 
 the MW and/or Andromeda (M31) GCSs. In particular, 
@@
 provide us with the history of the star particles, which allows us to investigate
-the differences between these properties for sub populations that have formed 
+the differences between these properties for sub-populations that have formed 
 {\it in~situ} versus those that have been accreted. We focus on the metallicity
@@
 The plan of the paper is as follows. We summarise the relevant characteristics 
-of the Auriga simulations in section~\ref{sec:auriga}, followed by a summary of 
+of the Auriga simulations in Section~\ref{sec:auriga}, followed by a summary of 
 the observations of the MW and M31 GCSs
-in section~\ref{sec:observations} that we use to compare our simulations to in
-section~\ref{sec:results}. We discuss our findings in section~\ref{sec:discussion}
-to come to our conclusions in section~\ref{sec:conclusions}.
-
-% Referee: ``\citet{2012MNRAS.426.1475U} shows the great variety in GC metallicity distributions
-% present in the sample of early-type galaxies of the SLUGGS survey contradicts
-% the classical idea that all the metallicity distributions of GCs should be bimodal.''
+in Section~\ref{sec:observations} that we compare our simulations to in
+Section~\ref{sec:results}. We discuss our findings in Section~\ref{sec:discussion}
+to come to our conclusions in Section~\ref{sec:conclusions}.
 
@@
 selected initial conditions in the range $1-2 \times 10^{12}$~M$_{\odot}$
-were selected from the \mbox{\textsc{eagle}} DM only box, see 
+were selected from the \mbox{\textsc{eagle}} DM-only box, see 
 \citetalias{2017MNRAS.467..179G} for details. The simulations are 
@@
 are described by processes important for star formation, such as the condensation 
-of cold clouds and the photoevaporation of clouds. Stars form stocastically in 
+of cold clouds and the photoevaporation of clouds. Stars form stochastically in 
 thermally unstable gas with a density threshold of $n = 0.13 \, \text{cm}^{-3}$,
@@
 Galactic winds enrich the ISM with metals from SNIa, SNII, and asymptotic giant 
-branch (AGB) stars \citep{2013MNRAS.436.3031V}. Supermassive
+branch stars \citep{2013MNRAS.436.3031V}. Supermassive
 black holes grow via Bondi–Hoyle–Lyttleton accretion \citep{1944MNRAS.104..273B,
@@
 The Auriga suite has a fiducial baryonic mass resolution $m_b$~=~$5 \times 10^4$~M\Sun,
-with gravitational softening of collissionless particles $\epsilon$~=~369~pc.
+with gravitational softening of collisionless particles $\epsilon$~=~369~pc.
 Simulations at this resolution are referred to as level 4 (L4). Selected
@@
 $\epsilon$~=~738~pc, and $m_b$~=~$6 \times 10^3$~M\Sun \, with $\epsilon$~=~184~pc,
-respectively. The mass resolution of the Auriga simulations is thus close to the 
-characteristic peak mass of the lognormal GC mass distribution of $10^{5}$~M\Sun 
+respectively. The mass resolution of the Auriga simulations is thus close $10^{5}$~M\Sun,
+to the characteristic peak mass of the lognormal GC mass distribution 
 \citep{1991ARA&A..29..543H}, although the gravitational softening is two orders 
@@
 single stellar population with a total mass that could be consistent with one GC. 
-This means that their formation sites and that of a real-world GC may be consistent.
+This means that their formation sites could be consistent with those of real-world GCs.
 
@@
 \label{sec:observations}
-We describe the observations of the MW GCS in Section~\ref{sec:milkyway},
-and of the M31 GCS in Section~\ref{sec:andromeda}. We discuss the age-estimates
-in Section~\ref{sec:age}, the distribution of galactocentric radius in 
-Section~\ref{sec:Rgc}, and the total mass in 2D bins of metallicity-galactocentric
-radius in Section~\ref{sec:observations_FeHRgc}. We focus on metallicity and
+We describe observations of the MW GCS in Section~\ref{sec:milkyway} for these clusters,
+and of the M31 GCS in Section~\ref{sec:andromeda}. We discuss age-estimates
+in Section~\ref{sec:age}, their distribution of galactocentric radius in 
+Section~\ref{sec:Rgc}, and their total mass in 2D bins of metallicity-galactocentric
+radius in Section~\ref{sec:observations_FeHRgc}. We focus on both metallicity and
 galactocentric radius because these data are available in the observations and
@@
 The authors initially estimated the number of GCs in the MW GCS to be 180~$\pm$~10,
-thus, their catalogue to be ${\sim}$85\% complete. However, an additional 59 GCs
-are claimed to have been discovered by various authors. The total number of GCs
-in the MW might add up to 216 with recent estimates now anticipating an additional 
+thus, their catalogue to be ${\sim}$85\% complete. However, an additional 59 GC
+candidates have been discovered more recently by various authors. The total number of GCs
+in the MW might thus be 216 with recent estimates now anticipating an additional 
 $30$~GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
@@
 assumed $M/L_V = 2$ independent of [Fe/H]}. We calculate the galactocentric radii 
-from the observed positions RA and DEC, further discussed in Sec.~\ref{sec:Rgc}.
+from the observed positions RA and DEC, as further discussed in Section~\ref{sec:Rgc}.
 
@@
 of $4.8$~Gyr. Based on these data, we find that the age distributions of the MW 
-and M31 GCSs are not statistically consistent. Moreover, the MW appears 
+and M31 GCSs are not statistically consistent. The MW appears 
 to host a GCS that is somewhat older than that of M31.
 This is somewhat surprising given that M31 is generally considered to be earlier
-type than the MW meaning that an older stellar population would be naively expected.
+type than the MW so that an older stellar population would naively be expected.
 However, we do caution that both data sets are incomplete and the age 
@@
 background density} $r_{\text{vir,M31}} = 299$~kpc and multiply by 
-$r_{\text{vir,MW}} = 261$~kpc to account for the different intrinsic sizes of both 
+$r_{\text{vir,MW}} = 261$~kpc to account for the different intrinsic sizes of the two
 galaxies, adopting the values and cosmology from \citet{2017MNRAS.464.3825P}.
@@
 (0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
-and distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}.
-We calculate $r_{\text{gal}}$ as `average deprojected distance`
+and the distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}.
+We estimate $r_{\text{gal}}$ as `average deprojected distance`
 $r_{\text{gal}} = r_{\text{proj}} \times (4/\pi)$.
@@
 for the innermost ($<1$~kpc) GCs, and none for those beyond roughly $20$~kpc
-(the halo GCs). We compare both distributions of the full data set (solid 
+(the halo GCs). We compare the two distributions of the full data set (solid 
 lines) and find that the MW has more GCs in the range $1-4$~kpc than M31
-when accounting for the larger number of total GCs in M31. Interestingly, both
+when accounting for the larger number of total GCs in M31. Interestingly, the two 
 distributions show a similar trend for $r_{\text{gal}} > 4$~kpc and host a 
 subpopulation of halo GCs. Our naive expectation would be that the spiral galaxies
-in the Local Group host similar GC systems. However, the radial distributions of
-the GCS of the MW and M31 are not statistically consistent with being drawn from 
-the same underlying distribution due to substantial differences at intermediate radii.
+in the Local Group host similar GC systems. However, based on a two-sample KS test
+we find that the radial distributions of the GCS of the MW and M31 are not statistically 
+consistent with being drawn from the same underlying distribution due to substantial 
+differences at intermediate radii.
 
@@
 \label{sec:observations_FeHRgc}
-We show the two-dimensional mass-weighted metallicity-radial distribution of the
+We show the two-dimensional mass-weighted metallicity-radius distribution of the
 MW and the M31 GCS in the top and bottom panel of Figure~\ref{fig:observations_FeHRgc},
@@
 
-The observations indicate that
-no GCs with high metallicities are to be expected at large radii (the three bins
-in the upper right corner, both for MW and M31), and relatively few GCs at large
+The observations indicate very few GCs with high metallicities at large radii (the three bins
+in the upper right corner, both for MW and for M31), and relatively few GCs at large
 radii in general ($r_{\text{gal}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
-the MW and $17$ or 4.6\% in M31). Moreover, the M31 hosts more metal-rich 
-([Fe/H]$ > -1$) GCs in each radial bin in comparison to the MW GCSs than what
-would be expected when accounting for the fact that M31 hosts a larger GCS
-than the MW. Finally, given that both marginalized (i.e. the metallicity 
-and radial) distributions are not statistically consistent, we find that the 
-two-dimensional distributions are also not consistent. More generally, the GCS
-of the MW differs significantly from that of M31. We compare these 
-observations to the Auriga simulations later on in Sec.~\ref{sec:results_FeHRgc}.
+the MW and $17$ or 4.6\% in M31). Moreover, M31 hosts more metal-rich ([Fe/H]$ > -1$) 
+GCs in each radial bin in comparison to the MW after accounting for the fact that M31
+hosts a larger GCS. Finally, given that the marginalized (i.e. the metallicity 
+and radial) distributions are not statistically consistent between the two galaxies, 
+we find that the two-dimensional distributions are also not consistent. More generally,
+the GCS of the MW differs significantly from that of M31, not only in the number of 
+clusters but also in their distribution over radius and metallicity. We compare these 
+observations to the Auriga simulations in Section~\ref{sec:results_FeHRgc}.
 
@@
 \citet{2010ARA&A..48..431P} and following the method of 
-\citet{2017MNRAS.465.3622R}. However, we caution that his definition does exclude 
-1 GC in the MW and 24 in M31 as stated in Section~\ref{sec:age}, and further
-discuss this in Section~\ref{sec:age_min}.
+\citet{2017MNRAS.465.3622R}. However, we caution that his definition, although 
+statistically consistent with the estimated ages of all GCs in the MW, is not 
+consistent with the tail of younger clusters as stated in Section~\ref{sec:age},
+and further discussed in Section~\ref{sec:age_min}.
 
@@
 candidates (age $>10$~Gyr) with those of all star particles (i.e.
-when no additional selection criterion is applied). The mean number of star 
+with no age cut). The mean number of star 
 particles in the Auriga L4 simulations that we select as GC candidates is 
@@
 bound to the most-massive halo/subhalo in the first snapshot that the particle 
-was recorded), and an accreted subpopulation (those that have formed {\it ex~situ} and 
+was recorded), and an accreted subpopulation (those that have formed {\it ex~situ} but
 are bound to the most-massive halo/subhalo at $z=0$). A GC candidate either formed
 {\it in~situ} or it was accreted. We consider the metallicity distribution in 
-Sec.~\ref{sec:results_FeH}, the distribution of galactocentric radii in 
-Sec.~\ref{sec:results_Rgc}, and the combination of both 
-in Sec.~\ref{sec:results_FeHRgc}.
+Section~\ref{sec:results_FeH}, the distribution of galactocentric radii in 
+Section~\ref{sec:results_Rgc}, and the combination of the two 
+in Section~\ref{sec:results_FeHRgc}.
 
@@
 distributions of three individual simulation runs that we consider representative
-for specific behaviour, and to highlight that different runs could give rise to 
+for specific behaviour, and to highlight that different runs give rise to 
 different distributions. We show the age-selected GC candidates as well as the 
@@
 $0.0$ to $-0.6$. This reflects the enrichment history of the galaxy because the
-age cut neglects the more metal-rich stellar population which shifts the mean
+age cut removes the more metal-rich stellar population which shifts the mean
 metallicity towards lower values. Furthermore, accreted GC candidates generally have
@@
 \mbox{Au4-1} is undergoing a major merger at redshift zero and we find a mean
-metallicity in this simulations $\mu = -1.51 \, ({-0.74})$ for the {\it in~situ} 
+metallicity in this simulation $\mu = -1.51 \, ({-0.74})$ for the {\it in~situ} 
 (accreted) GC candidates, although the former consists of only $1019$ particles 
@@
 has undergone a major merger around 2~Gyr lookback time, which is probably why
-the accreted population is more metal rich. After inspection of the same figure 
+the accreted population is more metal-rich. After inspection of the same figure 
 for every one of the $30$~Auriga L4 haloes we find that the simulations produce
@@
 full set of Auriga galaxies. The beige crosses are to be compared to the purple 
-and magenta cross, which shows the mean value of all MW and M31 GCs, respectively. 
+and magenta crosses, which show the mean value of all MW and M31 GCs, respectively. 
 In addition, we show the metal-rich population of the MW GCS using a solid dot, 
 and the metal-poor population with an open dot. We caution that
-these literature values result from individual Gaussian fits to sub sets of the 
+these literature values result from individual Gaussian fits to subsets of the 
 observational data cut at [Fe/H]~$= -1$. We do not include corresponding data 
@@
 age classification, hints at three populations separated at [Fe/H]~$=-0.4$ and 
-[Fe/H]~$ = 1.5$. None of the Auriga sub sets has a mean value that offers much 
-hope that the simulated distribution is consistent with the lowest metallicity 
+[Fe/H]~$ = 1.5$. None of the Auriga subsets has a mean value that offers much 
+hope of reconciling the simulated distribution with the lowest metallicity 
 group in the M31 GCS. This is also true for the metal-poor population of the 
@@
 that all Auriga L4 galaxies have metallicity distributions with (much) larger
-mean values than what is observed for the MW and M31 GCS, and that we 
+mean values than observed for the MW and M31 GCS, and that we 
 systematically find lower mean metallicities for the accreted GC candidates
 than for those that have formed {\it in~situ}.
-
-% Finally, we test the null hypothesis that MW (M31) and the GC candidates (all,
-% {\it in~situ}, and accreted) are drawn from the same underlying distribution 
-% by calculating the KS test statistic (i.e. $6$ KS tests per simulation). We 
-% reject $H_0$ at the 100.00~\% confidence level for virtually all subsets of all 
-% simulations, both for MW and M31, except when comparing the old accreted stars 
-% of \mbox{Au4-10} to the MW GCS. In this case we still reject $H_0$ with, but 
-% with $\leq 98.68$~\% confidence. When comparing to the M31 GCS, the `best' 
-% matches are the old accreted subpopulations of \mbox{Au4-13}, \mbox{Au4-15}, and 
-% \mbox{Au4-17} ($H_0$ rejected with $\leq$ 99.82~\% confidence, 99.95~\%,
-% and 98.32~\%). Here we find that the cumulative distributions are more or less
-% similar up to [Fe/H]~$-0.5$, above which the simulations yield higher number
-% counts which drives the KS test statistic over the critical values. This affirms
-% our finding that the simulations produce GC candidates that are more metal-rich
-% than the MW (M31) GCS. The main reasons that $H_0$ is rejected with such
-% high confidence are under-production of old stars with [Fe/H]~$\leq$~-1.5,
-% and over-production of stars with [Fe/H]$\geq$~-0.5.
 
@@
         stars (beige dotted) and GC candidates (i.e. stars with
-        age $>$~10~Gyr; beige solid). The latter sub set is further split up
+        age $>$~10~Gyr; beige solid). The latter subset is further split up
         between stars that formed {\it in~situ} (brown solid), and those that were accreted
@@
 \end{figure}
-We now turn to the second goal, which is to see whether sufficient total mass in 
+We now turn to our second goal, which is to see whether sufficient total mass in 
 GC candidates is produced by the Auriga simulations. To answer this question we plot
@@
 which shows the scatter between runs that have different initial 
-conditions, thus, have unique merger histories. We chose to aggregate the data 
+conditions, thus, have varying merger histories. We chose to aggregate the data 
 to indicate general trends that we find when the GC candidates are split up into
@@
 panels. This mass excess can be thought of the `mass budget' that the Auriga GC 
-candidates can `afford to lose' due to a combination of smaller than unity bound
-cluster formation efficiencies combined with a Hubble time of dynamical evolution,
+candidates can `afford to lose' (due to a combination of smaller than unity bound
+cluster formation efficiencies combined with a Hubble time of dynamical evolution),
 while still producing sufficient mass at the right metallicities. In particular,
-the cluster formation efficiency would have to decrease with decreasing 
+the combined efficiency would have to increase with decreasing 
 metallicity for Auriga GC candidates to produce a population of GC candidates 
@@
         stars (beige dotted) and GC candidates (i.e. stars with
-        age $>$~10~Gyr; beige solid). The latter sub set is further split up
+        age $>$~10~Gyr; beige solid). The latter subset is further split up
         between stars that formed {\it in~situ} (brown solid), and those that 
@@
 The lowest mass surplus for both galaxies is the bin with metallicities in the range
-[Fe/H]~$\in [-2.5, -1.5]$ and gallactocentric radius $r_{\text{gal}}\in [3,8]$~kpc,
+[Fe/H]~$\in [-2.5, -1.5]$ and galactocentric radius $r_{\text{gal}}\in [3,8]$~kpc,
 for which the simulations produce 
 a factor $10^{2.68}/10^{1.33} \approx 22$ and $10^{1.69}/10^{0.75} \approx 9$ 
-more mass in GC candidates than what is observed in the MW and M31 respectively.
+more mass in GC candidates than is observed in the MW and M31 respectively.
 The highest factor for the MW is $2.1 \times 10^{5}$, and $1.1 \times 10^{3}$
@@
 are expected to be particularly high for GCs in the inner regions of galaxies
-that are on orbits with pericentres close to the galactic bulge or bar. In addition, 
+which must have orbits with pericentres close to the galactic bulge or bar. In addition, 
 disk crossings in this region will cause spikes in the tidal tensor due to steep
@@
 an overabundance of regular stars. It could be that the resulting metallicity
-distribution is then biased towards higher values than what is observed for real 
+distribution is then biased towards higher values than observed for real 
 GCs. An alternative explanation could overmixing of metals at early times.
 
-In general, the colour (metallicity) distribution of most GCSs is bimodal 
+In general, the colour (metallicity) distribution of most GCSs appears to be bimodal 
 with typical separating value [Fe/H]$\sim -1$ \citep{1985ApJ...293..424Z,
@@
 populations of GCSs at [Fe/H]~=~$-1$, as for the MW. Moreover, we do find 
-that the mean metallicity shifts when we split the GC candidates up according 
+that the mean metallicity shifts when we split the GC candidates according 
 to birth location (accreted or {\it in~situ}). In particular, the mean values of 
 the {\it in~situ} GC candidates are roughly consistent with the metal-rich MW GCs.
-On the other hand, we also notice that a substantial number of simulations has similar 
-mean values for all GC candidates, and the simulated {\it in~situ} GC candidates 
-have larger dispersions than the metal-rich GCs. Moreover, the offset between 
-the mean of the metal-rich and metal-poor populations in the MW is $1$ dex, a
-factor $2-3$ larger than the offset that we find between the {\it in~situ} and 
-accreted populations. However, we caution that \citet{2019MNRAS.486.3134K} suggests 
+On the other hand, we also notice that most of the simulations have a similar 
+mean value for all GC candidates, and the simulated {\it in~situ} GC candidates 
+have larger dispersions than is claimed for metal-rich GCs in the MW. Moreover, the 
+offset between the means of the metal-rich and metal-poor populations in the MW is
+$1$ dex, a factor $2-3$ larger than the offset that we find between the {\it in~situ}
+and accreted populations. However, we caution that \citet{2019MNRAS.486.3134K} suggests 
 to reserve the `{\it ex~situ}' classification for accretion after $z=2$, when
 the central galaxy has formed and accretion unambigously contributes to the
-radially extended halo GC population. Our classification of accreted GC candidates
-is thus not consistent with the aforementioned definition because our selection
-function mostly includes star particles that have formed before roughly $z=2$.
+radially extended halo GC population. In fact, our classification might not hold for Au4-1.
 
@@
 
-% Copy-pasted from \citet{2019MNRAS.486.5838R}
-% ``Out of the cluster formation models considered, the `no formation physics' model,
-% in which both the CFE and the ICMF are fixed throughout cosmic time, is
-% approximately equivalent to those studies  that  use  `particle-tagging'
-% techniques  to  identify  GCs  in cosmological simulations (e.g. Tonini 2013,
-% Renaud et al. 2017). We find that this cluster formation model continues to form GCs
-% at a vigorous rate until the present time, which implies it overproduces
-% the total GC mass in the MW by a factor
-% 5.5 relative to the mass formed in the fiducial model. Likewise, the continued
-% formation  of  GCs  in  this  model  predicts  the  on-going  formation
-% of massive (M $>10^5$ M\Sun) clusters with [Fe/H]$ <-0.5$ should be observed in
-% MW-mass galaxies at $z=0$. For these reasons, an environmentally independent
-% cluster formation description is not compatible with observations.''
-
 \subsection{Lower age cut in the GC selection function}
@@
 a higher mass ratio with respect to the observed GC systems of the MW and M31.
-The qualitative behavour presented in Figure~\ref{fig:Au-FeHRgc-ratio} does not 
+The qualitative behaviour presented in Figure~\ref{fig:Au-FeHRgc-ratio} does not 
 change when the age cut is lowered to 8 or 6 Gyr. 
+GC candidates is not affected definition because our selection
+function mostly includes star particles that have formed before roughly $z=2$.
+Overall, reducing the age cut worsens the agreement between the observed GCSs 
+and the candidate GCs in the Auriga galaxies.
 
@@
 Auriga simulations and compare the simulations to the MW and M31 GCSs to test
-whether the star formation model implemented for the Auriga simulations can give
+whether the star formation model implemented for the Auriga simulations could give
 rise to metallicity and radial distributions that are consistent with these two
@@
     given that our selection function of star particles selects all stars bound
-    to the main subhalo in the main halo. The total mass of GC candidates is 
+    to the main subhalo of the halo. The total mass of GC candidates is 
     dominated by accreted star particles at radii beyond $20$~kpc. The GCs in 
@@
 % \appendix
-% \section{Scatter between individual Auriga haloes, and numerical convergence}
-% \label{sec:scatter-convergence}
-% We check whether the properties of the Auriga globular cluster candidates
-% are well converged between the three different resolution levels used for the
-% Auriga simulations. Here we consider all three Auriga haloes for which simulation
-% runs were performed at all three resolution levels: Au6, Au16, and Au24. Here
-% we can investigate differences between individual haloes.
-% 
-% Figure~\ref{fig:logMFeH_res} shows the mass-weighted metallicity distribution,
-% Figure~\ref{fig:logMRgc_res} shows the mass-weighted radial distribution, and
-% Figure~\ref{fig:logMRgcFeH_res}
-% 
-% 
-% 
-% \begin{figure*}
-%     \includegraphics[width=0.31\textwidth]{{logMFeH_Au6}.png}
-%     \includegraphics[width=0.31\textwidth]{{logMFeH_Au16}.png}
-%     \includegraphics[width=0.31\textwidth]{{logMFeH_Au24}.png}
-%     \caption{Similar to Figure~\ref{fig:FeH}, but showing one individual Auriga
-%         halo, where colours indicate the resolution level: L3 green, L4 orange,
-%         and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo 16.
-%         \emph{Right:} Auriga halo 24. For all three haloes we find marginal
-%         increases in the mass normalization with increasing resolution level.
-%         \label{fig:logMFeH_res}
-%     }
-% 
-% \end{figure*}
-% \begin{figure*}
-%     \includegraphics[width=0.31\textwidth]{{logMRgc_Au6}.png}
-%     \includegraphics[width=0.31\textwidth]{{logMRgc_Au16}.png}
-%     \includegraphics[width=0.31\textwidth]{{logMRgc_Au24}.png}
-%     \caption{Similar to Figure~\ref{fig:Rgc}, but showing one individual Auriga
-%         halo, where colours indicate the resolution level: L3 green, L4 orange,
-%         and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo 16.
-%         \emph{Right:} Auriga halo 24. For all three haloes we find marginal
-%         increases in the mass normalization with increasing resolution level.
-%         \label{fig:logMRgc_res}
-%     }
-% 
-% \end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-05-13 latexdiff.sh

@@ -1,7 +1,7 @@
 #!/bin/bash
 set -e
 
-diff="diff_with_respect_to_20190905.tex"
+diff="diff_with_respect_to_20200414.tex"
 if [ -f "${diff}" ]; then
     rm -f "${diff}"
 fi
@@ -9,5 +9,5 @@ fi
 # Ignore (sub)sections: https://tex.stackexchange.com/questions/87536
 # NB, removed by hand Volker Springel from AurigaGCS_20180802.tex b/c
 # latexdiff breaks on changes in the \author block
-latexdiff --exclude-textcmd="section,subsection" AurigaGCS_20190905.tex AurigaGCS.tex > "${diff}"
+latexdiff --exclude-textcmd="section,subsection" AurigaGCS_20200414.tex AurigaGCS.tex > "${diff}"
 timotex "${diff}"

### 2020-06-02 AurigaGCS_20200513.tex
License + changes in proof

--- 2020-05-13 AurigaGCS_20200414.tex
@@
 1985ApJ...293..424Z,1999AJ....118.1526G,2001AJ....121.2974L} where the former class
-is more metal-poor, more radially extended, and showing little to no rotation wheras
-the later is more metal-rich, radially concentrated, and rotating with the galaxy.
+is more metal-poor, more radially extended, and showing little to no rotation whereas
+the latter is more metal-rich, radially concentrated, and rotating with the galaxy.
 
@@
 
-Yet another hypothesis is that star cluster formation is triggered by major 
-gas-rich (spiral) galaxy mergers \citep{1987nngp.proc...18S, 1992ApJ...384...50A},
-which is naturally expected within the framework of hierarchical assembly. One
-testable prediction of this scenario is the formation of young clusters in
-interacting and merging galaxies, which has been observed and are found to show 
-remarkable similarities with GCs in the Milky Way (MW) \citep[e.g.][]{
+Yet another hypothesis is that star cluster formation traces periods of high-intensity
+star formation, which can be triggered by major gas-rich (spiral) galaxy mergers 
+\citep{1987nngp.proc...18S, 1992ApJ...384...50A}. Such a scenario is naturally 
+expected within the framework of hierarchical assembly and predicts formation 
+of young clusters in interacting and merging galaxies, which has been observed 
+and are found to show remarkable similarities with GCs in the Milky Way (MW) \citep[e.g.][]{
 1995AJ....109..960W, 1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}.
@@
 The (mass) resolution of cosmological zoom simulations has reached the mass range 
-populated by GCs, and the gravitational force softening can be as low several 
+populated by GCs, and the gravitational force softening can be as low as several 
 parsec. A number of groups can thus incorporate formation of (globular) star 
@@
 type than the MW so that an older stellar population would naively be expected.
-However, we do caution that both data sets are incomplete and the age 
+On the other hand, the MW could be an outlier as it may have formed and assembled 
+most of its mass earlier than galaxies with a similar mass \citep[e.g.][]{2014ApJ...781L..31S,
+2015A&A...578A..87S,2018MNRAS.477.5072M}.
+In addition, we caution that both data sets are incomplete and the age 
 measurements have large uncertainties (of $1-2$~Gyr). On the other hand, the 
@@
 \citet{2010ARA&A..48..431P} and following the method of 
-\citet{2017MNRAS.465.3622R}. However, we caution that his definition, although 
+\citet{2017MNRAS.465.3622R}. However, we caution that this definition, although 
 statistically consistent with the estimated ages of all GCs in the MW, is not 
@@
 We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
-resolution level (4) and halo number (10, indicating which set of initial
-conditions was used).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
+resolution level 4 and halo number 10, indicating which set of initial
+conditions was used.}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
 distributions of three individual simulation runs that we consider representative
@@
 age classification, hints at three populations separated at [Fe/H]~$=-0.4$ and 
-[Fe/H]~$ = 1.5$. None of the Auriga subsets has a mean value that offers much 
+[Fe/H]~$ = -1.5$. None of the Auriga subsets has a mean value that offers much 
 hope of reconciling the simulated distribution with the lowest metallicity 
@@
 change when the age cut is lowered to 8 or 6 Gyr. 
-GC candidates is not affected definition because our selection
-function mostly includes star particles that have formed before roughly $z=2$.
 Overall, reducing the age cut worsens the agreement between the observed GCSs 

### 2020-06-02 latexdiff.sh

@@ -1,7 +1,7 @@
 #!/bin/bash
 set -e
 
-diff="diff_with_respect_to_20200414.tex"
+diff="diff_with_respect_to_20200513.tex"
 if [ -f "${diff}" ]; then
     rm -f "${diff}"
 fi
@@ -9,5 +9,5 @@ fi
 # Ignore (sub)sections: https://tex.stackexchange.com/questions/87536
 # NB, removed by hand Volker Springel from AurigaGCS_20180802.tex b/c
 # latexdiff breaks on changes in the \author block
-latexdiff --exclude-textcmd="section,subsection" AurigaGCS_20200414.tex AurigaGCS.tex > "${diff}"
+latexdiff --exclude-textcmd="section,subsection" AurigaGCS_20200513.tex AurigaGCS.tex > "${diff}"
 timotex "${diff}"

### 2020-06-02 AurigaGCS.tex
Smallcase for code and programming languages

@@
 supershells \citep{2017Ap&SS.362..183R}, in supersonically induced gaseous objects
-\citep{2019arXiv190408941C}, or in high-speed collisions of dark matter subhaloes
-\citep{2019arXiv190508951M}. \citet{2017MNRAS.472.3120B} suggests
+\citep{2019ApJ...878L..23C}, or in high-speed collisions of dark matter subhaloes
+\citep{2020ApJ...890...18M}. \citet{2017MNRAS.472.3120B} suggests
 that (the blue subpopulation of) GCs could form in high density regions along
@@
 very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$~pc) 
-produces star clusters that could be GC progenitors \citep{
-2019arXiv190509840L}.
+produces star clusters that could be GC progenitors \citep{2019ApJ...879L..18L}.
 
@@
 simulations \citep{2010ApJ...718.1266M,2014ApJ...796...10L,2018MNRAS.480.2343C,
-2019MNRAS.486..331C,2019arXiv190505199C}, as is done in the work by 
+2019MNRAS.486..331C,2019MNRAS.488.5409C}, also done in the work by 
 \citet{2019MNRAS.482.4528E}.
@@
 of $4.8$~Gyr. Based on these data, we find that the age distributions of the MW 
-and M31 GCSs are not statistically consistent. Moreover, the MW appears 
+and M31 GCSs are not statistically consistent. The MW appears 
 to host a GCS that is somewhat older than that of M31.
 This is somewhat surprising given that M31 is generally considered to be earlier
-type than the MW meaning that an older stellar population would be naively expected.
-However, we do caution that both data sets are incomplete and the age 
+type than the MW so that an older stellar population would naively be expected.
+On the other hand, the MW could be an outlier as it may have formed and assembled 
+most of its mass earlier than galaxies with a similar mass \citep[e.g.][]{2014ApJ...781L..31S,
+2015A&A...578A..87S,2018MNRAS.477.5072M}.
+In addition, we caution that both data sets are incomplete and the age 
 measurements have large uncertainties (of $1-2$~Gyr). On the other hand, the 
@@
 but the galactocentric radius of GCs in M31 is not available in CR16. Therefore, we 
-follow \citet[][section~4.1]{2019arXiv190111229W} 
+follow \citet[][section~4.1]{2019A&A...623A..65W} 
 to calculate the projected radius $r_{\text{proj}}$ from the observed positions,
@@
 \citet{2010ARA&A..48..431P} and following the method of 
-\citet{2017MNRAS.465.3622R}. However, we caution that his definition does exclude 
-1 GC in the MW and 24 in M31 as stated in Section~\ref{sec:age}, and further
-discuss this in Section~\ref{sec:age_min}.
+\citet{2017MNRAS.465.3622R}. However, we caution that this definition, although 
+statistically consistent with the estimated ages of all GCs in the MW, is not 
+consistent with the tail of younger clusters as stated in Section~\ref{sec:age},
+and further discussed in Section~\ref{sec:age_min}.
 
@@
 We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
-resolution level (4) and halo number (10, indicating which set of initial
-conditions was used).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
+resolution level 4 and halo number 10, indicating which set of initial
+conditions was used.}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
 distributions of three individual simulation runs that we consider representative
-for specific behaviour, and to highlight that different runs could give rise to 
+for specific behaviour, and to highlight that different runs give rise to 
 different distributions. We show the age-selected GC candidates as well as the 
@@
 age classification, hints at three populations separated at [Fe/H]~$=-0.4$ and 
-[Fe/H]~$ = 1.5$. None of the Auriga sub sets has a mean value that offers much 
-hope that the simulated distribution is consistent with the lowest metallicity 
+[Fe/H]~$ = -1.5$. None of the Auriga subsets has a mean value that offers much 
+hope of reconciling the simulated distribution with the lowest metallicity 
 group in the M31 GCS. This is also true for the metal-poor population of the 
@@
 number number of GCs would be determined by the satellite halo mass, given the 
-$M_{vir}-N_{\text{gal}}$ correlation found by \citet{2019arXiv190100900B}. However,
+$M_{vir}-N_{\text{gal}}$ correlation found by \citet{2020AJ....159...56B}. However,
 we did not include such an analysis in this study.
-
-% Copy-pasted from \citet{2019MNRAS.486.5838R}
-% ``Out of the cluster formation models considered, the `no formation physics' model,
-% in which both the CFE and the ICMF are fixed throughout cosmic time, is
-% approximately equivalent to those studies  that  use  `particle-tagging'
-% techniques  to  identify  GCs  in cosmological simulations (e.g. Tonini 2013,
-% Renaud et al. 2017). We find that this cluster formation model continues to form GCs
-% at a vigorous rate until the present time, which implies it overproduces
-% the total GC mass in the MW by a factor
-% 5.5 relative to the mass formed in the fiducial model. Likewise, the continued
-% formation  of  GCs  in  this  model  predicts  the  on-going  formation
-% of massive (M $>10^5$ M\Sun) clusters with [Fe/H]$ <-0.5$ should be observed in
-% MW-mass galaxies at $z=0$. For these reasons, an environmentally independent
-% cluster formation description is not compatible with observations.''
 
@@
 a higher mass ratio with respect to the observed GC systems of the MW and M31.
-The qualitative behavour presented in Figure~\ref{fig:Au-FeHRgc-ratio} does not 
+The qualitative behaviour presented in Figure~\ref{fig:Au-FeHRgc-ratio} does not 
 change when the age cut is lowered to 8 or 6 Gyr. 
+Overall, reducing the age cut worsens the agreement between the observed GCSs 
+and the candidate GCs in the Auriga galaxies.
 
@@
 
-The analysis in this work was performed using the Python \citep{python}
-programming language, the IPython \citep{2007CSE.....9c..21P} environment, 
-the NumPy \citep{2011CSE....13b..22V}, SciPy \citep{scipy}, and Astropy 
-\citep{2013A&A...558A..33A} packages. Plots were created with Matplotlib 
+The analysis in this work was performed using the \textsc{python} \citep{python}
+programming language, the \textsc{ipython} \citep{2007CSE.....9c..21P} environment, 
+the \textsc{numpy} \citep{2011CSE....13b..22V}, \textsc{scipy} \citep{2020SciPy-NMeth}, and \textsc{astropy}
+\citep{2013A&A...558A..33A} packages. Plots were created with \textsc{matplotlib}
 \citep{2007CSE.....9...90H}, using the perceptually uniform colour maps
